### 2016-04-10 paper/UIST2016/paper.tex
paper.tex追加

%
% password manager?
%
\documentclass{article}

\usepackage{times}
\usepackage{uist}
\usepackage{graphicx}
\usepackage{here} % [H]とするとその場所に配置されるらしい

\long\def\EP{\textsf{EpisoPass}}
\long\def\PW{password}
\long\def\SS{seed string}
\long\def\EM{episodic memory}
\long\def\SQ{secret question}

\begin{document}

% Copyright notice ---
\conferenceinfo{UIST'16}{Tokyo}
\CopyrightYear{2016}
\crdata{x-xxxxx-xxx-x/xx/xxxx}

\title{EpisoPass: Password Management based on Episodic Memories}

\author{
\parbox[t]{9cm}{\centering
	     {\em Author Name removed for blind review}\\
	     Affiliation removed for blind review\\
	     Address removed for blind review\\
	     Email removed for blind review}
\parbox[t]{9cm}{\centering
	     {\em Author Name removed for blind review}\\
	     Affiliation removed for blind review\\
	     Address removed for blind review\\
	     Email removed for blind review}
}

\maketitle

\abstract
abst abst abst abst abst abst abst abst abst abst abst abst abst abst 
abst abst abst abst abst abst abst abst abst abst abst abst abst abst 
abst abst abst abst abst abst abst abst abst abst abst abst abst abst 
abst abst abst abst abst abst abst abst abst abst abst abst abst abst 
abst abst abst abst abst abst abst abst abst abst abst abst abst abst

\classification{H5.2 [Information interfaces and presentation]:
User Interfaces. - Graphical user interfaces.}

\terms{Design, Human Factors}

\keywords{Passwords, authentication}

\tolerance=400 
  % makes some lines with lots of white space, but 	
  % tends to prevent words from sticking out in the margin

\section{INTRODUCTION}

% Passwordは使われている
% 
% Passwordが辛いのは一般的事実である[?]
%   基本的に強くするには長くしなければならない
%   忘れる
%   覚えられない
%   サービスごとにパスワードは変えるべきである[?] でも無理
%   定期的に更新させられる
% 強いパスワードを頭で覚えて管理するのは不可能
%       特に弱者には
%   パスワード作成アルゴリズムを自力で使っている人もいるがそれは難しい

Passwords have been used for various Web services and applications
for a long time, and currently the most popular authentication method
on the Internet.
Since short passwords are easy to crack and
using a single password for different services is unsafe,
different long passwords should be used for different services,
but remembering many long passwords is almost impossible for
most of the users.

% もっと別の認証もいろいろ提案されている
%   画像認証[MALASYM][その他いろいろ]
%   
%   特殊ハードのような持ち物を使う方法など[Pico][YubiKey][RSA]
%   生体認証 指紋認証
%   行動からの認証[]
%   位置ベースの認証[SOUPS]
%  完全置き換えはしばらくは不可能だろう

Since passwords are so difficult to handle,
various other authentication methods have been proposed.
For example,
image-based authentication methods\cite{xxx},
bio-based methods\cite{},
behavior-based methods\cite{},

% というのもパスワードには利点があるから[Bonneau]
%   すでに普及
%   KB以外の特殊ハードが要らない
%   アタック方法はいろいろあるし[] 流出もしばしばだが
%     うまく実装したシステム上でうまく使えば安全
%     ハッシュ、ソルト
%     実装が比較的簡単
% なのでパスワードが近い将来死滅するとは考えられない

In spite of these attempts,
password-based authentication is still the most
convenient and strong method\cite{Bonneau}
and it will not be extinct in a short time.

%   
% % なのでパスワードと生きる方法が工夫されている
% %   強いパスワードを考える方法[]
% %     覚える方法が提案されてたり[Bonneau]
% %       万人むけはむり

% パスワードが死滅しないならパスワードと生きる方法が必要である
%   たとえば様々なパスワード管理システム[][][][]の利用がすすめられている
%   しかしマスターパスワードがいったり特殊ハードがいったりする
%   特殊システムがいる場合がある
%   特殊ハードやソフトは利用がどうしても難しい

If we have to use password-based authentication systems,
we have to devise a way to handle many passwords.
For handling many strong passwords,
various password management systems (PMSs) have been proposed\cite{xxx}\cite{yyy}.
PMSs remember users' passwords and help them use passwords for different services.
Althought PMSs are useful, users should remember a 'master password' for
keeping the secret data, and
some PMSs are not available on all environment.

% このように、実際のパスワード運用はとても大変であるが、
%   * パスワードを使わなければならないのは確かだし、
%   * 漏洩や紛失の危険がないのは脳内情報ぐらいである
%      鍵デバイスや生体情報などはダメ

% 読みとることができない脳内情報を利用するという基本手法は良いのだが覚えられないのが問題である
%   だとすると...パスワードを記憶するかわりに、****脳が既に覚えている秘密の記憶からパスワードを生成すればよいはずである***
%   確かな脳内情報を使ってパスワードを利用する必要があるが、
%     沢山の強力なパスワードそのものを覚えることは不可能に近い
%   だとすると、確かな脳内秘密情報からパスワードをGenerateするしかない
%   そこでエピソード記憶を使う
%   秘密の知識からGenerateするとよい
%

We believe that a PMS should have the following features.
(1) It should be available on any platform including PCs, smartphones, and the Web.
(2) Users should not have secret information (e.g. master password) or special device.
(3) Rely only on the information in the user's brain.

We propose a PMS called \textit{EpisoPass}, that generates strong passwords
based on the user's secret episodic memories that
the user can never forget.

\section{EpisoPass}

EpisoPass is a password management system that supports generating
strong passwords based on users' secret episodic memories.
A user provides a seed string and many question-answer pairs to EpisoPass,
and candidate passwords are generated based on the user's selections.

(figure)

Episodic memory is ....

Figure XXX shows the password generation interface of EpisoPass.
Several questions are shown to the user,
many candidate answers are shown for each question.
When a user selects one of the answers for each question,
the seed string is converted to a random-looking string
based on the selections.
If the q-a is based on the user's episodic memories and
nobody knows the correct answer,
only the user can select the set of right answers and
use the converted string as the password.

(figure)

EpisoPass is just a string-conversion system and it does not
have any information on which candidate is the correct answer.
Also, it does not save any password information and
it is almost impossible to get the right password 
without having the episodic memory.

% あらたに記憶するのではなく、忘れないエピソード記憶からパスワードを生成する
% 
% エピソード記憶とは
% 
% EpisoPass.com
%   インプリかく
%

\subsection{EpisoPass}

% 利点
%   絶対忘れない
%     30年忘れなかったものは40年忘れないだろう
%   老人など、頭が弱くても対応できる
%   変えるのが簡単
%     問題に「2016」とか「April」とか書いておけばいい
%   全情報を公開して大丈夫
%     マスターパスワードが要らない
%     秘密裏などは誤って流出する可能性があるが...
%   強度を自由に設定できる
%   画像を使える
%   実装が簡単
%

\subsection{EpisoPass}
% ■ 安全性

% 答を書くわけではないから安全
% 心配ならオフラインでやれば大丈夫
% 
% 弱いパスワードを強くすることも簡単
% 
% そのためにAndroidアプリも用意した
% 
% Bookmarkletも用意した
%   拡張機能も用意したい
%

\section{Related Work}

% ■ Related work
% 
% 様々なシステムがあるが、エピソード記憶からパスワードを直接生成するものは無い
% 
% パスワード管理システム
%   沢山ある
% 
% 強いパスワードを作るシステム
%   ランダムに生成するサイトが沢山ある
% 
% 強いパスワードを覚えるための工夫
%   Bonneau
% 
% 画像を使う
% 
% パスワードに関する全情報を公開してどこかに置いておける
%   ググれるかもしれない
%   紛失する可能性が少ない
%

\section{Experiences}
% ■ 運用実績

\section{Limitations}

% ■ 問題点
% 
% なぞなぞ問題を考えるのが難しい
%   自分だけ知ってる秘密など思いつかない人が多い
%   しかしインタビューを行なうとそういうのは出てくる
%     子供のときの怪我、ケンカ、失敗など
%     特に、自慢にならないものが良い
% 
% 強度が直感的でない
%   誰でも簡単にとけるのじゃないかと思う
%   safe感覚が足りない

{\scriptsize
\bibliographystyle{acm-sigchi}
\bibliography{paper}
}

\end{document}

### 2016-04-12 paper/UIST2016/paper.tex
...

@@
 %
-% password manager?
+% password manager? password management system?
 %
@@
 \abstract
-abst abst abst abst abst abst abst abst abst abst abst abst abst abst 
-abst abst abst abst abst abst abst abst abst abst abst abst abst abst 
-abst abst abst abst abst abst abst abst abst abst abst abst abst abst 
-abst abst abst abst abst abst abst abst abst abst abst abst abst abst 
-abst abst abst abst abst abst abst abst abst abst abst abst abst abst
+% 忘れることがない{\EM}にもとづく{\SQ}を使って強力な{\PW}を生成/管理するシステム「\textsf{\EP}」を提案する。
+% {\EP}は、ユーザが作成した{\SQ}への回答にもとづいて{\SS}を換字することによって{\PW}を生成する。
+% {\SS}や回答のバリエーションにより異なる{\PW}が生成されるので様々なサービスに対して異なる{\PW}を生成できることに加え、
+% {\SS}を逆計算することにより既存の{\PW}の管理もできる。
+% 適切な運用により、{\PW}に関連するあらゆる情報を秘密にすることなく
+% 強力な{\PW}の生成/管理が可能である。
+
+We propose a new password management system \textit{EpisoPass} that supports
+generating strong passwords based on users' secret episodic memories.
+EpisoPass shows the user multiple secret questions and possible answers to
+each question, and
+EpisoPass generates a password by substituting characters of the
+'seed' string based on the user's selections.
+If the right answers to the questions are known only to the user,
+the password cannot be guessable by other people, and
+various strong passwords can be easily managed
+without having master passwords or secret devices that are
+usually required for password management systems.
+
+% We introduce a password generation/management system called EpisoPass,
+% which converts a seed string into a password using the user's
+% episodic memories represented as a set of questions and answers
+% which can be solved only by the user.
+% Using EpisoPass with well-defined questions and answers,
+% a user can always retrieve various passwords without worrying about
+% remembering secret information.
 
@@
 
+{\PW}の長期的記憶が難しいことは{\PW}認証の大きな問題点のひとつである。
+安全に運用するためには{\PW}はランダムで長い文字列であることが望ましいが、
+そのようなものを頭の中に記憶しておくことは難しい。
+また複数のサービスを利用する場合、
+サービスごとに異なる{\PW}を利用することが望ましいが、
+すべての{\PW}を記憶しておくことはほとんど不可能である。
+%
+Flor\^{e}ncioの2007年の大規模な調査によれば、
+ユーザは平均25個のサイトで6.5個の{\PW}を利用しており、
+3ヶ月間にユーザの4.28\%が{\PW}を忘れていた\cite{Florencio:2007:LSW:1242572.1242661}。
+また2011年の野村総研の調査によれば、
+一般的なユーザが{\PW}認証を行なうサイトは平均19.4個で、
+利用している{\PW}は平均3.1個であった\cite{野村総研}。
+多数の{\PW}を記憶することが困難であるため、
+多くのユーザが同じ{\PW}を複数サイトで使い回しているのだと思われる。
+
+People are frequently asked to register a password when
+they try to use a new service.
+
 % もっと別の認証もいろいろ提案されている
@@
 For example,
-image-based authentication methods\cite{xxx},
+image-based authentication methods\cite{Biddle:2012:GPL:2333112.2333114}\cite{小池英樹:2006-05-15}\cite{GraphicalPasswords}, 
 bio-based methods\cite{},
@@
 convenient and strong method\cite{Bonneau}
-and it will not be extinct in a short time.
+and it will not be extinct in a short time\cite{Herley:2009:PSS:1601990.1602010}.
 
@@
 For handling many strong passwords,
-various password management systems (PMSs) have been proposed\cite{xxx}\cite{yyy}.
+various password management systems (PMSs) have been proposed
+{\PW}管理システムは
+ひとつの「マスター{\PW}」を利用して他のすべての{\PW}を管理するもので、
+暗号化されたデータベースに{\PW}を格納するもの%
+\cite{OnePassword}%
+\cite{Dashlane}%
+\cite{ミルパス}%
+\cite{LastPass}%
+\cite{KeyPass}%
+\cite{NortonIDSafe}%
+\cite{IDManager}%
+が多いが、サービス名をもとにマスター{\PW}を変換することによって
+複数の{\PW}を生成するシステム\cite{SuperGenPass}もある。
+両者ともにマスター{\PW}の記憶は必須であり、
+マスター{\PW}を盗まれたり忘れたりする危険がある。
+
 PMSs remember users' passwords and help them use passwords for different services.
@@
 
+\begin{enumerate}
+\item {\PW}生成の「種」となる文字列を用意する。
+以下ではこれを「{\SS}」と表現する。
+\item 忘れることがない個人的な{\EM}にもとづく{\SQ}を複数作成し、
+それぞれについてひとつの正答と複数の偽答を用意する。
+\item 質問と回答の組にもとづいて{\SS}に換字操作を行なう。
+すべてに正しく回答したとき生成される文字列を{\PW}として利用する。
+\end{enumerate}
+
 (figure)
 
-Episodic memory is ....
+\begin{quote}
+Episodic memory is the memory of autobiographical events (times,
+places, associated emotions, and other contextual who, what, when,
+where, why knowledge) that can be explicitly stated. It is the
+collection of past personal experiences that occurred at a particular
+time and place. For example, if one remembers the party on his or her
+6th birthday, this is an episodic memory. They allow an individual to
+figuratively travel back in time to remember the event that took place
+at that particular time and place.[1]
+
+Semantic memory is one of the two types of declarative or explicit
+memory (our memory of facts or events that is explicitly stored and
+retrieved).[1] Semantic memory refers to general world knowledge that
+we have accumulated throughout our lives.[2] This general knowledge
+(facts, ideas, meaning and concepts) is intertwined in experience and
+dependent on culture. Semantic memory is distinct from episodic
+memory, which is our memory of experiences and specific events that
+occur during our lives, from which we can recreate at any given
+point.[3] For instance, semantic memory might contain information
+about what a cat is, whereas episodic memory might contain a specific
+memory of petting a particular cat. We can learn about new concepts by
+applying our knowledge learned from things in the past.[4] The
+counterpart to declarative, or explicit memory, is procedural memory,
+or implicit memory.[5]
+\end{quote}
+
+\subsection{Using EpisoPass on a browser}
 
@@
 
+{\SS}として「\textsf{Twitter123456}」という文字列を指定しており、
+4個の{\SQ}に対する回答選択に応じて
+「\textsf{Mfveabn574923}」のような{\PW}候補が生成される。
+異なる答をを選択すると全く異なる文字列が生成される。
+{\SS}の8文字目が数字である場合は{\PW}の8文字目も数字になるなど、
+{\SS}の文字種に対応した{\PW}候補が生成される。
+
+最初の{\SQ}は筆者の小学校の同級生に関するもので、
+最後の質問は数年前の体験に関するものである。
+これらの質問は古い{\EM}にもとづいており、
+筆者が将来答を忘れることはほとんど考えられないが、
+本人以外がこのような質問に答えることは難しいので
+正しい{\PW}を得ることはできない。
+
+{\SQ}と答はブラウザで編集でき、
+右上の「サーバにセーブ」ボタンを押すことにより{\SS}、秘密の問題、答のリストがサーバにセーブされる。
+「ファイルにセーブ」ボタンを押すとJSONデータをパソコンにダウンロードでき、
+パソコン上のJSONデータをブラウザにドラッグ\&ドロップするとサーバにアップロードできる。
+ユーザはどれが正答かを指定するわけではないので
+問題データを見てもユーザの{\PW}はわからない。
+
+{\SS}を「\textsf{Facebook123456}」に変更すると、生成される{\PW}は図\ref{web2}のように変化する。
+このように、サービスごとに異なる{\SS}を利用することによって
+様々な{\PW}を簡単に生成できる。
+
+問題と回答から文字列を生成し、そのMD5値によって{\SS}を換字することにより
+{\PW}を生成している。
+{\PW}文字列の計算方法は附録に示す。
+
+\subsubsection{回答選択により{\PW}を切り換え}
+\label{pwgen}
+
+サービスごとに{\SS}を変えるのではなく、
+図\ref{web3}のように
+サービス名に応じて回答を変えることによって異なる{\PW}を作成することも可能である。
+{\PW}としての長さや文字種に特種な制約が無いサービスに関してはこの方法が便利である。
+
+\begin{figure}[H]
+\centerline{\includegraphics[width=83mm,bb=0 0 718 428]{figures/a9167a6ec6af9c70dd1617e3fc25ec30.png}}
+\centerline{\includegraphics[width=83mm,bb=0 0 718 428]{figures/5b887fabeb8e3319623901fe4a6c56f2.png}}
+\caption{サービス名に対応する回答で異なる{\PW}を生成.}
+\label{web3}
+\end{figure}
+
+定期的に{\PW}変更を求められるシステムでは、
+「利用期間は?」という質問に対して
+「2013/1」「2013/2」のような答を用意しておけば、
+時期を選択することによって簡単に{\PW}を変更することができるので便利である。
+
+\subsubsection{Androidアプリ}
+
+Webサービスを利用する場合、ブラウザとサーバとの間の通信を
+記録されたり盗み見されたりされる心配を完全に払拭することはできない。
+% 危険を完全になくすことはできない。
+前述の例において、
+{\PW}はブラウザ内部でJavaScriptにより生成されるので、
+一度ページを表示した後は
+ネットワークを遮断しても{\PW}計算を行なえるようになっているが、
+最初から全く通信を行なわずに{\PW}を作成できる方がより安心であろう。
+このため、通信を全く行なわずにマシン単体で{\PW}計算を行なうための
+Androidアプリを用意した。
+ページの右上の「Androidアプリ」ボタンを押すと、
+現在表示している秘密の問題と答を内蔵したAndroidアプリが
+サーバ上でビルドされてダウンロードされる。
+
+Android端末でアプリを実行すると図\ref{android1}のような画面が表示される。
+{\SS}を設定して「開始」ボタンを押すと図\ref{android2}のように質問がひとつずつ表示され、
+ボタンを押してすべて回答すると{\PW}が計算され図\ref{android3}のように表示される。
+
+回答入力と{\PW}計算はAndroid端末で実行されるため、
+端末を「機内モード」に設定するなどの方法で
+ネットワーク接続を遮断した状態でも{\PW}を計算することができる。
+{\EP}をインストールしたAndroid端末を持っていれば常に各種の{\PW}を計算できるので、
+他人のマシンや公共の場所に設置されたパソコンなどでも
+容易にtwitterなどのネットサービスを利用することができる。
+
+前述の方法で{\EP}アプリをサーバからダウンロードする場合は、
+ブラウザ上で秘密の問題をサーバに登録する必要があるが、
+秘密の問題を全くネット上に露出することなくアプリを利用することもできる。
+
+\subsection{{\PW}文字列の計算方法}
+
+問題と回答から文字列を生成し、そのMD5値によって{\SS}を換字することにより
+{\PW}を生成している。
+{\PW}文字列の計算方法は附録に示す。
+
+\section{Discussions}
+
 EpisoPass is just a string-conversion system and it does not
 have any information on which candidate is the correct answer.
-Also, it does not save any password information and
+Also, it does not save any password information at any form, and
 it is almost impossible to get the right password 
@@
 
-% あらたに記憶するのではなく、忘れないエピソード記憶からパスワードを生成する
-% 
-% エピソード記憶とは
-% 
-% EpisoPass.com
-%   インプリかく
-%
+\subsection{Advantages of using EpisoPass}
 
-\subsection{EpisoPass}
+\paragraph{Unforgettable}
 
-% 利点
 %   絶対忘れない
 %     30年忘れなかったものは40年忘れないだろう
+
+The biggest advantage of using EpisoPass is that
+users don't have to worry about forgetting or losing passwords.
+Users of EpisoPass can always save the seed string and question-answer
+pairs at any place, and easily generate passwords by answering questions.
+If the question is based on old episodic memories,
+there is little chance of forgetting correct answers and losing passwords
+generated from the selections.
+If the episodic memory is based on 20 years ago and the user clearly
+remembers it at this moment, it is unlikely that he forgets the episode after
+several years.
+
+\paragraph{Usable for everyone}
+
 %   老人など、頭が弱くても対応できる
+
+Not everyone is familiar with handling passwords.
+Even experienced computer users sometimes use weak passwords,
+since choosing a good password is not a straightforward task.
+Using EpisoPass, people who cannot create and remember strong passwords
+can easily generate strong passwords just by providing secret
+questions and answers.
+With a good interface, people can even use various password-based
+services without noticing the problem of passwords.
+
+% 強いパスワードの作成と記憶が同時にできる
+
+\paragraph{Easy to change passwords}
+
 %   変えるのが簡単
 %     問題に「2016」とか「April」とか書いておけばいい
+
+On some systems, users are requested to change passwords periodically
+to strenghen security.
+A user can generate a new strong password by using a randam character generator
+on a PMS, but he might want to old passwords in case some trouble happens.
+Using EpisoPass, user can just provide a date-related question-answer pairs,
+and generate different strong passwords based on the answer.
+(Figure xxx)
+
+\paragraph{All information can be put public}
 %   全情報を公開して大丈夫
@@
 %     秘密裏などは誤って流出する可能性があるが...
+
+\paragraph{Strong passwords can be generated}
 %   強度を自由に設定できる
+
+\paragraph{Image-based authentication}
 %   画像を使える
+
+Old pictures can be used as the questions of EpisoPass.
+Even when people cannot create good secret questions,
+people can fairly easily select a secret image from their photo collections
+and use it as the question.
+For example, if you have a n old picture of your friend,
+you can use it as the question
+and use his real name and other similar names as candidate answers.
+
+例をここでいろいろ出す
+
+% 画像検索とかされないようにする必要はある
+
+Of course, the photo should not have information related to the
+person's real name, since image search is fiarly easy on the Web these days.
+
+\paragraph{Simple implementation}
 %   実装が簡単
+
+The algorithm of generating a password is quite simple and
+it can be implemented on any browser JavaScripts or
+applications on smartphones and small devices.
+
+\paragraph{パスワード自体の漏洩の心配が不要}
+% 聞かれてもわからないし書き留める必要がないからウッカリもらす可能性はない
+% ローカルに実行すればネットでもれる心配もない
+
+Since the password is generated by the algorithm and the password
+string is not kept on a computer in any form,
+unexpected leak of the password is unlikely.
+The user doesn't have to remember the string and
+there is no chance he will reveal it to somebody
+even when he is forced to tell the password.
+
+% そのためにAndroidアプリも用意した
+
+\subsection{Risks of using EpisoPass}
+
+\paragraph{Security strength of EpisoPass}
+% ■ 安全性
+
+{\PW}は長年利用されているため
+強度や実際の運用に関して多くの研究が存在するが%
+\cite{Hayashi:2011:DSP:1978942.1979326}%
+\cite{Komanduri:2011:PPM:1978942.1979321}% どういうパスワードが強いか
+、{\SQ}の強度に関しては充分研究されていない。
+{\EP}の運用実績は長くないが安全性などについて考察を行なう。
+
+{\EP}で
+選択枝が10個の{\SQ}を8個使用する場合、
+総当たりで{\PW}を生成するには
+1億($10^8$)通りの試行が必要であり、
+% エントロピーは26.6 ($ = 8 \times \log_2 10$) ビット
+エントロピーは26.6ビットとなる。
+英字からランダムに8文字を並べて作成した{\PW}のエントロピーは37.6ビットになるが、
+``\textsf{pmvixuzq}''のように全く意味のない{\PW}を記憶して利用することは少ないため、
+実際に利用される{\PW}のエントロピーは20ビット程度と考えられているので\cite{NIST}、
+{\SQ}と選択枝の数を10個程度用意すれば
+通常の{\PW}と同程度の強度が期待できることになる。
 %
+総当たり攻撃が可能なオフライン運用ではエントロピーの大きさは重要であるが、
+オンラインサービスでは
+{\PW}入力を何度か間違えるとサービスがブロックされるのが普通なので、
+それほど長い{\PW}を用意する必要は無いと考えられている\cite{Florencio:2007:SWP:1361419.1361429}。
 
-\subsection{EpisoPass}
-% ■ 安全性
+一方、{\SQ}を利用する認証の脆弱性を利用した攻撃が近年問題になっている。
+{\PW}を忘れたときのために、
+あらかじめ設定した{\SQ}に答えることによって{\PW}をリセットできるサービスがあり、
+「母親の旧姓は?」や「最初に飼ったペットの名前は?」のような
+質問に対してユーザが答を登録するようになっている。
+このような問題は他人が調べたり推測したりすることが容易であるうえに
+{\SQ}の数は一般的に少なく、
+{\PW}よりも脆弱だといえる\cite{Rabkin:2008:PKQ:1408664.1408667}。% 銀行20個調べて{\SQ}の弱さを指摘
+%
+ユーザが作成した{\SQ}を使えばこのような問題はなくなるはずであるが、
+他人に解かれにくい問題をユーザが作成することは難しく、
+またユーザ自身が答を忘れてしまうことも多いと考えられている\cite{Just:2009:PCC:1572532.1572543}\cite{Schechter:2009:NSM:1607723.1608145}。
+%
+また、古い記憶にもとづいて作成した秘密の問題は
+ユーザが想像するよりも解かれやすいという実験結果にもとづき、
+忘れない{\SQ}を複数利用する方法、
+問題と答を連想するために画像を利用する方法、
+複数の問題を連続的に利用する手法などが提案されている\cite{Renaud:2010:PQE:2146303.2146318}。
+
+{\EP}では、
+他人には解くことが難しく自分では忘れないような{\SQ}を自由にいくつでも利用できるようになっている。
+問題作成に慣れていないユーザには有効な{\SQ}を作成することは難しいかもしれないが、
+次節で述べるように、適切な質問を選ぶことによりこの問題を解決できるはずである。
+
+The strength of the generated password depends on the number of
+questions and the 'secretness' of the questions.
+If the episodic memory is shared by someone else,
+that personn can easily answer the question and generate the
+password just like the user.
+
+Questions like "Which one is your favorite?" should be avoided,
+since some of the friends might know the user's taste.
+Questions related to a episode which the user is proud of should also be
+avoided, since the user might talk aboutu the episode to somebody else.
+
+If, one of the passwords generated by EpisoPass is revealed
+for some reason,... フルートフォースでとかれる可能性はある
+
+To prevent such troble, it is safer to keep all the q-a pairs secret.
+
+問題を時々変えるのが安全だろう
+
+問題自体が秘密であればひとつ漏れても大丈夫
+
+\subsection{問題の選択}
+
+{\EP}利用において{\SQ}の選択は非常に重要である。
+他人が推測することが難しく、自分が決して忘れないような{\EM}を{\SQ}として利用すべきであり、
+以下のような性質をもつ記憶は{\SQ}として利用すべきではない。
+
+\begin{itemize}
+\item \textsf{自慢になるもの
+(何かの機会にうっかり他人に話してしまう可能性がある)}
+
+\vspace{-1mm}
+\item \textsf{ネット上に記録が残っているもの}
+
+\vspace{-1mm}
+\item \textsf{他人と情報を共有しているもの}
+
+\vspace{-1mm}
+\item \textsf{趣味や嗜好に関連するもの
+(他人に推測されやすいうえに嗜好が変化する可能性がある)}
+
+\end{itemize}
+
+\noindent
+このようなものではなく、
+「わざわざ人に話すことはないが自分の記憶に強く残っているような無難な{\EM}」を
+{\SQ}として利用するのが良いであろう。
+具体例としては以下のようなものがある。
+
+\begin{itemize}
+\item 昔のちょっとした怪我の場所や種類
+
+\vspace{-1mm}
+\item 昔のちょっと悔しい思い出
+
+\vspace{-1mm}
+\item 昔何かを見つけた場所
+\end{itemize}
+
+たとえば図\ref{kega}のような{\SQ}は他人に話したことが無いが、
+痛い思いをしたことは忘れないし、
+偽答を作成するのも簡単なので、
+認証のための{\SQ}として適切であると考えられる。
+
+\subsection{偽答の作成方法}
+
+{\SQ}の種類によっては偽答の生成が難しい場合がある。
+図\ref{atmega}は電子工作に関する{\SQ}の例であるが、
+正答と区別がつかない偽答を充分リストすることは難しい。
+
+\begin{figure}[H]
+\centerline{\includegraphics[width=83mm,bb=0 0 512 113]{figures/2f63ceb9ab6faf8d81393953f2f95a8c.png}}
+\caption{偽答の生成が難しい例.}
+\label{atmega}
+\end{figure}
+
+一方、正答として人名や地名を利用する場合、
+正答に似た人名や地名をリストすることは難しくない。
+「世田谷」が正答であるとき、
+「目黒」「杉並」のような偽答を用意するのは簡単である。
+%
+正答と同じカテゴリに属する単語を自動的にリストすることができれば
+正答をもとにして簡単に偽答のリストを生成することができる。
+%
+ひとつの単語もしくは単語の集合と同じカテゴリに属する単語を検索する手法は
+「同位語検索」と呼ばれ、
+Webのデータを利用した様々な同位語検索システムが提案されている%
+\cite{Huang:2012:LFC:2426725.2426728}% 読んでないけど
+\cite{BooWa}% Boo!Wa!というサイトをやっている
+\cite{Wang:2007:LSE:1441428.1442086}% BooWa
+\cite{大島裕明:2006-12-15}% ライバルサーチ「やーやら」
+。
+たとえば「ライバルサーチ『やーやら』」\cite{大島裕明:2006-12-15}は、
+Web上の「AやBが」のような表現を抽出することによって
+AとBのカテゴリが近いことを判断している。
+
+人名や地名の偽答を作成したい場合は
+人名や地名のデータベースを利用して偽答を生成することができる。
+市町村の人口ランキングや位置関係のデータなどを利用すれば
+似た地名を偽答としてリストすることが可能であるし、
+人名ランキングを利用すれば
+似た苗字を偽答とすることができる。
+たとえば日本の名字ランキングの40位近辺に
+「長谷川」「近藤」「石井」「斉藤」「坂本」「遠藤」「藤井」
+などの名字があるので、
+「石井」が正答のときこれらの名字を偽答にすればよい。
+しかし、
+「小学生のとき〜だった同級生は誰?」という{\SQ}の正答が「石井」であるとき
+この方法で偽答を生成すると、
+「長谷川」「近藤」などの同級生の存在を確認することにより
+正答が「石井」であることが判明してしまう可能性があるので注意が必要である。
+
+\subsection{{\PW}漏洩時の問題}
+
+{\SQ}を公開している場合、
+{\SS}と{\PW}の対応がひとつでも漏洩してしまうと、
+総当たり計算でチェックすることにより、
+すべて{\SQ}の正答が判明してしまう。
+{\SQ}の正答を知っていれば
+{\SS}から{\PW}を計算することができるので、
+漏洩した{\SQ}は利用不可能になってしまう。
+%
+\ref{pattern1}や
+\ref{pattern2}のような運用をしている場合は
+{\PW}がひとつ漏洩しても他の{\PW}は安全だが、
+\ref{pattern3}のような運用をしている場合は
+ひとつでも{\PW}が漏洩するとあらゆる{\PW}が漏洩してしまうことになる。
+
+\subsection{画像認証の利用}
+
+忘れにくい{\EM}を利用する認証手法として
+様々な画像認証システム\cite{Biddle:2012:GPL:2333112.2333114}\cite{GraphicalPasswords}\cite{小池英樹:2006-05-15}が提案されている。
+複数の画像の中から正答を選択するもの(Cognometric方式)、
+ひとつの画像の中の特定の場所を指定するもの(Locimetric方式)、
+画像の上で描画操作を行なうもの(Drawmetric方式)
+が広く利用されているが\cite{Biddle:2012:GPL:2333112.2333114}\cite{GraphicalPasswords}\cite{Guideline}、
+{\EP}は図\ref{web1}のように
+文字列のかわりに画像URLを{\SQ}として利用する点が異なっている。
+%
+Cognometric方式は{\EM}を効果的に利用できるが、
+多数の偽答画像が必要だという問題がある。
+Locimetric方式は
+{\EM}を効果的に利用できないことに加え、
+クリックしやすい「ホットスポット」は限られているため
+充分なエントロピーを確保できないことが問題になる\cite{Dirik:2007:MUC:1280680.1280684}。
+またDrawmetric方式も{\EM}を効果的に利用できないし、
+ユーザは似た傾向のストロークを選びがちであるため
+充分なエントロピーを確保しにくいことが知られている\cite{Nali}。
+%
+{\EP}のように画像を{\SQ}として利用する場合、
+通常の{\SQ}の場合と同様に偽答を増やすことが容易であることに加え、
+画像に関連した{\EM}を有効に利用できるという利点がある\cite{増井:CSS}。
+
+図\ref{leiko}は
+本棚.org\cite{hondana}\cite{hondanaorg}
+のユーザのひとり\footnote{
+  \textsf{http://hondana.org/Leiko}
+}が利用している画像認証問題である。
+このユーザ以外には正答は見当もつかないが、
+本人にとっては忘れることがない{\EM}と結びついた画像だということであった。
 
@@
 % 
-% そのためにAndroidアプリも用意した
 % 
@@
 
-% ■ Related work
-% 
+認証手法は本当に沢山あり、パスワードを置き換えようとするものも多いが
+まだ成功はしていない
+
+パスワード管理システムは充分広く使われている
+
+% A Password Manager that Doesn’t Remember Passwords
+\cite{Stobert:2014:PMD:2683467.2683471} % Visipass 画像クルーからパスワード生成
+
 % 様々なシステムがあるが、エピソード記憶からパスワードを直接生成するものは無い
@@
 
-% ■ 問題点
-% 
 % なぞなぞ問題を考えるのが難しい
@@
 
+\section{CONCLUSION}
+
+{\EM}に結びついた{\SQ}を利用して{\PW}を生成/管理できるシステム{\EP}を提案した。
+{\EP}は単純な原理にもとづいており柔軟な利用形態が可能であり、
+強力な{\SQ}を用意することにより
+秘密情報を全く覚えることなく安全な認証を行なうことができる。
+%
+強力な{\SQ}を作成して安全に運用が可能かどうかを長期的に評価したいと考えている。
+%
+%欠点:
+%なぞなぞを考えるのがめんどくさい
+%安全になぞなぞを扱うのが面倒
+%  ネットなしで運用したりとか
+%運用を間違うと思わぬところで回答がバレる可能性がある
+%
+{\EP}は\textsf{http://Episopass.com/}で運用しており、
+ソースはGitHubで公開している\footnote{
+  \textsf{http://GitHub.com/masui/EpisoPass}
+}。
+
 {\scriptsize
@@
 
+\section*{Appendix: Algorithm for generationg a password}
+
+% {\PW}は、
+% {\SQ}と回答の組合せにもとづいて{\SS}を換字することによって計算される。
+% 換字は文字種ごとに行なわれる。
+% たとえば
+% {\SS}の1桁目が数字のときは{\PW}の1桁目は数字に変換され、
+% {\SS}の1桁目が記号のときは{\PW}の1桁目は記号に変換される。
+
+% https://ja.wikipedia.org/wiki/換字式暗号
+
+The password string is generated by
+substituting the characters in the seed string
+based on the user's selections of candidate answers.
+Character substitution is performed based on the chracter types.
+For example, if the first character of the seed string is a digit,
+the first character of the generated password string is also a digit.
+
+% {\SS}内の数字$A$は、換字関数$f_N()$によって{\PW}内の数字$B$に変換される。
+% $f_N()$ は以下のような関数である。
+
+A digit $A$ in the seed string is converted to a digit $B$
+in the password string by the following
+character substitution function $f_N()$.
+
+\[ f_N(x) = (10 + N - x) \bmod 10 \]
+
+% ここで$N$は{\SS}と回答の組み合わせから計算される自然数で、
+% 答の選択により変化する。
+% たとえば$N = 5$ のとき、$f_5(x) = (15-x) \bmod 10$ となるので、
+% $x$と$f_5(x)$の対応は以下のようになる。
+
+Here, $N$ is a number calculated from the user's selection of
+candidate answers.
+If the value of $N$ if $5$, $f_5(x) = (15-x) \bmod 10$, and
+$x$と$f_5(x)$の対応は以下のようになる。
+
+\[ f_5(0) = 5 \]
+\[ f_5(1) = 4 \]
+\[ f_5(2) = 3 \]
+\[ ... \]
+\[ f_5(8) = 7 \]
+\[ f_5(9) = 6 \]
+
+% $f_N()$は$N$により変化するので、$N$がわからなければ$f_N()$もわからない。
+% $N$は{\SS}と回答の組み合わせから計算される自然数なので、
+% {\SS}の答を知らなければ$N$を計算することはできず、
+% 問題と答の組み合わせを知らない限り{\SS}から{\PW}を計算することはできない。
+
+$f_N()$ depends on the value of $N$, and
+it is impossible to know about $f_N()$ without knowing the value of $N$.
+
+% {\EP}では以下のようにして$f_N()$を計算している。
+
+$N$ is calculated by the following algorithm in EpisoPass.
+
+\begin{enumerate}
+  % \item 問題文字列と選択した答の文字列の組を連結して長い文字列$S$を生成
+  \item Generate a string $S$ by concatinating all the question strings and selected candidate answers.
+
+    \vspace{-1mm}
+  % \item $S$のMD5ハッシュ値$M$(16進32桁の文字列)を計算
+  \item Calculate the MD5 value of $S$ and generate 32-byte hexadecimal string $M$.
+
+    \vspace{-1mm}
+  %\item {\SS}の$k$桁目の文字に対し、
+  %  $M$の$k \times 4$文字目から$k \times 4 + 3$文字目までの部分文字列(16進4桁)を取得し、
+  %  それを$N$とする
+  \item For each $k$th chracter of {\SS},
+    get the 4-character substring of $M$ beginning at $k \times 4$, and use it as the value of $N$
+
+    %たとえばハッシュ値$M$が$12345678...$だったとき、1桁目を計算する$f()$についてはN=0x1234となる。
+    If the hash value $M$ is $12345678...$,
+    $f_0x1234$ is used as the substitution function for the first character,
+    $f_0x5678$ is used as the substitution function for the secound character, etc.
+\end{enumerate}
+
 \end{document}
+
+* このサービスが終了したらネットライフが終了する
+* 増井さんが飽きてサービス止めちゃったら多くの道連れがでるという罠
+
+=> EpisoPassのHTMLやAndroidアプリを持っていればEpisoPass.comが無くても計算可能です。
+アルゴリズムは単純ですし公開されているわけですから別実装してもいいでしょう。
+
+* いまいちよくわからないです。seed というのもおぼえてないといけないのでしょうか？
+
+=> Seedは覚えておいてもいいですし公開してもかまいません。私は全部公開しています。
+
+* 使うのちょっとめんどくさそう
+
+=> パスワード入力のたびに使うわけではありませんし、問題に答えるのにそれほど
+時間はかかりません。新しくスマホを買ったら使うぐらいです。
+問題を作るのは確かにめんどくさいかもしれません。
+
+* 秘密の質問に入れる偽装の答えをどこにメモしたか忘れるという事もしばしば
+
+=> 問題も答も公開しておけば忘れることはないでしょう。
+
+* クイズにできるエピソードがない人はどうすればいいんでしょう
+
+=> そういう話はよく聞くのですがエピソードが無い人なんているのでしょうかね?
+小学校のときちょっとしたケガ体験とかエピソードとか覚えてませんか?
+
+* EpisoPassのフィッシングサイトができたらどうしましょう
+
+=> 完全にローカルHTMLかローカルアプリで使えば安心でしょう。
+
+* URLがseed込みなので、ブックマークつくっておけば辿りつける、という主張だったかと
+
+=> これは誤解です。URLは計算には関係ありません。
+
+* Q:(1)seedはどうやって作るのか？(2)質問はどうやって作るのか？
+
+=> (1) Seedはなんでもいいです (2) 質問は頑張って作ります
+
+* 親しい人が協力すると突破できるなあ
+
+=> それは問題次第です。私が公開してるものは無理だと思います。
+汚い乱暴者は誰でしょう? ケガした町名は?
+
+* これは本当に使ってみたいんだけど、ちょっと勇気いるんですよね。
+
+=> 勇気は確かに必要だと思います...
+
+* 同じ旅行に行った人だけが分かるエピソードをパスにして、写真共有とかいけますかね
+
+=> 複数の人間で秘密を共有できますし認証の強度も自由に制御できます
+
+* 増井さんのパスワードの質問と解答、誰でも自由に書き換え可能なように見えるんですが、こういう仕様？
+
+=> そうです。編集に認証入れたくないですので。確かに消されたりする問題はあるのですが
+ローカルに問題をセーブしておけば大丈夫です。
+
+* 僕はEpisoPassを使っていて、「好きな○○は？」という質問を作ったら、正解が変質して、正解が生成出来なくなったことがありますね。
+
+=> 絶対忘れない事実を問題として登録しておけばいいでしょう。好みは変わる可能性があるので問題として適切ではありません。
+
+* Seedと問題を全部公開できるのは素晴らしい発想ですが、Passwordが
+一個でもばれると、残りが全部ばれるのは何とかできないですかね。。。
+一つばれるとヤバイ、という点では同一パスワードの使いまわしと原理的に同じ？
+
+=> 問題を全部変えればいいんですが難しいですね... これは対策を考えたいと思います。
+しかしそもそもパスワード流出させるサービスの存在がアウトオブ論外なわけですが...
+
+* あれ、問題を増やしたら、過去に登録したパスワードを全部変えなければ
+ならなくなる、ということでしょうか？
+
+=> 過去に登録したパスワード計算には過去の問題を使い、新しく登録したいパスワードは
+新しい問題を使えばいいかもしれません。あらゆるパスワード生成に同じ問題を
+使う必要はありませんので。

### 2016-04-12 paper/UIST2016/paper.tex
...

@@
 
-We propose a new password management system \textit{EpisoPass} that supports
+We propose a new password manager \textit{EpisoPass} that supports
 generating strong passwords based on users' secret episodic memories.
+When a user want to enter a password,
 EpisoPass shows the user multiple secret questions and possible answers to
@@
 without having master passwords or secret devices that are
-usually required for password management systems.
+usually required for password managers.
 
@@
 Passwords have been used for various Web services and applications
-for a long time, and currently the most popular authentication method
-on the Internet.
+for a long time, and currently the most popular authentication method on the Internet
+without doubt.
 Since short passwords are easy to crack and
-using a single password for different services is unsafe,
+using the same password for different services is unsafe,
 different long passwords should be used for different services,
-but remembering many long passwords is almost impossible for
-most of the users.
+but remembering many long passwords is almost impossible for ordinary people.
+%
+According to Flor\^{e}ncio's reearch in 2007,
+people use 6.5 passwords on 25 Web services on average, and
+4.28\% of the users forget their passwords in 3 months\cite{Florencio:2007:LSW:1242572.1242661}.
 
-{\PW}の長期的記憶が難しいことは{\PW}認証の大きな問題点のひとつである。
-安全に運用するためには{\PW}はランダムで長い文字列であることが望ましいが、
-そのようなものを頭の中に記憶しておくことは難しい。
-また複数のサービスを利用する場合、
-サービスごとに異なる{\PW}を利用することが望ましいが、
-すべての{\PW}を記憶しておくことはほとんど不可能である。
-%
-Flor\^{e}ncioの2007年の大規模な調査によれば、
-ユーザは平均25個のサイトで6.5個の{\PW}を利用しており、
-3ヶ月間にユーザの4.28\%が{\PW}を忘れていた\cite{Florencio:2007:LSW:1242572.1242661}。
-また2011年の野村総研の調査によれば、
-一般的なユーザが{\PW}認証を行なうサイトは平均19.4個で、
-利用している{\PW}は平均3.1個であった\cite{野村総研}。
-多数の{\PW}を記憶することが困難であるため、
-多くのユーザが同じ{\PW}を複数サイトで使い回しているのだと思われる。
+%また2011年の野村総研の調査によれば、
+%一般的なユーザが{\PW}認証を行なうサイトは平均19.4個で、
+%利用している{\PW}は平均3.1個であった\cite{野村総研}。
+%多数の{\PW}を記憶することが困難であるため、
+%多くのユーザが同じ{\PW}を複数サイトで使い回しているのだと思われる。
 
@@
 
-Since passwords are so difficult to handle,
+Since passwords are difficult to handle,
 various other authentication methods have been proposed.
 For example,
-image-based authentication methods\cite{Biddle:2012:GPL:2333112.2333114}\cite{小池英樹:2006-05-15}\cite{GraphicalPasswords}, 
+image-based authentication\cite{Biddle:2012:GPL:2333112.2333114}\cite{小池英樹:2006-05-15}\cite{GraphicalPasswords}, 
 bio-based methods\cite{},
 behavior-based methods\cite{},
+and many other authentication methods have been proposed.
 
@@
 password-based authentication is still the most
-convenient and strong method\cite{Bonneau}
-and it will not be extinct in a short time\cite{Herley:2009:PSS:1601990.1602010}.
+convenient and strong method\cite{Bonneau},
+and it is not supposed to become extinct
+in a short period of time\cite{Herley:2009:PSS:1601990.1602010}.
 
-%   
 % % なのでパスワードと生きる方法が工夫されている
@@
 
-If we have to use password-based authentication systems,
-we have to devise a way to handle many passwords.
+If we have to live with password-based authentication systems,
+we have to devise a way to handle many passwords somehow.
 For handling many strong passwords,
-various password management systems (PMSs) have been proposed
+various password managers (PMs) have been proposed
 {\PW}管理システムは
@@
 
-PMSs remember users' passwords and help them use passwords for different services.
-Althought PMSs are useful, users should remember a 'master password' for
+Password managers remember users' passwords and help them use passwords for different services.
+Althought PMs are useful, users should remember a 'master password' for
 keeping the secret data, and
-some PMSs are not available on all environment.
+some password managers are not available on all environment.
 
@@
 
-We believe that a PMS should have the following features.
+We believe that the biggest problem of brain-based authentication systems is that
+users cannot keep new memories which corresponds to authentication methods,
+and we believe that
+it is far better to ``generate'' symbols for authentication based on
+users' episodic memories which they can never forget.
+
+We believe that a password manager should have the following features.
 (1) It should be available on any platform including PCs, smartphones, and the Web.
@@
 
-We propose a PMS called \textit{EpisoPass}, that generates strong passwords
-based on the user's secret episodic memories that
-the user can never forget.
+We propose a password manager called \textit{EpisoPass}, that generates strong passwords
+based on the user's secret episodic memories that the user can never forget,
+instead of systems based on remembering semantic memories.
 
@@
 
-EpisoPass is a password management system that supports generating
+EpisoPass is a password manager that supports generating
 strong passwords based on users' secret episodic memories.
 A user provides a seed string and many question-answer pairs to EpisoPass,
-and candidate passwords are generated based on the user's selections.
+and a password is generated based on the user's selections.
 
 \begin{enumerate}
-\item {\PW}生成の「種」となる文字列を用意する。
-以下ではこれを「{\SS}」と表現する。
-\item 忘れることがない個人的な{\EM}にもとづく{\SQ}を複数作成し、
-それぞれについてひとつの正答と複数の偽答を用意する。
-\item 質問と回答の組にもとづいて{\SS}に換字操作を行なう。
-すべてに正しく回答したとき生成される文字列を{\PW}として利用する。
+\item Provide a long string for generating a password.
+We call it the ``seed string''
+
+\item Create many question strings based on personal
+secret episodic memories that the user never forgets,
+and provide many candidate answers only one of which is the correct one.
+
+% 忘れることがない個人的な{\EM}にもとづく{\SQ}を複数作成し、
+% それぞれについてひとつの正答と複数の偽答を用意する。
+
+\item Based on the user's selection of answers,
+substitute characters in the seed string and generate a
+string for password.
+
+% 質問と回答の組にもとづいて{\SS}に換字操作を行なう。
+% すべてに正しく回答したとき生成される文字列を{\PW}として利用する。
+
 \end{enumerate}
-
-(figure)
 
@@
 
-Figure XXX shows the password generation interface of EpisoPass.
-Several questions are shown to the user,
-many candidate answers are shown for each question.
-When a user selects one of the answers for each question,
+\begin{figure}[H]
+\centerline{\includegraphics[width=83mm,bb=0 0 718 796]{../WISS/figures/785ff09b4233804d2ec89c3af71ee5d0.png}}
+\caption{ブラウザ上でTwitterの{\PW}を生成.}
+\label{web1}
+\end{figure}
+
+Figure \ref{web1} shows how to generate a password
+on EpisoPass running on a browser.
+Many questions related to episodic memories are shown to the user
+as well as many candidate answers are shown for each question.
+When a user clicks and selects one of the answers for each question,
 the seed string is converted to a random-looking string
@@
 
-{\SS}として「\textsf{Twitter123456}」という文字列を指定しており、
-4個の{\SQ}に対する回答選択に応じて
-「\textsf{Mfveabn574923}」のような{\PW}候補が生成される。
-異なる答をを選択すると全く異なる文字列が生成される。
-{\SS}の8文字目が数字である場合は{\PW}の8文字目も数字になるなど、
-{\SS}の文字種に対応した{\PW}候補が生成される。
+Here, ``\textsf{Twitter123456}'' is set as the seed string,
+and according to the selection to four questions,
+the seed string is converted to strings like
+``\textsf{Mfveabn574923}'', which can be used as the password
+for Twitter.
+The string changes when the user selects different candidates.
 
-最初の{\SQ}は筆者の小学校の同級生に関するもので、
-最後の質問は数年前の体験に関するものである。
-これらの質問は古い{\EM}にもとづいており、
-筆者が将来答を忘れることはほとんど考えられないが、
-本人以外がこのような質問に答えることは難しいので
-正しい{\PW}を得ることはできない。
+% {\SS}として「\textsf{Twitter123456}」という文字列を指定しており、
+% 4個の{\SQ}に対する回答選択に応じて
+% 「\textsf{Mfveabn574923}」のような{\PW}候補が生成される。
+% 異なる答をを選択すると全く異なる文字列が生成される。
+% {\SS}の8文字目が数字である場合は{\PW}の8文字目も数字になるなど、
+% {\SS}の文字種に対応した{\PW}候補が生成される。
 
-{\SQ}と答はブラウザで編集でき、
-右上の「サーバにセーブ」ボタンを押すことにより{\SS}、秘密の問題、答のリストがサーバにセーブされる。
-「ファイルにセーブ」ボタンを押すとJSONデータをパソコンにダウンロードでき、
-パソコン上のJSONデータをブラウザにドラッグ\&ドロップするとサーバにアップロードできる。
-ユーザはどれが正答かを指定するわけではないので
-問題データを見てもユーザの{\PW}はわからない。
+The first secret question is based on the author's episodic memory
+at elementary scholl,
+and the last secret questionois related to a event which the author
+can never forget.
+All the questions are related to the author's episodic memory
+that he never forgets, and nobody else knows which one of the
+candidate answers is the right answer.
 
-{\SS}を「\textsf{Facebook123456}」に変更すると、生成される{\PW}は図\ref{web2}のように変化する。
-このように、サービスごとに異なる{\SS}を利用することによって
-様々な{\PW}を簡単に生成できる。
+% 最初の{\SQ}は筆者の小学校の同級生に関するもので、
+% 最後の質問は数年前の体験に関するものである。
+% これらの質問は古い{\EM}にもとづいており、
+% 筆者が将来答を忘れることはほとんど考えられないが、
+% 本人以外がこのような質問に答えることは難しいので
+% 正しい{\PW}を得ることはできない。
 
-問題と回答から文字列を生成し、そのMD5値によって{\SS}を換字することにより
-{\PW}を生成している。
-{\PW}文字列の計算方法は附録に示す。
+Questions and answers can be edited on a browser, and they can be
+saved on the server by clicking the ``save on server'' button.
+Although questions and answers are saved on the server,
+no information about the correct answer is saved anywhere,
+so nobody can tell which one is the correct answer.
 
-\subsubsection{回答選択により{\PW}を切り換え}
-\label{pwgen}
+% {\SQ}と答はブラウザで編集でき、
+% 右上の「サーバにセーブ」ボタンを押すことにより{\SS}、秘密の問題、答のリストがサーバにセーブされる。
+% 「ファイルにセーブ」ボタンを押すとJSONデータをパソコンにダウンロードでき、
+% パソコン上のJSONデータをブラウザにドラッグ\&ドロップするとサーバにアップロードできる。
+% ユーザはどれが正答かを指定するわけではないので
+% 問題データを見てもユーザの{\PW}はわからない。
 
-サービスごとに{\SS}を変えるのではなく、
-図\ref{web3}のように
-サービス名に応じて回答を変えることによって異なる{\PW}を作成することも可能である。
-{\PW}としての長さや文字種に特種な制約が無いサービスに関してはこの方法が便利である。
+When we change the secret string to ``\textsf{Facebook123456}'',
+the generated password changes to Figure \ref{web2}.
+In this way, we can generate different passwords for
+different services just by changing the seed string.
 
 \begin{figure}[H]
-\centerline{\includegraphics[width=83mm,bb=0 0 718 428]{figures/a9167a6ec6af9c70dd1617e3fc25ec30.png}}
-\centerline{\includegraphics[width=83mm,bb=0 0 718 428]{figures/5b887fabeb8e3319623901fe4a6c56f2.png}}
-\caption{サービス名に対応する回答で異なる{\PW}を生成.}
-\label{web3}
+\centerline{\includegraphics[width=83mm,bb=0 0 718 265]{../figures/36c371a13a8250c60fb9c03174382443.png}}
+\caption{Generating the password for FaceBook.}
+\label{web2}
 \end{figure}
 
-定期的に{\PW}変更を求められるシステムでは、
-「利用期間は?」という質問に対して
-「2013/1」「2013/2」のような答を用意しておけば、
-時期を選択することによって簡単に{\PW}を変更することができるので便利である。
+% {\SS}を「\textsf{Facebook123456}」に変更すると、生成される{\PW}は図\ref{web2}のように変化する。
+% このように、サービスごとに異なる{\SS}を利用することによって
+% 様々な{\PW}を簡単に生成できる。
 
-\subsubsection{Androidアプリ}
+% 問題と回答から文字列を生成し、そのMD5値によって{\SS}を換字することにより
+% {\PW}を生成している。
+% {\PW}文字列の計算方法は附録に示す。
+
+% \subsubsection{回答選択により{\PW}を切り換え}
+% \label{pwgen}
+% 
+% サービスごとに{\SS}を変えるのではなく、
+% 図\ref{web3}のように
+% サービス名に応じて回答を変えることによって異なる{\PW}を作成することも可能である。
+% {\PW}としての長さや文字種に特種な制約が無いサービスに関してはこの方法が便利である。
+% 
+% \begin{figure}[H]
+% \centerline{\includegraphics[width=83mm,bb=0 0 718 428]{../WISS/figures/a9167a6ec6af9c70dd1617e3fc25ec30.png}}
+% \centerline{\includegraphics[width=83mm,bb=0 0 718 428]{../WISS/figures/5b887fabeb8e3319623901fe4a6c56f2.png}}
+% \caption{サービス名に対応する回答で異なる{\PW}を生成.}
+% \label{web3}
+% \end{figure}
+
+% 定期的に{\PW}変更を求められるシステムでは、
+% 「利用期間は?」という質問に対して
+% 「2013/1」「2013/2」のような答を用意しておけば、
+% 時期を選択することによって簡単に{\PW}を変更することができるので便利である。
+
+\subsubsection{Android application}
 
@@
 
-\subsection{{\PW}文字列の計算方法}
+\subsection{Algorithm for calculating password from selections}
 
-問題と回答から文字列を生成し、そのMD5値によって{\SS}を換字することにより
-{\PW}を生成している。
-{\PW}文字列の計算方法は附録に示す。
+% {\PW}文字列の計算方法}
+% 問題と回答から文字列を生成し、そのMD5値によって{\SS}を換字することにより
+% {\PW}を生成している。
+% {\PW}文字列の計算方法は附録に示す。
 
@@
 A user can generate a new strong password by using a randam character generator
-on a PMS, but he might want to old passwords in case some trouble happens.
+on a password manager, but he might want to old passwords in case some trouble happens.
 Using EpisoPass, user can just provide a date-related question-answer pairs,
@@
 
-{\PW}は長年利用されているため
-強度や実際の運用に関して多くの研究が存在するが%
+% {\PW}は長年利用されているため
+% 強度や実際の運用に関して多くの研究が存在するが%
+% \cite{Hayashi:2011:DSP:1978942.1979326}%
+% \cite{Komanduri:2011:PPM:1978942.1979321}% どういうパスワードが強いか
+% 、{\SQ}の強度に関しては充分研究されていない。
+% {\EP}の運用実績は長くないが安全性などについて考察を行なう。
+
+There have been many studies on the strength of passwords
 \cite{Hayashi:2011:DSP:1978942.1979326}%
-\cite{Komanduri:2011:PPM:1978942.1979321}% どういうパスワードが強いか
-、{\SQ}の強度に関しては充分研究されていない。
-{\EP}の運用実績は長くないが安全性などについて考察を行なう。
+\cite{Komanduri:2011:PPM:1978942.1979321},% どういうパスワードが強いか
+but the strength of secret questions are not studied a lot so far.
 
-{\EP}で
-選択枝が10個の{\SQ}を8個使用する場合、
-総当たりで{\PW}を生成するには
-1億($10^8$)通りの試行が必要であり、
-% エントロピーは26.6 ($ = 8 \times \log_2 10$) ビット
-エントロピーは26.6ビットとなる。
+% {\EP}で選択枝が10個の{\SQ}を8個使用する場合、
+% 総当たりで{\PW}を生成するには
+% 1億($10^8$)通りの試行が必要であり、
+% % エントロピーは26.6 ($ = 8 \times \log_2 10$) ビット
+% エントロピーは26.6ビットとなる。
+
+When we use 8 secret questions with 10 answers,
+100 million ($10^8$) trials should be performed to check
+all the combinations of the answers,
+and the entropy of the system is 26.6 ($ = 8 \times \log_2 10$) bits.
+
 英字からランダムに8文字を並べて作成した{\PW}のエントロピーは37.6ビットになるが、
@@
 
-一方、{\SQ}を利用する認証の脆弱性を利用した攻撃が近年問題になっている。
-{\PW}を忘れたときのために、
-あらかじめ設定した{\SQ}に答えることによって{\PW}をリセットできるサービスがあり、
-「母親の旧姓は?」や「最初に飼ったペットの名前は?」のような
-質問に対してユーザが答を登録するようになっている。
-このような問題は他人が調べたり推測したりすることが容易であるうえに
-{\SQ}の数は一般的に少なく、
-{\PW}よりも脆弱だといえる\cite{Rabkin:2008:PKQ:1408664.1408667}。% 銀行20個調べて{\SQ}の弱さを指摘
-%
+% 一方、{\SQ}を利用する認証の脆弱性を利用した攻撃が近年問題になっている。
+% {\PW}を忘れたときのために、
+% あらかじめ設定した{\SQ}に答えることによって{\PW}をリセットできるサービスがあり、
+% 「母親の旧姓は?」や「最初に飼ったペットの名前は?」のような
+% 質問に対してユーザが答を登録するようになっている。
+% このような問題は他人が調べたり推測したりすることが容易であるうえに
+% {\SQ}の数は一般的に少なく、
+% {\PW}よりも脆弱だといえる\cite{Rabkin:2008:PKQ:1408664.1408667}。% 銀行20個調べて{\SQ}の弱さを指摘
+
+In many services, users are forced to define answers to secret questions like
+``what is your mother's maiden name''
+so that he can log in to the service even when he forgets the password.
+This kind of authentication is far less secure than simple password systems,
+since it is fairly easy to answer the question by atackers.
+The variation of system-provided questions are usually small, and
+such a method is considered to be insecure\cite{Rabkin:2008:PKQ:1408664.1408667}.
+
+if the user can create his own secret questions,
+
 ユーザが作成した{\SQ}を使えばこのような問題はなくなるはずであるが、
@@
 
-\subsection{問題の選択}
+\subsection{Selecting secret questions}
 
-{\EP}利用において{\SQ}の選択は非常に重要である。
-他人が推測することが難しく、自分が決して忘れないような{\EM}を{\SQ}として利用すべきであり、
-以下のような性質をもつ記憶は{\SQ}として利用すべきではない。
+% {\EP}利用において{\SQ}の選択は非常に重要である。
+% 他人が推測することが難しく、自分が決して忘れないような{\EM}を{\SQ}として利用すべきであり、
+% 以下のような性質をもつ記憶は{\SQ}として利用すべきではない。
+
+Selecting good questions is very important for using EpisoPass.
+The episode related to the question should not be known to other people,
+and the episode should be an unforgettable one.
+%
 
@@
 \noindent
-このようなものではなく、
-「わざわざ人に話すことはないが自分の記憶に強く残っているような無難な{\EM}」を
-{\SQ}として利用するのが良いであろう。
-具体例としては以下のようなものがある。
+% このようなものではなく、
+% 「わざわざ人に話すことはないが自分の記憶に強く残っているような無難な{\EM}」を
+% {\SQ}として利用するのが良いであろう。
+% 具体例としては以下のようなものがある。
+Instead, more subtle and
+
+Specifically, questions like the following are good candidates for
+questions used in EpisoPass.
 
 \begin{itemize}
-\item 昔のちょっとした怪我の場所や種類
+% \item 昔のちょっとした怪我の場所や種類
+\item Memory of small injury
 
 \vspace{-1mm}
-\item 昔のちょっと悔しい思い出
+% \item 昔のちょっと悔しい思い出
+\item Memories of bad experience like blunders or defeat
 
 \vspace{-1mm}
-\item 昔何かを見つけた場所
+% \item 昔何かを見つけた場所
+\item Experience of finding a small item
 \end{itemize}
 
-たとえば図\ref{kega}のような{\SQ}は他人に話したことが無いが、
-痛い思いをしたことは忘れないし、
-偽答を作成するのも簡単なので、
-認証のための{\SQ}として適切であると考えられる。
+% たとえば図\ref{kega}のような{\SQ}は他人に話したことが無いが、
+% 痛い思いをしたことは忘れないし、
+% 偽答を作成するのも簡単なので、
+% 認証のための{\SQ}として適切であると考えられる。
 
-\subsection{偽答の作成方法}
+For example, a question like xxxx is about a trivial experience
+that people do not mention, but an experience like this is
+not forgettable because it was a very bad experiance.
 
-{\SQ}の種類によっては偽答の生成が難しい場合がある。
-図\ref{atmega}は電子工作に関する{\SQ}の例であるが、
-正答と区別がつかない偽答を充分リストすることは難しい。
+% \subsection{偽答の作成方法}
+\subsection{Creating fake answers}
+
+% {\SQ}の種類によっては偽答の生成が難しい場合がある。
+% 図\ref{atmega}は電子工作に関する{\SQ}の例であるが、
+% 正答と区別がつかない偽答を充分リストすることは難しい。
+
+It is sometimes difficult to provid fake answers to a secret question.
 
 \begin{figure}[H]
-\centerline{\includegraphics[width=83mm,bb=0 0 512 113]{figures/2f63ceb9ab6faf8d81393953f2f95a8c.png}}
+\centerline{\includegraphics[width=83mm,bb=0 0 512 113]{../figures/2f63ceb9ab6faf8d81393953f2f95a8c.png}}
 \caption{偽答の生成が難しい例.}
@@
 
-一方、正答として人名や地名を利用する場合、
-正答に似た人名や地名をリストすることは難しくない。
-「世田谷」が正答であるとき、
-「目黒」「杉並」のような偽答を用意するのは簡単である。
+% 一方、正答として人名や地名を利用する場合、
+% 正答に似た人名や地名をリストすることは難しくない。
+% 「世田谷」が正答であるとき、
+% 「目黒」「杉並」のような偽答を用意するのは簡単である。
+
+On the other hand, if the right answer to the question is a name of a place or a person,
+generating similar answers is farly easy.
+For example, if the answer to the question is ``Colorado'',
+providing fake answers like ``California'', ``Utah'', etc.
+is easy because getting a list of similar items is very easy.
+
 %
-正答と同じカテゴリに属する単語を自動的にリストすることができれば
-正答をもとにして簡単に偽答のリストを生成することができる。
+% 正答と同じカテゴリに属する単語を自動的にリストすることができれば
+% 正答をもとにして簡単に偽答のリストを生成することができる。
+In this way, fake answers can be easily listed
+if it is possible to collect words which belong to the same
+category as the right answer.
 %
-ひとつの単語もしくは単語の集合と同じカテゴリに属する単語を検索する手法は
-「同位語検索」と呼ばれ、
-Webのデータを利用した様々な同位語検索システムが提案されている%
+% ひとつの単語もしくは単語の集合と同じカテゴリに属する単語を検索する手法は
+% 「同位語検索」と呼ばれ、
+% Webのデータを利用した様々な同位語検索システムが提案されている%
+Various methods have been proposed for collecting such words.
 \cite{Huang:2012:LFC:2426725.2426728}% 読んでないけど
@@
 \cite{Wang:2007:LSE:1441428.1442086}% BooWa
-\cite{大島裕明:2006-12-15}% ライバルサーチ「やーやら」
-。
-たとえば「ライバルサーチ『やーやら』」\cite{大島裕明:2006-12-15}は、
-Web上の「AやBが」のような表現を抽出することによって
-AとBのカテゴリが近いことを判断している。
+\cite{大島裕明:2006-12-15}.% ライバルサーチ「やーやら」
 
-人名や地名の偽答を作成したい場合は
-人名や地名のデータベースを利用して偽答を生成することができる。
-市町村の人口ランキングや位置関係のデータなどを利用すれば
-似た地名を偽答としてリストすることが可能であるし、
-人名ランキングを利用すれば
-似た苗字を偽答とすることができる。
-たとえば日本の名字ランキングの40位近辺に
-「長谷川」「近藤」「石井」「斉藤」「坂本」「遠藤」「藤井」
-などの名字があるので、
-「石井」が正答のときこれらの名字を偽答にすればよい。
-しかし、
-「小学生のとき〜だった同級生は誰?」という{\SQ}の正答が「石井」であるとき
-この方法で偽答を生成すると、
-「長谷川」「近藤」などの同級生の存在を確認することにより
-正答が「石井」であることが判明してしまう可能性があるので注意が必要である。
+% たとえば「ライバルサーチ『やーやら』」\cite{大島裕明:2006-12-15}は、
+% Web上の「AやBが」のような表現を抽出することによって
+% AとBのカテゴリが近いことを判断している。
+
+% 人名や地名の偽答を作成したい場合は
+% 人名や地名のデータベースを利用して偽答を生成することができる。
+% 市町村の人口ランキングや位置関係のデータなどを利用すれば
+% 似た地名を偽答としてリストすることが可能であるし、
+% 人名ランキングを利用すれば
+% 似た苗字を偽答とすることができる。
+% たとえば日本の名字ランキングの40位近辺に
+% 「長谷川」「近藤」「石井」「斉藤」「坂本」「遠藤」「藤井」
+% などの名字があるので、
+% 「石井」が正答のときこれらの名字を偽答にすればよい。
+% しかし、
+% 「小学生のとき〜だった同級生は誰?」という{\SQ}の正答が「石井」であるとき
+% この方法で偽答を生成すると、
+% 「長谷川」「近藤」などの同級生の存在を確認することにより
+% 正答が「石井」であることが判明してしまう可能性があるので注意が必要である。
 
@@
 
-% A Password Manager that Doesn’t Remember Passwords
-\cite{Stobert:2014:PMD:2683467.2683471} % Visipass 画像クルーからパスワード生成
+% A Password Manager that Doesn’t Remember
+\cite{Stobert:2014:PMD:2683467.2683471} % Visipass 画像のヒントからパスワード生成
 

### 2016-04-12 paper/UIST2016/paper.tex
...

@@
 
-\begin{figure}[H]
-\centerline{\includegraphics[width=83mm,bb=0 0 718 796]{../WISS/figures/785ff09b4233804d2ec89c3af71ee5d0.png}}
-\caption{ブラウザ上でTwitterの{\PW}を生成.}
-\label{web1}
-\end{figure}
-
 Figure \ref{web1} shows how to generate a password
@@
 
-(figure)
-
-Here, ``\textsf{Twitter123456}'' is set as the seed string,
+\begin{figure}[H]
+\centerline{\includegraphics[width=83mm,bb=0 0 718 796]{../WISS/figures/785ff09b4233804d2ec89c3af71ee5d0.png}}
+\caption{Generating a Twitter password with EpisoPass.}
+\label{web1}
+\end{figure}
+
+Here, ``\textsf{Twitter123456}'' is provided as the seed string,
 and according to the selection to four questions,
 the seed string is converted to strings like
-``\textsf{Mfveabn574923}'', which can be used as the password
-for Twitter.
-The string changes when the user selects different candidates.
+``\textsf{Mfveabn574923}'', which can be used as the password for Twitter.
+
+When the user clicks another candidate,
+the seed string is converted to another trings like
+``\textsf{Xfveabn123456}''.
+
+\begin{figure}[H]
+\centerline{\includegraphics[width=83mm,bb=0 0 718 796]{../WISS/figures/785ff09b4233804d2ec89c3af71ee5d0.png}}
+\caption{Generating a Twitter password with EpisoPass.}
+\label{web11}
+\end{figure}
+
+In this way, different selections yields different password strings, and
+the password string generated after selecting all correct answers can be
+used as the password for the service. (Twitter in this case.)
+
+Capital letters in the seed strings are substituted to capital letters in the password,
+and digits in the seed string are substituted to digits,
+so that the generated passwords conforms to password character restrictions
+sometimes required by the service.
 
@@
 
-The first secret question is based on the author's episodic memory
-at elementary scholl,
-and the last secret questionois related to a event which the author
-can never forget.
+The first secret question in Figure \ref{web1}
+is based on the author's episodic memory at elementary scholl,
+and the last secret questionois related to a recent event which the author
+thinks he can never forget.
 All the questions are related to the author's episodic memory
@@
 
-Webサービスを利用する場合、ブラウザとサーバとの間の通信を
-記録されたり盗み見されたりされる心配を完全に払拭することはできない。
-% 危険を完全になくすことはできない。
-前述の例において、
-{\PW}はブラウザ内部でJavaScriptにより生成されるので、
-一度ページを表示した後は
-ネットワークを遮断しても{\PW}計算を行なえるようになっているが、
-最初から全く通信を行なわずに{\PW}を作成できる方がより安心であろう。
-このため、通信を全く行なわずにマシン単体で{\PW}計算を行なうための
-Androidアプリを用意した。
-ページの右上の「Androidアプリ」ボタンを押すと、
-現在表示している秘密の問題と答を内蔵したAndroidアプリが
-サーバ上でビルドされてダウンロードされる。
-
-Android端末でアプリを実行すると図\ref{android1}のような画面が表示される。
-{\SS}を設定して「開始」ボタンを押すと図\ref{android2}のように質問がひとつずつ表示され、
-ボタンを押してすべて回答すると{\PW}が計算され図\ref{android3}のように表示される。
-
-回答入力と{\PW}計算はAndroid端末で実行されるため、
-端末を「機内モード」に設定するなどの方法で
-ネットワーク接続を遮断した状態でも{\PW}を計算することができる。
-{\EP}をインストールしたAndroid端末を持っていれば常に各種の{\PW}を計算できるので、
-他人のマシンや公共の場所に設置されたパソコンなどでも
-容易にtwitterなどのネットサービスを利用することができる。
-
-前述の方法で{\EP}アプリをサーバからダウンロードする場合は、
-ブラウザ上で秘密の問題をサーバに登録する必要があるが、
-秘密の問題を全くネット上に露出することなくアプリを利用することもできる。
+% Webサービスを利用する場合、ブラウザとサーバとの間の通信を
+% 記録されたり盗み見されたりされる心配を完全に払拭することはできない。
+% % 危険を完全になくすことはできない。
+% 前述の例において、
+% {\PW}はブラウザ内部でJavaScriptにより生成されるので、
+% 一度ページを表示した後は
+% ネットワークを遮断しても{\PW}計算を行なえるようになっているが、
+% 最初から全く通信を行なわずに{\PW}を作成できる方がより安心であろう。
+% このため、通信を全く行なわずにマシン単体で{\PW}計算を行なうための
+% Androidアプリを用意した。
+% ページの右上の「Androidアプリ」ボタンを押すと、
+% 現在表示している秘密の問題と答を内蔵したAndroidアプリが
+% サーバ上でビルドされてダウンロードされる。
+
+If a user doesn't like to use EpisoPass service on the net,
+he can use an EpisoPass application on Android
+which does not use any network connection.
+After registering questions and answers on the EpisoPass service,
+the user can download an Android application from the server
+which contain all the information required for generating passwords.
+(The application is compiled and built on the server.)
+
+% Android端末でアプリを実行すると図\ref{android1}のような画面が表示される。
+% {\SS}を設定して「開始」ボタンを押すと図\ref{android2}のように質問がひとつずつ表示され、
+% ボタンを押してすべて回答すると{\PW}が計算され図\ref{android3}のように表示される。
+
+When the user runs the application and selects the right answer
+to each question, he can eventually get the password and copy it to the password entry.
+(Figure \ref{android1})
+
+% 回答入力と{\PW}計算はAndroid端末で実行されるため、
+% 端末を「機内モード」に設定するなどの方法で
+% ネットワーク接続を遮断した状態でも{\PW}を計算することができる。
+% {\EP}をインストールしたAndroid端末を持っていれば常に各種の{\PW}を計算できるので、
+% 他人のマシンや公共の場所に設置されたパソコンなどでも
+% 容易にtwitterなどのネットサービスを利用することができる。
+
+The calculation is performed on Android without network connection,
+and the user can safely use ...
+without feeling the fear of ...
+
+% 前述の方法で{\EP}アプリをサーバからダウンロードする場合は、
+% ブラウザ上で秘密の問題をサーバに登録する必要があるが、
+% 秘密の問題を全くネット上に露出することなくアプリを利用することもできる。
 

### 2016-04-13 paper/UIST2016/paper.tex
...

@@
 
-\title{EpisoPass: Password Management based on Episodic Memories}
+\title{EpisoPass: Password Management based on \\ Episodic Memories}
 
@@
 
-We propose a new password manager \textit{EpisoPass} that supports
-generating strong passwords based on users' secret episodic memories.
-When a user want to enter a password,
-EpisoPass shows the user multiple secret questions and possible answers to
-each question, and
-EpisoPass generates a password by substituting characters of the
-'seed' string based on the user's selections.
-If the right answers to the questions are known only to the user,
-the password cannot be guessable by other people, and
-various strong passwords can be easily managed
-without having master passwords or secret devices that are
-usually required for password managers.
-
+%
 % We introduce a password generation/management system called EpisoPass,
@@
 % which can be solved only by the user.
+%
 % Using EpisoPass with well-defined questions and answers,
@@
 % remembering secret information.
+
+We propose a password manager \textit{EpisoPass} that supports
+generating strong passwords based on the user's secret and unforgettable
+episodic memories.
+%
+To use EpisoPass,
+a user first collects question-answer pairs related to his episodic memory
+and registers them with many fake answers.
+%
+When a user wants to generate a password,
+EpisoPass shows the questions and lists of possible answers and asks
+the user to select correct ones.
+Then EpisoPass generates a password by substituting characters of the
+seed string based on the answer selections.
+%
+If only the user knows the correct answer,
+% If the right answers to the questions are known only to the user,
+the password cannot be guessable by other people, and
+various strong passwords can be easily managed
+without using master passwords or secret devices that are
+usually required on conventional password managers.
+%
 
@@
 Passwords have been used for various Web services and applications
-for a long time, and currently the most popular authentication method on the Internet
-without doubt.
-Since short passwords are easy to crack and
+for a long time, and currently the most popular authentication method on the Internet.
+%
+Since short passwords are easily guessed by atackers, and
 using the same password for different services is unsafe,
-different long passwords should be used for different services,
-but remembering many long passwords is almost impossible for ordinary people.
-%
-According to Flor\^{e}ncio's reearch in 2007,
+different long passwords should be used for different services.
+However,
+remembering many long passwords is almost impossible for ordinary people.
+%
+% According to Flor\^{e}ncio,
+According to a research in 2007,
 people use 6.5 passwords on 25 Web services on average, and
@@
 
-People are frequently asked to register a password when
-they try to use a new service.
+% People are frequently asked to register a password when
+% they try to use a new service.
 
@@
 
-In spite of these attempts,
+In spite of such attempts,
 password-based authentication is still the most
 convenient and strong method\cite{Bonneau},
-and it is not supposed to become extinct
+and it is not supposed to get extinct
 in a short period of time\cite{Herley:2009:PSS:1601990.1602010}.
@@
 If we have to live with password-based authentication systems,
-we have to devise a way to handle many passwords somehow.
-For handling many strong passwords,
-various password managers (PMs) have been proposed
+we have to devise some ways to handle many passwords, and
+various ``password managers'' have been proposed
+for handling many strong passwords.
+%
 {\PW}管理システムは
@@
 
-Password managers remember users' passwords and help them use passwords for different services.
-Althought PMs are useful, users should remember a 'master password' for
-keeping the secret data, and
-some password managers are not available on all environment.
+Password managers remember users' passwords and help them enter
+passwords on various services.
+Althought password managers are useful,
+users are usually forced to remember a ``master password''
+or a special hardware device
+for safely handle password managers, and
+password managers usually run on limited devices.
 
@@
 
-We believe that the biggest problem of brain-based authentication systems is that
-users cannot keep new memories which corresponds to authentication methods,
-and we believe that
-it is far better to ``generate'' symbols for authentication based on
-users' episodic memories which they can never forget.
-
-We believe that a password manager should have the following features.
-(1) It should be available on any platform including PCs, smartphones, and the Web.
-(2) Users should not have secret information (e.g. master password) or special device.
-(3) Rely only on the information in the user's brain.
-
-We propose a password manager called \textit{EpisoPass}, that generates strong passwords
-based on the user's secret episodic memories that the user can never forget,
-instead of systems based on remembering semantic memories.
+If we don't want to carry any special device for authentication,
+all the information required for the authentication should be
+kept in the brain.
+%
+However, we believe that the biggest problem of brain-based authentication is that
+users cannot keep memories like long passwords or master password.
+For this reason, we believe that
+it is far better to ``generate'' something for the authentication,
+based on users' episodic memories which they can never forget.
+
+% We believe that a password manager should have the following features.
+% (1) It should be available on any platform including PCs, smartphones, and the Web.
+% (2) Users should not have secret information (e.g. master password) or special device.
+% (3) Rely only on the information in the user's brain.
+
+We propose a password manager \textit{EpisoPass}, that generates strong passwords
+based only on the user's secret episodic memories that the user can never forget.
 
@@
 strong passwords based on users' secret episodic memories.
-A user provides a seed string and many question-answer pairs to EpisoPass,
-and a password is generated based on the user's selections.
-
-\begin{enumerate}
-\item Provide a long string for generating a password.
-We call it the ``seed string''
-
-\item Create many question strings based on personal
-secret episodic memories that the user never forgets,
-and provide many candidate answers only one of which is the correct one.
-
-% 忘れることがない個人的な{\EM}にもとづく{\SQ}を複数作成し、
-% それぞれについてひとつの正答と複数の偽答を用意する。
-
-\item Based on the user's selection of answers,
-substitute characters in the seed string and generate a
-string for password.
-
-% 質問と回答の組にもとづいて{\SS}に換字操作を行なう。
-% すべてに正しく回答したとき生成される文字列を{\PW}として利用する。
-
-\end{enumerate}
+%
+% Before using EpisoPass for generating passwords,
+% a user provides a seed string and many question-answer pairs to EpisoPass,
+% and a password is generated based on the user's selections.
+%
+
+According to Wikipedia, ...
 
@@
 
+Password generation on EpisoPass is performed through the following procedures:
+
+\begin{enumerate}
+\item A user registers many question texts based on the user's personal
+secret episodic memories that the user never forgets,
+and provide a correct answer and many fake answers.
+
+\item The user provides a long ``seed string'' for each service that requires
+a password.
+
+\item EpisoPass shows the registered data to the user so that
+the user can select an answer for each question.
+Based on the user's selection,
+EpisoPass substitute characters in the seed string and generate different
+strings for different selections.
+The user copies the string calculated when correct answers are selected,
+and use it as the password for the service.
+\end{enumerate}
+
 \subsection{Using EpisoPass on a browser}
@@
 on EpisoPass running on a browser.
-Many questions related to episodic memories are shown to the user
-as well as many candidate answers are shown for each question.
+Many questions related to the user's episodic memories are shown to the user,
+and many candidate answers are also shown for each question.
 When a user clicks and selects one of the answers for each question,
@@
 based on the selections.
-If the q-a is based on the user's episodic memories and
-nobody knows the correct answer,
-only the user can select the set of right answers and
-use the converted string as the password.
+When the user selects the right answer to all the questions,
+the right password is calculated and shown at the top.
+
+% If the q-a is based on the user's episodic memories and
+% nobody knows the correct answer,
+% only the user can select the set of right answers and
+% use the converted string as the password.
 
@@
 
-Here, ``\textsf{Twitter123456}'' is provided as the seed string,
-and according to the selection to four questions,
-the seed string is converted to strings like
-``\textsf{Mfveabn574923}'', which can be used as the password for Twitter.
+In Figure \ref{web1},
+``\textsf{Twitter123456}'' is provided as the seed string,
+and according to the selections to the four questions,
+the seed string is converted to a string like
+``\textsf{Mfveabn574923}'',
+which can be used as the password for Twitter.
 
@@
 
-In this way, different selections yields different password strings, and
-the password string generated after selecting all correct answers can be
+In this way, different selections yields different password strings and
+the password string generated after selecting correct answers can be
 used as the password for the service. (Twitter in this case.)
@@
 is based on the author's episodic memory at elementary scholl,
-and the last secret questionois related to a recent event which the author
-thinks he can never forget.
-All the questions are related to the author's episodic memory
-that he never forgets, and nobody else knows which one of the
-candidate answers is the right answer.
-
-% 最初の{\SQ}は筆者の小学校の同級生に関するもので、
-% 最後の質問は数年前の体験に関するものである。
-% これらの質問は古い{\EM}にもとづいており、
-% 筆者が将来答を忘れることはほとんど考えられないが、
-% 本人以外がこのような質問に答えることは難しいので
-% 正しい{\PW}を得ることはできない。
-
-Questions and answers can be edited on a browser, and they can be
+and the last secret question is related to a more recent event
+which the author thinks he can never forget.
+All the questions are related to the author's episodic memories
+that he thinks he never forgets, and nobody else knows which one of the
+candidate answers is the right one.
+
+Questions and answers can be edited directly on a browser, and they can be
 saved on the server by clicking the ``save on server'' button.
-Although questions and answers are saved on the server,
-no information about the correct answer is saved anywhere,
-so nobody can tell which one is the correct answer.
+The Q-A data sets are saved on the server,
+but no information about the correct answer or the
+generated password is saved on the server.
 
@@
 When we change the secret string to ``\textsf{Facebook123456}'',
-the generated password changes to Figure \ref{web2}.
+the generated password changes to ``\textsf{Xxxxxxx123456}'',
+as shown in Figure \ref{web2}.
 In this way, we can generate different passwords for
@@
 
-% {\SS}を「\textsf{Facebook123456}」に変更すると、生成される{\PW}は図\ref{web2}のように変化する。
-% このように、サービスごとに異なる{\SS}を利用することによって
-% 様々な{\PW}を簡単に生成できる。
+% {\PW}文字列の計算方法}
+% 問題と回答から文字列を生成し、そのMD5値によって{\SS}を換字することにより
+% {\PW}を生成している。
+% {\PW}文字列の計算方法は附録に示す。
+
+%アルゴリズムはここ? Algorithm
+
+Character substitution is performed based on the hash value
+calculated from putting all the selected answers.
+For example, if the user selects ``answer1-3'' to the question ``question1'',
+a hash value calculated from  ``\texttt{question1:answer1-3}''
+is used for the substitution.
+Details of the algorithm is showin in Appedix.
 
@@
 
-\subsubsection{Android application}
+\subsection{Android application}
 
@@
 
-If a user doesn't like to use EpisoPass service on the net,
+If a user doesn't like to use EpisoPass service on the browser,
 he can use an EpisoPass application on Android
@@
 
+(Figure of Android app)
+
 % 回答入力と{\PW}計算はAndroid端末で実行されるため、
@@
 
-\subsection{Algorithm for calculating password from selections}
-
-% {\PW}文字列の計算方法}
-% 問題と回答から文字列を生成し、そのMD5値によって{\SS}を換字することにより
-% {\PW}を生成している。
-% {\PW}文字列の計算方法は附録に示す。
-
-\section{Discussions}
-
-EpisoPass is just a string-conversion system and it does not
-have any information on which candidate is the correct answer.
-Also, it does not save any password information at any form, and
-it is almost impossible to get the right password 
-without having the episodic memory.
-
-\subsection{Advantages of using EpisoPass}
-
-\paragraph{Unforgettable}
-
-%   絶対忘れない
-%     30年忘れなかったものは40年忘れないだろう
+\section{DISCUSSIONS}
+
+In this section, we discuss the advantages and caveats of
+using EpisoPass.
+
+\subsection{Unforgettability}
 
 The biggest advantage of using EpisoPass is that
-users don't have to worry about forgetting or losing passwords.
-Users of EpisoPass can always save the seed string and question-answer
+users don't have to remember passwords of any kind and
+they can stop worrying about password-related troubles.
+%
+Users of EpisoPass can save the seed string and question-answer
 pairs at any place, and easily generate passwords by answering questions.
-If the question is based on old episodic memories,
-there is little chance of forgetting correct answers and losing passwords
-generated from the selections.
-If the episodic memory is based on 20 years ago and the user clearly
-remembers it at this moment, it is unlikely that he forgets the episode after
-several years.
-
-\paragraph{Usable for everyone}
-
-%   老人など、頭が弱くても対応できる
-
-Not everyone is familiar with handling passwords.
-Even experienced computer users sometimes use weak passwords,
-since choosing a good password is not a straightforward task.
-Using EpisoPass, people who cannot create and remember strong passwords
-can easily generate strong passwords just by providing secret
-questions and answers.
-With a good interface, people can even use various password-based
-services without noticing the problem of passwords.
-
-% 強いパスワードの作成と記憶が同時にできる
-
-\paragraph{Easy to change passwords}
-
-%   変えるのが簡単
-%     問題に「2016」とか「April」とか書いておけばいい
-
-On some systems, users are requested to change passwords periodically
-to strenghen security.
-A user can generate a new strong password by using a randam character generator
-on a password manager, but he might want to old passwords in case some trouble happens.
-Using EpisoPass, user can just provide a date-related question-answer pairs,
-and generate different strong passwords based on the answer.
-(Figure xxx)
-
-\paragraph{All information can be put public}
-%   全情報を公開して大丈夫
-%     マスターパスワードが要らない
-%     秘密裏などは誤って流出する可能性があるが...
-
-\paragraph{Strong passwords can be generated}
-%   強度を自由に設定できる
-
-\paragraph{Image-based authentication}
-%   画像を使える
-
-Old pictures can be used as the questions of EpisoPass.
-Even when people cannot create good secret questions,
-people can fairly easily select a secret image from their photo collections
-and use it as the question.
-For example, if you have a n old picture of your friend,
-you can use it as the question
-and use his real name and other similar names as candidate answers.
-
-例をここでいろいろ出す
-
-% 画像検索とかされないようにする必要はある
-
-Of course, the photo should not have information related to the
-person's real name, since image search is fiarly easy on the Web these days.
-
-\paragraph{Simple implementation}
-%   実装が簡単
-
-The algorithm of generating a password is quite simple and
-it can be implemented on any browser JavaScripts or
-applications on smartphones and small devices.
-
-\paragraph{パスワード自体の漏洩の心配が不要}
-% 聞かれてもわからないし書き留める必要がないからウッカリもらす可能性はない
-% ローカルに実行すればネットでもれる心配もない
-
-Since the password is generated by the algorithm and the password
-string is not kept on a computer in any form,
-unexpected leak of the password is unlikely.
-The user doesn't have to remember the string and
-there is no chance he will reveal it to somebody
-even when he is forced to tell the password.
-
-% そのためにAndroidアプリも用意した
-
-\subsection{Risks of using EpisoPass}
-
-\paragraph{Security strength of EpisoPass}
-% ■ 安全性
-
-% {\PW}は長年利用されているため
-% 強度や実際の運用に関して多くの研究が存在するが%
-% \cite{Hayashi:2011:DSP:1978942.1979326}%
-% \cite{Komanduri:2011:PPM:1978942.1979321}% どういうパスワードが強いか
-% 、{\SQ}の強度に関しては充分研究されていない。
-% {\EP}の運用実績は長くないが安全性などについて考察を行なう。
-
-There have been many studies on the strength of passwords
-\cite{Hayashi:2011:DSP:1978942.1979326}%
-\cite{Komanduri:2011:PPM:1978942.1979321},% どういうパスワードが強いか
-but the strength of secret questions are not studied a lot so far.
-
-% {\EP}で選択枝が10個の{\SQ}を8個使用する場合、
-% 総当たりで{\PW}を生成するには
-% 1億($10^8$)通りの試行が必要であり、
-% % エントロピーは26.6 ($ = 8 \times \log_2 10$) ビット
-% エントロピーは26.6ビットとなる。
-
-When we use 8 secret questions with 10 answers,
-100 million ($10^8$) trials should be performed to check
-all the combinations of the answers,
-and the entropy of the system is 26.6 ($ = 8 \times \log_2 10$) bits.
-
-英字からランダムに8文字を並べて作成した{\PW}のエントロピーは37.6ビットになるが、
-``\textsf{pmvixuzq}''のように全く意味のない{\PW}を記憶して利用することは少ないため、
-実際に利用される{\PW}のエントロピーは20ビット程度と考えられているので\cite{NIST}、
-{\SQ}と選択枝の数を10個程度用意すれば
-通常の{\PW}と同程度の強度が期待できることになる。
-%
-総当たり攻撃が可能なオフライン運用ではエントロピーの大きさは重要であるが、
-オンラインサービスでは
-{\PW}入力を何度か間違えるとサービスがブロックされるのが普通なので、
-それほど長い{\PW}を用意する必要は無いと考えられている\cite{Florencio:2007:SWP:1361419.1361429}。
-
-% 一方、{\SQ}を利用する認証の脆弱性を利用した攻撃が近年問題になっている。
-% {\PW}を忘れたときのために、
-% あらかじめ設定した{\SQ}に答えることによって{\PW}をリセットできるサービスがあり、
-% 「母親の旧姓は?」や「最初に飼ったペットの名前は?」のような
-% 質問に対してユーザが答を登録するようになっている。
-% このような問題は他人が調べたり推測したりすることが容易であるうえに
-% {\SQ}の数は一般的に少なく、
-% {\PW}よりも脆弱だといえる\cite{Rabkin:2008:PKQ:1408664.1408667}。% 銀行20個調べて{\SQ}の弱さを指摘
-
-In many services, users are forced to define answers to secret questions like
-``what is your mother's maiden name''
-so that he can log in to the service even when he forgets the password.
-This kind of authentication is far less secure than simple password systems,
-since it is fairly easy to answer the question by atackers.
-The variation of system-provided questions are usually small, and
-such a method is considered to be insecure\cite{Rabkin:2008:PKQ:1408664.1408667}.
-
-if the user can create his own secret questions,
-
-ユーザが作成した{\SQ}を使えばこのような問題はなくなるはずであるが、
-他人に解かれにくい問題をユーザが作成することは難しく、
-またユーザ自身が答を忘れてしまうことも多いと考えられている\cite{Just:2009:PCC:1572532.1572543}\cite{Schechter:2009:NSM:1607723.1608145}。
-%
-また、古い記憶にもとづいて作成した秘密の問題は
-ユーザが想像するよりも解かれやすいという実験結果にもとづき、
-忘れない{\SQ}を複数利用する方法、
-問題と答を連想するために画像を利用する方法、
-複数の問題を連続的に利用する手法などが提案されている\cite{Renaud:2010:PQE:2146303.2146318}。
-
-{\EP}では、
-他人には解くことが難しく自分では忘れないような{\SQ}を自由にいくつでも利用できるようになっている。
-問題作成に慣れていないユーザには有効な{\SQ}を作成することは難しいかもしれないが、
-次節で述べるように、適切な質問を選ぶことによりこの問題を解決できるはずである。
-
-The strength of the generated password depends on the number of
-questions and the 'secretness' of the questions.
-If the episodic memory is shared by someone else,
-that personn can easily answer the question and generate the
-password just like the user.
-
-Questions like "Which one is your favorite?" should be avoided,
-since some of the friends might know the user's taste.
-Questions related to a episode which the user is proud of should also be
-avoided, since the user might talk aboutu the episode to somebody else.
-
-If, one of the passwords generated by EpisoPass is revealed
-for some reason,... フルートフォースでとかれる可能性はある
-
-To prevent such troble, it is safer to keep all the q-a pairs secret.
-
-問題を時々変えるのが安全だろう
-
-問題自体が秘密であればひとつ漏れても大丈夫
-
-\subsection{Selecting secret questions}
+If the question is based on old unforgettable episodic memories,
+there is little chance of losing passwords.
+If the user's memory is related to an episode of 20 years ago and the user clearly
+remembers it now, it is unlikely that he forgets the episode after 10 years.
+
+\subsection{Selecting good questions}
 
@@
 
-Selecting good questions is very important for using EpisoPass.
+The quality of secret questions is the key to using EpisoPass.
 The episode related to the question should not be known to other people,
-and the episode should be an unforgettable one.
-%
+and the episode should be unforgettable.
+%
+Finding such episodes seems difficult at first, but
+when we try to remember experiences of old days,
+we can recall many trivial episodes which are not
+important for other people.
+%
+Questions like the following are good candidates for
+questions used in EpisoPass.
+
+\begin{itemize}
+% \item 昔のちょっとした怪我の場所や種類
+\item Memory of small injury
+
+\vspace{-1mm}
+% \item 昔のちょっと悔しい思い出
+\item Memories of bad experience like blunders or defeat
+
+\vspace{-1mm}
+% \item 昔何かを見つけた場所
+\item Experience of finding a small item
+\end{itemize}
+
+% たとえば図\ref{kega}のような{\SQ}は他人に話したことが無いが、
+% 痛い思いをしたことは忘れないし、
+% 偽答を作成するのも簡単なので、
+% 認証のための{\SQ}として適切であると考えられる。
 
@@
 Instead, more subtle and
-
-Specifically, questions like the following are good candidates for
-questions used in EpisoPass.
-
-\begin{itemize}
-% \item 昔のちょっとした怪我の場所や種類
-\item Memory of small injury
-
-\vspace{-1mm}
-% \item 昔のちょっと悔しい思い出
-\item Memories of bad experience like blunders or defeat
-
-\vspace{-1mm}
-% \item 昔何かを見つけた場所
-\item Experience of finding a small item
-\end{itemize}
-
-% たとえば図\ref{kega}のような{\SQ}は他人に話したことが無いが、
-% 痛い思いをしたことは忘れないし、
-% 偽答を作成するのも簡単なので、
-% 認証のための{\SQ}として適切であると考えられる。
 
@@
 
+\subsection{Usable for everyone}
+
+Not everyone is familiar with handling passwords.
+Even experienced computer users have trouble with passwords,
+since choosing a good password is difficult and people forget passwords frequently.
+Using EpisoPass, people who cannot create and remember strong passwords
+can easily generate strong passwords just by providing secret
+questions and answers.
+By integrating EpisoPass into existing password-based services,
+people can even use such services without noticing the problem of passwords.
+
+% 強いパスワードの作成と記憶が同時にできる
+
+\subsection{Easy to change passwords}
+
+%   変えるのが簡単
+%     問題に「2016」とか「April」とか書いておけばいい
+
+On many services, users are requested to change passwords periodically
+to strenghen security.
+A user can generate a new strong password by using a randam character generator
+on a password manager, but he might want to old passwords in case some trouble happens.
+Using EpisoPass, user can just provide a date-related question-answer pairs,
+and generate different strong passwords based on the answer.
+
+(Figure xxx)
+
+\subsection{Security strength of EpisoPass}
+
+There have been many studies on the strength of passwords
+\cite{Hayashi:2011:DSP:1978942.1979326}%
+\cite{Komanduri:2011:PPM:1978942.1979321},% どういうパスワードが強いか
+but the strength of secret questions has not been studied.
+%
+% {\EP}で選択枝が10個の{\SQ}を8個使用する場合、
+% 総当たりで{\PW}を生成するには
+% 1億($10^8$)通りの試行が必要であり、
+% % エントロピーは26.6 ($ = 8 \times \log_2 10$) ビット
+% エントロピーは26.6ビットとなる。
+%
+When we use 10 secret questions with 20 answers,
+1 billion ($20^8$) trials should be performed to check
+all the combinations of the answers,
+and the entropy of the system is 43.2 ($ = 10 \times \log_2 20$) bits.  % 10.0 * (Math.log(20.0)/Math.log(2.0))
+%
+% 英字からランダムに8文字を並べて作成した{\PW}のエントロピーは37.6ビットになるが、
+% ``\textsf{pmvixuzq}''のように全く意味のない{\PW}を記憶して利用することは少ないため、
+% 実際に利用される{\PW}のエントロピーは20ビット程度と考えられているので\cite{NIST}、
+% {\SQ}と選択枝の数を10個程度用意すれば
+% 通常の{\PW}と同程度の強度が期待できることになる。
+%
+It is almost the same entropy as using random 8-character English letters
+as a password, in which case the entropy is 45.6 bits, 
+and this level of strength is considered to be enough for most Web services,
+where online blute-force attack is impossible\cite{Florencio:2007:SWP:1361419.1361429}.
+
+% 総当たり攻撃が可能なオフライン運用ではエントロピーの大きさは重要であるが、
+% オンラインサービスでは
+% {\PW}入力を何度か間違えるとサービスがブロックされるのが普通なので、
+% それほど長い{\PW}を用意する必要は無いと考えられている\cite{Florencio:2007:SWP:1361419.1361429}。
+
+\subsection{Issues on EpisoPass questions}
+
+% 一方、{\SQ}を利用する認証の脆弱性を利用した攻撃が近年問題になっている。
+% {\PW}を忘れたときのために、
+% あらかじめ設定した{\SQ}に答えることによって{\PW}をリセットできるサービスがあり、
+% 「母親の旧姓は?」や「最初に飼ったペットの名前は?」のような
+% 質問に対してユーザが答を登録するようになっている。
+% このような問題は他人が調べたり推測したりすることが容易であるうえに
+% {\SQ}の数は一般的に少なく、
+% {\PW}よりも脆弱だといえる\cite{Rabkin:2008:PKQ:1408664.1408667}。% 銀行20個調べて{\SQ}の弱さを指摘
+
+In many services, users are forced to define answers to secret questions like
+``what is your mother's maiden name''
+so that he can log in to the service even when he forgets the password.
+This kind of authentication is far less secure than simple password systems,
+since it is fairly easy to answer the question by atackers.
+The variation of system-provided questions are usually small, and
+such a method is considered to be insecure\cite{Rabkin:2008:PKQ:1408664.1408667}.
+
+if the user can create his own secret questions,
+
+ユーザが作成した{\SQ}を使えばこのような問題はなくなるはずであるが、
+他人に解かれにくい問題をユーザが作成することは難しく、
+またユーザ自身が答を忘れてしまうことも多いと考えられている\cite{Just:2009:PCC:1572532.1572543}\cite{Schechter:2009:NSM:1607723.1608145}。
+%
+また、古い記憶にもとづいて作成した秘密の問題は
+ユーザが想像するよりも解かれやすいという実験結果にもとづき、
+忘れない{\SQ}を複数利用する方法、
+問題と答を連想するために画像を利用する方法、
+複数の問題を連続的に利用する手法などが提案されている\cite{Renaud:2010:PQE:2146303.2146318}。
+
+{\EP}では、
+他人には解くことが難しく自分では忘れないような{\SQ}を自由にいくつでも利用できるようになっている。
+問題作成に慣れていないユーザには有効な{\SQ}を作成することは難しいかもしれないが、
+次節で述べるように、適切な質問を選ぶことによりこの問題を解決できるはずである。
+
+The strength of the generated password depends on the number of
+questions and the 'secretness' of the questions.
+If the episodic memory is shared by someone else,
+that personn can easily answer the question and generate the
+password just like the user.
+
+Questions like "Which one is your favorite?" should be avoided,
+since some of the friends might know the user's taste.
+Questions related to a episode which the user is proud of should also be
+avoided, since the user might talk aboutu the episode to somebody else.
+
+\subsection{All information can be put public}
+
+Questions and answers can be put on a public place
+if enough amount of questions and fake answers are provided.
+%
+Keeping the secret of something is always a pain for many people including
+the authors, but if the whole questions and answers used on EpisoPass
+can be put on a public place,
+handling it becomes very easy.
+Usually we have to be very careful about handling
+secret information like passwords, secret key for SSH, etc.
+so that they are not copied or saved to unsafe places.
+On the other hand,
+we can save the EpisoPass data as a plain text file and put it at
+any place without great care, since malicious person cannot calculate
+passwords without having the owner's episodic memories.
+
+%   全情報を公開して大丈夫
+%     マスターパスワードが要らない
+
+\subsection{Risk of password leak}
+
+EpisoPass is just a string-conversion system and it does not
+have any information on which candidate is the correct answer.
+Also, it does not save any password information at any form, and
+it is almost impossible to get the right password 
+without having the episodic memory.
+
+% 聞かれてもわからないし書き留める必要がないからウッカリもらす可能性はない
+% ローカルに実行すればネットでもれる心配もない
+
+Since the password is generated by the algorithm and the password
+string is not kept on a computer in any form,
+unexpected leak of the password is unlikely.
+The user doesn't have to remember the string and
+there is no chance he will reveal it to somebody
+even when he is forced to tell the password.
+
+% そのためにAndroidアプリも用意した
+
+% \subsection{Strong passwords can be generated}
+%   強度を自由に設定できる
+
+\subsection{Using images}
+%   画像を使える
+
+Old pictures can be used as the questions of EpisoPass.
+Even when people cannot create good secret questions,
+people can fairly easily select a secret image from their photo collections
+and use it as the question.
+For example, if you have a n old picture of your friend,
+you can use it as the question
+and use his real name and other similar names as candidate answers.
+
+例をここでいろいろ出す
+
+% 画像検索とかされないようにする必要はある
+
+Of course, the photo should not have information related to the
+person's real name, since image search is fiarly easy on the Web these days.
+
+\subsection{Simple implementation}
+%   実装が簡単
+
+The algorithm of generating a password is quite simple and
+it can be implemented on any browser JavaScripts or
+applications on smartphones and small devices.
+
+If, one of the passwords generated by EpisoPass is revealed
+for some reason,... フルートフォースでとかれる可能性はある
+
+To prevent such troble, it is safer to keep all the q-a pairs secret.
+
+問題を時々変えるのが安全だろう
+
+問題自体が秘密であればひとつ漏れても大丈夫
+
 \subsection{{\PW}漏洩時の問題}
@@
 
-{\scriptsize
+{% \scriptsize
 \bibliographystyle{acm-sigchi}
@@
 
-* 秘密の質問に入れる偽装の答えをどこにメモしたか忘れるという事もしばしば
-
-=> 問題も答も公開しておけば忘れることはないでしょう。
-
 * クイズにできるエピソードがない人はどうすればいいんでしょう
@@
 小学校のときちょっとしたケガ体験とかエピソードとか覚えてませんか?
-
-* EpisoPassのフィッシングサイトができたらどうしましょう
-
-=> 完全にローカルHTMLかローカルアプリで使えば安心でしょう。
 

### 2016-04-13 paper/UIST2016/paper.tex
...

@@
 %
-Users of EpisoPass can save the seed string and question-answer
-pairs at any place, and easily generate passwords by answering questions.
+Users of EpisoPass can save the seed string and question-answers
+at any place, and easily generate passwords by answering questions.
 If the question is based on old unforgettable episodic memories,
@@
 If the user's memory is related to an episode of 20 years ago and the user clearly
-remembers it now, it is unlikely that he forgets the episode after 10 years.
+remembers it now, it is unlikely that he forgets the episode 10 years later.
 
@@
 
+The strength of the generated password depends on the number of
+questions and the 'secretness' of the questions.
+If the episodic memory is shared by someone else,
+that personn can easily answer the question and generate the
+password just like the user.
+
 The quality of secret questions is the key to using EpisoPass.
-The episode related to the question should not be known to other people,
+The episode related to each question should not be known to other people,
 and the episode should be unforgettable.
@@
 when we try to remember experiences of old days,
-we can recall many trivial episodes which are not
-important for other people.
-%
-Questions like the following are good candidates for
+we can recall many trivial episodes which are unforgettable but
+not important to other people.
+%
+Old experienceslike the following are good candidates for
 questions used in EpisoPass.
@@
 \begin{itemize}
-% \item 昔のちょっとした怪我の場所や種類
-\item Memory of small injury
-
-\vspace{-1mm}
-% \item 昔のちょっと悔しい思い出
-\item Memories of bad experience like blunders or defeat
-
-\vspace{-1mm}
-% \item 昔何かを見つけた場所
-\item Experience of finding a small item
+\item Memory of small injury. (Nobody cares it but you.)
+
+\item Memories of bad experience like blunders or defeat.
+
+\item Experience of finding a small special item.
 \end{itemize}
 
-% たとえば図\ref{kega}のような{\SQ}は他人に話したことが無いが、
-% 痛い思いをしたことは忘れないし、
-% 偽答を作成するのも簡単なので、
-% 認証のための{\SQ}として適切であると考えられる。
-
-\begin{itemize}
-\item \textsf{自慢になるもの
-(何かの機会にうっかり他人に話してしまう可能性がある)}
-
-\vspace{-1mm}
-\item \textsf{ネット上に記録が残っているもの}
-
-\vspace{-1mm}
-\item \textsf{他人と情報を共有しているもの}
-
-\vspace{-1mm}
-\item \textsf{趣味や嗜好に関連するもの
-(他人に推測されやすいうえに嗜好が変化する可能性がある)}
-
-\end{itemize}
-
-\noindent
-% このようなものではなく、
-% 「わざわざ人に話すことはないが自分の記憶に強く残っているような無難な{\EM}」を
-% {\SQ}として利用するのが良いであろう。
-% 具体例としては以下のようなものがある。
-Instead, more subtle and
-
-For example, a question like xxxx is about a trivial experience
-that people do not mention, but an experience like this is
-not forgettable because it was a very bad experiance.
-
-% \subsection{偽答の作成方法}
+For example, a question like
+``who hit you when you were 6 years old?''
+is about a trivial experience that people do not mention,
+but a bad experience like this is not forgettable.
+
+Questions like "Which one is your favorite?" should be avoided,
+since some of the friends might know the user's taste.
+Questions related to a episode which the user is proud of should also be
+avoided, since the user might talk aboutu the episode to somebody else.
+
+We usually don't tell our bad experiences to other people,
+but we might boast of good experiences or even write a blog about it.
+Also, our tastes (e.g. favorite food) might change in the long run.
+Using such episodes for questions should be avoided.
+
+% \begin{itemize}
+% \item \textsf{自慢になるもの
+% (何かの機会にうっかり他人に話してしまう可能性がある)}
+% 
+% \vspace{-1mm}
+% \item \textsf{ネット上に記録が残っているもの}
+% 
+% \vspace{-1mm}
+% \item \textsf{他人と情報を共有しているもの}
+% 
+% \vspace{-1mm}
+% \item \textsf{趣味や嗜好に関連するもの
+% (他人に推測されやすいうえに嗜好が変化する可能性がある)}
+% 
+% \end{itemize}
+
 \subsection{Creating fake answers}
@@
 
-It is sometimes difficult to provid fake answers to a secret question.
-
-\begin{figure}[H]
-\centerline{\includegraphics[width=83mm,bb=0 0 512 113]{../figures/2f63ceb9ab6faf8d81393953f2f95a8c.png}}
-\caption{偽答の生成が難しい例.}
-\label{atmega}
-\end{figure}
+It is sometimes difficult to provid fake answers to a secret question like
+``what was your favorite sport?''
+because possible answers are limited.
+
+% \begin{figure}[H]
+% \centerline{\includegraphics[width=83mm,bb=0 0 512 113]{../figures/2f63ceb9ab6faf8d81393953f2f95a8c.png}}
+% \caption{偽答の生成が難しい例.}
+% \label{atmega}
+% \end{figure}
 
@@
 On the other hand, if the right answer to the question is a name of a place or a person,
-generating similar answers is farly easy.
+generating similar answers is easy.
 For example, if the answer to the question is ``Colorado'',
-providing fake answers like ``California'', ``Utah'', etc.
-is easy because getting a list of similar items is very easy.
-
-%
+we can easily provide fake answers like ``California'', ``Utah'', etc.
+because we can use the list of states in the U.S.
+
 % 正答と同じカテゴリに属する単語を自動的にリストすることができれば
@@
 % Webのデータを利用した様々な同位語検索システムが提案されている%
-Various methods have been proposed for collecting such words.
+For information retrieval purposes,
+various methods have been proposed for collecting words in the
+same category.
 \cite{Huang:2012:LFC:2426725.2426728}% 読んでないけど
@@
 \cite{大島裕明:2006-12-15}.% ライバルサーチ「やーやら」
-
-% たとえば「ライバルサーチ『やーやら』」\cite{大島裕明:2006-12-15}は、
-% Web上の「AやBが」のような表現を抽出することによって
-% AとBのカテゴリが近いことを判断している。
-
-% 人名や地名の偽答を作成したい場合は
-% 人名や地名のデータベースを利用して偽答を生成することができる。
-% 市町村の人口ランキングや位置関係のデータなどを利用すれば
-% 似た地名を偽答としてリストすることが可能であるし、
-% 人名ランキングを利用すれば
-% 似た苗字を偽答とすることができる。
-% たとえば日本の名字ランキングの40位近辺に
-% 「長谷川」「近藤」「石井」「斉藤」「坂本」「遠藤」「藤井」
-% などの名字があるので、
-% 「石井」が正答のときこれらの名字を偽答にすればよい。
-% しかし、
-% 「小学生のとき〜だった同級生は誰?」という{\SQ}の正答が「石井」であるとき
-% この方法で偽答を生成すると、
-% 「長谷川」「近藤」などの同級生の存在を確認することにより
-% 正答が「石井」であることが判明してしまう可能性があるので注意が必要である。
+We can use such systems for getting similar names.
 
@@
 
-Not everyone is familiar with handling passwords.
+Although everyone has to use authentication systems on the Net these days,
+not everyone is familiar with handling passwords.
 Even experienced computer users have trouble with passwords,
@@
 Using EpisoPass, people who cannot create and remember strong passwords
-can easily generate strong passwords just by providing secret
+can easily generate strong passwords just by providing secret episodic
 questions and answers.
 By integrating EpisoPass into existing password-based services,
-people can even use such services without noticing the problem of passwords.
-
-% 強いパスワードの作成と記憶が同時にできる
+people can even use services without noticing that passwords are
+used for the authentication.
 
 \subsection{Easy to change passwords}
-
-%   変えるのが簡単
-%     問題に「2016」とか「April」とか書いておけばいい
 
@@
 
-(Figure xxx)
+(Figure xxx) 最初の例に入れておく
 
@@
 \cite{Hayashi:2011:DSP:1978942.1979326}%
-\cite{Komanduri:2011:PPM:1978942.1979321},% どういうパスワードが強いか
-but the strength of secret questions has not been studied.
+\cite{Komanduri:2011:PPM:1978942.1979321}, % どういうパスワードが強いか
+but the strength of secret questions has not been studied enough.
 %
@@
 all the combinations of the answers,
-and the entropy of the system is 43.2 ($ = 10 \times \log_2 20$) bits.  % 10.0 * (Math.log(20.0)/Math.log(2.0))
+and the entropy of the system is 43.2 ($10 \times \log_2 20$) bits.  % 10.0 * (Math.log(20.0)/Math.log(2.0))
 %
@@
 %
-It is almost the same entropy as using random 8-character English letters
-as a password, in which case the entropy is 45.6 bits, 
-and this level of strength is considered to be enough for most Web services,
+It is almost the same entropy as using random 8-character English alphabets
+as a password, in which case the entropy is 45.6 bits.
+This level is considered to be strong enough for using Web services,
 where online blute-force attack is impossible\cite{Florencio:2007:SWP:1361419.1361429}.
 
-% 総当たり攻撃が可能なオフライン運用ではエントロピーの大きさは重要であるが、
-% オンラインサービスでは
-% {\PW}入力を何度か間違えるとサービスがブロックされるのが普通なので、
-% それほど長い{\PW}を用意する必要は無いと考えられている\cite{Florencio:2007:SWP:1361419.1361429}。
-
-\subsection{Issues on EpisoPass questions}
+\subsection{Comparison with challenge-response authentication systems}
 
@@
 This kind of authentication is far less secure than simple password systems,
-since it is fairly easy to answer the question by atackers.
+since it is fairly easy for atackers to get the right answer.
 The variation of system-provided questions are usually small, and
-such a method is considered to be insecure\cite{Rabkin:2008:PKQ:1408664.1408667}.
-
-if the user can create his own secret questions,
-
-ユーザが作成した{\SQ}を使えばこのような問題はなくなるはずであるが、
-他人に解かれにくい問題をユーザが作成することは難しく、
-またユーザ自身が答を忘れてしまうことも多いと考えられている\cite{Just:2009:PCC:1572532.1572543}\cite{Schechter:2009:NSM:1607723.1608145}。
-%
-また、古い記憶にもとづいて作成した秘密の問題は
-ユーザが想像するよりも解かれやすいという実験結果にもとづき、
-忘れない{\SQ}を複数利用する方法、
-問題と答を連想するために画像を利用する方法、
-複数の問題を連続的に利用する手法などが提案されている\cite{Renaud:2010:PQE:2146303.2146318}。
+such challenge-response systems are considered to be insecure\cite{Rabkin:2008:PKQ:1408664.1408667}.
+
+It would be better if the user can register his own secret questions
+based on his episodic memory.
+However, answers to user-generated challenge questions are more easily
+forgotten or cracked,
+and using simple challenge-responce is not considered to be safe enough
+\cite{Just:2009:PCC:1572532.1572543}\cite{Schechter:2009:NSM:1607723.1608145}.
+%
+Also, in this case,
+the user should register the answer to the system in additon to the question.
+Telling secret facts to service providers is like
+registering raw password string on the server,
+and it is not safe unless the strings are properly hashed and salted on the server.
+
+%
+%ユーザが作成した{\SQ}を使えばこのような問題はなくなるはずであるが、
+%他人に解かれにくい問題をユーザが作成することは難しく、
+%またユーザ自身が答を忘れてしまうことも多いと考えられている\cite{Just:2009:PCC:1572532.1572543}\cite{Schechter:2009:NSM:1607723.1608145}。
+%
+%また、古い記憶にもとづいて作成した秘密の問題は
+%ユーザが想像するよりも解かれやすいという実験結果にもとづき、
+%忘れない{\SQ}を複数利用する方法、
+%問題と答を連想するために画像を利用する方法、
+%複数の問題を連続的に利用する手法などが提案されている\cite{Renaud:2010:PQE:2146303.2146318}。
 
@@
 次節で述べるように、適切な質問を選ぶことによりこの問題を解決できるはずである。
-
-The strength of the generated password depends on the number of
-questions and the 'secretness' of the questions.
-If the episodic memory is shared by someone else,
-that personn can easily answer the question and generate the
-password just like the user.
-
-Questions like "Which one is your favorite?" should be avoided,
-since some of the friends might know the user's taste.
-Questions related to a episode which the user is proud of should also be
-avoided, since the user might talk aboutu the episode to somebody else.
 
@@
 
-% そのためにAndroidアプリも用意した
-
 % \subsection{Strong passwords can be generated}
 %   強度を自由に設定できる
+
+\subsection{Simple implementation}
+%   実装が簡単
+
+The algorithm of generating a password (Appendix)
+is fairly simple and
+it can be implemented on any browser JavaScripts or
+applications on smartphones and small devices.
+
+\subsection{{\PW}漏洩時の問題}
+
+If, one of the passwords generated by EpisoPass is revealed
+for some reason,... フルートフォースでとかれる可能性はある
+
+To prevent such troble, it is safer to keep all the q-a pairs secret.
+
+問題を時々変えるのが安全だろう
+
+問題自体が秘密であればひとつ漏れても大丈夫
+
+{\SQ}を公開している場合、
+{\SS}と{\PW}の対応がひとつでも漏洩してしまうと、
+総当たり計算でチェックすることにより、
+すべて{\SQ}の正答が判明してしまう。
+{\SQ}の正答を知っていれば
+{\SS}から{\PW}を計算することができるので、
+漏洩した{\SQ}は利用不可能になってしまう。
+%
+\ref{pattern1}や
+\ref{pattern2}のような運用をしている場合は
+{\PW}がひとつ漏洩しても他の{\PW}は安全だが、
+\ref{pattern3}のような運用をしている場合は
+ひとつでも{\PW}が漏洩するとあらゆる{\PW}が漏洩してしまうことになる。
 
@@
 person's real name, since image search is fiarly easy on the Web these days.
-
-\subsection{Simple implementation}
-%   実装が簡単
-
-The algorithm of generating a password is quite simple and
-it can be implemented on any browser JavaScripts or
-applications on smartphones and small devices.
-
-If, one of the passwords generated by EpisoPass is revealed
-for some reason,... フルートフォースでとかれる可能性はある
-
-To prevent such troble, it is safer to keep all the q-a pairs secret.
-
-問題を時々変えるのが安全だろう
-
-問題自体が秘密であればひとつ漏れても大丈夫
-
-\subsection{{\PW}漏洩時の問題}
-
-{\SQ}を公開している場合、
-{\SS}と{\PW}の対応がひとつでも漏洩してしまうと、
-総当たり計算でチェックすることにより、
-すべて{\SQ}の正答が判明してしまう。
-{\SQ}の正答を知っていれば
-{\SS}から{\PW}を計算することができるので、
-漏洩した{\SQ}は利用不可能になってしまう。
-%
-\ref{pattern1}や
-\ref{pattern2}のような運用をしている場合は
-{\PW}がひとつ漏洩しても他の{\PW}は安全だが、
-\ref{pattern3}のような運用をしている場合は
-ひとつでも{\PW}が漏洩するとあらゆる{\PW}が漏洩してしまうことになる。
-
-\subsection{画像認証の利用}
 
@@
 
-\section{Limitations}
-
-% なぞなぞ問題を考えるのが難しい
-%   自分だけ知ってる秘密など思いつかない人が多い
-%   しかしインタビューを行なうとそういうのは出てくる
-%     子供のときの怪我、ケンカ、失敗など
-%     特に、自慢にならないものが良い
-% 
 % 強度が直感的でない
@@
 
-    \vspace{-1mm}
   % \item $S$のMD5ハッシュ値$M$(16進32桁の文字列)を計算
@@
 
-    \vspace{-1mm}
   %\item {\SS}の$k$桁目の文字に対し、

### 2016-04-13 paper/UIST2016/paper.tex
...

@@
 %
-{\PW}管理システムは
-ひとつの「マスター{\PW}」を利用して他のすべての{\PW}を管理するもので、
-暗号化されたデータベースに{\PW}を格納するもの%
+%{\PW}管理システムは
+%ひとつの「マスター{\PW}」を利用して他のすべての{\PW}を管理するもので、
+%暗号化されたデータベースに{\PW}を格納するもの%
+%
+Most password managers remembers various passwords and
+asks users to remember a single ``master password'' to access the database
 \cite{OnePassword}%
@@
 \cite{NortonIDSafe}%
-\cite{IDManager}%
-が多いが、サービス名をもとにマスター{\PW}を変換することによって
-複数の{\PW}を生成するシステム\cite{SuperGenPass}もある。
-両者ともにマスター{\PW}の記憶は必須であり、
-マスター{\PW}を盗まれたり忘れたりする危険がある。
-
+\cite{IDManager}.
+%
+%が多いが、サービス名をもとにマスター{\PW}を変換することによって
+%複数の{\PW}を生成するシステム\cite{SuperGenPass}もある。
+%両者ともにマスター{\PW}の記憶は必須であり、
+%マスター{\PW}を盗まれたり忘れたりする危険がある。
+%
 Password managers remember users' passwords and help them enter
@@
 password managers usually run on limited devices.
-
-% このように、実際のパスワード運用はとても大変であるが、
-%   * パスワードを使わなければならないのは確かだし、
-%   * 漏洩や紛失の危険がないのは脳内情報ぐらいである
-%      鍵デバイスや生体情報などはダメ
 
@@
 \begin{figure}[H]
-\centerline{\includegraphics[width=83mm,bb=0 0 718 796]{../WISS/figures/785ff09b4233804d2ec89c3af71ee5d0.png}}
+\includegraphics[width=110mm,bb=-30 0 803 662]{figures/c1bd6e7f67698c70978f528ccd2339d9.png}
 \caption{Generating a Twitter password with EpisoPass.}
@@
 the seed string is converted to a string like
-``\textsf{Mfveabn574923}'',
+``\textsf{Lbasnln542202}'',
 which can be used as the password for Twitter.
@@
 the seed string is converted to another trings like
-``\textsf{Xfveabn123456}''.
+``\textsf{Bhtuyna904127}''.
 
 \begin{figure}[H]
-\centerline{\includegraphics[width=83mm,bb=0 0 718 796]{../WISS/figures/785ff09b4233804d2ec89c3af71ee5d0.png}}
+\includegraphics[width=110mm,bb=-30 0 803 660]{figures/01e5507d090eb494a20bcbc47c86b1d2.png}
 \caption{Generating a Twitter password with EpisoPass.}
@@
 
-(Figure of Android app)
+\begin{figure}[H]
+\includegraphics[width=80mm,bb=-30 0 399 386]{figures/429eec261024dc6c85351f51c12f09b4.png}
+\caption{Running EpisoPass on Android.}
+\label{android1}
+\end{figure}
+
+\begin{figure}[H]
+\includegraphics[width=80mm,bb=-30 0 400 106]{figures/ba8f5aeaa935ad63437969f4d746746b.png}
+\caption{Running EpisoPass on Android.}
+\label{android2}
+\end{figure}
 
@@
 
-{\EM}に結びついた{\SQ}を利用して{\PW}を生成/管理できるシステム{\EP}を提案した。
-{\EP}は単純な原理にもとづいており柔軟な利用形態が可能であり、
-強力な{\SQ}を用意することにより
-秘密情報を全く覚えることなく安全な認証を行なうことができる。
-%
-強力な{\SQ}を作成して安全に運用が可能かどうかを長期的に評価したいと考えている。
+We have developed a
+
+% {\EM}に結びついた{\SQ}を利用して{\PW}を生成/管理できるシステム{\EP}を提案した。
+% {\EP}は単純な原理にもとづいており柔軟な利用形態が可能であり、
+% 強力な{\SQ}を用意することにより
+% 秘密情報を全く覚えることなく安全な認証を行なうことができる。
+% %
+% 強力な{\SQ}を作成して安全に運用が可能かどうかを長期的に評価したいと考えている。
 %
@@
 %
-{\EP}は\textsf{http://Episopass.com/}で運用しており、
-ソースはGitHubで公開している\footnote{
-  \textsf{http://GitHub.com/masui/EpisoPass}
-}。
+% {\EP}は\textsf{http://Episopass.com/}で運用しており、
+% ソースはGitHubで公開している\footnote{
+%   \textsf{http://GitHub.com/masui/EpisoPass}
+% }。
 

### 2016-04-13 lib/config.rb

@@ -1,5 +1,7 @@
 # -*- coding: utf-8 -*-
 
-ROOT = "/home/masui/EpisoPass"
-FILEROOT = "/home/masui/EpisoPass/data"
+#ROOT = "/home/masui/EpisoPass"
+#FILEROOT = "/home/masui/EpisoPass/data"
+ROOT = "/Users/masui/EpisoPass"
+FILEROOT = "/Users/masui/EpisoPass/data"
 # FILEROOT = "/tmp"

### 2016-04-13 paper/UIST2016/paper.tex
...

@@
 %
-Since short passwords are easily guessed by atackers, and
+Since short passwords are easily guessed by attackers, and
 using the same password for different services is unsafe,
@@
 password-based authentication is still the most
-convenient and strong method\cite{Bonneau},
+convenient and strong method\cite{Bonnearu:ReplacePasswords},
 and it is not supposed to get extinct
@@
 %
-However, we believe that the biggest problem of brain-based authentication is that
-users cannot keep memories like long passwords or master password.
+However, the biggest problem of brain-based authentication is that
+users cannot safely keep memories like long passwords or master password.
 For this reason, we believe that
@@
 based on users' episodic memories which they can never forget.
-
+%
 % We believe that a password manager should have the following features.
@@
 % (3) Rely only on the information in the user's brain.
-
-We propose a password manager \textit{EpisoPass}, that generates strong passwords
+%
+We propose a password manager \textit{EpisoPass} that generates strong passwords
 based only on the user's secret episodic memories that the user can never forget.
@@
 %
-
-According to Wikipedia, ...
-
-\begin{quote}
-Episodic memory is the memory of autobiographical events (times,
-places, associated emotions, and other contextual who, what, when,
-where, why knowledge) that can be explicitly stated. It is the
-collection of past personal experiences that occurred at a particular
-time and place. For example, if one remembers the party on his or her
-6th birthday, this is an episodic memory. They allow an individual to
-figuratively travel back in time to remember the event that took place
-at that particular time and place.[1]
-
-Semantic memory is one of the two types of declarative or explicit
-memory (our memory of facts or events that is explicitly stored and
-retrieved).[1] Semantic memory refers to general world knowledge that
-we have accumulated throughout our lives.[2] This general knowledge
-(facts, ideas, meaning and concepts) is intertwined in experience and
-dependent on culture. Semantic memory is distinct from episodic
-memory, which is our memory of experiences and specific events that
-occur during our lives, from which we can recreate at any given
-point.[3] For instance, semantic memory might contain information
-about what a cat is, whereas episodic memory might contain a specific
-memory of petting a particular cat. We can learn about new concepts by
-applying our knowledge learned from things in the past.[4] The
-counterpart to declarative, or explicit memory, is procedural memory,
-or implicit memory.[5]
-\end{quote}
+Memories in human brain is not uniform.
+Some memories are very short-lived, and others are unforgettable.
+When we have a very impressive experience,
+that memory will stay in the brain for a long time and
+cannot easily disappear.
+On the other hand, when we study math and try to remember a formula,
+it is usually hard to memorize it unless we practice a lot,
+since the knowledge about the formula is not related to
+any personal experiences.
+The former type of memory is called the episodic memory and
+people cannot easily forget it.
+Memories of passwords belong to the latter type and
+people cannot easily remember them, just like people cannot
+remember math formulas easily.
+%
+
+% \begin{quote}
+% Episodic memory is the memory of autobiographical events (times,
+% places, associated emotions, and other contextual who, what, when,
+% where, why knowledge) that can be explicitly stated. It is the
+% collection of past personal experiences that occurred at a particular
+% time and place. For example, if one remembers the party on his or her
+% 6th birthday, this is an episodic memory. They allow an individual to
+% figuratively travel back in time to remember the event that took place
+% at that particular time and place.[1]
+% 
+% Semantic memory is one of the two types of declarative or explicit
+% memory (our memory of facts or events that is explicitly stored and
+% retrieved).[1] Semantic memory refers to general world knowledge that
+% we have accumulated throughout our lives.[2] This general knowledge
+% (facts, ideas, meaning and concepts) is intertwined in experience and
+% dependent on culture. Semantic memory is distinct from episodic
+% memory, which is our memory of experiences and specific events that
+% occur during our lives, from which we can recreate at any given
+% point.[3] For instance, semantic memory might contain information
+% about what a cat is, whereas episodic memory might contain a specific
+% memory of petting a particular cat. We can learn about new concepts by
+% applying our knowledge learned from things in the past.[4] The
+% counterpart to declarative, or explicit memory, is procedural memory,
+% or implicit memory.[5]
+% \end{quote}
 
@@
 \begin{enumerate}
-\item A user registers many question texts based on the user's personal
+\item A user registers many question texts related to the user's personal
 secret episodic memories that the user never forgets,
-and provide a correct answer and many fake answers.
+and provide a correct answer and fake answers.
 
@@
 
-\item EpisoPass shows the registered data to the user so that
+\item EpisoPass shows the data to the user so that
 the user can select an answer for each question.
 Based on the user's selection,
-EpisoPass substitute characters in the seed string and generate different
-strings for different selections.
-The user copies the string calculated when correct answers are selected,
-and use it as the password for the service.
+EpisoPass substitutes characters in the seed string and generate
+random-looking password candidate strings.
+After selecting all right answers,
+the user copies the calculated string
+and register it as the password for the service.
 \end{enumerate}
@@
 When a user clicks and selects one of the answers for each question,
-the seed string is converted to a random-looking string
+the seed string shown at the top-left is converted to a random-looking string
 based on the selections.
@@
 
-\begin{figure}[H]
+\begin{figure}[t]
 \includegraphics[width=110mm,bb=-30 0 803 662]{figures/c1bd6e7f67698c70978f528ccd2339d9.png}
@@
 and according to the selections to the four questions,
-the seed string is converted to a string like
+the seed string is converted to a string
 ``\textsf{Lbasnln542202}'',
@@
 the seed string is converted to another trings like
-``\textsf{Bhtuyna904127}''.
+``\textsf{Bhtuyna904127}'' (Figure \ref{web11}).
 
@@
 \includegraphics[width=110mm,bb=-30 0 803 660]{figures/01e5507d090eb494a20bcbc47c86b1d2.png}
-\caption{Generating a Twitter password with EpisoPass.}
+\caption{Selecting a different answer.}
 \label{web11}
@@
 the password string generated after selecting correct answers can be
-used as the password for the service. (Twitter in this case.)
-
-Capital letters in the seed strings are substituted to capital letters in the password,
+used as the password for the service.
+
+Capital letters in the seed string are substituted to capital letters in the password,
 and digits in the seed string are substituted to digits,
-so that the generated passwords conforms to password character restrictions
+so that generated passwords conforms to password character restrictions
 sometimes required by the service.
@@
 
-The first secret question in Figure \ref{web1}
+The second question in Figure \ref{web1}
 is based on the author's episodic memory at elementary scholl,
@@
 
-Questions and answers can be edited directly on a browser, and they can be
-saved on the server by clicking the ``save on server'' button.
+Questions and answers can be edited directly on the browser, and they can be
+saved on the server by clicking the ``save to server'' button.
 The Q-A data sets are saved on the server,
@@
 When we change the secret string to ``\textsf{Facebook123456}'',
-the generated password changes to ``\textsf{Xxxxxxx123456}'',
+the generated password changes to ``\textsf{Zxghfbqu533131}'',
 as shown in Figure \ref{web2}.
@@
 \begin{figure}[H]
-\centerline{\includegraphics[width=83mm,bb=0 0 718 265]{../figures/36c371a13a8250c60fb9c03174382443.png}}
+\includegraphics[width=110mm,bb=-30 0 800 285]{figures/0e2820c279afc70520482e0fc53b6ed9.png}
 \caption{Generating the password for FaceBook.}
@@
 Character substitution is performed based on the hash value
-calculated from putting all the selected answers.
-For example, if the user selects ``answer1-3'' to the question ``question1'',
-a hash value calculated from  ``\texttt{question1:answer1-3}''
+calculated from concatinating all the selected answers.
+For example, if the user selects ``\texttt{Ebisawa}'' to the question ``\texttt{Who's the bully?}'',
+a hash value calculated from  ``\texttt{Who's the bully:Ebisawa}''
 is used for the substitution.
-Details of the algorithm is showin in Appedix.
+Details of the algorithm is showin in the Appedix.
 
@@
 
-If a user doesn't like to use EpisoPass service on the browser,
+If a user doesn't like to use EpisoPass service on the Net,
 he can use an EpisoPass application on Android
-which does not use any network connection.
+which does not require network connection.
 After registering questions and answers on the EpisoPass service,
 the user can download an Android application from the server
-which contain all the information required for generating passwords.
+by clicking the ``Android app'' button.
+The application contains all the information required for generating passwords.
 (The application is compiled and built on the server.)
@@
 to each question, he can eventually get the password and copy it to the password entry.
-(Figure \ref{android1})
+(Figure \ref{android1},\ref{android2})
 
@@
 \includegraphics[width=80mm,bb=-30 0 400 106]{figures/ba8f5aeaa935ad63437969f4d746746b.png}
-\caption{Running EpisoPass on Android.}
+\caption{After finishing selections.}
 \label{android2}
@@
 
-The calculation is performed on Android without network connection,
-and the user can safely use ...
-without feeling the fear of ...
+% The calculation is performed on Android without network connection,
+% and the user can safely generate passwords 
+% without feeling the fear of ...
 
@@
 %
-Users of EpisoPass can save the seed string and question-answers
-at any place, and easily generate passwords by answering questions.
+Users of EpisoPass can save the seed string and question-answer data
+at any place, and easily generate passwords by running
+EpisoPass and answering questions.
 If the question is based on old unforgettable episodic memories,
@@
 If the user's memory is related to an episode of 20 years ago and the user clearly
-remembers it now, it is unlikely that he forgets the episode 10 years later.
+remembers the episode now, it is unlikely that he forgets the episode 10 years later.
+
+\subsection{Security strength of EpisoPass}
+
+The strength of the generated password depends on the number of
+questions and the secretness of the questions.
+%
+There have been many studies on the strength of passwords
+\cite{Hayashi:2011:DSP:1978942.1979326}%
+\cite{Komanduri:2011:PPM:1978942.1979321}, % どういうパスワードが強いか
+but the strength of secret questions has not been studied enough.
+%
+% {\EP}で選択枝が10個の{\SQ}を8個使用する場合、
+% 総当たりで{\PW}を生成するには
+% 1億($10^8$)通りの試行が必要であり、
+% % エントロピーは26.6 ($ = 8 \times \log_2 10$) ビット
+% エントロピーは26.6ビットとなる。
+%
+When we use 10 secret questions with 20 answers and
+there's no clue for the answer,
+1 billion ($20^8$) trials should be performed to check
+all the combinations of the answers,
+and the entropy of the system is 43.2 ($10 \times \log_2 20$) bits.  % 10.0 * (Math.log(20.0)/Math.log(2.0))
+%
+% 英字からランダムに8文字を並べて作成した{\PW}のエントロピーは37.6ビットになるが、
+% ``\textsf{pmvixuzq}''のように全く意味のない{\PW}を記憶して利用することは少ないため、
+% 実際に利用される{\PW}のエントロピーは20ビット程度と考えられているので\cite{NIST}、
+% {\SQ}と選択枝の数を10個程度用意すれば
+% 通常の{\PW}と同程度の強度が期待できることになる。
+%
+It is almost the same entropy as using random 8-character English alphabets
+as a password, in which case the entropy is 45.6 bits.
+This level is considered to be strong enough for Web services,
+where online blute-force attack is impossible\cite{Florencio:2007:SWP:1361419.1361429}.
 
@@
 
-The strength of the generated password depends on the number of
-questions and the 'secretness' of the questions.
+The quality of secret questions is the key to using EpisoPass.
 If the episodic memory is shared by someone else,
-that personn can easily answer the question and generate the
+that person can easily answer the question and generate the
 password just like the user.
-
-The quality of secret questions is the key to using EpisoPass.
+%
 The episode related to each question should not be known to other people,
@@
 %
-Old experienceslike the following are good candidates for
-questions used in EpisoPass.
+Old experiences like the following are candidates for
+good questions used in EpisoPass.
 
@@
 
-\item Experience of finding a small special item.
+\item Experience of finding a small special item which only you are interested in.
 \end{itemize}
@@
 
-Questions like "Which one is your favorite?" should be avoided,
+Questions like ``Which one do you like best?'' should be avoided,
 since some of the friends might know the user's taste.
@@
 
-We usually don't tell our bad experiences to other people,
+We usually don't tell our bad trivial experiences to other people,
 but we might boast of good experiences or even write a blog about it.
@@
 
-It is sometimes difficult to provid fake answers to a secret question like
+It is difficult to provide enough number of fake answers to a question like
 ``what was your favorite sport?''
 because possible answers are limited.
-
+%
 % \begin{figure}[H]
@@
 % \end{figure}
-
+%
 % 一方、正答として人名や地名を利用する場合、
@@
 % 「目黒」「杉並」のような偽答を用意するのは簡単である。
-
+%
 On the other hand, if the right answer to the question is a name of a place or a person,
@@
 % Webのデータを利用した様々な同位語検索システムが提案されている%
-For information retrieval purposes,
-various methods have been proposed for collecting words in the
-same category.
+Various methods have been proposed for collecting words in the
+same category, mainly for information retrieval purposes
 \cite{Huang:2012:LFC:2426725.2426728}% 読んでないけど
@@
 \cite{大島裕明:2006-12-15}.% ライバルサーチ「やーやら」
-We can use such systems for getting similar names.
-
-\subsection{Usable for everyone}
+We can use such techniques for getting similar names.
+
+\subsection{Universality}
 
@@
 Even experienced computer users have trouble with passwords,
-since choosing a good password is difficult and people forget passwords frequently.
-Using EpisoPass, people who cannot create and remember strong passwords
-can easily generate strong passwords just by providing secret episodic
-questions and answers.
+since choosing a good password is not intuitive and
+people forget passwords frequently.
+%
+Using EpisoPass, people can use password-based systems without knowing
+techniques for creating and remembering strong passwords.
+They only have to provide
+questions and answers based on secret episodic memories.
+%
 By integrating EpisoPass into existing password-based services,
@@
 
-\subsection{Easy to change passwords}
+\subsection{Periodic password update}
 
@@
 to strenghen security.
-A user can generate a new strong password by using a randam character generator
-on a password manager, but he might want to old passwords in case some trouble happens.
-Using EpisoPass, user can just provide a date-related question-answer pairs,
+%
+% A user can generate a new strong password by using a randam character generator
+% on a password manager, but he might want to old passwords in case some trouble happens.
+%
+Using EpisoPass, users can just provide a date-related question
+like the first question showin in Figure \ref{web1},
 and generate different strong passwords based on the answer.
-
-(Figure xxx) 最初の例に入れておく
-
-\subsection{Security strength of EpisoPass}
-
-There have been many studies on the strength of passwords
-\cite{Hayashi:2011:DSP:1978942.1979326}%
-\cite{Komanduri:2011:PPM:1978942.1979321}, % どういうパスワードが強いか
-but the strength of secret questions has not been studied enough.
-%
-% {\EP}で選択枝が10個の{\SQ}を8個使用する場合、
-% 総当たりで{\PW}を生成するには
-% 1億($10^8$)通りの試行が必要であり、
-% % エントロピーは26.6 ($ = 8 \times \log_2 10$) ビット
-% エントロピーは26.6ビットとなる。
-%
-When we use 10 secret questions with 20 answers,
-1 billion ($20^8$) trials should be performed to check
-all the combinations of the answers,
-and the entropy of the system is 43.2 ($10 \times \log_2 20$) bits.  % 10.0 * (Math.log(20.0)/Math.log(2.0))
-%
-% 英字からランダムに8文字を並べて作成した{\PW}のエントロピーは37.6ビットになるが、
-% ``\textsf{pmvixuzq}''のように全く意味のない{\PW}を記憶して利用することは少ないため、
-% 実際に利用される{\PW}のエントロピーは20ビット程度と考えられているので\cite{NIST}、
-% {\SQ}と選択枝の数を10個程度用意すれば
-% 通常の{\PW}と同程度の強度が期待できることになる。
-%
-It is almost the same entropy as using random 8-character English alphabets
-as a password, in which case the entropy is 45.6 bits.
-This level is considered to be strong enough for using Web services,
-where online blute-force attack is impossible\cite{Florencio:2007:SWP:1361419.1361429}.
-
-\subsection{Comparison with challenge-response authentication systems}
+Using this technique, people can easily manage old and new passwords.
+
+\subsection{Comparison with challenge-response authentication}
 
@@
 
-In many services, users are forced to define answers to secret questions like
+In many services, users are adviced to define answers to secret questions like
 ``what is your mother's maiden name''
-so that he can log in to the service even when he forgets the password.
+so that he can log into the service even when he forgets the password.
 This kind of authentication is far less secure than simple password systems,
-since it is fairly easy for atackers to get the right answer.
+since it is fairly easy for attackers to get to the right answer.
 The variation of system-provided questions are usually small, and
-such challenge-response systems are considered to be insecure\cite{Rabkin:2008:PKQ:1408664.1408667}.
+such challenge-response systems are considered to be
+insecure\cite{Rabkin:2008:PKQ:1408664.1408667}.
 
@@
     If the hash value $M$ is $12345678...$,
-    $f_0x1234$ is used as the substitution function for the first character,
-    $f_0x5678$ is used as the substitution function for the secound character, etc.
+    $f_{\texttt{\scriptsize 0x1234}}$ is used as the substitution function for the first character,
+    $f_{\texttt{\scriptsize 0x5678}}$ is used as the substitution function for the secound character, etc.
 \end{enumerate}

### 2016-04-13 paper/UIST2016/paper.tex
スタイル変更、スペルチェック

@@
 %
-\documentclass{article}
-
-\usepackage{times}
-\usepackage{uist}
-\usepackage{graphicx}
+% \documentclass{article}
+\documentclass{sigchi}
+
+\usepackage{balance}  % to better equalize the last page
+\usepackage{graphics} % for EPS, load graphicx instead
+\usepackage{times}    % comment if you want LaTeX's default font
+\usepackage{url}      % llt: nicely formatted URLs
+
+% \usepackage{times}
+% \usepackage{uist}
+% \usepackage{graphicx}
+
 \usepackage{here} % [H]とするとその場所に配置されるらしい
+
+% llt: Define a global style for URLs, rather that the default one
+\makeatletter
+\def\url@leostyle{%
+  \@ifundefined{selectfont}{\def\UrlFont{\sf}}{\def\UrlFont{\small\bf\ttfamily}}}
+\makeatother
+\urlstyle{leo}
+
+% To make various LaTeX processors do the right thing with page size.
+\def\pprw{8.5in}
+\def\pprh{11in}
+\special{papersize=\pprw,\pprh}
+\setlength{\paperwidth}{\pprw}
+\setlength{\paperheight}{\pprh}
+\setlength{\pdfpagewidth}{\pprw}
+\setlength{\pdfpageheight}{\pprh}
+
+% Make sure hyperref comes last of your loaded packages, 
+% to give it a fighting chance of not being over-written, 
+% since its job is to redefine many LaTeX commands.
+\usepackage[pdftex]{hyperref}
+\hypersetup{
+pdftitle={SIGCHI Conference Proceedings Format},
+pdfauthor={LaTeX},
+pdfkeywords={SIGCHI, proceedings, archival format},
+bookmarksnumbered,
+pdfstartview={FitH},
+colorlinks,
+citecolor=black,
+filecolor=black,
+linkcolor=black,
+urlcolor=black,
+breaklinks=true,
+}
+
+% create a shortcut to typeset table headings
+\newcommand\tabhead[1]{\small\textbf{#1}}
+
+\begin{document}
 
@@
 
-\begin{document}
-
 % Copyright notice ---
@@
 
+\numberofauthors{3}
 \author{
-\parbox[t]{9cm}{\centering
-	     {\em Author Name removed for blind review}\\
-	     Affiliation removed for blind review\\
-	     Address removed for blind review\\
-	     Email removed for blind review}
-\parbox[t]{9cm}{\centering
-	     {\em Author Name removed for blind review}\\
-	     Affiliation removed for blind review\\
-	     Address removed for blind review\\
-	     Email removed for blind review}
+  \alignauthor 1st Author Name\\
+    \affaddr{Affiliation}\\
+    \affaddr{Address}\\
+    \email{e-mail address}\\
+    \affaddr{Optional phone number}
+  \alignauthor 2nd Author Name\\
+    \affaddr{Affiliation}\\
+    \affaddr{Address}\\
+    \email{e-mail address}\\
+    \affaddr{Optional phone number}    
+  \alignauthor 3rd Author Name\\
+    \affaddr{Affiliation}\\
+    \affaddr{Address}\\
+    \email{e-mail address}\\
+    \affaddr{Optional phone number}
 }
@@
 
-\abstract
+\begin{abstract}
 % 忘れることがない{\EM}にもとづく{\SQ}を使って強力な{\PW}を生成/管理するシステム「\textsf{\EP}」を提案する。
@@
 %
-
-\classification{H5.2 [Information interfaces and presentation]:
-User Interfaces. - Graphical user interfaces.}
-
-\terms{Design, Human Factors}
-
-\keywords{Passwords, authentication}
+\end{abstract}
+
+\keywords{
+  Passwords; password managers; episodic memories; EpisoPass;
+%	keywords should be separated by a semi-colon. \newline
+%	\textcolor{red}{Optional section to be included in your final version, 
+%  but strongly encouraged.}
+}
+
+\category{H.5.2.}{Information Interfaces and Presentation (e.g. HCI)}{User Interfaces}
+\category{K.6.5.}{Management of Computing and Information Systems}{Security and Protection}
 
@@
 For example,
-image-based authentication\cite{Biddle:2012:GPL:2333112.2333114}\cite{小池英樹:2006-05-15}\cite{GraphicalPasswords}, 
-bio-based methods\cite{},
-behavior-based methods\cite{},
+image-based authentication\cite{Biddle:2012:GPL:2333112.2333114}\cite{GraphicalPasswords}, 
+biometrics authentication\footnote{
+  % \textsf{https:{\slash}{\slash}en.wikipedia.org{\slash}wiki{\slash}Biometrics}
+  \url{https://en.wikipedia.org/wiki/Biometrics}
+},
+behavior-based authentication\cite{Dandapat:2015:AYD:2702123.2702457}, 
 and many other authentication methods have been proposed.
@@
 passwords on various services.
-Althought password managers are useful,
+Although password managers are useful,
 users are usually forced to remember a ``master password''
@@
 \begin{figure}[t]
-\includegraphics[width=110mm,bb=-30 0 803 662]{figures/c1bd6e7f67698c70978f528ccd2339d9.png}
+\centering
+\includegraphics[width=1.0\columnwidth]{figures/c1bd6e7f67698c70978f528ccd2339d9}
 \caption{Generating a Twitter password with EpisoPass.}
@@
 When the user clicks another candidate,
-the seed string is converted to another trings like
+the seed string is converted to another strings like
 ``\textsf{Bhtuyna904127}'' (Figure \ref{web11}).
@@
 \begin{figure}[H]
-\includegraphics[width=110mm,bb=-30 0 803 660]{figures/01e5507d090eb494a20bcbc47c86b1d2.png}
+\centering
+\includegraphics[width=1.0\columnwidth]{figures/01e5507d090eb494a20bcbc47c86b1d2}
 \caption{Selecting a different answer.}
-\label{web11}
+\label{web1}
 \end{figure}
@@
 The second question in Figure \ref{web1}
-is based on the author's episodic memory at elementary scholl,
+is based on the author's episodic memory at elementary school,
 and the last secret question is related to a more recent event
@@
 \begin{figure}[H]
-\includegraphics[width=110mm,bb=-30 0 800 285]{figures/0e2820c279afc70520482e0fc53b6ed9.png}
+\centering
+\includegraphics[width=1.0\columnwidth]{figures/0e2820c279afc70520482e0fc53b6ed9}
 \caption{Generating the password for FaceBook.}
@@
 is used for the substitution.
-Details of the algorithm is showin in the Appedix.
+Details of the algorithm is shown in the Appendix.
 
@@
 \begin{figure}[H]
-\includegraphics[width=80mm,bb=-30 0 399 386]{figures/429eec261024dc6c85351f51c12f09b4.png}
+\centering
+\includegraphics[width=0.7\columnwidth]{figures/429eec261024dc6c85351f51c12f09b4}
 \caption{Running EpisoPass on Android.}
@@
 \begin{figure}[H]
-\includegraphics[width=80mm,bb=-30 0 400 106]{figures/ba8f5aeaa935ad63437969f4d746746b.png}
+\centering
+\includegraphics[width=0.7\columnwidth]{figures/ba8f5aeaa935ad63437969f4d746746b}
 \caption{After finishing selections.}
@@
 The strength of the generated password depends on the number of
-questions and the secretness of the questions.
+questions and the secret level of the questions.
 %
@@
 This level is considered to be strong enough for Web services,
-where online blute-force attack is impossible\cite{Florencio:2007:SWP:1361419.1361429}.
+where online brute-force attack is impossible\cite{Florencio:2007:SWP:1361419.1361429}.
 
@@
 Questions related to a episode which the user is proud of should also be
-avoided, since the user might talk aboutu the episode to somebody else.
+avoided, since the user might talk about the episode to somebody else.
 
@@
 \cite{BooWa}% Boo!Wa!というサイトをやっている
-\cite{Wang:2007:LSE:1441428.1442086}% BooWa
-\cite{大島裕明:2006-12-15}.% ライバルサーチ「やーやら」
+\cite{Wang:2007:LSE:1441428.1442086}.% BooWa
+%\cite{大島裕明:2006-12-15}.% ライバルサーチ「やーやら」
 We can use such techniques for getting similar names.
@@
 On many services, users are requested to change passwords periodically
-to strenghen security.
+to strengthen security.
 %
@@
 Using EpisoPass, users can just provide a date-related question
-like the first question showin in Figure \ref{web1},
+like the first question shown in Figure \ref{web1},
 and generate different strong passwords based on the answer.
@@
 Also, in this case,
-the user should register the answer to the system in additon to the question.
+the user should register the answer to the system in addition to the question.
 Telling secret facts to service providers is like
@@
 
-{\EP}では、
-他人には解くことが難しく自分では忘れないような{\SQ}を自由にいくつでも利用できるようになっている。
-問題作成に慣れていないユーザには有効な{\SQ}を作成することは難しいかもしれないが、
-次節で述べるように、適切な質問を選ぶことによりこの問題を解決できるはずである。
-
-\subsection{All information can be put public}
-
-Questions and answers can be put on a public place
+% {\EP}では、
+% 他人には解くことが難しく自分では忘れないような{\SQ}を自由にいくつでも利用できるようになっている。
+% 問題作成に慣れていないユーザには有効な{\SQ}を作成することは難しいかもしれないが、
+% 次節で述べるように、適切な質問を選ぶことによりこの問題を解決できるはずである。
+
+\subsection{Care for handling secret information}
+
+Users don't have to be very careful about handling questions and answers.
+They can even be put on a public place
 if enough amount of questions and fake answers are provided.
 %
-Keeping the secret of something is always a pain for many people including
+Keeping secret is always a pain for many people including
 the authors, but if the whole questions and answers used on EpisoPass
@@
 secret information like passwords, secret key for SSH, etc.
-so that they are not copied or saved to unsafe places.
+because they should not be copied or saved at unsafe places.
 On the other hand,
@@
 passwords without having the owner's episodic memories.
-
-%   全情報を公開して大丈夫
-%     マスターパスワードが要らない
 
@@
 
-The algorithm of generating a password (Appendix)
+The algorithm of generating a password (shown in Appendix)
 is fairly simple and
@@
 
-\subsection{{\PW}漏洩時の問題}
+\subsection{Risk of password leak at the service side}
 
 If, one of the passwords generated by EpisoPass is revealed
-for some reason,... フルートフォースでとかれる可能性はある
-
-To prevent such troble, it is safer to keep all the q-a pairs secret.
-
-問題を時々変えるのが安全だろう
-
-問題自体が秘密であればひとつ漏れても大丈夫
-
-{\SQ}を公開している場合、
-{\SS}と{\PW}の対応がひとつでも漏洩してしまうと、
-総当たり計算でチェックすることにより、
-すべて{\SQ}の正答が判明してしまう。
-{\SQ}の正答を知っていれば
-{\SS}から{\PW}を計算することができるので、
-漏洩した{\SQ}は利用不可能になってしまう。
-%
-\ref{pattern1}や
-\ref{pattern2}のような運用をしている場合は
-{\PW}がひとつ漏洩しても他の{\PW}は安全だが、
-\ref{pattern3}のような運用をしている場合は
-ひとつでも{\PW}が漏洩するとあらゆる{\PW}が漏洩してしまうことになる。
+for some reason, other passwords based on the same questions
+might also be revealed.
+%
+For example, if Twitter is attacked by a cracker and
+the password for Twitter (``\textsf{Lbasnln542202}'' in Figure \ref{web1})
+is revealed to the attacker,
+the attacker can try all the answer combinations and find out
+the answers to all the questions,
+if questions and answers are also known by the attacker.
+Once all the answers to the questions are known,
+the attacker can freely generate all the passwords
+generated by EpisoPass.
+
+To prevent such troble, it is safer to keep all the questions and answers
+in a secret place or
+use many number of questions so that brute-force does not work.
+
+% 問題自体が秘密であればひとつ漏れても大丈夫
+% 
+% {\SQ}を公開している場合、
+% {\SS}と{\PW}の対応がひとつでも漏洩してしまうと、
+% 総当たり計算でチェックすることにより、
+% すべて{\SQ}の正答が判明してしまう。
+% {\SQ}の正答を知っていれば
+% {\SS}から{\PW}を計算することができるので、
+% 漏洩した{\SQ}は利用不可能になってしまう。
+%
+% \ref{pattern1}や
+% \ref{pattern2}のような運用をしている場合は
+% {\PW}がひとつ漏洩しても他の{\PW}は安全だが、
+% \ref{pattern3}のような運用をしている場合は
+% ひとつでも{\PW}が漏洩するとあらゆる{\PW}が漏洩してしまうことになる。
 
 \subsection{Using images}
-%   画像を使える
-
-Old pictures can be used as the questions of EpisoPass.
+
+Old pictures can be used as the questions of EpisoPass,
+just like the 5th question shown in Figure \ref{web1}.
 Even when people cannot create good secret questions,
@@
 and use it as the question.
-For example, if you have a n old picture of your friend,
+For example, if you have an old picture of your friend,
 you can use it as the question
@@
 
-例をここでいろいろ出す
-
 % 画像検索とかされないようにする必要はある
@@
 Of course, the photo should not have information related to the
-person's real name, since image search is fiarly easy on the Web these days.
-
-忘れにくい{\EM}を利用する認証手法として
-様々な画像認証システム\cite{Biddle:2012:GPL:2333112.2333114}\cite{GraphicalPasswords}\cite{小池英樹:2006-05-15}が提案されている。
-複数の画像の中から正答を選択するもの(Cognometric方式)、
-ひとつの画像の中の特定の場所を指定するもの(Locimetric方式)、
-画像の上で描画操作を行なうもの(Drawmetric方式)
-が広く利用されているが\cite{Biddle:2012:GPL:2333112.2333114}\cite{GraphicalPasswords}\cite{Guideline}、
-{\EP}は図\ref{web1}のように
-文字列のかわりに画像URLを{\SQ}として利用する点が異なっている。
-%
-Cognometric方式は{\EM}を効果的に利用できるが、
-多数の偽答画像が必要だという問題がある。
-Locimetric方式は
-{\EM}を効果的に利用できないことに加え、
-クリックしやすい「ホットスポット」は限られているため
-充分なエントロピーを確保できないことが問題になる\cite{Dirik:2007:MUC:1280680.1280684}。
-またDrawmetric方式も{\EM}を効果的に利用できないし、
-ユーザは似た傾向のストロークを選びがちであるため
-充分なエントロピーを確保しにくいことが知られている\cite{Nali}。
-%
-{\EP}のように画像を{\SQ}として利用する場合、
-通常の{\SQ}の場合と同様に偽答を増やすことが容易であることに加え、
-画像に関連した{\EM}を有効に利用できるという利点がある\cite{増井:CSS}。
-
-図\ref{leiko}は
-本棚.org\cite{hondana}\cite{hondanaorg}
-のユーザのひとり\footnote{
-  \textsf{http://hondana.org/Leiko}
-}が利用している画像認証問題である。
-このユーザ以外には正答は見当もつかないが、
-本人にとっては忘れることがない{\EM}と結びついた画像だということであった。
+person's real name, since image search is fairly easy on the Web these days.
+
+% 忘れにくい{\EM}を利用する認証手法として
+% 様々な画像認証システム\cite{Biddle:2012:GPL:2333112.2333114}\cite{GraphicalPasswords}\cite{小池英樹:2006-05-15}が提案されている。
+% 複数の画像の中から正答を選択するもの(Cognometric方式)、
+% ひとつの画像の中の特定の場所を指定するもの(Locimetric方式)、
+% 画像の上で描画操作を行なうもの(Drawmetric方式)
+% が広く利用されているが\cite{Biddle:2012:GPL:2333112.2333114}\cite{GraphicalPasswords}\cite{Guideline}、
+% {\EP}は図\ref{web1}のように
+% 文字列のかわりに画像URLを{\SQ}として利用する点が異なっている。
+% %
+% Cognometric方式は{\EM}を効果的に利用できるが、
+% 多数の偽答画像が必要だという問題がある。
+% Locimetric方式は
+% {\EM}を効果的に利用できないことに加え、
+% クリックしやすい「ホットスポット」は限られているため
+% 充分なエントロピーを確保できないことが問題になる\cite{Dirik:2007:MUC:1280680.1280684}。
+% またDrawmetric方式も{\EM}を効果的に利用できないし、
+% ユーザは似た傾向のストロークを選びがちであるため
+% 充分なエントロピーを確保しにくいことが知られている\cite{Nali}。
+% %
+% {\EP}のように画像を{\SQ}として利用する場合、
+% 通常の{\SQ}の場合と同様に偽答を増やすことが容易であることに加え、
+% 画像に関連した{\EM}を有効に利用できるという利点がある\cite{増井:CSS}。
+
+% 図\ref{leiko}は
+% 本棚.org\cite{hondana}\cite{hondanaorg}
+% のユーザのひとり\footnote{
+%   \textsf{http://hondana.org/Leiko}
+% }が利用している画像認証問題である。
+% このユーザ以外には正答は見当もつかないが、
+% 本人にとっては忘れることがない{\EM}と結びついた画像だということであった。
 
@@
 
-\section{Related Work}
-
-認証手法は本当に沢山あり、パスワードを置き換えようとするものも多いが
-まだ成功はしていない
-
-パスワード管理システムは充分広く使われている
-
-% A Password Manager that Doesn’t Remember
-\cite{Stobert:2014:PMD:2683467.2683471} % Visipass 画像のヒントからパスワード生成
+\section{RELATED WORK}
+
+As shown in previous sections,
+there are many attemps for replacing password-based authentication systems,
+none of which has succeeded so far.
+
+Various types of image-based authentication systems have been proposed recently,
+in the hope that images are easier to remember than text
+because images are usually more directly linked to episodic memories.
+However, on many systems,
+users have to remember new information related to the images
+used in the authentication process, or
+perform special operation on the image, and
+it is not much easier than using passwords.
+%
+Image-based authentication based on episodic memories might work
+if anyone can prepare many images 
+which are tightly linked to his episodic memories.
+However, finding such images is usually not easy, and
+image-only authentication systems would not take off
+unless simple and effective technique is invented.
+% [Malasym]
+
+Even when a new ideal authentication method is invented,
+replacing all the password-based systems should take very long, and
+various password managers should be used until the ideal method
+prevails in the whole world.
+In the age of password-based authentication,
+using password managers seems to be the only way to tackle
+the problem of passwords.
+%
+While most of the password manager only remember passwords given by the user,
+generating passwords with a password manager is a new approach for
+handling password-based systems.
+Just like EpisoPass generates passwords,
+Versipass\cite{Stobert:2014:PMD:2683467.2683471}% Versipass 画像のヒントからパスワード生成 % A Password Manager that Doesn’t Remember
+helps the user to generate password strings
+using ``visual cues'' on an arbitrary image.
+Instead of directly using images for authentication,
+users use the system to generate a password text with the help of
+the image shown to the user.
 
@@
 
-\section{Experiences}
-% ■ 運用実績
-
-% 強度が直感的でない
-%   誰でも簡単にとけるのじゃないかと思う
-%   safe感覚が足りない
+\section{EXPERIENCES}
+
+EpisoPass has been used by the authors for more than three years, and
+the authors are using it for various services including
+Twitter, Facebook, Amazon, Skype, etc.
+Since passwords for these services are remembered on the browser,
+EpisoPass is used only once in one week at most.
+%
+Before using EpisoPass, taking care of many passwords was really
+a problem for the authors, but
+currently all the information for generating passswords is put on the Net
+and no trouble has been found during the period.
+
+Unfortunately EpisoPass is currently not used by many people.
+One big reason is that most people cannot fully understand the
+idea of EpisoPass and also cannot fully trust it
+because it is not operated by a big IT company nor supported by
+famous computer users.
+Another reason might be that users cannot estimate the strength
+of EpisoPass.
+Since all the questions and answers are
+quite obvious to the users,
+they might feel that everyone else also know the episode
+and easily solve all the questions.
+These kinds of psychological issues are quite important for
+an authentication system for everybody,
+and we hope to remove such obstacles in the future.
 
@@
 
-We have developed a
+We introduced a password management system EpisoPass
+that converts a seed string into a password using the user's
+episodic memories represented as a set of questions and answers
+which can be solved only by the user.
+%
+Using EpisoPass with well-defined questions and answers,
+a user can always retrieve various passwords without worrying about
+remembering secret information.
+%
+We'll try to integrate the system with existing password-based
+services, and finally hope to remove all the problems
+derived from password-based authentication.
 
@@
 based on the user's selections of candidate answers.
-Character substitution is performed based on the chracter types.
+Character substitution is performed based on the character types.
 For example, if the first character of the seed string is a digit,
@@
 If the value of $N$ if $5$, $f_5(x) = (15-x) \bmod 10$, and
-$x$と$f_5(x)$の対応は以下のようになる。
+the $f_5(x)$ value for each $x$ is calculated like below:
 
@@
   % \item 問題文字列と選択した答の文字列の組を連結して長い文字列$S$を生成
-  \item Generate a string $S$ by concatinating all the question strings and selected candidate answers.
+  \item Generate a string $S$ by concatenating all the question strings and selected candidate answers.
 
@@
   %  それを$N$とする
-  \item For each $k$th chracter of {\SS},
+  \item For each $k$-th character of {\SS},
     get the 4-character substring of $M$ beginning at $k \times 4$, and use it as the value of $N$
@@
     $f_{\texttt{\scriptsize 0x1234}}$ is used as the substitution function for the first character,
-    $f_{\texttt{\scriptsize 0x5678}}$ is used as the substitution function for the secound character, etc.
+    $f_{\texttt{\scriptsize 0x5678}}$ is used as the substitution function for the second character, etc.
 \end{enumerate}
@@
 
-* クイズにできるエピソードがない人はどうすればいいんでしょう
-
-=> そういう話はよく聞くのですがエピソードが無い人なんているのでしょうかね?
-小学校のときちょっとしたケガ体験とかエピソードとか覚えてませんか?
-
-* URLがseed込みなので、ブックマークつくっておけば辿りつける、という主張だったかと
-
-=> これは誤解です。URLは計算には関係ありません。
-
 * Q:(1)seedはどうやって作るのか？(2)質問はどうやって作るのか？

### 2016-04-13 paper/UIST2016/paper.tex
...

@@
 a user first collects question-answer pairs related to his episodic memory
-and registers them with many fake answers.
+and registers them with fake answers.
 %
@@
 calculated from concatinating all the selected answers.
-For example, if the user selects ``\texttt{Ebisawa}'' to the question ``\texttt{Who's the bully?}'',
-a hash value calculated from  ``\texttt{Who's the bully:Ebisawa}''
+For example, if the user selects ``\textbf{\texttt{Ebisawa}}'' to the question ``\textbf{\texttt{Who's the bully?}}'',
+a hash value calculated from  ``\textbf{\texttt{Who's the bully:Ebisawa}}''
 is used for the substitution.
@@
 
-\subsection{Simple implementation}
-%   実装が簡単
+\subsection{Simplicity}
 
@@
     If the hash value $M$ is $12345678...$,
-    $f_{\texttt{\scriptsize 0x1234}}$ is used as the substitution function for the first character,
-    $f_{\texttt{\scriptsize 0x5678}}$ is used as the substitution function for the second character, etc.
+    $f_{\textbf{\texttt{\scriptsize 0x1234}}}$ is used as the substitution function for the first character,
+    $f_{\textbf{\texttt{\scriptsize 0x5678}}}$ is used as the substitution function for the second character, etc.
 \end{enumerate}

### 2016-04-13 paper/UIST2016/paper.tex
...

@@
 %
-When a user wants to generate a password,
+When the user wants to generate a password,
 EpisoPass shows the questions and lists of possible answers and asks
@@
 Then EpisoPass generates a password by substituting characters of the
-seed string based on the answer selections.
-%
-If only the user knows the correct answer,
+seed string based on the selected answers.
+%
+If the user is the only person who knows the correct answer,
 % If the right answers to the questions are known only to the user,
@@
 %
-Since short passwords are easily guessed by attackers, and
+Since short passwords are easily guessed by attackers and
 using the same password for different services is unsafe,
@@
 However,
-remembering many long passwords is almost impossible for ordinary people.
+remembering many long passwords is almost impossible for ordinary humans.
 %
@@
 
-In spite of such attempts,
+However,
 password-based authentication is still the most
@@
 various ``password managers'' have been proposed
-for handling many strong passwords.
-%
-%{\PW}管理システムは
-%ひとつの「マスター{\PW}」を利用して他のすべての{\PW}を管理するもので、
-%暗号化されたデータベースに{\PW}を格納するもの%
-%
-Most password managers remembers various passwords and
-asks users to remember a single ``master password'' to access the database
 \cite{OnePassword}%
@@
 %
+Password managers remember users' passwords and help them enter
+passwords on various services.
+%
+%{\PW}管理システムは
+%ひとつの「マスター{\PW}」を利用して他のすべての{\PW}を管理するもので、
+%暗号化されたデータベースに{\PW}を格納するもの%
+%
+Most password managers can manage various passwords by
+asking users to remember a single ``master password'' to access the database.
+%
 %が多いが、サービス名をもとにマスター{\PW}を変換することによって
@@
 %
-Password managers remember users' passwords and help them enter
-passwords on various services.
 Although password managers are useful,
-users are usually forced to remember a ``master password''
-or a special hardware device
+users have to remember the master password
+or use a special hardware device
 for safely handle password managers, and
@@
 %
-Memories in human brain is not uniform.
+Memories in human brain are not uniform.
 Some memories are very short-lived, and others are unforgettable.
@@
 The former type of memory is called the episodic memory and
-people cannot easily forget it.
+people cannot easily lose it.
 Memories of passwords belong to the latter type and
@@
 
-Password generation on EpisoPass is performed through the following procedures:
+Password generation on EpisoPass is performed through the following steps:
 
@@
 secret episodic memories that the user never forgets,
-and provide a correct answer and fake answers.
+and provides a correct answer and additional fake answers.
 
@@
 \item EpisoPass shows the data to the user so that
-the user can select an answer for each question.
-Based on the user's selection,
-EpisoPass substitutes characters in the seed string and generate
+the user can select the right answer for each question.
+Based on the user's selections,
+EpisoPass substitutes characters in the seed string and generates
 random-looking password candidate strings.
-After selecting all right answers,
+After selecting all the right answers,
 the user copies the calculated string
@@
 based on the selections.
-When the user selects the right answer to all the questions,
+When the user selects the right answers to all the questions,
 the right password is calculated and shown at the top.
@@
 ``\textsf{Twitter123456}'' is provided as the seed string,
-and according to the selections to the four questions,
+and according to the selections to the five questions,
 the seed string is converted to a string
@@
 \caption{Selecting a different answer.}
-\label{web1}
+\label{web11}
 \end{figure}
@@
 so that generated passwords conforms to password character restrictions
-sometimes required by the service.
+sometimes requested by the service.
 
@@
 is based on the author's episodic memory at elementary school,
-and the last secret question is related to a more recent event
+and the last question is related to a more recent event
 which the author thinks he can never forget.
@@
 there's no clue for the answer,
-1 billion ($20^8$) trials should be performed to check
+1 billion ($20^10$) trials should be performed to check
 all the combinations of the answers,
@@
 
-The quality of secret questions is the key to using EpisoPass.
-If the episodic memory is shared by someone else,
+The quality of the questions is the key to using EpisoPass.
+If the episode is shared by someone else,
 that person can easily answer the question and generate the
@@
 \item Memories of bad experience like blunders or defeat.
+(You don't tell it to anybody.)
 
@@
 
-Questions like ``Which one do you like best?'' should be avoided,
+Questions like ``Which food do you like best?'' should be avoided,
 since some of the friends might know the user's taste.
-Questions related to a episode which the user is proud of should also be
+Questions related to an episode which the user is proud of should also be
 avoided, since the user might talk about the episode to somebody else.
@@
 % 正答をもとにして簡単に偽答のリストを生成することができる。
-In this way, fake answers can be easily listed
+In this way, fake answers can be easily generated
 if it is possible to collect words which belong to the same
@@
 Various methods have been proposed for collecting words in the
-same category, mainly for information retrieval purposes
+same category, mainly for information retrieval tasks%
 \cite{Huang:2012:LFC:2426725.2426728}% 読んでないけど
@@
 
-Although everyone has to use authentication systems on the Net these days,
-not everyone is familiar with handling passwords.
+Although everyone has to use authentication systems on the Internet these days,
+not all the people are good at handling passwords.
 Even experienced computer users have trouble with passwords,
@@
 people can even use services without noticing that passwords are
-used for the authentication.
-
-\subsection{Periodic password update}
+required for the service.
+
+\subsection{Frequent password update}
 
@@
 This kind of authentication is far less secure than simple password systems,
-since it is fairly easy for attackers to get to the right answer.
+since it is fairly easy for attackers to know the right answer.
 The variation of system-provided questions are usually small, and
@@
 %
-Keeping secret is always a pain for many people including
+Keeping secrets is always a pain for many people including
 the authors, but if the whole questions and answers used on EpisoPass
@@
 EpisoPass is just a string-conversion system and it does not
-have any information on which candidate is the correct answer.
-Also, it does not save any password information at any form, and
+have any information on which one is the correct answer.
+Also, it does not save any password information in any form, and
 it is almost impossible to get the right password 
@@
 unexpected leak of the password is unlikely.
-The user doesn't have to remember the string and
+The user doesn't have to remember the password string, and
 there is no chance he will reveal it to somebody
@@
 
-If, one of the passwords generated by EpisoPass is revealed
+If one of the passwords generated by EpisoPass is revealed
 for some reason, other passwords based on the same questions
@@
 the attacker can freely generate all the passwords
-generated by EpisoPass.
+generated with the same questions.
 
@@
 in a secret place or
-use many number of questions so that brute-force does not work.
+use sufficient number of questions so that brute-force does not work.
 
@@
 you can use it as the question
-and use his real name and other similar names as candidate answers.
+and use his real name as well as other similar fake names.
 
@@
 used in the authentication process, or
-perform special operation on the image, and
+perform special operations on the image, and
 it is not much easier than using passwords.
@@
 if anyone can prepare many images 
-which are tightly linked to his episodic memories.
+that are tightly linked to his episodic memories.
 However, finding such images is usually not easy, and
 image-only authentication systems would not take off
-unless simple and effective technique is invented.
+until simple and effective technique is invented.
 % [Malasym]
@@
 %
-While most of the password manager only remember passwords given by the user,
+While most of the password managers only remember passwords given by the user,
 generating passwords with a password manager is a new approach for
@@
 Just like EpisoPass generates passwords,
-Versipass\cite{Stobert:2014:PMD:2683467.2683471}% Versipass 画像のヒントからパスワード生成 % A Password Manager that Doesn’t Remember
+Versipass\cite{Stobert:2014:PMD:2683467.2683471} %Versipass 画像のヒントからパスワード生成 % A Password Manager that Doesn’t Remember
 helps the user to generate password strings
@@
 Before using EpisoPass, taking care of many passwords was really
-a problem for the authors, but
-currently all the information for generating passswords is put on the Net
+a pain for the authors, but
+currently all the information for generating passswords is put on the cloud
 and no trouble has been found during the period.
@@
 an authentication system for everybody,
-and we hope to remove such obstacles in the future.
+and we hope to eliminate such obstacles in the future.
 
@@
 We'll try to integrate the system with existing password-based
-services, and finally hope to remove all the problems
+services, and finally hope to eliminate all the problems
 derived from password-based authentication.

### 2016-05-20 paper/UIST2016/paper.tex
LinkedIn追加

@@
 there's no clue for the answer,
-1 billion ($20^10$) trials should be performed to check
+1 billion ($20^{10}$) trials should be performed to check
 all the combinations of the answers,

### 2016-08-26 paper/Password2016/paper.tex
...

%%%%%%%%%%%%%%%%%%%%%%% file typeinst.tex %%%%%%%%%%%%%%%%%%%%%%%%%
%
% This is the LaTeX source for the instructions to authors using
% the LaTeX document class 'llncs.cls' for contributions to
% the Lecture Notes in Computer Sciences series.
% http://www.springer.com/lncs       Springer Heidelberg 2006/05/04
%
% It may be used as a template for your own input - copy it
% to a new file with a new name and use it as the basis
% for your article.
%
% NB: the document class 'llncs' has its own and detailed documentation, see
% ftp://ftp.springer.de/data/pubftp/pub/tex/latex/llncs/latex2e/llncsdoc.pdf
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[runningheads,a4paper]{llncs}

\usepackage{amssymb}
\setcounter{tocdepth}{3}
\usepackage{graphicx}

\usepackage{url}
\urldef{\mailsa}\path|masui@pitecan.com|
\newcommand{\keywords}[1]{\par\addvspace\baselineskip
\noindent\keywordname\enspace\ignorespaces#1}

\begin{document}

\mainmatter  % start of an individual contribution

% first the title is needed
\title{EpisoPass: Password Management based on Episodic Memories}

% a short form should be given in case it is too long for the running head
\titlerunning{Lecture Notes in Computer Science: Authors' Instructions}

% the name(s) of the author(s) follow(s) next
%
% NB: Chinese authors should write their first names(s) in front of
% their surnames. This ensures that the names appear correctly in
% the running heads and the author index.
%
\author{Toshiyuki Masui%
\thanks{Thanks...}%
}
%
\authorrunning{Lecture Notes in Computer Science: Authors' Instructions}
% (feature abused for this document to repeat the title also on left hand pages)

% the affiliations are given next; don't give your e-mail address
% unless you accept that it will be published
\institute{Faculty of Environment and Information Studies, Keio University\\
5322 Endo, Fujisawa, Kanagawa 252-8520, Japan\\
\mailsa\\
\url{http://pitecan.com/}}

%
% NB: a more complex sample for affiliations and the mapping to the
% corresponding authors can be found in the file "llncs.dem"
% (search for the string "\mainmatter" where a contribution starts).
% "llncs.dem" accompanies the document class "llncs.cls".
%

\toctitle{Lecture Notes in Computer Science}
\tocauthor{Authors' Instructions}
\maketitle

\begin{abstract}
We propose a password manager {\it EpisoPoss\/} that supports the generation of strong passwords based on a user's secret episodic memories. To use EpisoPass, a user first collects question-answer pairs related to their own episodic memories. Each is registered with several possible answers: a single correct answer and multiple fake answers. When the user wants to generate a password, EpisoPass shows each question and list of possible answers and asks the user to select those that are correct. EpisoPass then generates a domain-unique password by substituting the characters of a seed string based on the selected answers. Through careful selection of memories and answers, EpisoPass provides an authentication step using memories that are easy to recall, but difficult for others to guess. In this way various strong passwords can be easily managed without the need for the master password or secret device that is otherwise required by conventional password managers. Using a browser extension, users can use EpisoPass directly on the login page of conventional Web services like Facebook, removing the need to type or copy a password string.

\keywords{Passwords; password managers; user authentication; episodic memories; EpisoPass}
\end{abstract}

\section{Introduction}
% Passwordは使われている
% 
% Passwordが辛いのは一般的事実である[?]
%   基本的に強くするには長くしなければならない
%   忘れる
%   覚えられない
%   サービスごとにパスワードは変えるべきである[?] でも無理
%   定期的に更新させられる
% 強いパスワードを頭で覚えて管理するのは不可能
%       特に弱者には
%   パスワード作成アルゴリズムを自力で使っている人もいるがそれは難しい

Passwords have been used for various Web services and applications
for a long time, and currently the most popular authentication method on the Internet.
%
Since short passwords are easily guessed by attackers and
using the same password for different services is unsafe,
different long passwords should be used for different services.
However,
remembering many long passwords is almost impossible for ordinary humans.
%
% According to Flor\^{e}ncio,
According to a research in 2007,
people use 6.5 passwords on 25 Web services on average, and
4.28\% of the users forget their passwords in 3 months\cite{Florencio:2007:LSW:1242572.1242661}.

%また2011年の野村総研の調査によれば、
%一般的なユーザが{\PW}認証を行なうサイトは平均19.4個で、
%利用している{\PW}は平均3.1個であった\cite{野村総研}。
%多数の{\PW}を記憶することが困難であるため、
%多くのユーザが同じ{\PW}を複数サイトで使い回しているのだと思われる。

% People are frequently asked to register a password when
% they try to use a new service.

% もっと別の認証もいろいろ提案されている
%   画像認証[MALASYM][その他いろいろ]
%   
%   特殊ハードのような持ち物を使う方法など[Pico][YubiKey][RSA]
%   生体認証 指紋認証
%   行動からの認証[]
%   位置ベースの認証[SOUPS]
%  完全置き換えはしばらくは不可能だろう

Since passwords are difficult to handle,
various other authentication methods have been proposed.
For example,
image-based authentication\cite{Biddle:2012:GPL:2333112.2333114}\cite{GraphicalPasswords}, 
biometrics authentication\footnote{
  % \textsf{https:{\slash}{\slash}en.wikipedia.org{\slash}wiki{\slash}Biometrics}
  \url{https://en.wikipedia.org/wiki/Biometrics}
},
behavior-based authentication\cite{Dandapat:2015:AYD:2702123.2702457}, 
and many other authentication methods have been proposed.

% というのもパスワードには利点があるから[Bonneau]
%   すでに普及
%   KB以外の特殊ハードが要らない
%   アタック方法はいろいろあるし[] 流出もしばしばだが
%     うまく実装したシステム上でうまく使えば安全
%     ハッシュ、ソルト
%     実装が比較的簡単
% なのでパスワードが近い将来死滅するとは考えられない

However,
password-based authentication is still the most
convenient and strong method\cite{Bonnearu:ReplacePasswords},
and it is not supposed to get extinct
in a short period of time\cite{Herley:2009:PSS:1601990.1602010}.

% % なのでパスワードと生きる方法が工夫されている
% %   強いパスワードを考える方法[]
% %     覚える方法が提案されてたり[Bonneau]
% %       万人むけはむり

% パスワードが死滅しないならパスワードと生きる方法が必要である
%   たとえば様々なパスワード管理システム[][][][]の利用がすすめられている
%   しかしマスターパスワードがいったり特殊ハードがいったりする
%   特殊システムがいる場合がある
%   特殊ハードやソフトは利用がどうしても難しい

If we have to live with password-based authentication systems,
we have to devise some ways to handle many passwords, and
various ``password managers'' have been proposed
\cite{OnePassword}%
\cite{Dashlane}%
\cite{ミルパス}%
\cite{LastPass}%
\cite{KeyPass}%
\cite{NortonIDSafe}%
\cite{IDManager}.
%
Password managers remember users' passwords and help them enter
passwords on various services.
%
%{\PW}管理システムは
%ひとつの「マスター{\PW}」を利用して他のすべての{\PW}を管理するもので、
%暗号化されたデータベースに{\PW}を格納するもの%
%
Most password managers can manage various passwords by
asking users to remember a single ``master password'' to access the database.
%
%が多いが、サービス名をもとにマスター{\PW}を変換することによって
%複数の{\PW}を生成するシステム\cite{SuperGenPass}もある。
%両者ともにマスター{\PW}の記憶は必須であり、
%マスター{\PW}を盗まれたり忘れたりする危険がある。
%
Although password managers are useful,
users have to remember the master password
or use a special hardware device
for safely handle password managers, and
password managers usually run on limited devices.

% 読みとることができない脳内情報を利用するという基本手法は良いのだが覚えられないのが問題である
%   だとすると...パスワードを記憶するかわりに、****脳が既に覚えている秘密の記憶からパスワードを生成すればよいはずである***
%   確かな脳内情報を使ってパスワードを利用する必要があるが、
%     沢山の強力なパスワードそのものを覚えることは不可能に近い
%   だとすると、確かな脳内秘密情報からパスワードをGenerateするしかない
%   そこでエピソード記憶を使う
%   秘密の知識からGenerateするとよい
%

If we don't want to carry any special device for authentication,
all the information required for the authentication should be
kept in the brain.
%
However, the biggest problem of brain-based authentication is that
users cannot safely keep memories like long passwords or master password.
For this reason, we believe that
it is far better to ``generate'' something for the authentication,
based on users' episodic memories which they can never forget.
%
% We believe that a password manager should have the following features.
% (1) It should be available on any platform including PCs, smartphones, and the Web.
% (2) Users should not have secret information (e.g. master password) or special device.
% (3) Rely only on the information in the user's brain.
%
We propose a password manager \textit{EpisoPass} that generates strong passwords
based only on the user's secret episodic memories that the user can never forget.

\subsection{Checking the PDF File}

Kindly assure that the Contact Volume Editor is given the name and email
address of the contact author for your paper. The Contact Volume Editor
uses these details to compile a list for our production department at
SPS in India. Once the files have been worked upon, SPS sends a copy of
the final pdf of each paper to its contact author. The contact author is
asked to check through the final pdf to make sure that no errors have
crept in during the transfer or preparation of the files. This should
not be seen as an opportunity to update or copyedit the papers, which is
not possible due to time constraints. Only errors introduced during the
preparation of the files will be corrected.

This round of checking takes place about two weeks after the files have
been sent to the Editorial by the Contact Volume Editor, i.e., roughly
seven weeks before the start of the conference for conference
proceedings, or seven weeks before the volume leaves the printer's, for
post-proceedings. If SPS does not receive a reply from a particular
contact author, within the timeframe given, then it is presumed that the
author has found no errors in the paper. The tight publication schedule
of LNCS does not allow SPS to send reminders or search for alternative
email addresses on the Internet.

In some cases, it is the Contact Volume Editor that checks all the final
pdfs. In such cases, the authors are not involved in the checking phase.

\subsection{Additional Information Required by the Volume Editor}

If you have more than one surname, please make sure that the Volume Editor
knows how you are to be listed in the author index.

\subsection{Copyright Forms}

The copyright form may be downloaded from the ``For Authors"
(Information for LNCS Authors) section of the LNCS Website:
\texttt{www.springer.com/lncs}. Please send your signed copyright form
to the Contact Volume Editor, either as a scanned pdf or by fax or by
courier. One author may sign on behalf of all of the other authors of a
particular paper. Digital signatures are acceptable.

\section{Paper Preparation}

Springer provides you with a complete integrated \LaTeX{} document class
(\texttt{llncs.cls}) for multi-author books such as those in the LNCS
series. Papers not complying with the LNCS style will be reformatted.
This can lead to an increase in the overall number of pages. We would
therefore urge you not to squash your paper.

Please always cancel any superfluous definitions that are
not actually used in your text. If you do not, these may conflict with
the definitions of the macro package, causing changes in the structure
of the text and leading to numerous mistakes in the proofs.

If you wonder what \LaTeX{} is and where it can be obtained, see the
``\textit{LaTeX project site}'' (\url{http://www.latex-project.org})
and especially the webpage ``\textit{How to get it}''
(\url{http://www.latex-project.org/ftp.html}) respectively.

When you use \LaTeX\ together with our document class file,
\texttt{llncs.cls},
your text is typeset automatically in Computer Modern Roman (CM) fonts.
Please do
\emph{not} change the preset fonts. If you have to use fonts other
than the preset fonts, kindly submit these with your files.

Please use the commands \verb+\label+ and \verb+\ref+ for
cross-references and the commands \verb+\bibitem+ and \verb+\cite+ for
references to the bibliography, to enable us to create hyperlinks at
these places.

For preparing your figures electronically and integrating them into
your source file we recommend using the standard \LaTeX{} \verb+graphics+ or
\verb+graphicx+ package. These provide the \verb+\includegraphics+ command.
In general, please refrain from using the \verb+\special+ command.

Remember to submit any further style files and
fonts you have used together with your source files.

\subsubsection{Headings.}

Headings should be capitalized
(i.e., nouns, verbs, and all other words
except articles, prepositions, and conjunctions should be set with an
initial capital) and should,
with the exception of the title, be aligned to the left.
Words joined by a hyphen are subject to a special rule. If the first
word can stand alone, the second word should be capitalized.

Here are some examples of headings: ``Criteria to Disprove
Context-Freeness of Collage Language", ``On Correcting the Intrusion of
Tracing Non-deterministic Programs by Software", ``A User-Friendly and
Extendable Data Distribution System", ``Multi-flip Networks:
Parallelizing GenSAT", ``Self-determinations of Man".

\subsubsection{Lemmas, Propositions, and Theorems.}

The numbers accorded to lemmas, propositions, and theorems, etc. should
appear in consecutive order, starting with Lemma 1, and not, for
example, with Lemma 11.

\subsection{Figures}

For \LaTeX\ users, we recommend using the \emph{graphics} or \emph{graphicx}
package and the \verb+\includegraphics+ command.

Please check that the lines in line drawings are not
interrupted and are of a constant width. Grids and details within the
figures must be clearly legible and may not be written one on top of
the other. Line drawings should have a resolution of at least 800 dpi
(preferably 1200 dpi). The lettering in figures should have a height of
2~mm (10-point type). Figures should be numbered and should have a
caption which should always be positioned \emph{under} the figures, in
contrast to the caption belonging to a table, which should always appear
\emph{above} the table; this is simply achieved as matter of sequence in
your source.

Please center the figures or your tabular material by using the \verb+\centering+
declaration. Short captions are centered by default between the margins
and typeset in 9-point type (Fig.~\ref{fig:example} shows an example).
The distance between text and figure is preset to be about 8~mm, the
distance between figure and caption about 6~mm.

To ensure that the reproduction of your illustrations is of a reasonable
quality, we advise against the use of shading. The contrast should be as
pronounced as possible.

If screenshots are necessary, please make sure that you are happy with
the print quality before you send the files.
\begin{figure}
\centering
% \includegraphics[height=6.2cm]{eijkel2}
%\includegraphics[height=6.2cm]{figures/429eec261024dc6c85351f51c12f09b4.png}
\includegraphics[width=12cm,bb=0 0 429 386]{figures/429eec261024dc6c85351f51c12f09b4.png}
\caption{One kernel at $x_s$ (\emph{dotted kernel}) or two kernels at
$x_i$ and $x_j$ (\textit{left and right}) lead to the same summed estimate
at $x_s$. This shows a figure consisting of different types of
lines. Elements of the figure described in the caption should be set in
italics, in parentheses, as shown in this sample caption.}
\label{fig:example}
\end{figure}

Please define figures (and tables) as floating objects. Please avoid
using optional location parameters like ``\verb+[h]+" for ``here".

\paragraph{Remark 1.}

In the printed volumes, illustrations are generally black and white
(halftones), and only in exceptional cases, and if the author is
prepared to cover the extra cost for color reproduction, are colored
pictures accepted. Colored pictures are welcome in the electronic
version free of charge. If you send colored figures that are to be
printed in black and white, please make sure that they really are
legible in black and white. Some colors as well as the contrast of
converted colors show up very poorly when printed in black and white.

\subsection{Formulas}

Displayed equations or formulas are centered and set on a separate
line (with an extra line or halfline space above and below). Displayed
expressions should be numbered for reference. The numbers should be
consecutive within each section or within the contribution,
with numbers enclosed in parentheses and set on the right margin --
which is the default if you use the \emph{equation} environment, e.g.,
\begin{equation}
  \psi (u) = \int_{o}^{T} \left[\frac{1}{2}
  \left(\Lambda_{o}^{-1} u,u\right) + N^{\ast} (-u)\right] dt \;  .
\end{equation}

Equations should be punctuated in the same way as ordinary
text but with a small space before the end punctuation mark.

\subsection{Footnotes}

The superscript numeral used to refer to a footnote appears in the text
either directly after the word to be discussed or -- in relation to a
phrase or a sentence -- following the punctuation sign (comma,
semicolon, or period). Footnotes should appear at the bottom of
the
normal text area, with a line of about 2~cm set
immediately above them.\footnote{The footnote numeral is set flush left
and the text follows with the usual word spacing.}

\subsection{Program Code}

Program listings or program commands in the text are normally set in
typewriter font, e.g., CMTT10 or Courier.

\medskip

\noindent
{\it Example of a Computer Program}
\begin{verbatim}
program Inflation (Output)
  {Assuming annual inflation rates of 7%, 8%, and 10%,...
   years};
   const
     MaxYears = 10;
   var
     Year: 0..MaxYears;
     Factor1, Factor2, Factor3: Real;
   begin
     Year := 0;
     Factor1 := 1.0; Factor2 := 1.0; Factor3 := 1.0;
     WriteLn('Year  7% 8% 10%'); WriteLn;
     repeat
       Year := Year + 1;
       Factor1 := Factor1 * 1.07;
       Factor2 := Factor2 * 1.08;
       Factor3 := Factor3 * 1.10;
       WriteLn(Year:5,Factor1:7:3,Factor2:7:3,Factor3:7:3)
     until Year = MaxYears
end.
\end{verbatim}
%
\noindent
{\small (Example from Jensen K., Wirth N. (1991) Pascal user manual and
report. Springer, New York)}

\subsection{Citations}

For citations in the text please use
square brackets and consecutive numbers: \cite{jour}, \cite{lncschap},
\cite{proceeding1} -- provided automatically
by \LaTeX 's \verb|\cite| \dots\verb|\bibitem| mechanism.

\subsection{Page Numbering and Running Heads}

There is no need to include page numbers. If your paper title is too
long to serve as a running head, it will be shortened. Your suggestion
as to how to shorten it would be most welcome.

\section{LNCS Online}

The online version of the volume will be available in LNCS Online.
Members of institutes subscribing to the Lecture Notes in Computer
Science series have access to all the pdfs of all the online
publications. Non-subscribers can only read as far as the abstracts. If
they try to go beyond this point, they are automatically asked, whether
they would like to order the pdf, and are given instructions as to how
to do so.

Please note that, if your email address is given in your paper,
it will also be included in the meta data of the online version.

\section{BibTeX Entries}

The correct BibTeX entries for the Lecture Notes in Computer Science
volumes can be found at the following Website shortly after the
publication of the book:
\url{http://www.informatik.uni-trier.de/~ley/db/journals/lncs.html}

\subsubsection*{Acknowledgments.} The heading should be treated as a
subsubsection heading and should not be assigned a number.

\section{The References Section}\label{references}

In order to permit cross referencing within LNCS-Online, and eventually
between different publishers and their online databases, LNCS will,
from now on, be standardizing the format of the references. This new
feature will increase the visibility of publications and facilitate
academic research considerably. Please base your references on the
examples below. References that don't adhere to this style will be
reformatted by Springer. You should therefore check your references
thoroughly when you receive the final pdf of your paper.
The reference section must be complete. You may not omit references.
Instructions as to where to find a fuller version of the references are
not permissible.

We only accept references written using the latin alphabet. If the title
of the book you are referring to is in Russian or Chinese, then please write
(in Russian) or (in Chinese) at the end of the transcript or translation
of the title.

The following section shows a sample reference list with entries for
journal articles \cite{jour}, an LNCS chapter \cite{lncschap}, a book
\cite{book}, proceedings without editors \cite{proceeding1} and
\cite{proceeding2}, as well as a URL \cite{url}.
Please note that proceedings published in LNCS are not cited with their
full titles, but with their acronyms!

\begin{thebibliography}{4}

\end{thebibliography}

\section*{Appendix: Springer-Author Discount}

LNCS authors are entitled to a 33.3\% discount off all Springer
publications. Before placing an order, the author should send an email, 
giving full details of his or her Springer publication,
to \url{orders-HD-individuals@springer.com} to obtain a so-called token. This token is a
number, which must be entered when placing an order via the Internet, in
order to obtain the discount.

\section{Checklist of Items to be Sent to Volume Editors}
Here is a checklist of everything the volume editor requires from you:

\begin{itemize}
\settowidth{\leftmargin}{{\Large$\square$}}\advance\leftmargin\labelsep
\itemsep8pt\relax
\renewcommand\labelitemi{{\lower1.5pt\hbox{\Large$\square$}}}

\item The final \LaTeX{} source files
\item A final PDF file
\item A copyright form, signed by one author on behalf of all of the
authors of the paper.
\item A readme giving the name and email address of the
corresponding author.
\end{itemize}
\end{document}

### 2016-08-26 paper/Password2016/paper.tex
...
EpisoPass論文にしたてた

@@
 \usepackage{graphicx}
+
+\usepackage{here} % [H]とするとその場所に配置されるらしい
 
@@
 \begin{abstract}
-We propose a password manager {\it EpisoPoss\/} that supports the generation of strong passwords based on a user's secret episodic memories.
-To use EpisoPass, a user first collects question-answer pairs related to their own episodic memories.
-Each is registered with several possible answers: a single correct answer and multiple fake answers.
-When the user wants to generate a password, EpisoPass shows each question and list of possible answers and asks the user to select those that are correct.
-EpisoPass then generates a domain-unique password by substituting the characters of a seed string based on the selected answers.
-Through careful selection of memories and answers, EpisoPass provides an authentication step using memories that are easy to recall, but difficult for others to guess.
-In this way various strong passwords can be easily managed without the need for the master password or secret device that is otherwise required by conventional password managers.
-Using a browser extension, users can use EpisoPass directly on the login page of conventional Web services like Facebook, removing the need to type or copy a password string.
+We propose a password manager \textit{EpisoPass} that supports the
+generation of strong passwords based on a user's secret episodic
+memories. To use EpisoPass, a user first collects question-answer
+pairs related to their own episodic memories. Each is registered with
+several possible answers: a single correct answer and multiple fake
+answers. When the user wants to generate a password, EpisoPass shows
+each question and list of possible answers and asks the user to select
+those that are correct. EpisoPass then generates a domain-unique
+password by substituting the characters of a seed string based on the
+selected answers. Through careful selection of memories and answers,
+EpisoPass provides an authentication step using memories that are easy
+to recall, but difficult for others to guess. In this way various
+strong passwords can be easily managed without the need for the master
+password or secret device that is otherwise required by conventional
+password managers. Using a browser extension, users can use EpisoPass
+directly on the login page of conventional Web services like Facebook,
+removing the need to type or copy a password string.
 
@@
 
-\subsection{Checking the PDF File}
+\section{EpisoPass}
 
-Kindly assure that the Contact Volume Editor is given the name and email
-address of the contact author for your paper. The Contact Volume Editor
-uses these details to compile a list for our production department at
-SPS in India. Once the files have been worked upon, SPS sends a copy of
-the final pdf of each paper to its contact author. The contact author is
-asked to check through the final pdf to make sure that no errors have
-crept in during the transfer or preparation of the files. This should
-not be seen as an opportunity to update or copyedit the papers, which is
-not possible due to time constraints. Only errors introduced during the
-preparation of the files will be corrected.
+EpisoPass is a password manager that supports generating
+strong passwords based on users' secret episodic memories.
+%
+% Before using EpisoPass for generating passwords,
+% a user provides a seed string and many question-answer pairs to EpisoPass,
+% and a password is generated based on the user's selections.
+%
+Memories in human brain are not uniform.
+Some memories are very short-lived, and others are unforgettable.
+When we have a very impressive experience,
+that memory will stay in the brain for a long time and
+cannot easily disappear.
+On the other hand, when we study math and try to remember a formula,
+it is usually hard to memorize it unless we practice a lot,
+since the knowledge about the formula is not related to
+any personal experiences.
+The former type of memory is called the episodic memory and
+people cannot easily lose it.
+Memories of passwords belong to the latter type and
+people cannot easily remember them, just like people cannot
+remember math formulas easily.
+%
 
-This round of checking takes place about two weeks after the files have
-been sent to the Editorial by the Contact Volume Editor, i.e., roughly
-seven weeks before the start of the conference for conference
-proceedings, or seven weeks before the volume leaves the printer's, for
-post-proceedings. If SPS does not receive a reply from a particular
-contact author, within the timeframe given, then it is presumed that the
-author has found no errors in the paper. The tight publication schedule
-of LNCS does not allow SPS to send reminders or search for alternative
-email addresses on the Internet.
+% \begin{quote}
+% Episodic memory is the memory of autobiographical events (times,
+% places, associated emotions, and other contextual who, what, when,
+% where, why knowledge) that can be explicitly stated. It is the
+% collection of past personal experiences that occurred at a particular
+% time and place. For example, if one remembers the party on his or her
+% 6th birthday, this is an episodic memory. They allow an individual to
+% figuratively travel back in time to remember the event that took place
+% at that particular time and place.[1]
+% 
+% Semantic memory is one of the two types of declarative or explicit
+% memory (our memory of facts or events that is explicitly stored and
+% retrieved).[1] Semantic memory refers to general world knowledge that
+% we have accumulated throughout our lives.[2] This general knowledge
+% (facts, ideas, meaning and concepts) is intertwined in experience and
+% dependent on culture. Semantic memory is distinct from episodic
+% memory, which is our memory of experiences and specific events that
+% occur during our lives, from which we can recreate at any given
+% point.[3] For instance, semantic memory might contain information
+% about what a cat is, whereas episodic memory might contain a specific
+% memory of petting a particular cat. We can learn about new concepts by
+% applying our knowledge learned from things in the past.[4] The
+% counterpart to declarative, or explicit memory, is procedural memory,
+% or implicit memory.[5]
+% \end{quote}
 
-In some cases, it is the Contact Volume Editor that checks all the final
-pdfs. In such cases, the authors are not involved in the checking phase.
+Password generation on EpisoPass is performed through the following steps:
 
-\subsection{Additional Information Required by the Volume Editor}
+\begin{enumerate}
+\item A user registers many question texts related to the user's personal
+secret episodic memories that the user never forgets,
+and provides a correct answer and additional fake answers.
 
-If you have more than one surname, please make sure that the Volume Editor
-knows how you are to be listed in the author index.
+\item The user provides a long ``seed string'' for each service that requires
+a password.
 
-\subsection{Copyright Forms}
+\item EpisoPass shows the data to the user so that
+the user can select the right answer for each question.
+Based on the user's selections,
+EpisoPass substitutes characters in the seed string and generates
+random-looking password candidate strings.
+After selecting all the right answers,
+the user copies the calculated string
+and register it as the password for the service.
+\end{enumerate}
 
-The copyright form may be downloaded from the ``For Authors"
-(Information for LNCS Authors) section of the LNCS Website:
-\texttt{www.springer.com/lncs}. Please send your signed copyright form
-to the Contact Volume Editor, either as a scanned pdf or by fax or by
-courier. One author may sign on behalf of all of the other authors of a
-particular paper. Digital signatures are acceptable.
+\subsection{Using EpisoPass on a browser}
 
-\section{Paper Preparation}
+Figure \ref{web1} shows how to generate a password
+on EpisoPass running on a browser.
+Many questions related to the user's episodic memories are shown to the user,
+and many candidate answers are also shown for each question.
+When a user clicks and selects one of the answers for each question,
+the seed string shown at the top-left is converted to a random-looking string
+based on the selections.
+When the user selects the right answers to all the questions,
+the right password is calculated and shown at the top.
 
-Springer provides you with a complete integrated \LaTeX{} document class
-(\texttt{llncs.cls}) for multi-author books such as those in the LNCS
-series. Papers not complying with the LNCS style will be reformatted.
-This can lead to an increase in the overall number of pages. We would
-therefore urge you not to squash your paper.
+% If the q-a is based on the user's episodic memories and
+% nobody knows the correct answer,
+% only the user can select the set of right answers and
+% use the converted string as the password.
 
-Please always cancel any superfluous definitions that are
-not actually used in your text. If you do not, these may conflict with
-the definitions of the macro package, causing changes in the structure
-of the text and leading to numerous mistakes in the proofs.
+\begin{figure}[t]
+\centering
+\includegraphics[width=1.0\columnwidth]{figures/c1bd6e7f67698c70978f528ccd2339d9}
+\caption{Generating a Twitter password with EpisoPass.}
+\label{web1}
+\end{figure}
 
-If you wonder what \LaTeX{} is and where it can be obtained, see the
-``\textit{LaTeX project site}'' (\url{http://www.latex-project.org})
-and especially the webpage ``\textit{How to get it}''
-(\url{http://www.latex-project.org/ftp.html}) respectively.
+In Figure \ref{web1},
+``\textsf{Twitter123456}'' is provided as the seed string,
+and according to the selections to the five questions,
+the seed string is converted to a string
+``\textsf{Lbasnln542202}'',
+which can be used as the password for Twitter.
 
-When you use \LaTeX\ together with our document class file,
-\texttt{llncs.cls},
-your text is typeset automatically in Computer Modern Roman (CM) fonts.
-Please do
-\emph{not} change the preset fonts. If you have to use fonts other
-than the preset fonts, kindly submit these with your files.
+When the user clicks another candidate,
+the seed string is converted to another strings like
+``\textsf{Bhtuyna904127}'' (Figure \ref{web11}).
 
-Please use the commands \verb+\label+ and \verb+\ref+ for
-cross-references and the commands \verb+\bibitem+ and \verb+\cite+ for
-references to the bibliography, to enable us to create hyperlinks at
-these places.
+\begin{figure}[H]
+\centering
+\includegraphics[width=1.0\columnwidth]{figures/01e5507d090eb494a20bcbc47c86b1d2}
+\caption{Selecting a different answer.}
+\label{web11}
+\end{figure}
 
-For preparing your figures electronically and integrating them into
-your source file we recommend using the standard \LaTeX{} \verb+graphics+ or
-\verb+graphicx+ package. These provide the \verb+\includegraphics+ command.
-In general, please refrain from using the \verb+\special+ command.
+In this way, different selections yields different password strings and
+the password string generated after selecting correct answers can be
+used as the password for the service.
 
-Remember to submit any further style files and
-fonts you have used together with your source files.
+Capital letters in the seed string are substituted to capital letters in the password,
+and digits in the seed string are substituted to digits,
+so that generated passwords conforms to password character restrictions
+sometimes requested by the service.
 
-\subsubsection{Headings.}
+% {\SS}として「\textsf{Twitter123456}」という文字列を指定しており、
+% 4個の{\SQ}に対する回答選択に応じて
+% 「\textsf{Mfveabn574923}」のような{\PW}候補が生成される。
+% 異なる答をを選択すると全く異なる文字列が生成される。
+% {\SS}の8文字目が数字である場合は{\PW}の8文字目も数字になるなど、
+% {\SS}の文字種に対応した{\PW}候補が生成される。
 
-Headings should be capitalized
-(i.e., nouns, verbs, and all other words
-except articles, prepositions, and conjunctions should be set with an
-initial capital) and should,
-with the exception of the title, be aligned to the left.
-Words joined by a hyphen are subject to a special rule. If the first
-word can stand alone, the second word should be capitalized.
+The second question in Figure \ref{web1}
+is based on the author's episodic memory at elementary school,
+and the last question is related to a more recent event
+which the author thinks he can never forget.
+All the questions are related to the author's episodic memories
+that he thinks he never forgets, and nobody else knows which one of the
+candidate answers is the right one.
 
-Here are some examples of headings: ``Criteria to Disprove
-Context-Freeness of Collage Language", ``On Correcting the Intrusion of
-Tracing Non-deterministic Programs by Software", ``A User-Friendly and
-Extendable Data Distribution System", ``Multi-flip Networks:
-Parallelizing GenSAT", ``Self-determinations of Man".
+Questions and answers can be edited directly on the browser, and they can be
+saved on the server by clicking the ``save to server'' button.
+The Q-A data sets are saved on the server,
+but no information about the correct answer or the
+generated password is saved on the server.
 
-\subsubsection{Lemmas, Propositions, and Theorems.}
+% {\SQ}と答はブラウザで編集でき、
+% 右上の「サーバにセーブ」ボタンを押すことにより{\SS}、秘密の問題、答のリストがサーバにセーブされる。
+% 「ファイルにセーブ」ボタンを押すとJSONデータをパソコンにダウンロードでき、
+% パソコン上のJSONデータをブラウザにドラッグ\&ドロップするとサーバにアップロードできる。
+% ユーザはどれが正答かを指定するわけではないので
+% 問題データを見てもユーザの{\PW}はわからない。
 
-The numbers accorded to lemmas, propositions, and theorems, etc. should
-appear in consecutive order, starting with Lemma 1, and not, for
-example, with Lemma 11.
+When we change the secret string to ``\textsf{Facebook123456}'',
+the generated password changes to ``\textsf{Zxghfbqu533131}'',
+as shown in Figure \ref{web2}.
+In this way, we can generate different passwords for
+different services just by changing the seed string.
 
-\subsection{Figures}
+\begin{figure}[H]
+\centering
+\includegraphics[width=1.0\columnwidth]{figures/0e2820c279afc70520482e0fc53b6ed9}
+\caption{Generating the password for FaceBook.}
+\label{web2}
+\end{figure}
 
-For \LaTeX\ users, we recommend using the \emph{graphics} or \emph{graphicx}
-package and the \verb+\includegraphics+ command.
+% {\PW}文字列の計算方法}
+% 問題と回答から文字列を生成し、そのMD5値によって{\SS}を換字することにより
+% {\PW}を生成している。
+% {\PW}文字列の計算方法は附録に示す。
 
-Please check that the lines in line drawings are not
-interrupted and are of a constant width. Grids and details within the
-figures must be clearly legible and may not be written one on top of
-the other. Line drawings should have a resolution of at least 800 dpi
-(preferably 1200 dpi). The lettering in figures should have a height of
-2~mm (10-point type). Figures should be numbered and should have a
-caption which should always be positioned \emph{under} the figures, in
-contrast to the caption belonging to a table, which should always appear
-\emph{above} the table; this is simply achieved as matter of sequence in
-your source.
+%アルゴリズムはここ? Algorithm
 
-Please center the figures or your tabular material by using the \verb+\centering+
-declaration. Short captions are centered by default between the margins
-and typeset in 9-point type (Fig.~\ref{fig:example} shows an example).
-The distance between text and figure is preset to be about 8~mm, the
-distance between figure and caption about 6~mm.
+Character substitution is performed based on the hash value
+calculated from concatinating all the selected answers.
+For example, if the user selects ``\textbf{\texttt{Ebisawa}}'' to the question ``\textbf{\texttt{Who's the bully?}}'',
+a hash value calculated from  ``\textbf{\texttt{Who's the bully:Ebisawa}}''
+is used for the substitution.
+Details of the algorithm is shown in the Appendix.
 
-To ensure that the reproduction of your illustrations is of a reasonable
-quality, we advise against the use of shading. The contrast should be as
-pronounced as possible.
+% 問題と回答から文字列を生成し、そのMD5値によって{\SS}を換字することにより
+% {\PW}を生成している。
+% {\PW}文字列の計算方法は附録に示す。
 
-If screenshots are necessary, please make sure that you are happy with
-the print quality before you send the files.
+% \subsubsection{回答選択により{\PW}を切り換え}
+% \label{pwgen}
+% 
+% サービスごとに{\SS}を変えるのではなく、
+% 図\ref{web3}のように
+% サービス名に応じて回答を変えることによって異なる{\PW}を作成することも可能である。
+% {\PW}としての長さや文字種に特種な制約が無いサービスに関してはこの方法が便利である。
+% 
+% \begin{figure}[H]
+% \centerline{\includegraphics[width=83mm,bb=0 0 718 428]{../WISS/figures/a9167a6ec6af9c70dd1617e3fc25ec30.png}}
+% \centerline{\includegraphics[width=83mm,bb=0 0 718 428]{../WISS/figures/5b887fabeb8e3319623901fe4a6c56f2.png}}
+% \caption{サービス名に対応する回答で異なる{\PW}を生成.}
+% \label{web3}
+% \end{figure}
+
+% 定期的に{\PW}変更を求められるシステムでは、
+% 「利用期間は?」という質問に対して
+% 「2013/1」「2013/2」のような答を用意しておけば、
+% 時期を選択することによって簡単に{\PW}を変更することができるので便利である。
+
+\subsection{Android application}
+
+% Webサービスを利用する場合、ブラウザとサーバとの間の通信を
+% 記録されたり盗み見されたりされる心配を完全に払拭することはできない。
+% % 危険を完全になくすことはできない。
+% 前述の例において、
+% {\PW}はブラウザ内部でJavaScriptにより生成されるので、
+% 一度ページを表示した後は
+% ネットワークを遮断しても{\PW}計算を行なえるようになっているが、
+% 最初から全く通信を行なわずに{\PW}を作成できる方がより安心であろう。
+% このため、通信を全く行なわずにマシン単体で{\PW}計算を行なうための
+% Androidアプリを用意した。
+% ページの右上の「Androidアプリ」ボタンを押すと、
+% 現在表示している秘密の問題と答を内蔵したAndroidアプリが
+% サーバ上でビルドされてダウンロードされる。
+
+If a user doesn't like to use EpisoPass service on the Net,
+he can use an EpisoPass application on Android
+which does not require network connection.
+After registering questions and answers on the EpisoPass service,
+the user can download an Android application from the server
+by clicking the ``Android app'' button.
+The application contains all the information required for generating passwords.
+(The application is compiled and built on the server.)
+
+% Android端末でアプリを実行すると図\ref{android1}のような画面が表示される。
+% {\SS}を設定して「開始」ボタンを押すと図\ref{android2}のように質問がひとつずつ表示され、
+% ボタンを押してすべて回答すると{\PW}が計算され図\ref{android3}のように表示される。
+
+When the user runs the application and selects the right answer
+to each question, he can eventually get the password and copy it to the password entry.
+(Figure \ref{android1},\ref{android2})
+
+\begin{figure}[H]
+\centering
+\includegraphics[width=0.7\columnwidth]{figures/429eec261024dc6c85351f51c12f09b4}
+\caption{Running EpisoPass on Android.}
+\label{android1}
+\end{figure}
+
+\begin{figure}[H]
+\centering
+\includegraphics[width=0.7\columnwidth]{figures/ba8f5aeaa935ad63437969f4d746746b}
+\caption{After finishing selections.}
+\label{android2}
+\end{figure}
+
+% 回答入力と{\PW}計算はAndroid端末で実行されるため、
+% 端末を「機内モード」に設定するなどの方法で
+% ネットワーク接続を遮断した状態でも{\PW}を計算することができる。
+% {\EP}をインストールしたAndroid端末を持っていれば常に各種の{\PW}を計算できるので、
+% 他人のマシンや公共の場所に設置されたパソコンなどでも
+% 容易にtwitterなどのネットサービスを利用することができる。
+
+% The calculation is performed on Android without network connection,
+% and the user can safely generate passwords 
+% without feeling the fear of ...
+
+% 前述の方法で{\EP}アプリをサーバからダウンロードする場合は、
+% ブラウザ上で秘密の問題をサーバに登録する必要があるが、
+% 秘密の問題を全くネット上に露出することなくアプリを利用することもできる。
+
+\section{DISCUSSIONS}
+
+In this section, we discuss the advantages and caveats of
+using EpisoPass.
+
+\subsection{Unforgettability}
+
+The biggest advantage of using EpisoPass is that
+users don't have to remember passwords of any kind and
+they can stop worrying about password-related troubles.
+%
+Users of EpisoPass can save the seed string and question-answer data
+at any place, and easily generate passwords by running
+EpisoPass and answering questions.
+If the question is based on old unforgettable episodic memories,
+there is little chance of losing passwords.
+If the user's memory is related to an episode of 20 years ago and the user clearly
+remembers the episode now, it is unlikely that he forgets the episode 10 years later.
+
+\subsection{Security strength of EpisoPass}
+
+The strength of the generated password depends on the number of
+questions and the secret level of the questions.
+%
+There have been many studies on the strength of passwords
+\cite{Hayashi:2011:DSP:1978942.1979326}%
+\cite{Komanduri:2011:PPM:1978942.1979321}, % どういうパスワードが強いか
+but the strength of secret questions has not been studied enough.
+%
+% {\EP}で選択枝が10個の{\SQ}を8個使用する場合、
+% 総当たりで{\PW}を生成するには
+% 1億($10^8$)通りの試行が必要であり、
+% % エントロピーは26.6 ($ = 8 \times \log_2 10$) ビット
+% エントロピーは26.6ビットとなる。
+%
+When we use 10 secret questions with 20 answers and
+there's no clue for the answer,
+1 billion ($20^{10}$) trials should be performed to check
+all the combinations of the answers,
+and the entropy of the system is 43.2 ($10 \times \log_2 20$) bits.  % 10.0 * (Math.log(20.0)/Math.log(2.0))
+%
+% 英字からランダムに8文字を並べて作成した{\PW}のエントロピーは37.6ビットになるが、
+% ``\textsf{pmvixuzq}''のように全く意味のない{\PW}を記憶して利用することは少ないため、
+% 実際に利用される{\PW}のエントロピーは20ビット程度と考えられているので\cite{NIST}、
+% {\SQ}と選択枝の数を10個程度用意すれば
+% 通常の{\PW}と同程度の強度が期待できることになる。
+%
+It is almost the same entropy as using random 8-character English alphabets
+as a password, in which case the entropy is 45.6 bits.
+This level is considered to be strong enough for Web services,
+where online brute-force attack is impossible\cite{Florencio:2007:SWP:1361419.1361429}.
+
+\subsection{Selecting good questions}
+
+% {\EP}利用において{\SQ}の選択は非常に重要である。
+% 他人が推測することが難しく、自分が決して忘れないような{\EM}を{\SQ}として利用すべきであり、
+% 以下のような性質をもつ記憶は{\SQ}として利用すべきではない。
+
+The quality of the questions is the key to using EpisoPass.
+If the episode is shared by someone else,
+that person can easily answer the question and generate the
+password just like the user.
+%
+The episode related to each question should not be known to other people,
+and the episode should be unforgettable.
+%
+Finding such episodes seems difficult at first, but
+when we try to remember experiences of old days,
+we can recall many trivial episodes which are unforgettable but
+not important to other people.
+%
+Old experiences like the following are candidates for
+good questions used in EpisoPass.
+
+\begin{itemize}
+\item Memory of small injury. (Nobody cares it but you.)
+
+\item Memories of bad experience like blunders or defeat.
+(You don't tell it to anybody.)
+
+\item Experience of finding a small special item which only you are interested in.
+\end{itemize}
+
+For example, a question like
+``who hit you when you were 6 years old?''
+is about a trivial experience that people do not mention,
+but a bad experience like this is not forgettable.
+
+Questions like ``Which food do you like best?'' should be avoided,
+since some of the friends might know the user's taste.
+Questions related to an episode which the user is proud of should also be
+avoided, since the user might talk about the episode to somebody else.
+
+We usually don't tell our bad trivial experiences to other people,
+but we might boast of good experiences or even write a blog about it.
+Also, our tastes (e.g. favorite food) might change in the long run.
+Using such episodes for questions should be avoided.
+
+% \begin{itemize}
+% \item \textsf{自慢になるもの
+% (何かの機会にうっかり他人に話してしまう可能性がある)}
+% 
+% \vspace{-1mm}
+% \item \textsf{ネット上に記録が残っているもの}
+% 
+% \vspace{-1mm}
+% \item \textsf{他人と情報を共有しているもの}
+% 
+% \vspace{-1mm}
+% \item \textsf{趣味や嗜好に関連するもの
+% (他人に推測されやすいうえに嗜好が変化する可能性がある)}
+% 
+% \end{itemize}
+
+\subsection{Creating fake answers}
+
+% {\SQ}の種類によっては偽答の生成が難しい場合がある。
+% 図\ref{atmega}は電子工作に関する{\SQ}の例であるが、
+% 正答と区別がつかない偽答を充分リストすることは難しい。
+
+It is difficult to provide enough number of fake answers to a question like
+``what was your favorite sport?''
+because possible answers are limited.
+%
+% \begin{figure}[H]
+% \centerline{\includegraphics[width=83mm,bb=0 0 512 113]{../figures/2f63ceb9ab6faf8d81393953f2f95a8c.png}}
+% \caption{偽答の生成が難しい例.}
+% \label{atmega}
+% \end{figure}
+%
+% 一方、正答として人名や地名を利用する場合、
+% 正答に似た人名や地名をリストすることは難しくない。
+% 「世田谷」が正答であるとき、
+% 「目黒」「杉並」のような偽答を用意するのは簡単である。
+%
+On the other hand, if the right answer to the question is a name of a place or a person,
+generating similar answers is easy.
+For example, if the answer to the question is ``Colorado'',
+we can easily provide fake answers like ``California'', ``Utah'', etc.
+because we can use the list of states in the U.S.
+
+% 正答と同じカテゴリに属する単語を自動的にリストすることができれば
+% 正答をもとにして簡単に偽答のリストを生成することができる。
+In this way, fake answers can be easily generated
+if it is possible to collect words which belong to the same
+category as the right answer.
+%
+% ひとつの単語もしくは単語の集合と同じカテゴリに属する単語を検索する手法は
+% 「同位語検索」と呼ばれ、
+% Webのデータを利用した様々な同位語検索システムが提案されている%
+Various methods have been proposed for collecting words in the
+same category, mainly for information retrieval tasks%
+\cite{Huang:2012:LFC:2426725.2426728}% 読んでないけど
+\cite{BooWa}% Boo!Wa!というサイトをやっている
+\cite{Wang:2007:LSE:1441428.1442086}.% BooWa
+%\cite{大島裕明:2006-12-15}.% ライバルサーチ「やーやら」
+We can use such techniques for getting similar names.
+
+\subsection{Universality}
+
+Although everyone has to use authentication systems on the Internet these days,
+not all the people are good at handling passwords.
+Even experienced computer users have trouble with passwords,
+since choosing a good password is not intuitive and
+people forget passwords frequently.
+%
+Using EpisoPass, people can use password-based systems without knowing
+techniques for creating and remembering strong passwords.
+They only have to provide
+questions and answers based on secret episodic memories.
+%
+By integrating EpisoPass into existing password-based services,
+people can even use services without noticing that passwords are
+required for the service.
+
+\subsection{Frequent password update}
+
+On many services, users are requested to change passwords periodically
+to strengthen security.
+%
+% A user can generate a new strong password by using a randam character generator
+% on a password manager, but he might want to old passwords in case some trouble happens.
+%
+Using EpisoPass, users can just provide a date-related question
+like the first question shown in Figure \ref{web1},
+and generate different strong passwords based on the answer.
+Using this technique, people can easily manage old and new passwords.
+
+\subsection{Comparison with challenge-response authentication}
+
+% 一方、{\SQ}を利用する認証の脆弱性を利用した攻撃が近年問題になっている。
+% {\PW}を忘れたときのために、
+% あらかじめ設定した{\SQ}に答えることによって{\PW}をリセットできるサービスがあり、
+% 「母親の旧姓は?」や「最初に飼ったペットの名前は?」のような
+% 質問に対してユーザが答を登録するようになっている。
+% このような問題は他人が調べたり推測したりすることが容易であるうえに
+% {\SQ}の数は一般的に少なく、
+% {\PW}よりも脆弱だといえる\cite{Rabkin:2008:PKQ:1408664.1408667}。% 銀行20個調べて{\SQ}の弱さを指摘
+
+In many services, users are adviced to define answers to secret questions like
+``what is your mother's maiden name''
+so that he can log into the service even when he forgets the password.
+This kind of authentication is far less secure than simple password systems,
+since it is fairly easy for attackers to know the right answer.
+The variation of system-provided questions are usually small, and
+such challenge-response systems are considered to be
+insecure\cite{Rabkin:2008:PKQ:1408664.1408667}.
+
+It would be better if the user can register his own secret questions
+based on his episodic memory.
+However, answers to user-generated challenge questions are more easily
+forgotten or cracked,
+and using simple challenge-responce is not considered to be safe enough
+\cite{Just:2009:PCC:1572532.1572543}\cite{Schechter:2009:NSM:1607723.1608145}.
+%
+Also, in this case,
+the user should register the answer to the system in addition to the question.
+Telling secret facts to service providers is like
+registering raw password string on the server,
+and it is not safe unless the strings are properly hashed and salted on the server.
+
+%
+%ユーザが作成した{\SQ}を使えばこのような問題はなくなるはずであるが、
+%他人に解かれにくい問題をユーザが作成することは難しく、
+%またユーザ自身が答を忘れてしまうことも多いと考えられている\cite{Just:2009:PCC:1572532.1572543}\cite{Schechter:2009:NSM:1607723.1608145}。
+%
+%また、古い記憶にもとづいて作成した秘密の問題は
+%ユーザが想像するよりも解かれやすいという実験結果にもとづき、
+%忘れない{\SQ}を複数利用する方法、
+%問題と答を連想するために画像を利用する方法、
+%複数の問題を連続的に利用する手法などが提案されている\cite{Renaud:2010:PQE:2146303.2146318}。
+
+% {\EP}では、
+% 他人には解くことが難しく自分では忘れないような{\SQ}を自由にいくつでも利用できるようになっている。
+% 問題作成に慣れていないユーザには有効な{\SQ}を作成することは難しいかもしれないが、
+% 次節で述べるように、適切な質問を選ぶことによりこの問題を解決できるはずである。
+
+\subsection{Care for handling secret information}
+
+Users don't have to be very careful about handling questions and answers.
+They can even be put on a public place
+if enough amount of questions and fake answers are provided.
+%
+Keeping secrets is always a pain for many people including
+the authors, but if the whole questions and answers used on EpisoPass
+can be put on a public place,
+handling it becomes very easy.
+Usually we have to be very careful about handling
+secret information like passwords, secret key for SSH, etc.
+because they should not be copied or saved at unsafe places.
+On the other hand,
+we can save the EpisoPass data as a plain text file and put it at
+any place without great care, since malicious person cannot calculate
+passwords without having the owner's episodic memories.
+
+\subsection{Risk of password leak}
+
+EpisoPass is just a string-conversion system and it does not
+have any information on which one is the correct answer.
+Also, it does not save any password information in any form, and
+it is almost impossible to get the right password 
+without having the episodic memory.
+
+% 聞かれてもわからないし書き留める必要がないからウッカリもらす可能性はない
+% ローカルに実行すればネットでもれる心配もない
+
+Since the password is generated by the algorithm and the password
+string is not kept on a computer in any form,
+unexpected leak of the password is unlikely.
+The user doesn't have to remember the password string, and
+there is no chance he will reveal it to somebody
+even when he is forced to tell the password.
+
+% \subsection{Strong passwords can be generated}
+%   強度を自由に設定できる
+
+\subsection{Simplicity}
+
+The algorithm of generating a password (shown in Appendix)
+is fairly simple and
+it can be implemented on any browser JavaScripts or
+applications on smartphones and small devices.
+
+\subsection{Risk of password leak at the service side}
+
+If one of the passwords generated by EpisoPass is revealed
+for some reason, other passwords based on the same questions
+might also be revealed.
+%
+For example, if Twitter is attacked by a cracker and
+the password for Twitter (``\textsf{Lbasnln542202}'' in Figure \ref{web1})
+is revealed to the attacker,
+the attacker can try all the answer combinations and find out
+the answers to all the questions,
+if questions and answers are also known by the attacker.
+Once all the answers to the questions are known,
+the attacker can freely generate all the passwords
+generated with the same questions.
+
+To prevent such troble, it is safer to keep all the questions and answers
+in a secret place or
+use sufficient number of questions so that brute-force does not work.
+
+% 問題自体が秘密であればひとつ漏れても大丈夫
+% 
+% {\SQ}を公開している場合、
+% {\SS}と{\PW}の対応がひとつでも漏洩してしまうと、
+% 総当たり計算でチェックすることにより、
+% すべて{\SQ}の正答が判明してしまう。
+% {\SQ}の正答を知っていれば
+% {\SS}から{\PW}を計算することができるので、
+% 漏洩した{\SQ}は利用不可能になってしまう。
+%
+% \ref{pattern1}や
+% \ref{pattern2}のような運用をしている場合は
+% {\PW}がひとつ漏洩しても他の{\PW}は安全だが、
+% \ref{pattern3}のような運用をしている場合は
+% ひとつでも{\PW}が漏洩するとあらゆる{\PW}が漏洩してしまうことになる。
+
+\subsection{Using images}
+
+Old pictures can be used as the questions of EpisoPass,
+just like the 5th question shown in Figure \ref{web1}.
+Even when people cannot create good secret questions,
+people can fairly easily select a secret image from their photo collections
+and use it as the question.
+For example, if you have an old picture of your friend,
+you can use it as the question
+and use his real name as well as other similar fake names.
+
+% 画像検索とかされないようにする必要はある
+
+Of course, the photo should not have information related to the
+person's real name, since image search is fairly easy on the Web these days.
+
+% 忘れにくい{\EM}を利用する認証手法として
+% 様々な画像認証システム\cite{Biddle:2012:GPL:2333112.2333114}\cite{GraphicalPasswords}\cite{小池英樹:2006-05-15}が提案されている。
+% 複数の画像の中から正答を選択するもの(Cognometric方式)、
+% ひとつの画像の中の特定の場所を指定するもの(Locimetric方式)、
+% 画像の上で描画操作を行なうもの(Drawmetric方式)
+% が広く利用されているが\cite{Biddle:2012:GPL:2333112.2333114}\cite{GraphicalPasswords}\cite{Guideline}、
+% {\EP}は図\ref{web1}のように
+% 文字列のかわりに画像URLを{\SQ}として利用する点が異なっている。
+% %
+% Cognometric方式は{\EM}を効果的に利用できるが、
+% 多数の偽答画像が必要だという問題がある。
+% Locimetric方式は
+% {\EM}を効果的に利用できないことに加え、
+% クリックしやすい「ホットスポット」は限られているため
+% 充分なエントロピーを確保できないことが問題になる\cite{Dirik:2007:MUC:1280680.1280684}。
+% またDrawmetric方式も{\EM}を効果的に利用できないし、
+% ユーザは似た傾向のストロークを選びがちであるため
+% 充分なエントロピーを確保しにくいことが知られている\cite{Nali}。
+% %
+% {\EP}のように画像を{\SQ}として利用する場合、
+% 通常の{\SQ}の場合と同様に偽答を増やすことが容易であることに加え、
+% 画像に関連した{\EM}を有効に利用できるという利点がある\cite{増井:CSS}。
+
+% 図\ref{leiko}は
+% 本棚.org\cite{hondana}\cite{hondanaorg}
+% のユーザのひとり\footnote{
+%   \textsf{http://hondana.org/Leiko}
+% }が利用している画像認証問題である。
+% このユーザ以外には正答は見当もつかないが、
+% 本人にとっては忘れることがない{\EM}と結びついた画像だということであった。
+
+% 答を書くわけではないから安全
+% 心配ならオフラインでやれば大丈夫
+% 
+% 弱いパスワードを強くすることも簡単
+% 
+% 
+% Bookmarkletも用意した
+%   拡張機能も用意したい
+%
+
+\section{RELATED WORK}
+
+As shown in previous sections,
+there are many attemps for replacing password-based authentication systems,
+none of which has succeeded so far.
+
+Various types of image-based authentication systems have been proposed recently,
+in the hope that images are easier to remember than text
+because images are usually more directly linked to episodic memories.
+However, on many systems,
+users have to remember new information related to the images
+used in the authentication process, or
+perform special operations on the image, and
+it is not much easier than using passwords.
+%
+Image-based authentication based on episodic memories might work
+if anyone can prepare many images 
+that are tightly linked to his episodic memories.
+However, finding such images is usually not easy, and
+image-only authentication systems would not take off
+until simple and effective technique is invented.
+% [Malasym]
+
+Even when a new ideal authentication method is invented,
+replacing all the password-based systems should take very long, and
+various password managers should be used until the ideal method
+prevails in the whole world.
+In the age of password-based authentication,
+using password managers seems to be the only way to tackle
+the problem of passwords.
+%
+While most of the password managers only remember passwords given by the user,
+generating passwords with a password manager is a new approach for
+handling password-based systems.
+Just like EpisoPass generates passwords,
+Versipass\cite{Stobert:2014:PMD:2683467.2683471} %Versipass 画像のヒントからパスワード生成 % A Password Manager that Doesn’t Remember
+helps the user to generate password strings
+using ``visual cues'' on an arbitrary image.
+Instead of directly using images for authentication,
+users use the system to generate a password text with the help of
+the image shown to the user.
+
+% 様々なシステムがあるが、エピソード記憶からパスワードを直接生成するものは無い
+% 
+% パスワード管理システム
+%   沢山ある
+% 
+% 強いパスワードを作るシステム
+%   ランダムに生成するサイトが沢山ある
+% 
+% 強いパスワードを覚えるための工夫
+%   Bonneau
+% 
+% 画像を使う
+% 
+% パスワードに関する全情報を公開してどこかに置いておける
+%   ググれるかもしれない
+%   紛失する可能性が少ない
+%
+
+\section{EXPERIENCES}
+
+EpisoPass has been used by the authors for more than three years, and
+the authors are using it for various services including
+Twitter, Facebook, Amazon, Skype, etc.
+Since passwords for these services are remembered on the browser,
+EpisoPass is used only once in one week at most.
+%
+Before using EpisoPass, taking care of many passwords was really
+a pain for the authors, but
+currently all the information for generating passswords is put on the cloud
+and no trouble has been found during the period.
+
+Unfortunately EpisoPass is currently not used by many people.
+One big reason is that most people cannot fully understand the
+idea of EpisoPass and also cannot fully trust it
+because it is not operated by a big IT company nor supported by
+famous computer users.
+Another reason might be that users cannot estimate the strength
+of EpisoPass.
+Since all the questions and answers are
+quite obvious to the users,
+they might feel that everyone else also know the episode
+and easily solve all the questions.
+These kinds of psychological issues are quite important for
+an authentication system for everybody,
+and we hope to eliminate such obstacles in the future.
+
+\section{CONCLUSION}
+
+We introduced a password management system EpisoPass
+that converts a seed string into a password using the user's
+episodic memories represented as a set of questions and answers
+which can be solved only by the user.
+%
+Using EpisoPass with well-defined questions and answers,
+a user can always retrieve various passwords without worrying about
+remembering secret information.
+%
+We'll try to integrate the system with existing password-based
+services, and finally hope to eliminate all the problems
+derived from password-based authentication.
+
+% {\EM}に結びついた{\SQ}を利用して{\PW}を生成/管理できるシステム{\EP}を提案した。
+% {\EP}は単純な原理にもとづいており柔軟な利用形態が可能であり、
+% 強力な{\SQ}を用意することにより
+% 秘密情報を全く覚えることなく安全な認証を行なうことができる。
+% %
+% 強力な{\SQ}を作成して安全に運用が可能かどうかを長期的に評価したいと考えている。
+%
+%欠点:
+%なぞなぞを考えるのがめんどくさい
+%安全になぞなぞを扱うのが面倒
+%  ネットなしで運用したりとか
+%運用を間違うと思わぬところで回答がバレる可能性がある
+%
+% {\EP}は\textsf{http://Episopass.com/}で運用しており、
+% ソースはGitHubで公開している\footnote{
+%   \textsf{http://GitHub.com/masui/EpisoPass}
+% }。
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{figure}
@@
 %\includegraphics[height=6.2cm]{figures/429eec261024dc6c85351f51c12f09b4.png}
-\includegraphics[width=12cm,bb=0 0 429 386]{figures/429eec261024dc6c85351f51c12f09b4.png}
+\includegraphics[width=6cm,bb=0 0 429 386]{figures/429eec261024dc6c85351f51c12f09b4.png}
 \caption{One kernel at $x_s$ (\emph{dotted kernel}) or two kernels at
@@
 
-Please define figures (and tables) as floating objects. Please avoid
-using optional location parameters like ``\verb+[h]+" for ``here".
-
-\paragraph{Remark 1.}
-
-In the printed volumes, illustrations are generally black and white
-(halftones), and only in exceptional cases, and if the author is
-prepared to cover the extra cost for color reproduction, are colored
-pictures accepted. Colored pictures are welcome in the electronic
-version free of charge. If you send colored figures that are to be
-printed in black and white, please make sure that they really are
-legible in black and white. Some colors as well as the contrast of
-converted colors show up very poorly when printed in black and white.
-
-\subsection{Formulas}
-
-Displayed equations or formulas are centered and set on a separate
-line (with an extra line or halfline space above and below). Displayed
-expressions should be numbered for reference. The numbers should be
-consecutive within each section or within the contribution,
-with numbers enclosed in parentheses and set on the right margin --
-which is the default if you use the \emph{equation} environment, e.g.,
-\begin{equation}
-  \psi (u) = \int_{o}^{T} \left[\frac{1}{2}
-  \left(\Lambda_{o}^{-1} u,u\right) + N^{\ast} (-u)\right] dt \;  .
-\end{equation}
-
-Equations should be punctuated in the same way as ordinary
-text but with a small space before the end punctuation mark.
-
-\subsection{Footnotes}
-
-The superscript numeral used to refer to a footnote appears in the text
-either directly after the word to be discussed or -- in relation to a
-phrase or a sentence -- following the punctuation sign (comma,
-semicolon, or period). Footnotes should appear at the bottom of
-the
-normal text area, with a line of about 2~cm set
-immediately above them.\footnote{The footnote numeral is set flush left
-and the text follows with the usual word spacing.}
-
-\subsection{Program Code}
-
-Program listings or program commands in the text are normally set in
-typewriter font, e.g., CMTT10 or Courier.
-
-\medskip
-
-\noindent
-{\it Example of a Computer Program}
-\begin{verbatim}
-program Inflation (Output)
-  {Assuming annual inflation rates of 7%, 8%, and 10%,...
-   years};
-   const
-     MaxYears = 10;
-   var
-     Year: 0..MaxYears;
-     Factor1, Factor2, Factor3: Real;
-   begin
-     Year := 0;
-     Factor1 := 1.0; Factor2 := 1.0; Factor3 := 1.0;
-     WriteLn('Year  7% 8% 10%'); WriteLn;
-     repeat
-       Year := Year + 1;
-       Factor1 := Factor1 * 1.07;
-       Factor2 := Factor2 * 1.08;
-       Factor3 := Factor3 * 1.10;
-       WriteLn(Year:5,Factor1:7:3,Factor2:7:3,Factor3:7:3)
-     until Year = MaxYears
-end.
-\end{verbatim}
-%
-\noindent
-{\small (Example from Jensen K., Wirth N. (1991) Pascal user manual and
-report. Springer, New York)}
-
 \subsection{Citations}
-
-For citations in the text please use
-square brackets and consecutive numbers: \cite{jour}, \cite{lncschap},
-\cite{proceeding1} -- provided automatically
-by \LaTeX 's \verb|\cite| \dots\verb|\bibitem| mechanism.
-
-\subsection{Page Numbering and Running Heads}
-
-There is no need to include page numbers. If your paper title is too
-long to serve as a running head, it will be shortened. Your suggestion
-as to how to shorten it would be most welcome.
-
-\section{LNCS Online}
-
-The online version of the volume will be available in LNCS Online.
-Members of institutes subscribing to the Lecture Notes in Computer
-Science series have access to all the pdfs of all the online
-publications. Non-subscribers can only read as far as the abstracts. If
-they try to go beyond this point, they are automatically asked, whether
-they would like to order the pdf, and are given instructions as to how
-to do so.
-
-Please note that, if your email address is given in your paper,
-it will also be included in the meta data of the online version.
-
-\section{BibTeX Entries}
-
-The correct BibTeX entries for the Lecture Notes in Computer Science
-volumes can be found at the following Website shortly after the
-publication of the book:
-\url{http://www.informatik.uni-trier.de/~ley/db/journals/lncs.html}
 
@@
 
-\section{The References Section}\label{references}
+\bibliographystyle{splncs03}
+\bibliography{paper}
 
-In order to permit cross referencing within LNCS-Online, and eventually
-between different publishers and their online databases, LNCS will,
-from now on, be standardizing the format of the references. This new
-feature will increase the visibility of publications and facilitate
-academic research considerably. Please base your references on the
-examples below. References that don't adhere to this style will be
-reformatted by Springer. You should therefore check your references
-thoroughly when you receive the final pdf of your paper.
-The reference section must be complete. You may not omit references.
-Instructions as to where to find a fuller version of the references are
-not permissible.
-
-We only accept references written using the latin alphabet. If the title
-of the book you are referring to is in Russian or Chinese, then please write
-(in Russian) or (in Chinese) at the end of the transcript or translation
-of the title.
-
-The following section shows a sample reference list with entries for
-journal articles \cite{jour}, an LNCS chapter \cite{lncschap}, a book
-\cite{book}, proceedings without editors \cite{proceeding1} and
-\cite{proceeding2}, as well as a URL \cite{url}.
-Please note that proceedings published in LNCS are not cited with their
-full titles, but with their acronyms!
-
-\begin{thebibliography}{4}
-
-\end{thebibliography}
-
-\section*{Appendix: Springer-Author Discount}
-
-LNCS authors are entitled to a 33.3\% discount off all Springer
-publications. Before placing an order, the author should send an email, 
-giving full details of his or her Springer publication,
-to \url{orders-HD-individuals@springer.com} to obtain a so-called token. This token is a
-number, which must be entered when placing an order via the Internet, in
-order to obtain the discount.
-
-\section{Checklist of Items to be Sent to Volume Editors}
-Here is a checklist of everything the volume editor requires from you:
-
-\begin{itemize}
-\settowidth{\leftmargin}{{\Large$\square$}}\advance\leftmargin\labelsep
-\itemsep8pt\relax
-\renewcommand\labelitemi{{\lower1.5pt\hbox{\Large$\square$}}}
-
-\item The final \LaTeX{} source files
-\item A final PDF file
-\item A copyright form, signed by one author on behalf of all of the
-authors of the paper.
-\item A readme giving the name and email address of the
-corresponding author.
-\end{itemize}
 \end{document}

### 2016-08-26 paper/Password2016/paper.tex
...

@@
 convenient and strong method\cite{Bonnearu:ReplacePasswords},
-and it is not supposed to get extinct
+and it is not supposed to become extinct
 in a short period of time\cite{Herley:2009:PSS:1601990.1602010}.
@@
 or use a special hardware device
-for safely handle password managers, and
+for safely handling password managers, and
 password managers usually run on limited devices.
@@
 it is far better to ``generate'' something for the authentication,
-based on users' episodic memories which they can never forget.
+based on users' episodic memories that they can never forget.
 %
@@
 We propose a password manager \textit{EpisoPass} that generates strong passwords
-based only on the user's secret episodic memories that the user can never forget.
+based only on the user's secret episodic memories that the user cannot forget.
 
@@
 %
-Memories in human brain are not uniform.
+% Memories in human brain are not uniform.
+We keep various memories in our brain, but different memories have different natures.
 Some memories are very short-lived, and others are unforgettable.
@@
 cannot easily disappear.
-On the other hand, when we study math and try to remember a formula,
+On the other hand, when we study math and try to remember a new formula,
 it is usually hard to memorize it unless we practice a lot,
@@
 remember math formulas easily.
-%
 
@@
 
+The idea of using episodic memories for authentication is not new.
+
+**** Cognitive Passwords *******
+
 Password generation on EpisoPass is performed through the following steps:
@@
 EpisoPass substitutes characters in the seed string and generates
-random-looking password candidate strings.
+strong password candidate strings.
 After selecting all the right answers,
@@
 When a user clicks and selects one of the answers for each question,
-the seed string shown at the top-left is converted to a random-looking string
-based on the selections.
+the seed string shown at the top-left is converted to a
+candidate password string based on the selections.
 When the user selects the right answers to all the questions,
@@
 
-\begin{figure}[t]
+\begin{figure}[H]
 \centering
-\includegraphics[width=1.0\columnwidth]{figures/c1bd6e7f67698c70978f528ccd2339d9}
-\caption{Generating a Twitter password with EpisoPass.}
+% \includegraphics[width=1.0\columnwidth]{figures/c1bd6e7f67698c70978f528ccd2339d9}
+\includegraphics[width=1.0\columnwidth]{figures/4d13e6804ba790624c1f8e2b8255bde5}
+\caption{Generating an Amazon password with EpisoPass.}
 \label{web1}
@@
 and the last question is related to a more recent event
-which the author thinks he can never forget.
+which the author thinks he will never forget.
 All the questions are related to the author's episodic memories
@@
 % 時期を選択することによって簡単に{\PW}を変更することができるので便利である。
+
+\subsection{EpisoPass on browser extension}
+
+\begin{figure}[H]
+\centering
+\includegraphics[width=0.7\columnwidth]{figures/43272f2003ed8c78307110c621eb12e5}
+\caption{Running EpisoPass on Browser Extension.}
+\label{extension}
+\end{figure}
 

### 2016-08-27 paper/Password2016/paper.tex
...

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+% 問題を沢山使ってる例を出す
+% わからない問題でもいいことを示す Who's the bully? when?
+% エピソードを使う認証は多いが、パスワードを生成するものは何故かない
+%   毎日の行動から認証するものもある
+% 家族や友人が知らない秘密は存在するはず
+% 秘密の質問が駄目と言われるのは質問の質が悪いから
+%
+% ○ 拡張機能の説明
+%
+% 参考文献たくさん
+% 大きなことをいわない
+% パスワードを覚えるのは無理
+% シード文字列の選びかた
+% エントロピーの計算
+% アルゴリズムの選択 
+% 偽答生成が簡単であることを示す 
+% サポートシステムを作っていることをかく ★
 
@@
 The idea of using episodic memories for authentication is not new.
-
-**** Cognitive Passwords *******
+Early papers suggested using episodic memories for creating passwords, and
+authentication by using secret questions,
+sometimes called as ``cognitive passwords'', has long been used as an
+alternative to password-based authentication systems.
+%
+However, conversion from episodic memories to password strings
+was not studied very much. *******
 
@@
 In Figure \ref{web1},
-``\textsf{Twitter123456}'' is provided as the seed string,
+``\textsf{Amazon123456}'' is provided as the seed string,
 and according to the selections to the five questions,
 the seed string is converted to a string
-``\textsf{Lbasnln542202}'',
-which can be used as the password for Twitter.
+``\textsf{Tblgeq808187}'',
+which can be used as the password for Amazon.com.
 
@@
 the seed string is converted to another strings like
-``\textsf{Bhtuyna904127}'' (Figure \ref{web11}).
+``\textsf{Xvdkzb940345}'' (Figure \ref{web11}).
 
@@
 \centering
-\includegraphics[width=1.0\columnwidth]{figures/01e5507d090eb494a20bcbc47c86b1d2}
+\includegraphics[width=1.0\columnwidth]{figures/8447eaba1ede0f678b3ce6fea63681f3}
 \caption{Selecting a different answer.}
@@
 When we change the secret string to ``\textsf{Facebook123456}'',
-the generated password changes to ``\textsf{Zxghfbqu533131}'',
+the generated password changes to ``\textsf{Onjbrppy030937}'',
 as shown in Figure \ref{web2}.
@@
   \centering
-\includegraphics[width=1.0\columnwidth]{figures/0e2820c279afc70520482e0fc53b6ed9}
-\caption{Generating the password for FaceBook.}
+%  \includegraphics[width=1.0\columnwidth]{figures/0e2820c279afc70520482e0fc53b6ed9}
+  \includegraphics[width=1.0\columnwidth]{figures/ab4517dd593c1cabab5fecef546f7e88}
+  \caption{Generating the password for Facebook.}
   \label{web2}
@@
 calculated from concatinating all the selected answers.
+
 For example, if the user selects ``\textbf{\texttt{Ebisawa}}'' to the question ``\textbf{\texttt{Who's the bully?}}'',
@@
 % 時期を選択することによって簡単に{\PW}を変更することができるので便利である。
-
-\subsection{EpisoPass on browser extension}
-
-\begin{figure}[H]
-\centering
-\includegraphics[width=0.7\columnwidth]{figures/43272f2003ed8c78307110c621eb12e5}
-\caption{Running EpisoPass on Browser Extension.}
-\label{extension}
-\end{figure}
 
@@
 
-\section{DISCUSSIONS}
+\subsection{Using browser extension}
+
+Using the EpisoPass service or the application,
+users have to type the password string after generating the password.
+Since it is not convenient for users,
+we provide a browser extension for using EpisoPass on the login window of
+various services.
+
+Figure \ref{extension} shows the login window of Amazon.com, where
+EpisoPass questions are displayed using the browser extension.
+
+A browser extension is a JavaScript add-on program which can
+run on top of existing HTML and JavaScript.
+In this case, when the Amazon login page is accessed from the browser,
+the extension automatically runs on the page and
+gets questions from the EpisoPass server, and
+shows the questions nad candidate answers just like the Android application.
+
+After answering all the questions, a password is calculated from the
+selected answers and pasted to the password section of the page.
+Using the extension, not only users don't have to type or copy the password,
+but users don't even see the string.
+It is almost as if Amazon had provided a EpisoPass-based authentication
+for its services.
+
+\begin{figure}[H]
+\centering
+% \includegraphics[width=0.7\columnwidth]{figures/43272f2003ed8c78307110c621eb12e5}
+\includegraphics[width=0.7\columnwidth]{figures/aeff16ffcab956e554364e9e5aca8359}
+\caption{Using EpisoPass on the login window.}
+\label{extension}
+\end{figure}
+
+\section{Discussions}
 

### 2016-08-28 paper/Password2016/paper.tex
...

@@
 users have to type the password string after generating the password.
-Since it is not convenient for users,
+Since it is not convenient,
 we provide a browser extension for using EpisoPass on the login window of
@@
 
-Figure \ref{extension} shows the login window of Amazon.com, where
-EpisoPass questions are displayed using the browser extension.
-
 A browser extension is a JavaScript add-on program which can
 run on top of existing HTML and JavaScript.
+%
+Figure \ref{extension} shows the login page of Amazon.com, where
+EpisoPass questions are displayed by the browser extension.
+%
 In this case, when the Amazon login page is accessed from the browser,
-the extension automatically runs on the page and
-gets questions from the EpisoPass server, and
-shows the questions nad candidate answers just like the Android application.
-
+the extension automatically runs on the page,
+acquires questions and andwers from the EpisoPass server,
+and shows them to the user just like the Android application.
+%
 After answering all the questions, a password is calculated from the
-selected answers and pasted to the password section of the page.
-Using the extension, not only users don't have to type or copy the password,
-but users don't even see the string.
-It is almost as if Amazon had provided a EpisoPass-based authentication
-for its services.
+selected answers and pasted to the password textbox of the page.
+Using the extension, users can login to various services
+without seeing a password string;
+It looks as if various services are offering
+EpisoPass-based authentication.
 

### 2016-08-28 paper/Password2016/paper.tex
...

@@
 
-The second question in Figure \ref{web1}
+The first question in Figure \ref{web1}
 is based on the author's episodic memory at elementary school,
-and the last question is related to a more recent event
-which the author thinks he will never forget.
-All the questions are related to the author's episodic memories
-that he thinks he never forgets, and nobody else knows which one of the
-candidate answers is the right one.
+and the question with a photo at the bottom is related to a more recent event
+which the author believes he will never forget.
+All the questions are based on the author's episodic memories
+that he thinks he never forgets, and he believes that
+nobody else knows which one of the candidate is the right answer.
 
@@
 generated password is saved on the server.
-
-% {\SQ}と答はブラウザで編集でき、
-% 右上の「サーバにセーブ」ボタンを押すことにより{\SS}、秘密の問題、答のリストがサーバにセーブされる。
-% 「ファイルにセーブ」ボタンを押すとJSONデータをパソコンにダウンロードでき、
-% パソコン上のJSONデータをブラウザにドラッグ\&ドロップするとサーバにアップロードできる。
+The Q-A data in JSON format can be downloaded to the local machine
+by cliking the ``save to file'' button.
+the data can be uploaded to the server by dragging the JSON file to the EpisoPass page.
+
 % ユーザはどれが正答かを指定するわけではないので
@@
 % {\PW}を生成している。
-% {\PW}文字列の計算方法は附録に示す。
-
-%アルゴリズムはここ? Algorithm
 
@@
 calculated from concatinating all the selected answers.
-
+%
 For example, if the user selects ``\textbf{\texttt{Ebisawa}}'' to the question ``\textbf{\texttt{Who's the bully?}}'',
@@
 is used for the substitution.
-Details of the algorithm is shown in the Appendix.
-
-% 問題と回答から文字列を生成し、そのMD5値によって{\SS}を換字することにより
-% {\PW}を生成している。
-% {\PW}文字列の計算方法は附録に示す。
-
-% \subsubsection{回答選択により{\PW}を切り換え}
-% \label{pwgen}
-% 
+
+The last question in Figure \ref{web1} is not a secret question, but a question
+for generating different passwords for different situations.
+By providing such a question, users can generate completely different passwords
+for different months and years.
+
 % サービスごとに{\SS}を変えるのではなく、
@@
 % \end{figure}
-
-% 定期的に{\PW}変更を求められるシステムでは、
-% 「利用期間は?」という質問に対して
-% 「2013/1」「2013/2」のような答を用意しておけば、
-% 時期を選択することによって簡単に{\PW}を変更することができるので便利である。
 
@@
 he can use an EpisoPass application on Android
-which does not require network connection.
+which does not use network connections.
 After registering questions and answers on the EpisoPass service,
 the user can download an Android application from the server
-by clicking the ``Android app'' button.
+by clicking the ``Android app'' button at the top.
 The application contains all the information required for generating passwords.
@@
 
-\subsection{Using browser extension}
-
-Using the EpisoPass service or the application,
-users have to type the password string after generating the password.
+\subsection{Using the browser extension}
+
+When a user use the EpisoPass service or the EpisoPass application,
+he has to type or copy the password string after generating the password.
 Since it is not convenient,
 we provide a browser extension for using EpisoPass on the login window of
-various services.
+various Web services.
 
@@
 %
-Figure \ref{extension} shows the login page of Amazon.com, where
-EpisoPass questions are displayed by the browser extension.
-%
-In this case, when the Amazon login page is accessed from the browser,
-the extension automatically runs on the page,
-acquires questions and andwers from the EpisoPass server,
-and shows them to the user just like the Android application.
+Figure \ref{extension} shows the login page of Amazon.com, with which
+EpisoPass questions are automatically displayed by the browser extension.
+%
+Here, when the Amazon login page is accessed from the browser,
+the browser extension program automatically runs on the page,
+acquires questions and answers from the EpisoPass server,
+and shows them to the user just the same as the Android application.
 %
 After answering all the questions, a password is calculated from the
-selected answers and pasted to the password textbox of the page.
-Using the extension, users can login to various services
-without seeing a password string;
-It looks as if various services are offering
+selected answers and pasted to the password input form of the page.
+Using the extension, users can login to various services just by
+answering questions, without seeing any password string.
+It looks as if these services are offering
 EpisoPass-based authentication.
@@
 % \includegraphics[width=0.7\columnwidth]{figures/43272f2003ed8c78307110c621eb12e5}
-\includegraphics[width=0.7\columnwidth]{figures/aeff16ffcab956e554364e9e5aca8359}
+\includegraphics[width=0.8\columnwidth]{figures/aeff16ffcab956e554364e9e5aca8359}
 \caption{Using EpisoPass on the login window.}

### 2016-08-28 paper/Password2016/paper.tex
...

@@
 password-based authentication is still the most
-convenient and strong method\cite{Bonnearu:ReplacePasswords},
+convenient and strong method\cite{Bonneau:ReplacePasswords},
 and it is not supposed to become extinct
@@
 
-A browser extension is a JavaScript add-on program which can
-run on top of existing HTML and JavaScript.
+A browser extension is a JavaScript add-on program which runs
+on top of existing HTML and JavaScript.
 %
@@
 acquires questions and answers from the EpisoPass server,
-and shows them to the user just the same as the Android application.
+and shows them to the user just the same way as the Android application.
 %
@@
 
-\subsection{Unforgettability}
+\subsection{Recallability of answers}
 
 The biggest advantage of using EpisoPass is that
-users don't have to remember passwords of any kind and
-they can stop worrying about password-related troubles.
+users don't have to remember strong password strings.
 %
@@
 If the question is based on old unforgettable episodic memories,
-there is little chance of losing passwords.
+there is little chance of losing passwords
+as long as the seed string and the questions are available.
 If the user's memory is related to an episode of 20 years ago and the user clearly
 remembers the episode now, it is unlikely that he forgets the episode 10 years later.
+
+\subsection{Selection of seed strings}
+
+In the previous examples showing the author's real EpisoPass questions,
+a seed string ``\textsf{Amazon123456}'' was used for Amazon.com, and
+``\textsf{Facebook123456}'' was used for Facebook.
+Such strings are used because they are easily memorable.
+Of course any seed string can be used as seeds for various services,
+and automatic generation of seed strings is possible,
+although generating service specific unique seed string is not trivial.
+For example, users can use the same username and password both
+for Amazon.com and Amazon.co.uk, but not for Amazon.co.jp.
 
@@
 
+\subsection{}
+
 \subsection{Selecting good questions}
-
-% {\EP}利用において{\SQ}の選択は非常に重要である。
-% 他人が推測することが難しく、自分が決して忘れないような{\EM}を{\SQ}として利用すべきであり、
-% 以下のような性質をもつ記憶は{\SQ}として利用すべきではない。
 
@@
 
-% \begin{itemize}
-% \item \textsf{自慢になるもの
-% (何かの機会にうっかり他人に話してしまう可能性がある)}
-% 
-% \vspace{-1mm}
-% \item \textsf{ネット上に記録が残っているもの}
-% 
-% \vspace{-1mm}
-% \item \textsf{他人と情報を共有しているもの}
-% 
-% \vspace{-1mm}
-% \item \textsf{趣味や嗜好に関連するもの
-% (他人に推測されやすいうえに嗜好が変化する可能性がある)}
-% 
-% \end{itemize}
-
 \subsection{Creating fake answers}
-
-% {\SQ}の種類によっては偽答の生成が難しい場合がある。
-% 図\ref{atmega}は電子工作に関する{\SQ}の例であるが、
-% 正答と区別がつかない偽答を充分リストすることは難しい。
 
@@
 because possible answers are limited.
-%
-% \begin{figure}[H]
-% \centerline{\includegraphics[width=83mm,bb=0 0 512 113]{../figures/2f63ceb9ab6faf8d81393953f2f95a8c.png}}
-% \caption{偽答の生成が難しい例.}
-% \label{atmega}
-% \end{figure}
-%
-% 一方、正答として人名や地名を利用する場合、
-% 正答に似た人名や地名をリストすることは難しくない。
-% 「世田谷」が正答であるとき、
-% 「目黒」「杉並」のような偽答を用意するのは簡単である。
 %
@@
 
-% 正答と同じカテゴリに属する単語を自動的にリストすることができれば
-% 正答をもとにして簡単に偽答のリストを生成することができる。
 In this way, fake answers can be easily generated
@@
 %
-% ひとつの単語もしくは単語の集合と同じカテゴリに属する単語を検索する手法は
-% 「同位語検索」と呼ばれ、
-% Webのデータを利用した様々な同位語検索システムが提案されている%
 Various methods have been proposed for collecting words in the
@@
 %\cite{大島裕明:2006-12-15}.% ライバルサーチ「やーやら」
-We can use such techniques for getting similar names.
+Using such systems, we can get a list of fake answers almost automatically.
 
@@
 since choosing a good password is not intuitive and
-people forget passwords frequently.
+people forget passwords very easily.
 %
@@
 required for the service.
+%
+Our experience of using browser extensions suggests that
+that approach is worth consideration.
 
@@
 to strengthen security.
+
+*****Shneier******
+
 %
@@
 
-\subsection{Risk of password leak}
-
-EpisoPass is just a string-conversion system and it does not
-have any information on which one is the correct answer.
-Also, it does not save any password information in any form, and
-it is almost impossible to get the right password 
-without having the episodic memory.
-
-% 聞かれてもわからないし書き留める必要がないからウッカリもらす可能性はない
-% ローカルに実行すればネットでもれる心配もない
-
-Since the password is generated by the algorithm and the password
-string is not kept on a computer in any form,
-unexpected leak of the password is unlikely.
-The user doesn't have to remember the password string, and
-there is no chance he will reveal it to somebody
-even when he is forced to tell the password.
-
-% \subsection{Strong passwords can be generated}
-%   強度を自由に設定できる
-
-\subsection{Simplicity}
-
-The algorithm of generating a password (shown in Appendix)
-is fairly simple and
-it can be implemented on any browser JavaScripts or
-applications on smartphones and small devices.
+% \subsection{Risk of password leak}
+% 
+% EpisoPass is just a string-conversion system and it does not
+% have any information on which one is the correct answer.
+% Also, it does not save any password information in any form, and
+% it is almost impossible to get the right password 
+% without having the episodic memory.
+% 
+% Since the password is generated by the algorithm and the password
+% string is not kept on a computer in any form,
+% unexpected leak of the password is unlikely.
+% The user doesn't have to remember the password string, and
+% there is no chance he will reveal it to somebody
+% even when he is forced to tell the password.
+
+\subsection{Using shared secrets}
+
+% \subsection{Simplicity}
+% 
+% The algorithm of generating a password (shown in Appendix)
+% is fairly simple and
+% it can be implemented on any browser JavaScripts or
+% applications on smartphones and small devices.
+
+\subsection{Hash function}
 
@@
 
-% 問題自体が秘密であればひとつ漏れても大丈夫
-% 
-% {\SQ}を公開している場合、
-% {\SS}と{\PW}の対応がひとつでも漏洩してしまうと、
-% 総当たり計算でチェックすることにより、
-% すべて{\SQ}の正答が判明してしまう。
-% {\SQ}の正答を知っていれば
-% {\SS}から{\PW}を計算することができるので、
-% 漏洩した{\SQ}は利用不可能になってしまう。
-%
-% \ref{pattern1}や
-% \ref{pattern2}のような運用をしている場合は
-% {\PW}がひとつ漏洩しても他の{\PW}は安全だが、
-% \ref{pattern3}のような運用をしている場合は
-% ひとつでも{\PW}が漏洩するとあらゆる{\PW}が漏洩してしまうことになる。
-
 \subsection{Using images}
@@
 
-% 忘れにくい{\EM}を利用する認証手法として
-% 様々な画像認証システム\cite{Biddle:2012:GPL:2333112.2333114}\cite{GraphicalPasswords}\cite{小池英樹:2006-05-15}が提案されている。
-% 複数の画像の中から正答を選択するもの(Cognometric方式)、
-% ひとつの画像の中の特定の場所を指定するもの(Locimetric方式)、
-% 画像の上で描画操作を行なうもの(Drawmetric方式)
-% が広く利用されているが\cite{Biddle:2012:GPL:2333112.2333114}\cite{GraphicalPasswords}\cite{Guideline}、
-% {\EP}は図\ref{web1}のように
-% 文字列のかわりに画像URLを{\SQ}として利用する点が異なっている。
-% %
-% Cognometric方式は{\EM}を効果的に利用できるが、
-% 多数の偽答画像が必要だという問題がある。
-% Locimetric方式は
-% {\EM}を効果的に利用できないことに加え、
-% クリックしやすい「ホットスポット」は限られているため
-% 充分なエントロピーを確保できないことが問題になる\cite{Dirik:2007:MUC:1280680.1280684}。
-% またDrawmetric方式も{\EM}を効果的に利用できないし、
-% ユーザは似た傾向のストロークを選びがちであるため
-% 充分なエントロピーを確保しにくいことが知られている\cite{Nali}。
-% %
-% {\EP}のように画像を{\SQ}として利用する場合、
-% 通常の{\SQ}の場合と同様に偽答を増やすことが容易であることに加え、
-% 画像に関連した{\EM}を有効に利用できるという利点がある\cite{増井:CSS}。
-
-% 図\ref{leiko}は
-% 本棚.org\cite{hondana}\cite{hondanaorg}
-% のユーザのひとり\footnote{
-%   \textsf{http://hondana.org/Leiko}
-% }が利用している画像認証問題である。
-% このユーザ以外には正答は見当もつかないが、
-% 本人にとっては忘れることがない{\EM}と結びついた画像だということであった。
-
-% 答を書くわけではないから安全
-% 心配ならオフラインでやれば大丈夫
-% 
-% 弱いパスワードを強くすることも簡単
-% 
-% 
-% Bookmarkletも用意した
-%   拡張機能も用意したい
-%
-
-\section{RELATED WORK}
+\section{Related Work}
+
+% 様々なシステムがあるが、エピソード記憶からパスワードを直接生成するものは少ない
 
@@
 none of which has succeeded so far.
+
+Various authentication systems have been proposed for replacing
+passwords, but none of them are found to be better than
+password-related systems\ref{Bonneau:ReplacePasswords}.
+
+Although cognitive password systems have been studied for a
+long time\ref{xxx}\ref{ZZZZ},
+they were meant to be implemented as a replacement to password-based systems,
+and few system has tried to convert episodic memories into passwords.
+
+% 普段の行動を質問に利用する[][]
+
+\ref{Dandapat:2015:AYD:2702123.2702457} % 日常行動からパスワード作るActivePass
+  % これはパスワードを作るのか
+\ref{Das:2013:ECE:2493432.2493453} % スマホの利用状況を認証に使う
+\ref{conf/percom/GuptaWRLGB12} % スマホの利用状況を認証に使う
+% これはEpisodicMemoryと関係ないなぁ
+
+The idea of using episodic memories for user authtication is also not new.
+In fact, using episodic memories for selecting password is gnerally recommended[],
+and many current computer users are probably using password that are
+related their episodic memories in some way.
 
@@
 
-% 様々なシステムがあるが、エピソード記憶からパスワードを直接生成するものは無い
-% 
-% パスワード管理システム
-%   沢山ある
+% パスワードに変換するシステムはみつからない
 % 

### 2016-08-28 paper/Password2016/paper.tex
...

@@
 
-% 問題を沢山使ってる例を出す
+% ○ 問題を沢山使ってる例を出す
 % わからない問題でもいいことを示す Who's the bully? when?
-% エピソードを使う認証は多いが、パスワードを生成するものは何故かない
-%   毎日の行動から認証するものもある
+% ○エピソードを使う認証は多いが、パスワードを生成するものは何故かない
+% ○  毎日の行動から認証するものもある
 % 家族や友人が知らない秘密は存在するはず
@@
 %
-% 参考文献たくさん
+% ○ 参考文献たくさん
 % 大きなことをいわない
 % パスワードを覚えるのは無理
-% シード文字列の選びかた
+% ○ シード文字列の選びかた
 % エントロピーの計算
@@
 %
-% According to Flor\^{e}ncio,
 According to a research in 2007,
@@
 4.28\% of the users forget their passwords in 3 months\cite{Florencio:2007:LSW:1242572.1242661}.
-
-%また2011年の野村総研の調査によれば、
-%一般的なユーザが{\PW}認証を行なうサイトは平均19.4個で、
-%利用している{\PW}は平均3.1個であった\cite{野村総研}。
-%多数の{\PW}を記憶することが困難であるため、
-%多くのユーザが同じ{\PW}を複数サイトで使い回しているのだと思われる。
-
-% People are frequently asked to register a password when
-% they try to use a new service.
-
-% もっと別の認証もいろいろ提案されている
-%   画像認証[MALASYM][その他いろいろ]
-%   
-%   特殊ハードのような持ち物を使う方法など[Pico][YubiKey][RSA]
-%   生体認証 指紋認証
-%   行動からの認証[]
-%   位置ベースの認証[SOUPS]
-%  完全置き換えはしばらくは不可能だろう
 
@@
 
-% % なのでパスワードと生きる方法が工夫されている
-% %   強いパスワードを考える方法[]
-% %     覚える方法が提案されてたり[Bonneau]
-% %       万人むけはむり
-
-% パスワードが死滅しないならパスワードと生きる方法が必要である
-%   たとえば様々なパスワード管理システム[][][][]の利用がすすめられている
-%   しかしマスターパスワードがいったり特殊ハードがいったりする
-%   特殊システムがいる場合がある
-%   特殊ハードやソフトは利用がどうしても難しい
-
 If we have to live with password-based authentication systems,
@@
 \cite{Dashlane}%
-\cite{ミルパス}%
+\cite{MilPass}%
 \cite{LastPass}%
@@
 %
-%{\PW}管理システムは
-%ひとつの「マスター{\PW}」を利用して他のすべての{\PW}を管理するもので、
-%暗号化されたデータベースに{\PW}を格納するもの%
-%
 Most password managers can manage various passwords by
 asking users to remember a single ``master password'' to access the database.
-%
-%が多いが、サービス名をもとにマスター{\PW}を変換することによって
-%複数の{\PW}を生成するシステム\cite{SuperGenPass}もある。
-%両者ともにマスター{\PW}の記憶は必須であり、
-%マスター{\PW}を盗まれたり忘れたりする危険がある。
 %
@@
 
-The idea of using episodic memories for authentication is not new.
+The idea of using episodic memories for authentication has a long history.
 Early papers suggested using episodic memories for creating passwords, and
 authentication by using secret questions,
-sometimes called as ``cognitive passwords'', has long been used as an
+sometimes called as ``cognitive passwords''\cite{Zviran:1990:UAC:100512.100538},
+has long been used as an
 alternative to password-based authentication systems.
@@
 However, conversion from episodic memories to password strings
-was not studied very much. *******
+was not studied at all.
 
@@
 
-% {\SS}として「\textsf{Twitter123456}」という文字列を指定しており、
-% 4個の{\SQ}に対する回答選択に応じて
-% 「\textsf{Mfveabn574923}」のような{\PW}候補が生成される。
-% 異なる答をを選択すると全く異なる文字列が生成される。
-% {\SS}の8文字目が数字である場合は{\PW}の8文字目も数字になるなど、
-% {\SS}の文字種に対応した{\PW}候補が生成される。
-
 The first question in Figure \ref{web1}
@@
 
-% ユーザはどれが正答かを指定するわけではないので
-% 問題データを見てもユーザの{\PW}はわからない。
-
 When we change the secret string to ``\textsf{Facebook123456}'',
@@
 
-% {\PW}文字列の計算方法}
-% 問題と回答から文字列を生成し、そのMD5値によって{\SS}を換字することにより
-% {\PW}を生成している。
-
 Character substitution is performed based on the hash value
@@
 By providing such a question, users can generate completely different passwords
-for different months and years.
-
-% サービスごとに{\SS}を変えるのではなく、
-% 図\ref{web3}のように
-% サービス名に応じて回答を変えることによって異なる{\PW}を作成することも可能である。
-% {\PW}としての長さや文字種に特種な制約が無いサービスに関してはこの方法が便利である。
-% 
-% \begin{figure}[H]
-% \centerline{\includegraphics[width=83mm,bb=0 0 718 428]{../WISS/figures/a9167a6ec6af9c70dd1617e3fc25ec30.png}}
-% \centerline{\includegraphics[width=83mm,bb=0 0 718 428]{../WISS/figures/5b887fabeb8e3319623901fe4a6c56f2.png}}
-% \caption{サービス名に対応する回答で異なる{\PW}を生成.}
-% \label{web3}
-% \end{figure}
+for different months and years, for example.
 
 \subsection{Android application}
-
-% Webサービスを利用する場合、ブラウザとサーバとの間の通信を
-% 記録されたり盗み見されたりされる心配を完全に払拭することはできない。
-% % 危険を完全になくすことはできない。
-% 前述の例において、
-% {\PW}はブラウザ内部でJavaScriptにより生成されるので、
-% 一度ページを表示した後は
-% ネットワークを遮断しても{\PW}計算を行なえるようになっているが、
-% 最初から全く通信を行なわずに{\PW}を作成できる方がより安心であろう。
-% このため、通信を全く行なわずにマシン単体で{\PW}計算を行なうための
-% Androidアプリを用意した。
-% ページの右上の「Androidアプリ」ボタンを押すと、
-% 現在表示している秘密の問題と答を内蔵したAndroidアプリが
-% サーバ上でビルドされてダウンロードされる。
 
@@
 
-% Android端末でアプリを実行すると図\ref{android1}のような画面が表示される。
-% {\SS}を設定して「開始」ボタンを押すと図\ref{android2}のように質問がひとつずつ表示され、
-% ボタンを押してすべて回答すると{\PW}が計算され図\ref{android3}のように表示される。
-
-When the user runs the application and selects the right answer
+When the user runs the application and selects the correct answer
 to each question, he can eventually get the password and copy it to the password entry.
@@
 
-% 回答入力と{\PW}計算はAndroid端末で実行されるため、
-% 端末を「機内モード」に設定するなどの方法で
-% ネットワーク接続を遮断した状態でも{\PW}を計算することができる。
-% {\EP}をインストールしたAndroid端末を持っていれば常に各種の{\PW}を計算できるので、
-% 他人のマシンや公共の場所に設置されたパソコンなどでも
-% 容易にtwitterなどのネットサービスを利用することができる。
-
-% The calculation is performed on Android without network connection,
-% and the user can safely generate passwords 
-% without feeling the fear of ...
-
-% 前述の方法で{\EP}アプリをサーバからダウンロードする場合は、
-% ブラウザ上で秘密の問題をサーバに登録する必要があるが、
-% 秘密の問題を全くネット上に露出することなくアプリを利用することもできる。
+The calculation is performed on Android without network connection,
+and the user can safely generate passwords 
+without feeling the fear of being observed by attackers
 
@@
 \centering
-% \includegraphics[width=0.7\columnwidth]{figures/43272f2003ed8c78307110c621eb12e5}
 \includegraphics[width=0.8\columnwidth]{figures/aeff16ffcab956e554364e9e5aca8359}
@@
 
-In this section, we discuss the advantages and caveats of
-using EpisoPass.
+In this section, we discuss the advantages and caveats of using EpisoPass.
 
@@
 \cite{Hayashi:2011:DSP:1978942.1979326}%
-\cite{Komanduri:2011:PPM:1978942.1979321}, % どういうパスワードが強いか
+\cite{Komanduri:2011:PPM:1978942.1979321}, % What password is strong
 but the strength of secret questions has not been studied enough.
-%
-% {\EP}で選択枝が10個の{\SQ}を8個使用する場合、
-% 総当たりで{\PW}を生成するには
-% 1億($10^8$)通りの試行が必要であり、
-% % エントロピーは26.6 ($ = 8 \times \log_2 10$) ビット
-% エントロピーは26.6ビットとなる。
 %
@@
 %
-% 英字からランダムに8文字を並べて作成した{\PW}のエントロピーは37.6ビットになるが、
-% ``\textsf{pmvixuzq}''のように全く意味のない{\PW}を記憶して利用することは少ないため、
-% 実際に利用される{\PW}のエントロピーは20ビット程度と考えられているので\cite{NIST}、
-% {\SQ}と選択枝の数を10個程度用意すれば
-% 通常の{\PW}と同程度の強度が期待できることになる。
-%
 It is almost the same entropy as using random 8-character English alphabets
@@
 where online brute-force attack is impossible\cite{Florencio:2007:SWP:1361419.1361429}.
-
-\subsection{}
 
@@
 same category, mainly for information retrieval tasks%
-\cite{Huang:2012:LFC:2426725.2426728}% 読んでないけど
-\cite{BooWa}% Boo!Wa!というサイトをやっている
-\cite{Wang:2007:LSE:1441428.1442086}.% BooWa
-%\cite{大島裕明:2006-12-15}.% ライバルサーチ「やーやら」
+\cite{Huang:2012:LFC:2426725.2426728}% 
+\cite{BooWa}% Boo!Wa!
+\cite{Wang:2007:LSE:1441428.1442086}.% 
 Using such systems, we can get a list of fake answers almost automatically.
@@
 to strengthen security.
-
-*****Shneier******
-
+%
+Such a practice is not recommended these days
+because humans cannot create strong passwords frequently\cite{Schneier:change}.
 %
@@
 Using EpisoPass, users can just provide a date-related question
-like the first question shown in Figure \ref{web1},
+like the last question shown in Figure \ref{web1},
 and generate different strong passwords based on the answer.
@@
 
-% \subsection{Risk of password leak}
+% \subsection{Using shared secrets}
 % 
-% EpisoPass is just a string-conversion system and it does not
-% have any information on which one is the correct answer.
-% Also, it does not save any password information in any form, and
-% it is almost impossible to get the right password 
-% without having the episodic memory.
-% 
-% Since the password is generated by the algorithm and the password
-% string is not kept on a computer in any form,
-% unexpected leak of the password is unlikely.
-% The user doesn't have to remember the password string, and
-% there is no chance he will reveal it to somebody
-% even when he is forced to tell the password.
-
-\subsection{Using shared secrets}
-
 % \subsection{Simplicity}
@@
 % applications on smartphones and small devices.
-
-\subsection{Hash function}
+%
+% \subsection{Hash function}
 
@@
 As shown in previous sections,
-there are many attemps for replacing password-based authentication systems,
-none of which has succeeded so far.
-
-Various authentication systems have been proposed for replacing
-passwords, but none of them are found to be better than
-password-related systems\ref{Bonneau:ReplacePasswords}.
-
+there have been many attemps for replacing password-based authentication systems,
+but none of them are found to be better than
+password-based systems\cite{Bonneau:ReplacePasswords}.
+%
 Although cognitive password systems have been studied for a
-long time\ref{xxx}\ref{ZZZZ},
-they were meant to be implemented as a replacement to password-based systems,
-and few system has tried to convert episodic memories into passwords.
+long time\cite{Lazar2011}\cite{Zviran:1990:UAC:100512.100538},
+they were implemented as a replacement to password-based systems,
+and no password-generation system have been proposed
+based on cognitive authentication.
 
 % 普段の行動を質問に利用する[][]
-
-\ref{Dandapat:2015:AYD:2702123.2702457} % 日常行動からパスワード作るActivePass
+% \ref{Dandapat:2015:AYD:2702123.2702457} % 日常行動からパスワード作るActivePass
 % これはパスワードを作るのか
-\ref{Das:2013:ECE:2493432.2493453} % スマホの利用状況を認証に使う
-\ref{conf/percom/GuptaWRLGB12} % スマホの利用状況を認証に使う
+% \ref{Das:2013:ECE:2493432.2493453} % スマホの利用状況を認証に使う
+% \ref{conf/percom/GuptaWRLGB12} % スマホの利用状況を認証に使う
 % これはEpisodicMemoryと関係ないなぁ
 
-The idea of using episodic memories for user authtication is also not new.
-In fact, using episodic memories for selecting password is gnerally recommended[],
+The idea of using episodic memories for authtication is not new.
+In fact, using episodic memories for selecting password
+has generally been recommended,
 and many current computer users are probably using password that are
-related their episodic memories in some way.
+in some way related to their episodic memories.
 
-Various types of image-based authentication systems have been proposed recently,
+Recently, people are trying to use mobile devices for authentication,
+because mobile devices remember all the user's behaviors and
+the user can easily recall what he did%
+\cite{Dandapat:2015:AYD:2702123.2702457}%
+\cite{Das:2013:ECE:2493432.2493453}%
+\cite{GuptaWRLGB12}%
+.
+For example, if a user can answer questions like
+``who did you call last night?'' correctly, the authentication will succeed.
+Using mobile or wearable devices for authentication works in many cases,
+but users should have a fairly good long-term memory about their behaviors,
+and that not easy for everybody.
+
+Various types of image-based authentication systems have been proposed recently%
+\cite{Biddle:2012:GPL:2333112.2333114}\cite{GraphicalPasswords},
 in the hope that images are easier to remember than text
@@
 perform special operations on the image, and
-it is not much easier than using passwords.
+it is not much easier than remembering passwords.
 %
@@
 until simple and effective technique is invented.
-% [Malasym]
 
@@
 various password managers should be used until the ideal method
-prevails in the whole world.
+prevails in the world.
 In the age of password-based authentication,
@@
 
-% パスワードに変換するシステムはみつからない
-% 
 % 強いパスワードを作るシステム
@@
 % 
-% 強いパスワードを覚えるための工夫
+% 強いパスワードを覚えるための工夫 ★
 %   Bonneau
-% 
-% 画像を使う
 % 
@@
 
-\section{EXPERIENCES}
+\section{Experiences}
 
@@
 Twitter, Facebook, Amazon, Skype, etc.
-Since passwords for these services are remembered on the browser,
-EpisoPass is used only once in one week at most.
+% Since passwords for these services are remembered on the browser,
+% EpisoPass is used only once in one week at most.
 %
@@
 and no trouble has been found during the period.
+%
+After the introduction of browser extension,
+logging into various services became even easier,
+because visiting the EpisoPass service is unneccesary.
 
@@
 
-\section{CONCLUSION}
+\section{Conclusion}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}
-\centering
-% \includegraphics[height=6.2cm]{eijkel2}
-%\includegraphics[height=6.2cm]{figures/429eec261024dc6c85351f51c12f09b4.png}
-\includegraphics[width=6cm,bb=0 0 429 386]{figures/429eec261024dc6c85351f51c12f09b4.png}
-\caption{One kernel at $x_s$ (\emph{dotted kernel}) or two kernels at
-$x_i$ and $x_j$ (\textit{left and right}) lead to the same summed estimate
-at $x_s$. This shows a figure consisting of different types of
-lines. Elements of the figure described in the caption should be set in
-italics, in parentheses, as shown in this sample caption.}
-\label{fig:example}
-\end{figure}
 
-\subsection{Citations}
+% \subsection{Citations}
 

### 2016-08-29 paper/Password2016/paper.tex
Davidの修正追加中

@@
 
+\usepackage{marginnote}
+
 \usepackage{here} % [H]とするとその場所に配置されるらしい
@@
 \usepackage{url}
-\urldef{\mailsa}\path|masui@pitecan.com|
+% \urldef{\mailsa}\path|masui@pitecan.com|
+\urldef{\mailsa}\path|***@***.***.***|
 \newcommand{\keywords}[1]{\par\addvspace\baselineskip
@@
 % a short form should be given in case it is too long for the running head
-\titlerunning{Lecture Notes in Computer Science: Authors' Instructions}
+\titlerunning{EpisoPass: Password Management based on Episodic Memories}
 
@@
 %
-\author{Toshiyuki Masui%
-\thanks{Thanks...}%
+% \author{Toshiyuki Masui%
+\author{***** ****
+% \thanks{Thanks...}%
 }
@@
 % unless you accept that it will be published
-\institute{Faculty of Environment and Information Studies, Keio University\\
-5322 Endo, Fujisawa, Kanagawa 252-8520, Japan\\
+%\institute{Faculty of Environment and Information Studies, Keio University\\
+%5322 Endo, Fujisawa, Kanagawa 252-8520, Japan\\
+%\mailsa\\
+%\url{http://pitecan.com/}}
+\institute{******* ******* ******* *******\\
+******, ****** *******, *******\\
 \mailsa\\
-\url{http://pitecan.com/}}
+% \url{http://pitecan.com/}}
+\url{http://*****.***.***/}}
 
@@
 \section{Introduction}
-% Passwordは使われている
+
+Passwords have been used as a means of authenticating to Web services
+and applications for a long time, and remain the most popular
+authentication method on the Internet.
 %
-% Passwordが辛いのは一般的事実である[?]
-%   基本的に強くするには長くしなければならない
-%   忘れる
-%   覚えられない
-%   サービスごとにパスワードは変えるべきである[?] でも無理
-%   定期的に更新させられる
-% 強いパスワードを頭で覚えて管理するのは不可能
-%       特に弱者には
-%   パスワード作成アルゴリズムを自力で使っている人もいるがそれは難しい
+Since short passwords are easily guessable by attackers and using the
+same password for multiple services is unsafe, a different long
+password should be used for each service a person uses.  However,
+remembering numerous long passwords is almost impossible for ordinary
+humans.
+%
+According to research conducted by Flor\^{e}ncio {\it et al.\/} in 2007,
+people use on average only 6.5 different passwords to access 25 Web services, and
+4.28\% of users forget their passwords within 3 months \cite{Florencio:2007:LSW:1242572.1242661}.
 
-Passwords have been used for various Web services and applications
-for a long time, and currently the most popular authentication method on the Internet.
-%
-Since short passwords are easily guessed by attackers and
-using the same password for different services is unsafe,
-different long passwords should be used for different services.
-However,
-remembering many long passwords is almost impossible for ordinary humans.
-%
-According to a research in 2007,
-people use 6.5 passwords on 25 Web services on average, and
-4.28\% of the users forget their passwords in 3 months\cite{Florencio:2007:LSW:1242572.1242661}.
-
-Since passwords are difficult to handle,
-various other authentication methods have been proposed.
-For example,
-image-based authentication\cite{Biddle:2012:GPL:2333112.2333114}\cite{GraphicalPasswords}, 
+Since passwords are difficult to handle, various other authentication methods have been proposed.
+For example, image-based authentication\cite{Biddle:2012:GPL:2333112.2333114,GraphicalPasswords},
 biometrics authentication\footnote{
   % \textsf{https:{\slash}{\slash}en.wikipedia.org{\slash}wiki{\slash}Biometrics}
-  \url{https://en.wikipedia.org/wiki/Biometrics}
+  % \url{https://en.wikipedia.org/wiki/Biometrics}
+  \url{https://en.wikipedia.org/w/index.php?title=Biometrics&oldid=736189000}
 },
-behavior-based authentication\cite{Dandapat:2015:AYD:2702123.2702457}, 
-and many other authentication methods have been proposed.
+behavior-based authentication\cite{Dandapat:2015:AYD:2702123.2702457}, and many others.
 
@@
 
-However,
-password-based authentication is still the most
-convenient and strong method\cite{Bonneau:ReplacePasswords},
-and it is not supposed to become extinct
-in a short period of time\cite{Herley:2009:PSS:1601990.1602010}.
+However, password-based authentication is still the most
+convenient and widely deployed method \cite{Bonneau:ReplacePasswords},
+and is not expected to disappear any time soon \cite{Herley:2009:PSS:1601990.1602010}.
 
-If we have to live with password-based authentication systems,
-we have to devise some ways to handle many passwords, and
-various ``password managers'' have been proposed
-\cite{OnePassword}%
-\cite{Dashlane}%
-\cite{MilPass}%
-\cite{LastPass}%
-\cite{KeyPass}%
-\cite{NortonIDSafe}%
-\cite{IDManager}.
+Given we will have to continue to live with password-based
+authentication systems for the foreseeable future, we have to devise
+practical methods for handling many passwords, and various ``password
+managers''
+have been proposed\cite{OnePassword,Dashlane,MilPass,LastPass,KeyPass,NortonIDSafe,IDManager}.
 %
-Password managers remember users' passwords and help them enter
-passwords on various services.
+Password managers remember users' passwords and aim to directly enter
+them into the login pages of the various services a user wants to
+access.
 %
-Most password managers can manage various passwords by
-asking users to remember a single ``master password'' to access the database.
+The burden on the user is reduced by requiring just a single ``master
+password'' to access the database of stored passwords.
 %
-Although password managers are useful,
-users have to remember the master password
-or use a special hardware device
-for safely handling password managers, and
-password managers usually run on limited devices.
+Although password managers are widely used and a clear step forward
+from having to remember multiple passwords, uses nonetheless have to
+remember the master password or use a special hardware device for
+safely handling the password database, and password managers usually
+run on only a limited set of devices.
 
@@
 
-If we don't want to carry any special device for authentication,
-all the information required for the authentication should be
-kept in the brain.
+If we want to avoid having to carry any special device for
+authentication, either we must used some form of biometrics, or all
+the information required for the authentication must be must be stored
+in the user's memory.
 %
-However, the biggest problem of brain-based authentication is that
-users cannot safely keep memories like long passwords or master password.
-For this reason, we believe that
-it is far better to ``generate'' something for the authentication,
-based on users' episodic memories that they can never forget.
+However, the biggest problem with memory-based authentication is that
+users cannot reliably remember passwords or master password that are
+long and complex enough to be secure.
+
+For this reason, we believe that it is far better to ``generate''
+something for the authentication, based on a user's episodic
+memories. This has the benefit that unlike a password, a person is
+highly unlikely to forget such episodic memories.
 %
@@
 %
-We propose a password manager \textit{EpisoPass} that generates strong passwords
-based only on the user's secret episodic memories that the user cannot forget.
+We therefore propose \textit{EpisoPass}, a password manager that
+generates strong passwords based only on a user's secret and
+unforgettable episodic memories.
 
@@
 
-EpisoPass is a password manager that supports generating
-strong passwords based on users' secret episodic memories.
+EpisoPass is a password manager that supports the generation of
+strong passwords based on a user's secret episodic memories.
 %
@@
 % Memories in human brain are not uniform.
-We keep various memories in our brain, but different memories have different natures.
-Some memories are very short-lived, and others are unforgettable.
-When we have a very impressive experience,
-that memory will stay in the brain for a long time and
-cannot easily disappear.
-On the other hand, when we study math and try to remember a new formula,
-it is usually hard to memorize it unless we practice a lot,
-since the knowledge about the formula is not related to
-any personal experiences.
-The former type of memory is called the episodic memory and
-people cannot easily lose it.
-Memories of passwords belong to the latter type and
-people cannot easily remember them, just like people cannot
-remember math formulas easily.
+Our brains store numerous memories, but different memories have
+different characteristics.  Some memories are very short-lived, while
+others are recallable for long periods of time.  When we have a
+particularly impressive experience, the memory of it will stay in our
+mind for a long time and can't be easily forgotten.  On the other
+hand, other topics are more difficult to remember. For example, when
+studying mathematics and trying to remember a new formula, it can be
+hard to memorize without significant practice, since knowledge of the
+formula is unrelated to any personal experiences.
+The former type of memory is called an {\it episodic\/} memory and most people find such
+memories easy to recollect and hard to forget.
+Memories of passwords belong in the latter category. People find them
+hard to remember and easy to forget, in the same way people find it difficult
+ to remember mathematical formulas.
 
@@
 The idea of using episodic memories for authentication has a long history.
-Early papers suggested using episodic memories for creating passwords, and
-authentication by using secret questions,
+Early papers suggested using episodic memories for creating passwords.
+Authentication by using secret questions,
 sometimes called as ``cognitive passwords''\cite{Zviran:1990:UAC:100512.100538},
@@
 %
-However, conversion from episodic memories to password strings
-was not studied at all.
+% However, conversion from episodic memories to password strings
+% was not studied at all.
 
@@
 
+\begin{figure}[H]
+\centering
+% \includegraphics[width=1.0\columnwidth]{figures/c1bd6e7f67698c70978f528ccd2339d9}
+\includegraphics[width=1.0\columnwidth]{figures/4d13e6804ba790624c1f8e2b8255bde5}
+\caption{Generating an Amazon password with EpisoPass.}
+\label{web1}
+\end{figure}
+
 \subsection{Using EpisoPass on a browser}
@@
 candidate password string based on the selections.
-When the user selects the right answers to all the questions,
+When the user selects the correct answers to all the questions,
 the right password is calculated and shown at the top.
@@
 % use the converted string as the password.
-
-\begin{figure}[H]
-\centering
-% \includegraphics[width=1.0\columnwidth]{figures/c1bd6e7f67698c70978f528ccd2339d9}
-\includegraphics[width=1.0\columnwidth]{figures/4d13e6804ba790624c1f8e2b8255bde5}
-\caption{Generating an Amazon password with EpisoPass.}
-\label{web1}
-\end{figure}
 
@@
 The Q-A data in JSON format can be downloaded to the local machine
-by cliking the ``save to file'' button.
+by clicking the ``save to file'' button.
 the data can be uploaded to the server by dragging the JSON file to the EpisoPass page.
@@
 Character substitution is performed based on the hash value
-calculated from concatinating all the selected answers.
+calculated from concatenating all the questions and selected answers.
 %
-For example, if the user selects ``\textbf{\texttt{Ebisawa}}'' to the question ``\textbf{\texttt{Who's the bully?}}'',
-a hash value calculated from  ``\textbf{\texttt{Who's the bully:Ebisawa}}''
-is used for the substitution.
+For example, if the user selects ``\textbf{\texttt{Ebisawa}}''
+to the question ``\textbf{\texttt{Who's the bully?}}'',
+a string including ``\textbf{\texttt{Who's the bully:Ebisawa}}''
+is used for calculating the hash value.
 
@@
 
-If a user doesn't like to use EpisoPass service on the Net,
+If a user doesn't like to use the EpisoPass service on the Net,
 he can use an EpisoPass application on Android
@@
 and the user can safely generate passwords 
-without feeling the fear of being observed by attackers
+without feeling the fear of being observed by attackers.
 
 \subsection{Using the browser extension}
+\label{extensionsection}
 
@@
 A browser extension is a JavaScript add-on program which runs
-on top of existing HTML and JavaScript.
+on top of existing Web pages.
 %
@@
 After answering all the questions, a password is calculated from the
-selected answers and pasted to the password input form of the page.
+selected answers and pasted to the password field of the page.
 Using the extension, users can login to various services just by
@@
 \centering
-\includegraphics[width=0.8\columnwidth]{figures/aeff16ffcab956e554364e9e5aca8359}
+\includegraphics[width=0.9\columnwidth]{figures/aeff16ffcab956e554364e9e5aca8359}
 \caption{Using EpisoPass on the login window.}
@@
 
-In the previous examples showing the author's real EpisoPass questions,
+In the previous examples showing the author's EpisoPass questions,
 a seed string ``\textsf{Amazon123456}'' was used for Amazon.com, and
@@
 Of course any seed string can be used as seeds for various services,
-and automatic generation of seed strings is possible,
-although generating service specific unique seed string is not trivial.
-For example, users can use the same username and password both
-for Amazon.com and Amazon.co.uk, but not for Amazon.co.jp.
+and automatic generation of seed strings is possible.
+
+% although generating service-specific unique seed string is not trivial.
+% For example, users can use the same username and password both
+% for Amazon.com and Amazon.co.uk, but not for Amazon.co.jp.
 
@@
 %
-It is almost the same entropy as using random 8-character English alphabets
-as a password, in which case the entropy is 45.6 bits.
+This represents roughly the same entropy as using a random 8-character Latin-alphabet
+password, for which the entropy is 45.6 bits.
 This level is considered to be strong enough for Web services,
-where online brute-force attack is impossible\cite{Florencio:2007:SWP:1361419.1361429}.
+where it's not possible to perform online brute-force attacks\cite{Florencio:2007:SWP:1361419.1361429}.
 
@@
 
-The quality of the questions is the key to using EpisoPass.
+The quality of the questions is key to using EpisoPass effectively.
 If the episode is shared by someone else,
-that person can easily answer the question and generate the
-password just like the user.
+this other person might easily be able to answer the question and generate the
+user's password.
 %
-The episode related to each question should not be known to other people,
+The episode related to each question should therefore not be known to any other person,
 and the episode should be unforgettable.
 %
-Finding such episodes seems difficult at first, but
-when we try to remember experiences of old days,
-we can recall many trivial episodes which are unforgettable but
-not important to other people.
+Finding such episodes seems difficult at first, but our experience
+has been that we try to remember such experiences from our personal past,
+we can soon recall many trivial episodes which are unforgettable but
+nonetheless not important to other people.
 %
-Old experiences like the following are candidates for
-good questions used in EpisoPass.
+The following list shows some examples of experiences that we believe
+make good candidates for EpisoPass questions.
 
 \begin{itemize}
-\item Memory of small injury. (Nobody cares it but you.)
+\item Memories of very minor injuries that nobody would have cared about apart from you.
 
-\item Memories of bad experience like blunders or defeat.
-(You don't tell it to anybody.)
+\item Memories of bad experience such as embarrassing blunders or failures,
+especially in the case where it was never admitted to anyone else.
 
-\item Experience of finding a small special item which only you are interested in.
+\item Experiences of finding inconsequential but special items which only you are interested in.
 \end{itemize}
 
-For example, a question like
-``who hit you when you were 6 years old?''
-is about a trivial experience that people do not mention,
-but a bad experience like this is not forgettable.
+For example, a question such as
+``who hit you when you were six years old?''
+is about a trivial experience that most people would never have reason to discuss,
+but an experience that may have been unpleasant at the time is hard to forget.
 
-Questions like ``Which food do you like best?'' should be avoided,
-since some of the friends might know the user's taste.
+Questions such as ``Which food do you like best?'' should be avoided,
+since friends or family might know the user's tastes, thereby allowing 
+others to select the correct answer.
+
 Questions related to an episode which the user is proud of should also be
-avoided, since the user might talk about the episode to somebody else.
-
-We usually don't tell our bad trivial experiences to other people,
-but we might boast of good experiences or even write a blog about it.
-Also, our tastes (e.g. favorite food) might change in the long run.
-Using such episodes for questions should be avoided.
+avoided, since this is a something the user might prefer to discuss with others.
+We don't usually talk about trivial bad experiences with other people,
+but we might boast about good experiences (some might even write blog posts about them).
+Similarly our tastes ({\it e.g.\/} favorite foods) might change in the long run.
+Using such episodes for questions should therefore be avoided.
 
@@
 
-It is difficult to provide enough number of fake answers to a question like
-``what was your favorite sport?''
-because possible answers are limited.
+It can be difficult to provide a large number of false answers to a question like
+``what is your favorite sport?''
+because the number of possible answers is limited.
 %
 On the other hand, if the right answer to the question is a name of a place or a person,
-generating similar answers is easy.
+generating similar answers is straightforward.
 For example, if the answer to the question is ``Colorado'',
 we can easily provide fake answers like ``California'', ``Utah'', etc.
-because we can use the list of states in the U.S.
 
-In this way, fake answers can be easily generated
+In this way, false answers can be easily generated
 if it is possible to collect words which belong to the same
@@
 same category, mainly for information retrieval tasks%
-\cite{Huang:2012:LFC:2426725.2426728}% 
-\cite{BooWa}% Boo!Wa!
-\cite{Wang:2007:LSE:1441428.1442086}.% 
-Using such systems, we can get a list of fake answers almost automatically.
+\cite{Huang:2012:LFC:2426725.2426728,BooWa,Wang:2007:LSE:1441428.1442086}. % Boo!Wa!
+We can use such systems to provide a list of potential false answers almost automatically.
 
@@
 
-Although everyone has to use authentication systems on the Internet these days,
-not all the people are good at handling passwords.
+Although everyone has to make use of authentication systems, not everyone
+is good at handling passwords.
 Even experienced computer users have trouble with passwords,
-since choosing a good password is not intuitive and
-people forget passwords very easily.
+since choosing a good password is unintuitive and remembering complex
+passwords is hard.
 %
-Using EpisoPass, people can use password-based systems without knowing
-techniques for creating and remembering strong passwords.
-They only have to provide
-questions and answers based on secret episodic memories.
+Using EpisoPass, people can use password-based systems without having to invent
+techniques for creating and remembering strong passwords. The Q-A configuration step
+is a one-time process, after which the system becomes straightforward to use.
 %
@@
 Our experience of using browser extensions suggests that
-that approach is worth consideration.
+this approach offers the most seamless experience.
 
-\subsection{Frequent password update}
+\subsection{Password requiring frequent updates}
 
-On many services, users are requested to change passwords periodically
+Many services still require users to change passwords periodically in an attempt
 to strengthen security.
 %
-Such a practice is not recommended these days
-because humans cannot create strong passwords frequently\cite{Schneier:change}.
+Although this is no longer considered good-practice, since humans struggle to
+generate a stream of strong passwords \cite{Schneier:change}, the practice is
+still widespread.
 %
-% A user can generate a new strong password by using a randam character generator
+% A user can generate a new strong password by using a random character generator
 % on a password manager, but he might want to old passwords in case some trouble happens.
 %
-Using EpisoPass, users can just provide a date-related question
-like the last question shown in Figure \ref{web1},
-and generate different strong passwords based on the answer.
-Using this technique, people can easily manage old and new passwords.
+Using EpisoPass, users can provide a date-related question
+similar to that shown as the final question in Figure \ref{web1}. This allows
+different strong passwords to be generated depending on the answer chosen
+for this question. Using this technique, people can easily manage both old and new 
+passwords efficiently.
 
-\subsection{Comparison with challenge-response authentication}
-
-% 一方、{\SQ}を利用する認証の脆弱性を利用した攻撃が近年問題になっている。
-% {\PW}を忘れたときのために、
-% あらかじめ設定した{\SQ}に答えることによって{\PW}をリセットできるサービスがあり、
-% 「母親の旧姓は?」や「最初に飼ったペットの名前は?」のような
-% 質問に対してユーザが答を登録するようになっている。
-% このような問題は他人が調べたり推測したりすることが容易であるうえに
-% {\SQ}の数は一般的に少なく、
-% {\PW}よりも脆弱だといえる\cite{Rabkin:2008:PKQ:1408664.1408667}。% 銀行20個調べて{\SQ}の弱さを指摘
-
-In many services, users are adviced to define answers to secret questions like
-``what is your mother's maiden name''
-so that he can log into the service even when he forgets the password.
-This kind of authentication is far less secure than simple password systems,
-since it is fairly easy for attackers to know the right answer.
-The variation of system-provided questions are usually small, and
-such challenge-response systems are considered to be
-insecure\cite{Rabkin:2008:PKQ:1408664.1408667}.
-
-It would be better if the user can register his own secret questions
-based on his episodic memory.
-However, answers to user-generated challenge questions are more easily
-forgotten or cracked,
-and using simple challenge-responce is not considered to be safe enough
-\cite{Just:2009:PCC:1572532.1572543}\cite{Schechter:2009:NSM:1607723.1608145}.
+% \subsection{Comparison with challenge-response authentication}
 % 
-Also, in this case,
-the user should register the answer to the system in addition to the question.
-Telling secret facts to service providers is like
-registering raw password string on the server,
-and it is not safe unless the strings are properly hashed and salted on the server.
-
+% % 一方、{\SQ}を利用する認証の脆弱性を利用した攻撃が近年問題になっている。
+% % {\PW}を忘れたときのために、
+% % あらかじめ設定した{\SQ}に答えることによって{\PW}をリセットできるサービスがあり、
+% % 「母親の旧姓は?」や「最初に飼ったペットの名前は?」のような
+% % 質問に対してユーザが答を登録するようになっている。
+% % このような問題は他人が調べたり推測したりすることが容易であるうえに
+% % {\SQ}の数は一般的に少なく、
+% % {\PW}よりも脆弱だといえる\cite{Rabkin:2008:PKQ:1408664.1408667}。% 銀行20個調べて{\SQ}の弱さを指摘
 % 
-%ユーザが作成した{\SQ}を使えばこのような問題はなくなるはずであるが、
-%他人に解かれにくい問題をユーザが作成することは難しく、
-%またユーザ自身が答を忘れてしまうことも多いと考えられている\cite{Just:2009:PCC:1572532.1572543}\cite{Schechter:2009:NSM:1607723.1608145}。
+% In many services, users are advised to define answers to secret questions like
+% ``what is your mother's maiden name''
+% so that he can log into the service even when he forgets the password.
+% This kind of authentication is far less secure than simple password systems,
+% since it is fairly easy for attackers to know the right answer.
+% The variation of system-provided questions are usually small, and
+% such challenge-response systems are considered to be
+% insecure\cite{Rabkin:2008:PKQ:1408664.1408667}.
 % 
-%また、古い記憶にもとづいて作成した秘密の問題は
-%ユーザが想像するよりも解かれやすいという実験結果にもとづき、
-%忘れない{\SQ}を複数利用する方法、
-%問題と答を連想するために画像を利用する方法、
-%複数の問題を連続的に利用する手法などが提案されている\cite{Renaud:2010:PQE:2146303.2146318}。
-
-% {\EP}では、
-% 他人には解くことが難しく自分では忘れないような{\SQ}を自由にいくつでも利用できるようになっている。
-% 問題作成に慣れていないユーザには有効な{\SQ}を作成することは難しいかもしれないが、
-% 次節で述べるように、適切な質問を選ぶことによりこの問題を解決できるはずである。
+% It would be better if the user can register his own secret questions
+% based on his episodic memory.
+% However, answers to user-generated challenge questions are more easily
+% forgotten or cracked,
+% and using simple challenge-responce is not considered to be safe enough
+% \cite{Just:2009:PCC:1572532.1572543}\cite{Schechter:2009:NSM:1607723.1608145}.
+% %
+% Also, in this case,
+% the user should register the answer to the system in addition to the question.
+% Telling secret facts to service providers is like
+% registering raw password string on the server,
+% and it is not safe unless the strings are properly hashed and salted on the server.
 
@@
 
-To prevent such troble, it is safer to keep all the questions and answers
+To prevent such trouble, it is safer to keep all the questions and answers
 in a secret place or
@@
 Old pictures can be used as the questions of EpisoPass,
-just like the 5th question shown in Figure \ref{web1}.
+just like the question shown at the bottom of Figure \ref{web1}.
 Even when people cannot create good secret questions,
@@
 As shown in previous sections,
-there have been many attemps for replacing password-based authentication systems,
+there have been many attempts for replacing password-based authentication systems,
 but none of them are found to be better than
@@
 
-The idea of using episodic memories for authtication is not new.
+The idea of using episodic memories for authentication is not new.
 In fact, using episodic memories for selecting password
@@
 ``who did you call last night?'' correctly, the authentication will succeed.
-Using mobile or wearable devices for authentication works in many cases,
+Using mobile or wearable devices for authentication will become more usable
+in the future,
 but users should have a fairly good long-term memory about their behaviors,
@@
 a pain for the authors, but
-currently all the information for generating passswords is put on the cloud
+currently all the information for generating passwords is put on the cloud
 and no trouble has been found during the period.
@@
 
-Unfortunately EpisoPass is currently not used by many people.
+EpisoPass service have been on the Web and the source code is
+available on GitHub\footnote{
+  (url removed for double-blind review)
+  % \url{https://EpisoPass.com/},
+  % \url{https://github.com/masui/EpisoPass}
+}, but
+unfortunately EpisoPass is currently not used by many people.
 One big reason is that most people cannot fully understand the
 idea of EpisoPass and also cannot fully trust it
-because it is not operated by a big IT company nor supported by
-famous computer users.
+because it is not operated by a big IT company.
+% nor supported by famous computer users.
 Another reason might be that users cannot estimate the strength
@@
 
+\subsection*{Note.}
+
+This paper is largely a translation of a 2013 paper published by the
+author in Japanese\cite{WISS2013}. This is the first time that the
+work is presented to an international audience in English.
+Additionally, in the intervening three years the author has
+developed the browser extension described in section \ref{extensionsection}.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2016-08-29 paper/Password2016/paper.tex
Joannaによる添削を入れたもの

@@
 \usepackage{graphicx}
-
 \usepackage{marginnote}
@@
 
-Passwords have been used as a means of authenticating to Web services
-and applications for a long time, and remain the most popular
-authentication method on the Internet.
+Passwords have been used as a means of authenticating to Web services and applications
+for a long time, and remain the most popular authentication method on the Internet.
 %
-Since short passwords are easily guessable by attackers and using the
-same password for multiple services is unsafe, a different long
-password should be used for each service a person uses.  However,
-remembering numerous long passwords is almost impossible for ordinary
-humans.
+Since short passwords are easily guessable by attackers and
+using the same password for multiple services is unsafe,
+a different long password should be used for each service a person uses.
+However, remembering numerous long passwords is almost impossible for ordinary humans.
 %
@@
 Since passwords are difficult to handle, various other authentication methods have been proposed.
-For example, image-based authentication\cite{Biddle:2012:GPL:2333112.2333114,GraphicalPasswords},
-biometrics authentication\footnote{
+For example, image-based authentication \cite{Biddle:2012:GPL:2333112.2333114,GraphicalPasswords}, 
+biometrics\footnote{
   % \textsf{https:{\slash}{\slash}en.wikipedia.org{\slash}wiki{\slash}Biometrics}
-  % \url{https://en.wikipedia.org/wiki/Biometrics}
   \url{https://en.wikipedia.org/w/index.php?title=Biometrics&oldid=736189000}
 },
-behavior-based authentication\cite{Dandapat:2015:AYD:2702123.2702457}, and many others.
+behavior-based authentication \cite{Dandapat:2015:AYD:2702123.2702457}, and many others.
 
@@
 
+% \marginnote{I'd hesitate to call passwords the {\it strongest\/} method. Perhaps {\it most widely deployed\/} would be less contreversial?}
 However, password-based authentication is still the most
@@
 
-Given we will have to continue to live with password-based
-authentication systems for the foreseeable future, we have to devise
-practical methods for handling many passwords, and various ``password
-managers''
-have been proposed\cite{OnePassword,Dashlane,MilPass,LastPass,KeyPass,NortonIDSafe,IDManager}.
+Given we will have to continue to live with password-based authentication systems for the foreseeable future,
+we have to devise practical methods for handling many passwords, and various ``password managers'' have been proposed
+\cite{OnePassword,Dashlane,MilPass,LastPass,KeyPass,NortonIDSafe,IDManager}.
 %
-Password managers remember users' passwords and aim to directly enter
-them into the login pages of the various services a user wants to
-access.
+Password managers remember users' passwords and aim to directly enter them into the login pages of the various services a user wants to access.
 %
-The burden on the user is reduced by requiring just a single ``master
-password'' to access the database of stored passwords.
+The burden on the user is reduced by requiring just a single ``master password'' to access the database of stored passwords.
 %
-Although password managers are widely used and a clear step forward
-from having to remember multiple passwords, uses nonetheless have to
-remember the master password or use a special hardware device for
-safely handling the password database, and password managers usually
-run on only a limited set of devices.
+Although password managers are widely used and a clear step forward from having to remember multiple passwords, uses nonetheless have to remember the master password or use a special hardware device for safely handling the password database, and password managers usually run on only a limited set of devices.
 
@@
 
-If we want to avoid having to carry any special device for
-authentication, either we must used some form of biometrics, or all
-the information required for the authentication must be must be stored
-in the user's memory.
+If we want to avoid having to carry any special device for authentication,
+either we must used some form of biometrics, or all the information required 
+for the authentication must be
+must be stored in the user's memory.
 %
 However, the biggest problem with memory-based authentication is that
-users cannot reliably remember passwords or master password that are
-long and complex enough to be secure.
-
-For this reason, we believe that it is far better to ``generate''
-something for the authentication, based on a user's episodic
-memories. This has the benefit that unlike a password, a person is
-highly unlikely to forget such episodic memories.
+users cannot reliably remember passwords or master password that are long and complex enough to be secure.
+For this reason, we believe that
+it is far better to ``generate'' something for the authentication,
+based on a user's episodic memories. This has the benefit that unlike a password, a person is highly unlikely to forget such episodic memories.
 %
@@
 %
-We therefore propose \textit{EpisoPass}, a password manager that
-generates strong passwords based only on a user's secret and
-unforgettable episodic memories.
+We therefore propose \textit{EpisoPass}, a password manager that generates strong passwords
+based only on a user's secret and unforgettable episodic memories.
 
@@
 % Memories in human brain are not uniform.
-Our brains store numerous memories, but different memories have
-different characteristics.  Some memories are very short-lived, while
-others are recallable for long periods of time.  When we have a
-particularly impressive experience, the memory of it will stay in our
-mind for a long time and can't be easily forgotten.  On the other
-hand, other topics are more difficult to remember. For example, when
-studying mathematics and trying to remember a new formula, it can be
-hard to memorize without significant practice, since knowledge of the
-formula is unrelated to any personal experiences.
+Our brains store numerous memories, but different memories have different characteristics.
+Some memories are very short-lived, while others are recallable for long periods of time.
+When we have a particularly impressive experience,
+the memory of it will stay in our mind for a long time and can't be easily forgotten.
+On the other hand, other topics are more difficult to remember. For example, when studying mathematics and trying to remember a new formula,
+it can be hard to memorize without significant practice,
+since knowledge of the formula is unrelated to
+any personal experiences.
 The former type of memory is called an {\it episodic\/} memory and most people find such
@@
 
-The idea of using episodic memories for authentication has a long history.
-Early papers suggested using episodic memories for creating passwords.
-Authentication by using secret questions,
-sometimes called as ``cognitive passwords''\cite{Zviran:1990:UAC:100512.100538},
-has long been used as an
-alternative to password-based authentication systems.
-%
-% However, conversion from episodic memories to password strings
-% was not studied at all.
-
-Password generation on EpisoPass is performed through the following steps:
-
-\begin{enumerate}
-\item A user registers many question texts related to the user's personal
-secret episodic memories that the user never forgets,
-and provides a correct answer and additional fake answers.
-
-\item The user provides a long ``seed string'' for each service that requires
-a password.
-
-\item EpisoPass shows the data to the user so that
-the user can select the right answer for each question.
-Based on the user's selections,
-EpisoPass substitutes characters in the seed string and generates
-strong password candidate strings.
-After selecting all the right answers,
-the user copies the calculated string
-and register it as the password for the service.
-\end{enumerate}
-
-\begin{figure}[H]
+\begin{figure}
 \centering
@@
 
-\subsection{Using EpisoPass on a browser}
+% \marginnote{You mention that episodic memories and cognitive passwords
+%   have been used in the past, but it's not clear to me (from the text
+%   here) why your system is different. Perhaps you could put a sentence
+%   or two about this?}
+
+The idea of using episodic memories for authentication has a long
+history and early papers suggested using episodic memories for
+creating passwords. Authentication using secret questions is sometimes
+referred to as ``cognitive
+passwords''\cite{Zviran:1990:UAC:100512.100538}, and such approaches
+have been used as an alternative to password-based authentication
+systems.
+%
+While cognitive passwords were aimed to be alternatives to
+password-based systems, EpisoPass is a system for supporting
+password-based systems using episodic memories.
+
+Password generation on EpisoPass is performed through the following steps:
+
+\begin{enumerate}
+\item A user registers multiple question texts related to their own personal
+secret unforgettable episodic memories. For each question they must provides
+a single correct answer and multiple additional incorrect answers.
+
+\item The user provides a long ``seed string'' for each service that requires
+a password.
+
+\item EpisoPass shows the questions and answers to the user allowing
+them to select the correct answer for each question.
+Based on the user's selections,
+EpisoPass substitutes characters in the seed string and generates a
+strong password candidate string.
+After selecting all of the correct answers,
+the user copies the calculated string
+and registers it as the password for the service.
+\end{enumerate}
+
+\subsection{Using EpisoPass in a browser}
 
 Figure \ref{web1} shows how to generate a password
-on EpisoPass running on a browser.
+on EpisoPass running in a browser by accessing the EpisoPass site.
 Many questions related to the user's episodic memories are shown to the user,
 and many candidate answers are also shown for each question.
-When a user clicks and selects one of the answers for each question,
+When a user clicks and selects one of the answers for a question,
 the seed string shown at the top-left is converted to a
 candidate password string based on the selections.
-When the user selects the correct answers to all the questions,
-the right password is calculated and shown at the top.
+If incorrect answers are chosen the wrong password will be generated.
+On the other hand, when the user selects the correct answers for all of the questions,
+the correct password is calculated and shown at the top of the page.
 
@@
 ``\textsf{Amazon123456}'' is provided as the seed string,
-and according to the selections to the five questions,
-the seed string is converted to a string
+and based on the selections to the ten questions,
+the seed string is converted to the string
 ``\textsf{Tblgeq808187}'',
-which can be used as the password for Amazon.com.
+to be used as the password for Amazon.com.
 
-When the user clicks another candidate,
-the seed string is converted to another strings like
-``\textsf{Xvdkzb940345}'' (Figure \ref{web11}).
+When the user clicks on different candidate answers 
+the seed string is converted to a completely different strings, such as
+``\textsf{Xvdkzb940345}'', as shown in Figure \ref{web11}.
 
-\begin{figure}[H]
-\centering
-\includegraphics[width=1.0\columnwidth]{figures/8447eaba1ede0f678b3ce6fea63681f3}
-\caption{Selecting a different answer.}
-\label{web11}
-\end{figure}
-
-In this way, different selections yields different password strings and
-the password string generated after selecting correct answers can be
+In this way, different selections yield different password strings and
+the unique password string generated after selecting the correct answers should be
 used as the password for the service.
 
-Capital letters in the seed string are substituted to capital letters in the password,
-and digits in the seed string are substituted to digits,
-so that generated passwords conforms to password character restrictions
-sometimes requested by the service.
+Capital letters in the seed string are substituted for capital letters in the password,
+and digits in the seed string are substituted for digits. In this way
+the generated password can be arranged to conform with any password character restrictions
+the site might impose.
 
@@
 which the author believes he will never forget.
-All the questions are based on the author's episodic memories
-that he thinks he never forgets, and he believes that
-nobody else knows which one of the candidate is the right answer.
+All the questions are based on the author's episodic memories that he's unlikely to ever forget,
+and that he believes nobody else will know the correct answer for.
 
-Questions and answers can be edited directly on the browser, and they can be
-saved on the server by clicking the ``save to server'' button.
-The Q-A data sets are saved on the server,
-but no information about the correct answer or the
-generated password is saved on the server.
-The Q-A data in JSON format can be downloaded to the local machine
-by clicking the ``save to file'' button.
-the data can be uploaded to the server by dragging the JSON file to the EpisoPass page.
+\begin{figure}
+\centering
+\includegraphics[width=1.0\columnwidth]{figures/8447eaba1ede0f678b3ce6fea63681f3}
+\caption{Selecting a different set of answers.}
+\label{web11}
+\end{figure}
 
-When we change the secret string to ``\textsf{Facebook123456}'',
+Usability has been considered as a key consideration, and the questions 
+and answers in the figures can be edited directly in the browser. They can be
+saved on the server by clicking the ``save to server'' button or saved locally
+if the user prefers.
+While the Q-A data sets are saved, no information about the correct answer or the
+generated password is saved on the server. Consequently there is no requirement for the user
+to trust the server to keep the data secret.
+The Q-A data can be downloaded to the user's local machine in JSON format 
+by clicking the ``save to file'' button. To upload the data back to the server, the user
+simply drags the JSON file to the EpisoPass page.
+
+When the secret string is changed to ``\textsf{Facebook123456}'',
 the generated password changes to ``\textsf{Onjbrppy030937}'',
 as shown in Figure \ref{web2}.
-In this way, we can generate different passwords for
+In this way, the user can generate different passwords for
 different services just by changing the seed string.
 
-\begin{figure}[H]
+\begin{figure}
   \centering
@@
   \includegraphics[width=1.0\columnwidth]{figures/ab4517dd593c1cabab5fecef546f7e88}
-  \caption{Generating the password for Facebook.}
+  \caption{Generating a new password for Facebook.}
   \label{web2}
@@
 
-Character substitution is performed based on the hash value
-calculated from concatenating all the questions and selected answers.
+Character substitution is performed based on the value
+calculated by hashing a concatenation of all the questions and selected answers.
 %
 For example, if the user selects ``\textbf{\texttt{Ebisawa}}''
-to the question ``\textbf{\texttt{Who's the bully?}}'',
+as the answer to the question ``\textbf{\texttt{Who's the bully?}}'',
 a string including ``\textbf{\texttt{Who's the bully:Ebisawa}}''
@@
 
-The last question in Figure \ref{web1} is not a secret question, but a question
+The last question in Figure \ref{web1} is not intended as a secret question based on an
+episodic memory, but is instead a question
 for generating different passwords for different situations.
-By providing such a question, users can generate completely different passwords
-for different months and years, for example.
+By providing a question like this, the user can generate completely different passwords
+for different months and years, say.
 
@@
 
-If a user doesn't like to use the EpisoPass service on the Net,
-he can use an EpisoPass application on Android
-which does not use network connections.
-After registering questions and answers on the EpisoPass service,
-the user can download an Android application from the server
-by clicking the ``Android app'' button at the top.
-The application contains all the information required for generating passwords.
-(The application is compiled and built on the server.)
+% \marginnote{Is the Android app generated as a unique app for each
+%  user? If so, I think it's worth making this clear.}
+
+If a user prefers not to use the EpisoPass service on the Web, there
+is an alternative EpisoPass application for Android which requires no
+network connection.  After registering questions and answers on the
+EpisoPass service, the user can download an Android application from
+the server by clicking the ``Android app'' button at the top of the
+page.  The application unique to the user is compiled and built on the
+server and contains all of the information needed for the particular
+user to generate passwords using the Q-A sets entered.
 
 When the user runs the application and selects the correct answer
-to each question, he can eventually get the password and copy it to the password entry.
-(Figure \ref{android1},\ref{android2})
+to each question, the password will be generated in the same way as
+on the site, as shown in Figures \ref{android1} and \ref{android2}.
+This can then be copied to the password entry for access
+to a particular service.
 
-\begin{figure}[H]
+\begin{figure}
 \centering
-\includegraphics[width=0.7\columnwidth]{figures/429eec261024dc6c85351f51c12f09b4}
+\includegraphics[width=0.4\columnwidth]{figures/429eec261024dc6c85351f51c12f09b4}
 \caption{Running EpisoPass on Android.}
@@
 
-\begin{figure}[H]
+\begin{figure}
 \centering
-\includegraphics[width=0.7\columnwidth]{figures/ba8f5aeaa935ad63437969f4d746746b}
+\includegraphics[width=0.4\columnwidth]{figures/ba8f5aeaa935ad63437969f4d746746b}
 \caption{After finishing selections.}
@@
 
-The calculation is performed on Android without network connection,
-and the user can safely generate passwords 
-without feeling the fear of being observed by attackers.
+The calculation is performed on Android without the need for a network connection,
+so the user can safely generate passwords without being concerned about an
+attacker observing any data transfer.
 
@@
 
-When a user use the EpisoPass service or the EpisoPass application,
-he has to type or copy the password string after generating the password.
-Since it is not convenient,
-we provide a browser extension for using EpisoPass on the login window of
-various Web services.
+One of the difficulties of the previous two approaches is that the user 
+must re-type or copy the password string into the service's password
+field after it's been generated.
+This isn't ideally convenient, so we have also developed a browser 
+extension that allows EpisoPass to be used directly with the login
+page of services on the Web.
+
+\begin{figure}
+\centering
+\includegraphics[width=0.8\columnwidth]{figures/aeff16ffcab956e554364e9e5aca8359}
+\caption{Using EpisoPass on the login window.}
+\label{extension}
+\end{figure}
 
@@
 %
-Figure \ref{extension} shows the login page of Amazon.com, with which
-EpisoPass questions are automatically displayed by the browser extension.
+Figure \ref{extension} shows the login page of Amazon.com, with the 
+EpisoPass questions automatically overlaid directly onto the page
+by the browser extension.
 %
-Here, when the Amazon login page is accessed from the browser,
-the browser extension program automatically runs on the page,
-acquires questions and answers from the EpisoPass server,
-and shows them to the user just the same way as the Android application.
+When the user accesses the Amazon login page,
+the browser extension automatically runs on the page,
+acquires the questions and answers from the EpisoPass server,
+and displays them using the same style as for the Android application.
 %
-After answering all the questions, a password is calculated from the
-selected answers and pasted to the password field of the page.
-Using the extension, users can login to various services just by
-answering questions, without seeing any password string.
-It looks as if these services are offering
-EpisoPass-based authentication.
+After answering all of the questions, a password is calculated from the
+selected answers and automatically pasted into the password field of the page
+by the extension. In this way users can log in to various services just by
+answering the questions presented, and without even seeing the password string.
+It appears as if the EpisoPass-based authentication is being provided directly
+by the services themselves.
 
-\begin{figure}[H]
-\centering
-\includegraphics[width=0.9\columnwidth]{figures/aeff16ffcab956e554364e9e5aca8359}
-\caption{Using EpisoPass on the login window.}
-\label{extension}
-\end{figure}
+\section{Discussion}
 
-\section{Discussions}
-
-In this section, we discuss the advantages and caveats of using EpisoPass.
+In this section, we discuss the advantages and potential disadvantages of using EpisoPass.
 
 \subsection{Recallability of answers}
+
+% \marginnote{The fact that an `old' memory is unlikely to be forgotten
+%   is perhaps obvious, but this could be a good place to cite a paper
+%   on memory/psychology about this if you're aware of any?}
 
@@
 %
-Users of EpisoPass can save the seed string and question-answer data
-at any place, and easily generate passwords by running
-EpisoPass and answering questions.
-If the question is based on old unforgettable episodic memories,
-there is little chance of losing passwords
-as long as the seed string and the questions are available.
-If the user's memory is related to an episode of 20 years ago and the user clearly
-remembers the episode now, it is unlikely that he forgets the episode 10 years later.
+The seed string and question-answer data is essentially public,
+and users of EpisoPass can save them wherever is convenient. They can
+then easily generate passwords by running
+EpisoPass and answering the questions.
+If a question is based on old unforgettable episodic memory,
+there is little chance of losing the password for a service
+as long as the seed string and questions are available.
+If the user's memory is related to an episode that took place 20 years ago, say, and the user clearly
+still remembers the episode now, it is unlikely the episode will be forgotten in the future.
 
@@
 
-In the previous examples showing the author's EpisoPass questions,
-a seed string ``\textsf{Amazon123456}'' was used for Amazon.com, and
-``\textsf{Facebook123456}'' was used for Facebook.
-Such strings are used because they are easily memorable.
-Of course any seed string can be used as seeds for various services,
-and automatic generation of seed strings is possible.
+% \marginnote{In the comments you mention that ``generating
+%   service-specific unique seed string is not trivial''. I think this
+%   is worth mentioning in the paper.}
 
-% although generating service-specific unique seed string is not trivial.
-% For example, users can use the same username and password both
-% for Amazon.com and Amazon.co.uk, but not for Amazon.co.jp.
+In the previous examples showing the author's EpisoPass questions, a
+seed string ``\textsf{Amazon123456}'' was used for Amazon.com, and
+``\textsf{Facebook123456}'' was used for Facebook.  Such strings were
+chosen because they are easily memorable.  In practice any seed string
+could be used as the seeds for the various services, and automatic
+generation of seed strings is a possibility, although generating
+service-specific unique seed string is not trivial.  For example,
+users can use the same username and password both for Amazon.com and
+Amazon.co.uk, but not for Amazon.co.jp.
 
@@
 
-The strength of the generated password depends on the number of
-questions and the secret level of the questions.
+The strength of the generated passwords depends on the number and 
+level of secrecy of the questions.
 %
 There have been many studies on the strength of passwords
-\cite{Hayashi:2011:DSP:1978942.1979326}%
-\cite{Komanduri:2011:PPM:1978942.1979321}, % What password is strong
-but the strength of secret questions has not been studied enough.
-%
-When we use 10 secret questions with 20 answers and
-there's no clue for the answer,
-1 billion ($20^{10}$) trials should be performed to check
-all the combinations of the answers,
+\cite{Hayashi:2011:DSP:1978942.1979326,Komanduri:2011:PPM:1978942.1979321}, % What password is strong
+but measuring the strength of secret questions is an area where more study is needed.
+% \marginnote{I calculate $20^{10} = 10,240,000,000,000$. This is
+% considerably more than a billion (closer to 10 thousand billion,
+% (US) or 10 million million (UK).}
+Using ten secret questions each with twenty answers, where each answer is considered equally likely,
+an attacker would need to cover a search space of over ten trillion ($20^{10}$) values to check
+every potential combination of answers,
 and the entropy of the system is 43.2 ($10 \times \log_2 20$) bits.  % 10.0 * (Math.log(20.0)/Math.log(2.0))
@@
 This level is considered to be strong enough for Web services,
-where it's not possible to perform online brute-force attacks\cite{Florencio:2007:SWP:1361419.1361429}.
+where it's not possible to perform online brute-force attacks \cite{Florencio:2007:SWP:1361419.1361429}.
 
@@
 %
-The following list shows some examples of experiences that we believe
-make good candidates for EpisoPass questions.
+The following list shows some examples of experiences that we believe make good candidates for
+EpisoPass questions.
 
@@
 
-\item Memories of bad experience such as embarrassing blunders or failures,
-especially in the case where it was never admitted to anyone else.
+\item Memories of bad experience such as embarrassing blunders or failures, especially in the case where
+it was never admitted to anyone else.
 
@@
 others to select the correct answer.
-
 Questions related to an episode which the user is proud of should also be
 avoided, since this is a something the user might prefer to discuss with others.
+
 We don't usually talk about trivial bad experiences with other people,
@@
 we can easily provide fake answers like ``California'', ``Utah'', etc.
+because we can use the list of states in the U.S. as possible answers.
 
@@
 Various methods have been proposed for collecting words in the
-same category, mainly for information retrieval tasks%
+same category, mainly for information retrieval tasks
 \cite{Huang:2012:LFC:2426725.2426728,BooWa,Wang:2007:LSE:1441428.1442086}. % Boo!Wa!
@@
 Users don't have to be very careful about handling questions and answers.
-They can even be put on a public place
-if enough amount of questions and fake answers are provided.
+They can even be stored in a public place
+given a sufficient number of questions and fake answers are provided.
 %
-Keeping secrets is always a pain for many people including
-the authors, but if the whole questions and answers used on EpisoPass
-can be put on a public place,
-handling it becomes very easy.
-Usually we have to be very careful about handling
-secret information like passwords, secret key for SSH, etc.
-because they should not be copied or saved at unsafe places.
-On the other hand,
-we can save the EpisoPass data as a plain text file and put it at
-any place without great care, since malicious person cannot calculate
-passwords without having the owner's episodic memories.
+Keeping secrets is a considerable effort for most people (including
+the authors), but if the entire set of questions and answers used for EpisoPass
+can stored publicly,
+handling it becomes straightforward.
+This is in contrast to the care needed when handling 
+secrets like passwords, secret keys for SSH, {\it etc}. which should
+never be copied to or saved in an unsafe place.
+The EpisoPass data can be stored as a plain text file wherever is convenient
+for the user, since a malicious attacker isn't able to generate
+a valid password without also knowing the owner's relevant episodic memories.
 
@@
 
-\subsection{Risk of password leak at the service side}
+\subsection{Risk of server-side password leaks}
 
-If one of the passwords generated by EpisoPass is revealed
-for some reason, other passwords based on the same questions
+If one of the passwords generated by EpisoPass were to be revealed
+for some reason, there is a danger that other passwords based on the same questions
 might also be revealed.
 %
-For example, if Twitter is attacked by a cracker and
+For example, if Twitter is attacked by a hacker and
 the password for Twitter (``\textsf{Lbasnln542202}'' in Figure \ref{web1})
 is revealed to the attacker,
-the attacker can try all the answer combinations and find out
-the answers to all the questions,
-if questions and answers are also known by the attacker.
+the attacker could test all answer combinations. If the attacker also had access
+to the question and answer strings used, they could then establish the correct 
+answers used to generate the password.
 Once all the answers to the questions are known,
-the attacker can freely generate all the passwords
-generated with the same questions.
+the attacker can then freely generate all of the user's passwords
+generated from the same set of questions.
 
-To prevent such trouble, it is safer to keep all the questions and answers
+% \marginnote{It may be helpful to give an indication of how many Q-A sets you think
+% would be considered `sufficient' here.}
+%
+To prevent this, it is safer to keep all of the questions and answers
 in a secret place or
-use sufficient number of questions so that brute-force does not work.
+use sufficient questions to prevent such a brute-force attack from being viable.
 
@@
 
-Old pictures can be used as the questions of EpisoPass,
-just like the question shown at the bottom of Figure \ref{web1}.
-Even when people cannot create good secret questions,
-people can fairly easily select a secret image from their photo collections
-and use it as the question.
-For example, if you have an old picture of your friend,
-you can use it as the question
-and use his real name as well as other similar fake names.
+% \marginnote{The use of images is nice, but I don't find your argument
+%   so convincing here. I have two concerns: first the claim that
+%   selecting images will be easy. Second, the example you provide
+%   doesn't seem strong, since other people are likely to be able to
+%   identify a friend from a photograph.}
 
-% 画像検索とかされないようにする必要はある
+Pictures can also be used as EpisoPass questions,
+similar to that shown at the bottom of Figure \ref{web1}.
+Even if people find it difficult to create good secret questions,
+selecting an image from their photo collections
+and using it as the question should be straightforward.
+For example, if you have an old special picture of a place you visited,
+you can use it as the question and use the name of the place
+as well as other similar fake place names.
+For a secret question, a low-quality photo is better than a
+high-quality photo because a low-quality photo
+like the one shown in Figure \ref{web1} are not
+easily recognizable by other people.
 
-Of course, the photo should not have information related to the
-person's real name, since image search is fairly easy on the Web these days.
+Of course, it's important the photo should have no information related
+to the location, especially given how sophisticated
+Web-based image searching has become.
 
@@
 
-As shown in previous sections,
-there have been many attempts for replacing password-based authentication systems,
-but none of them are found to be better than
-password-based systems\cite{Bonneau:ReplacePasswords}.
+As discussed in previous sections,
+there have been many attempts to replace password-based authentication systems,
+but none of them have yet become as widely deployed as
+passwords \cite{Bonneau:ReplacePasswords}.
 %
-Although cognitive password systems have been studied for a
-long time\cite{Lazar2011}\cite{Zviran:1990:UAC:100512.100538},
-they were implemented as a replacement to password-based systems,
-and no password-generation system have been proposed
+Although cognitive password systems have been an area of study for 
+many years \cite{Lazar2011,Zviran:1990:UAC:100512.100538},
+implementations up to now have all been intended as replacements 
+to password-based systems, requiring support from the services involved.
+As far as the authors are aware, ours is the first password-generation systems to be
 based on cognitive authentication.
@@
 
-The idea of using episodic memories for authentication is not new.
-In fact, using episodic memories for selecting password
+The idea of using episodic memories for authentication is also not new.
+In fact, using episodic memories for selecting passwords
 has generally been recommended,
 and many current computer users are probably using password that are
-in some way related to their episodic memories.
+in some way informally related to their episodic memories.
 
-Recently, people are trying to use mobile devices for authentication,
-because mobile devices remember all the user's behaviors and
-the user can easily recall what he did%
-\cite{Dandapat:2015:AYD:2702123.2702457}%
-\cite{Das:2013:ECE:2493432.2493453}%
-\cite{GuptaWRLGB12}%
+Recent work has considered the use of mobile devices for authentication,
+in particular harnessing the fact that a mobile device captures large quantities
+of personal information. A mobile device may therefore be able to identify
+its user based on their previous behavior; events which only the user would be able to recall \cite{Dandapat:2015:AYD:2702123.2702457,Das:2013:ECE:2493432.2493453,GuptaWRLGB12}%
 .
-For example, if a user can answer questions like
+For example, if a user can answer questions such as
 ``who did you call last night?'' correctly, the authentication will succeed.
@@
 in the future,
-but users should have a fairly good long-term memory about their behaviors,
-and that not easy for everybody.
+but in order for this to work effectively users must be able to remember potentially
+arbitrary behavior over the long-term. This may be a challenge for many people, and the 
+benefit of EpisoPass in comparison is that the user is able to select memories that they
+know to be memorable, rather than having their mobile device choose them arbitrarily.
 
 Various types of image-based authentication systems have been proposed recently%
-\cite{Biddle:2012:GPL:2333112.2333114}\cite{GraphicalPasswords},
-in the hope that images are easier to remember than text
-because images are usually more directly linked to episodic memories.
-However, on many systems,
-users have to remember new information related to the images
-used in the authentication process, or
-perform special operations on the image, and
-it is not much easier than remembering passwords.
+\cite{Biddle:2012:GPL:2333112.2333114,GraphicalPasswords},
+based on the realisation that images are easier to remember than text
+given they are usually more directly linked to episodic memories.
+However, some image-based authentication systems request
+users to remember new secrets related to the images instead of
+using the users' old episodic memories.
+This turns out to be not much easier to remember than passwords.
 %
+% \marginnote{This statement seems to contradict what you said above
+%   about it being easy to find images. Probably the phrasing just needs
+%   a bit of refinement.}
+
 Image-based authentication based on episodic memories might work
-if anyone can prepare many images 
-that are tightly linked to his episodic memories.
-However, finding such images is usually not easy, and
-image-only authentication systems would not take off
-until simple and effective technique is invented.
+if users can prepare many images 
+that are tightly linked to their episodic memories.
+However, finding such images is usually not straightforward, and
+image-only authentication systems are unlikely to become popular
+until simple and effective techniques for doing so have been developed.
 
 Even when a new ideal authentication method is invented,
-replacing all the password-based systems should take very long, and
-various password managers should be used until the ideal method
-prevails in the world.
+replacing all the password-based systems will still be a lengthy process. 
+Password managers will therefore remain important until this hypothetical
+ideal solution has become ubiquitous.
 In the age of password-based authentication,
@@
 Just like EpisoPass generates passwords,
-Versipass\cite{Stobert:2014:PMD:2683467.2683471} %Versipass 画像のヒントからパスワード生成 % A Password Manager that Doesn’t Remember
+Versipass \cite{Stobert:2014:PMD:2683467.2683471} %Versipass 画像のヒントからパスワード生成 % A Password Manager that Doesn’t Remember
 helps the user to generate password strings
-using ``visual cues'' on an arbitrary image.
+using ``visual cues'' from an arbitrary image.
 Instead of directly using images for authentication,
-users use the system to generate a password text with the help of
+users use the system to generate a password string with the help of
 the image shown to the user.
@@
 
-EpisoPass has been used by the authors for more than three years, and
-the authors are using it for various services including
-Twitter, Facebook, Amazon, Skype, etc.
+EpisoPass has been used by the authors for more than three years
+for various services including Twitter, Facebook, Amazon, Skype, {\it etc}.
 % Since passwords for these services are remembered on the browser,
@@
 %
-Before using EpisoPass, taking care of many passwords was really
-a pain for the authors, but
-currently all the information for generating passwords is put on the cloud
-and no trouble has been found during the period.
+Before using EpisoPass, managing multiple passwords was a significant challenge
+for the authors. We now have all the information for generating passwords 
+stored in the cloud and no problems have arisen from this during this period.
 %
-After the introduction of browser extension,
-logging into various services became even easier,
-because visiting the EpisoPass service is unneccesary.
+Since the introduction of our browser extension, visiting the EpisoPass 
+service has now become unnecessary, making authentication to the various
+services even easier.
 
-EpisoPass service have been on the Web and the source code is
+The EpisoPass service is available via the Website and the source code is
 available on GitHub\footnote{
@@
   % \url{https://github.com/masui/EpisoPass}
-}, but
-unfortunately EpisoPass is currently not used by many people.
-One big reason is that most people cannot fully understand the
-idea of EpisoPass and also cannot fully trust it
-because it is not operated by a big IT company.
+}. EpisoPass currently has only a small user-base, one major
+reason being that most people cannot fully understand the
+idea behind EpisoPass, and may not trust it without the 
+support of a well-known IT company.
 % nor supported by famous computer users.
-Another reason might be that users cannot estimate the strength
-of EpisoPass.
-Since all the questions and answers are
-quite obvious to the users,
-they might feel that everyone else also know the episode
-and easily solve all the questions.
-These kinds of psychological issues are quite important for
-an authentication system for everybody,
-and we hope to eliminate such obstacles in the future.
+Another reason is that it's difficult for general users to 
+assess the security of EpisoPass.
+Since the intention is for the questions and answers to be obvious
+to those that know them (but not to others), users may lack
+confidence in their answers being unknown to others.
+Any authentication system expecting widespread use must take
+such psychological issues seriously, and we hope to address 
+such issues in future work.
 
@@
 
-We introduced a password management system EpisoPass
+We introduced a password management system {\it EpisoPass\/}
 that converts a seed string into a password using the user's
-episodic memories represented as a set of questions and answers
-which can be solved only by the user.
+episodic memories. These memories are represented as a set of questions and answers
+which can be solved only by the user in order to generate a site-specific password.
 %
 Using EpisoPass with well-defined questions and answers,
-a user can always retrieve various passwords without worrying about
-remembering secret information.
+a user can always retrieve a service's passwords without worrying about
+having to remember any secret information, other than the episodic memories
+that have been chosen specifically to be easy to recall.
 %
-We'll try to integrate the system with existing password-based
-services, and finally hope to eliminate all the problems
+In future work we hope to integrate the system with more existing password-based
+services, and ultimately aim to address the problems
 derived from password-based authentication.
@@
 This paper is largely a translation of a 2013 paper published by the
-author in Japanese\cite{WISS2013}. This is the first time that the
+author in Japanese \cite{WISS2013}. This is the first time that the
 work is presented to an international audience in English.
@@
 
-\subsubsection*{Acknowledgments.} The heading should be treated as a
-subsubsection heading and should not be assigned a number.
+% \marginnote{I've added some text in about the grant. Please change it
+%   as you see fit of course. I'm afraid I don't know the grant number
+%   so have left a gap; ideally this should be added in too.}
+
+% \subsubsection*{Acknowledgments.} 
+% The work presented in this paper was in part conducted while on
+% sabbatical at the University of Cambridge, hosted by Frank Stajano and
+% the Pico group, and supported by EPSRC grant number ??????.
 

### 2016-08-30 paper/Password2016/paper.tex
Frankのコメントに対応中

@@
 history and early papers suggested using episodic memories for
-creating passwords. Authentication using secret questions is sometimes
+creating passwords \cite{Barton:Password}.
+Authentication using secret questions is sometimes
 referred to as ``cognitive
@@
 
+\subsection{Password entry time}
+
+Answering to many questions takes much longer time than typing a
+remembered password, so most people may prefer typing password
+rather than using EpisoPass if they have to log in to a service frequently.
+The tradeoff betwee security and usability has long been a big issue
+of authentication systems \cite{Braz:2007:DTU:1778331.1778344},
+but we believe we can approach the best solution by
+improving the user interface of answering questions.
+
+% Frank's comment
+% 3.11. It takes a rather long time to enter one password!''
+% should also be discussed, and may be a killer in some cases. Maybe
+% Episopass is good for infrequently used passwords where the penalty of
+% a slow login is less relevant.
+
 \section{Related Work}
@@
 
-Various types of image-based authentication systems have been proposed recently%
+Various types of image-based authentication systems have been proposed recently
 \cite{Biddle:2012:GPL:2333112.2333114,GraphicalPasswords},
@@
 for the authors. We now have all the information for generating passwords 
-stored in the cloud and no problems have arisen from this during this period.
+stored in the cloud and no problems have arisen during this period.
 %
@@
 % nor supported by famous computer users.
-Another reason is that it's difficult for general users to 
+Another reason is that it's difficult for users to
 assess the security of EpisoPass.
@@
 % \subsubsection*{Acknowledgments.}
-% The work presented in this paper was in part conducted while on
+% This paper was written while on
 % sabbatical at the University of Cambridge, hosted by Frank Stajano and
-% the Pico group, and supported by EPSRC grant number ??????.
+% the Pico group, and supported by EPSRC grant number
+% EPSRC IRIS grant EP/M019055/1 on  ``Future Authentication Systems''.
 

### 2016-12-11 paper/Password2016/cameraready.tex
...

--- 2016-08-30 paper/Password2016/paper.tex
@@
 \usepackage{url}
-% \urldef{\mailsa}\path|masui@pitecan.com|
-\urldef{\mailsa}\path|***@***.***.***|
+\urldef{\mailsa}\path|masui@sfc.keio.ac.jp|
 \newcommand{\keywords}[1]{\par\addvspace\baselineskip
@@
 %
-% \author{Toshiyuki Masui%
-\author{***** ****
+\author{Toshiyuki Masui%
 % \thanks{Thanks...}%
@@
 % unless you accept that it will be published
-%\institute{Faculty of Environment and Information Studies, Keio University\\
-%5322 Endo, Fujisawa, Kanagawa 252-8520, Japan\\
-%\mailsa\\
-%\url{http://pitecan.com/}}
-\institute{******* ******* ******* *******\\
-******, ****** *******, *******\\
+\institute{Faculty of Environment and Information Studies, Keio University\\
+5322 Endo, Fujisawa, Kanagawa 252-8520, Japan\\
 \mailsa\\
-% \url{http://pitecan.com/}}
-\url{http://*****.***.***/}}
+\url{http://pitecan.com/}}
 
@@
 When the user clicks on different candidate answers 
-the seed string is converted to a completely different strings, such as
+the seed string is converted to a completely different string, such as
 ``\textsf{Xvdkzb940345}'', as shown in Figure \ref{web11}.
@@
 used as the password for the service.
+
+% Frank:
+% This is a very overconstraining way of saying ``upper, lower and
+% digits''. First, it says ``one upper, five lower, six
+% digits''. Second, it puts them in specific places. Aren't you being a
+% lot more prescriptive than the site's own policy? This reduces the
+% space of passwords that can be generated, for very little benefit.
+%
+% そうかな? まぁ言いたいことはわかるけど
 
@@
 different services just by changing the seed string.
+Seed strings like ``\textsf{Amazon123456}'' and ``\textsf{Facebook123456}'' are used
+in the examples because users can easily remember
+for which service the set of seeds and Q-A pairs are used.
+Users don't have to remember the seed strings,
+just like users don't have to remember the Q-A pairs.
 
@@
 
+% David opinion
 % \marginnote{The fact that an `old' memory is unlikely to be forgotten
@@
 %   on memory/psychology about this if you're aware of any?}
+
+% Frank:
+% I second David's margin note. Can you back this claim--or more
+% precisely the implied claim that old episodic memories will be
+% unforgettable? (You could argue that no, you only said that IF the
+% memory is old, episodic and unforgettable, THEN there's little chance
+% to lose the password; you haven't said that IF the memory is old and
+% episodic THEN it is unforgettable. Ok, ok, but then the question
+% becomes: if I come up with and old and episodic memory, how do I know
+% if it's a good one (unforgettable) or one that I will forget later? If
+% you answer ``it never happens'' then you must back this claim. If it
+% can happen, you should give me a criterion to tell in advance if it
+% will, and why I should trust it.
 
@@
 
-\item Memories of bad experience such as embarrassing blunders or failures, especially in the case where
-it was never admitted to anyone else.
+\item Memories of bad experience such as embarrassing blunders or failures,
+especially in the case where it was never admitted to anyone else.
 
@@
 For example, if the answer to the question is ``Colorado'',
-we can easily provide fake answers like ``California'', ``Utah'', etc.
+we can easily provide fake answers like ``California'', ``Utah'', {\it etc}.
 because we can use the list of states in the U.S. as possible answers.
@@
 %
-To prevent this, it is safer to keep all of the questions and answers
-in a secret place or
+To prevent this, users can prefer saving questions and answers in a secret place or
 use sufficient questions to prevent such a brute-force attack from being viable.
+The entropy of 12 questions with 30 candidate answers 
+is 58.9 ($12 \times \log_2 30$) bits, and this is considered to be safe
+enough at this moment.
 
@@
 Answering to many questions takes much longer time than typing a
-remembered password, so most people may prefer typing password
+remembered password, so people may prefer typing password
 rather than using EpisoPass if they have to log in to a service frequently.
@@
 available on GitHub\footnote{
-  (url removed for double-blind review)
-  % \url{https://EpisoPass.com/},
-  % \url{https://github.com/masui/EpisoPass}
+  \url{https://EpisoPass.com/},
+  \url{https://github.com/masui/EpisoPass}
 }. EpisoPass currently has only a small user-base, one major
@@
 
-\subsection*{Note.}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\subsubsection*{Acknowledgments.}
+
+This paper was written while on
+sabbatical at the University of Cambridge, hosted by Frank Stajano and
+the Pico group, and supported by EPSRC grant number
+EPSRC IRIS grant EP/M019055/1 on  ``Future Authentication Systems''.
+%
+We would like to thank Frank Stajano and David Llewellyn-Jones for
+giving many valuable advices to our work.
+
+\subsubsection*{Note.}
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% \subsection{Citations}
-
-% \marginnote{I've added some text in about the grant. Please change it
-%   as you see fit of course. I'm afraid I don't know the grant number
-%   so have left a gap; ideally this should be added in too.}
-
-% \subsubsection*{Acknowledgments.}
-% This paper was written while on
-% sabbatical at the University of Cambridge, hosted by Frank Stajano and
-% the Pico group, and supported by EPSRC grant number
-% EPSRC IRIS grant EP/M019055/1 on  ``Future Authentication Systems''.
-
 \bibliographystyle{splncs03}
-\bibliography{paper}
+\bibliography{cameraready}
 

### 2016-12-11 paper/Password2016/david.tex
...

--- 2016-08-29 paper/Password2016/paper.tex
@@
 
+\marginnote{I'd hesitate to call passwords the {\it strongest\/} method. Perhaps {\it most widely deployed\/} would be less contreversial?}
 However, password-based authentication is still the most
@@
 
-The idea of using episodic memories for authentication has a long history.
-Early papers suggested using episodic memories for creating passwords.
-Authentication by using secret questions,
-sometimes called as ``cognitive passwords''\cite{Zviran:1990:UAC:100512.100538},
-has long been used as an
-alternative to password-based authentication systems.
+\begin{figure}
+\centering
+% \includegraphics[width=1.0\columnwidth]{figures/c1bd6e7f67698c70978f528ccd2339d9}
+\includegraphics[width=1.0\columnwidth]{figures/4d13e6804ba790624c1f8e2b8255bde5}
+\caption{Generating an Amazon password with EpisoPass.}
+\label{web1}
+\end{figure}
+
+\marginnote{You mention that episodic memories and cognitive passwords have been used in the past, but it's not clear to me (from the text here) why your system is different.
+Perhaps you could put a sentence or two about this?}
+
+The idea of using episodic memories for authentication has a long history and early papers suggested using episodic memories for creating passwords.
+Authentication using secret questions is sometimes referred to as ``cognitive passwords''\cite{Zviran:1990:UAC:100512.100538}, and such approaches have been used as an alternative to password-based authentication systems.
 %
@@
 \begin{enumerate}
-\item A user registers many question texts related to the user's personal
-secret episodic memories that the user never forgets,
-and provides a correct answer and additional fake answers.
+\item A user registers multiple question texts related to their own personal
+secret unforgettable episodic memories. For each question they must provides
+a single correct answer and multiple additional incorrect answers.
 
@@
 
-\item EpisoPass shows the data to the user so that
-the user can select the right answer for each question.
+\item EpisoPass shows the questions and answers to the user allowing
+them to select the correct answer for each question.
 Based on the user's selections,
-EpisoPass substitutes characters in the seed string and generates
-strong password candidate strings.
-After selecting all the right answers,
+EpisoPass substitutes characters in the seed string and generates a
+strong password candidate string.
+After selecting all of the correct answers,
 the user copies the calculated string
-and register it as the password for the service.
+and registers it as the password for the service.
 \end{enumerate}
 
-\begin{figure}[H]
-\centering
-% \includegraphics[width=1.0\columnwidth]{figures/c1bd6e7f67698c70978f528ccd2339d9}
-\includegraphics[width=1.0\columnwidth]{figures/4d13e6804ba790624c1f8e2b8255bde5}
-\caption{Generating an Amazon password with EpisoPass.}
-\label{web1}
-\end{figure}
-
-\subsection{Using EpisoPass on a browser}
+\subsection{Using EpisoPass in a browser}
 
 Figure \ref{web1} shows how to generate a password
-on EpisoPass running on a browser.
+on EpisoPass running in a browser by accessing the EpisoPass site.
 Many questions related to the user's episodic memories are shown to the user,
 and many candidate answers are also shown for each question.
-When a user clicks and selects one of the answers for each question,
+When a user clicks and selects one of the answers for a question,
 the seed string shown at the top-left is converted to a
 candidate password string based on the selections.
-When the user selects the correct answers to all the questions,
-the right password is calculated and shown at the top.
+If incorrect answers are chosen the wrong password will be generated.
+On the other hand, when the user selects the correct answers for all of the questions,
+the correct password is calculated and shown at the top of the page.
 
@@
 
-If a user doesn't like to use the EpisoPass service on the Net,
-he can use an EpisoPass application on Android
-which does not use network connections.
+\marginnote{Is the Android app generated as a unique app for each user? If so, I think it's worth making this clear.}
+If a user prefers not to use the EpisoPass service on the Web,
+there is an alternative EpisoPass application for Android
+which requires no network connection.
 After registering questions and answers on the EpisoPass service,
 the user can download an Android application from the server
-by clicking the ``Android app'' button at the top.
-The application contains all the information required for generating passwords.
-(The application is compiled and built on the server.)
+by clicking the ``Android app'' button at the top of the page.
+The application is compiled and built on the server and contains
+all of the information needed for the particular user to
+generate passwords using the Q-A sets entered.
 
 When the user runs the application and selects the correct answer
-to each question, he can eventually get the password and copy it to the password entry.
-(Figure \ref{android1},\ref{android2})
+to each question, the password will be generated in the same way as
+on the site, as shown in Figures \ref{android1} and \ref{android2}.
+This can then be copied to the password entry for access
+to a particular service.
 
-\begin{figure}[H]
+\begin{figure}
 \centering
-\includegraphics[width=0.7\columnwidth]{figures/429eec261024dc6c85351f51c12f09b4}
+\includegraphics[width=0.4\columnwidth]{figures/429eec261024dc6c85351f51c12f09b4}
 \caption{Running EpisoPass on Android.}
@@
 %
-Figure \ref{extension} shows the login page of Amazon.com, with which
-EpisoPass questions are automatically displayed by the browser extension.
+Figure \ref{extension} shows the login page of Amazon.com, with the 
+EpisoPass questions automatically overlaid directly onto the page
+by the browser extension.
 %
-Here, when the Amazon login page is accessed from the browser,
-the browser extension program automatically runs on the page,
-acquires questions and answers from the EpisoPass server,
-and shows them to the user just the same way as the Android application.
+When the user accesses the Amazon login page,
+the browser extension automatically runs on the page,
+acquires the questions and answers from the EpisoPass server,
+and displays them using the same style as for the Android application.
 %
-After answering all the questions, a password is calculated from the
-selected answers and pasted to the password field of the page.
-Using the extension, users can login to various services just by
-answering questions, without seeing any password string.
-It looks as if these services are offering
-EpisoPass-based authentication.
+After answering all of the questions, a password is calculated from the
+selected answers and automatically pasted into the password field of the page
+by the extension. In this way users can log in to various services just by
+answering the questions presented, and without even seeing the password string.
+It appears as if the EpisoPass-based authentication is being provided directly
+by the services themselves.
 
-\begin{figure}[H]
-\centering
-\includegraphics[width=0.9\columnwidth]{figures/aeff16ffcab956e554364e9e5aca8359}
-\caption{Using EpisoPass on the login window.}
-\label{extension}
-\end{figure}
+\section{Discussion}
 
-\section{Discussions}
-
-In this section, we discuss the advantages and caveats of using EpisoPass.
+In this section, we discuss the advantages and potential disadvantages of using EpisoPass.
 
 \subsection{Recallability of answers}
+
+\marginnote{The fact that an `old' memory is unlikely to be forgotten is perhaps obvious, but this could be a good place
+to cite a paper on memory/psychology about this if you're aware of any?}
 
@@
 %
-Users of EpisoPass can save the seed string and question-answer data
-at any place, and easily generate passwords by running
-EpisoPass and answering questions.
-If the question is based on old unforgettable episodic memories,
-there is little chance of losing passwords
-as long as the seed string and the questions are available.
-If the user's memory is related to an episode of 20 years ago and the user clearly
-remembers the episode now, it is unlikely that he forgets the episode 10 years later.
+The seed string and question-answer data is essentially public,
+and users of EpisoPass can save them wherever is convenient. They can
+then easily generate passwords by running
+EpisoPass and answering the questions.
+If a question is based on old unforgettable episodic memory,
+there is little chance of losing the password for a service
+as long as the seed string and questions are available.
+If the user's memory is related to an episode that took place 20 years ago, say, and the user clearly
+still remembers the episode now, it is unlikely the episode will be forgotten in the future.
 
 \subsection{Selection of seed strings}
+
+\marginnote{In the comments you mention that ``generating service-specific unique seed string is not trivial''. I think this is worth mentioning in the paper.}
 
@@
 ``\textsf{Facebook123456}'' was used for Facebook.
-Such strings are used because they are easily memorable.
-Of course any seed string can be used as seeds for various services,
-and automatic generation of seed strings is possible.
+Such strings were chosen because they are easily memorable.
+In practice any seed string could be used as the seeds for the various services,
+and automatic generation of seed strings is a possibility.
 
@@
 
-The strength of the generated password depends on the number of
-questions and the secret level of the questions.
+The strength of the generated passwords depends on the number and 
+level of secrecy of the questions.
 %
 There have been many studies on the strength of passwords
-\cite{Hayashi:2011:DSP:1978942.1979326}%
-\cite{Komanduri:2011:PPM:1978942.1979321}, % What password is strong
-but the strength of secret questions has not been studied enough.
+\cite{Hayashi:2011:DSP:1978942.1979326,Komanduri:2011:PPM:1978942.1979321}, % What password is strong
+but measuring the strength of secret questions is an area where more study is needed.
 %
-When we use 10 secret questions with 20 answers and
-there's no clue for the answer,
-1 billion ($20^{10}$) trials should be performed to check
-all the combinations of the answers,
+\marginnote{I calculate $20^{10} = 10,240,000,000,000$. This is considerably more than a billion (closer to 10 thousand billion, (US) or 10 million million (UK).}
+%
+Using ten secret questions each with twenty answers, where each answer is considered equally likely,
+an attacker would need to cover a search space of over a billion ($20^{10}$) values to check
+every potential combination of answers,
 and the entropy of the system is 43.2 ($10 \times \log_2 20$) bits.  % 10.0 * (Math.log(20.0)/Math.log(2.0))

### 2016-12-11 paper/Password2016/dlj.tex
...

--- 2016-12-11 paper/Password2016/david.tex
@@
 If we want to avoid having to carry any special device for authentication,
-either we must used some form of biometrics, or all the information required 
-for the authentication must be
-must be stored in the user's memory.
+all the information required for the authentication should be
+kept in the users' brain.
 %
-However, the biggest problem with memory-based authentication is that
-users cannot reliably remember passwords or master password that are long and complex enough to be secure.
+However, the biggest problem of brain-based authentication is that
+users cannot safely keep memories like long passwords or master password.
 For this reason, we believe that
 it is far better to ``generate'' something for the authentication,
-based on a user's episodic memories. This has the benefit that unlike a password, a person is highly unlikely to forget such episodic memories.
+based on users' episodic memories that they can never forget.
 %
@@
 %
-We therefore propose \textit{EpisoPass}, a password manager that generates strong passwords
-based only on a user's secret and unforgettable episodic memories.
+We propose a password manager \textit{EpisoPass} that generates strong passwords
+based only on the user's secret episodic memories that the user cannot forget.
 
@@
 
-EpisoPass is a password manager that supports the generation of
-strong passwords based on a user's secret episodic memories.
+EpisoPass is a password manager that supports generating
+strong passwords based on users' secret episodic memories.
 %
@@
 % Memories in human brain are not uniform.
-Our brains store numerous memories, but different memories have different characteristics.
-Some memories are very short-lived, while others are recallable for long periods of time.
-When we have a particularly impressive experience,
-the memory of it will stay in our mind for a long time and can't be easily forgotten.
-On the other hand, other topics are more difficult to remember. For example, when studying mathematics and trying to remember a new formula,
-it can be hard to memorize without significant practice,
-since knowledge of the formula is unrelated to
+We keep various memories in our brain, but different memories have different natures.
+Some memories are very short-lived, and others remain for a long time.
+When we have a very impressive experience,
+that memory will stay in the brain for a long time and
+cannot easily disappear.
+On the other hand, when we study math and try to remember a new formula,
+it is usually hard to memorize it unless we practice a lot,
+since the knowledge about the formula is not related to
 any personal experiences.
-The former type of memory is called an {\it episodic\/} memory and most people find such
-memories easy to recollect and hard to forget.
-Memories of passwords belong in the latter category. People find them
-hard to remember and easy to forget, in the same way people find it difficult
-to remember mathematical formulas.
+The former type of memory is called the episodic memory and
+people cannot easily lose it.
+Memories of passwords belong to the latter type and
+people cannot easily remember them, just like people cannot
+remember math formulas easily.
 
@@
 
-\begin{figure}
+The idea of using episodic memories for authentication has a long history.
+Early papers suggested using episodic memories for creating passwords.
+Authentication by using secret questions,
+sometimes called as ``cognitive passwords''\cite{Zviran:1990:UAC:100512.100538},
+has long been used as an
+alternative to password-based authentication systems.
+%
+% However, conversion from episodic memories to password strings
+% was not studied at all.
+
+Password generation on EpisoPass is performed through the following steps:
+
+\begin{enumerate}
+\item A user registers many question texts related to the user's personal
+secret episodic memories that the user never forgets,
+and provides a correct answer and additional fake answers.
+
+\item The user provides a long ``seed string'' for each service that requires
+a password.
+
+\item EpisoPass shows the data to the user so that
+the user can select the right answer for each question.
+Based on the user's selections,
+EpisoPass substitutes characters in the seed string and generates
+strong password candidate strings.
+After selecting all the right answers,
+the user copies the calculated string
+and register it as the password for the service.
+\end{enumerate}
+
+\begin{figure}[H]
 \centering
@@
 
-\marginnote{You mention that episodic memories and cognitive passwords have been used in the past, but it's not clear to me (from the text here) why your system is different.
-Perhaps you could put a sentence or two about this?}
-
-The idea of using episodic memories for authentication has a long history and early papers suggested using episodic memories for creating passwords.
-Authentication using secret questions is sometimes referred to as ``cognitive passwords''\cite{Zviran:1990:UAC:100512.100538}, and such approaches have been used as an alternative to password-based authentication systems.
-%
-% However, conversion from episodic memories to password strings
-% was not studied at all.
-
-Password generation on EpisoPass is performed through the following steps:
-
-\begin{enumerate}
-\item A user registers multiple question texts related to their own personal
-secret unforgettable episodic memories. For each question they must provides
-a single correct answer and multiple additional incorrect answers.
-
-\item The user provides a long ``seed string'' for each service that requires
-a password.
-
-\item EpisoPass shows the questions and answers to the user allowing
-them to select the correct answer for each question.
-Based on the user's selections,
-EpisoPass substitutes characters in the seed string and generates a
-strong password candidate string.
-After selecting all of the correct answers,
-the user copies the calculated string
-and registers it as the password for the service.
-\end{enumerate}
-
-\subsection{Using EpisoPass in a browser}
+\subsection{Using EpisoPass on a browser}
 
 Figure \ref{web1} shows how to generate a password
-on EpisoPass running in a browser by accessing the EpisoPass site.
+on EpisoPass running on a browser.
 Many questions related to the user's episodic memories are shown to the user,
 and many candidate answers are also shown for each question.
-When a user clicks and selects one of the answers for a question,
+When a user clicks and selects one of the answers for each question,
 the seed string shown at the top-left is converted to a
 candidate password string based on the selections.
-If incorrect answers are chosen the wrong password will be generated.
-On the other hand, when the user selects the correct answers for all of the questions,
-the correct password is calculated and shown at the top of the page.
+When the user selects the correct answers to all the questions,
+the right password is calculated and shown at the top.
 
@@
 ``\textsf{Amazon123456}'' is provided as the seed string,
-and based on the selections to the ten questions,
-the seed string is converted to the string
+and according to the selections to the five questions,
+the seed string is converted to a string
 ``\textsf{Tblgeq808187}'',
-to be used as the password for Amazon.com.
+which can be used as the password for Amazon.com.
 
-When the user clicks on different candidate answers 
-the seed string is converted to a completely different strings, such as
-``\textsf{Xvdkzb940345}'', as shown in Figure \ref{web11}.
+When the user clicks another candidate,
+the seed string is converted to another strings like
+``\textsf{Xvdkzb940345}'' (Figure \ref{web11}).
 
-In this way, different selections yield different password strings and
-the unique password string generated after selecting the correct answers should be
+\begin{figure}[H]
+\centering
+\includegraphics[width=1.0\columnwidth]{figures/8447eaba1ede0f678b3ce6fea63681f3}
+\caption{Selecting a different answer.}
+\label{web11}
+\end{figure}
+
+In this way, different selections yields different password strings and
+the password string generated after selecting correct answers can be
 used as the password for the service.
 
-Capital letters in the seed string are substituted for capital letters in the password,
-and digits in the seed string are substituted for digits. In this way
-the generated password can be arranged to conform with any password character restrictions
-the site might impose.
+Capital letters in the seed string are substituted to capital letters in the password,
+and digits in the seed string are substituted to digits,
+so that generated passwords conforms to password character restrictions
+sometimes requested by the service.
 
@@
 which the author believes he will never forget.
-All the questions are based on the author's episodic memories that he's unlikely to ever forget,
-and that he believes nobody else will know the correct answer for.
+All the questions are based on the author's episodic memories
+that he thinks he never forgets, and he believes that
+nobody else knows which one of the candidate is the right answer.
 
-\begin{figure}
-\centering
-\includegraphics[width=1.0\columnwidth]{figures/8447eaba1ede0f678b3ce6fea63681f3}
-\caption{Selecting a different set of answers.}
-\label{web11}
-\end{figure}
+Questions and answers can be edited directly on the browser, and they can be
+saved on the server by clicking the ``save to server'' button.
+The Q-A data sets are saved on the server,
+but no information about the correct answer or the
+generated password is saved on the server.
+The Q-A data in JSON format can be downloaded to the local machine
+by clicking the ``save to file'' button.
+the data can be uploaded to the server by dragging the JSON file to the EpisoPass page.
 
-Usability has been considered as a key consideration, and the questions 
-and answers in the figures can be edited directly in the browser. They can be
-saved on the server by clicking the ``save to server'' button or saved locally
-if the user prefers.
-While the Q-A data sets are saved, no information about the correct answer or the
-generated password is saved on the server. Consequently there is no requirement for the user
-to trust the server to keep the data secret.
-The Q-A data can be downloaded to the user's local machine in JSON format 
-by clicking the ``save to file'' button. To upload the data back to the server, the user
-simply drags the JSON file to the EpisoPass page.
-
-When the secret string is changed to ``\textsf{Facebook123456}'',
+When we change the secret string to ``\textsf{Facebook123456}'',
 the generated password changes to ``\textsf{Onjbrppy030937}'',
 as shown in Figure \ref{web2}.
-In this way, the user can generate different passwords for
+In this way, we can generate different passwords for
 different services just by changing the seed string.
 
-\begin{figure}
+\begin{figure}[H]
   \centering
@@
   \includegraphics[width=1.0\columnwidth]{figures/ab4517dd593c1cabab5fecef546f7e88}
-  \caption{Generating a new password for Facebook.}
+  \caption{Generating the password for Facebook.}
   \label{web2}
@@
 
-Character substitution is performed based on the value
-calculated by hashing a concatenation of all the questions and selected answers.
+Character substitution is performed based on the hash value
+calculated from concatenating all the questions and selected answers.
 %
 For example, if the user selects ``\textbf{\texttt{Ebisawa}}''
-as the answer to the question ``\textbf{\texttt{Who's the bully?}}'',
+to the question ``\textbf{\texttt{Who's the bully?}}'',
 a string including ``\textbf{\texttt{Who's the bully:Ebisawa}}''
@@
 
-The last question in Figure \ref{web1} is not intended as a secret question based on an
-episodic memory, but is instead a question
+The last question in Figure \ref{web1} is not a secret question, but a question
 for generating different passwords for different situations.
-By providing a question like this, the user can generate completely different passwords
-for different months and years, say.
+By providing such a question, users can generate completely different passwords
+for different months and years, for example.
 
@@
 
-\marginnote{Is the Android app generated as a unique app for each user? If so, I think it's worth making this clear.}
-If a user prefers not to use the EpisoPass service on the Web,
-there is an alternative EpisoPass application for Android
-which requires no network connection.
+If a user doesn't like to use the EpisoPass service on the Net,
+he can use an EpisoPass application on Android
+which does not use network connections.
 After registering questions and answers on the EpisoPass service,
 the user can download an Android application from the server
-by clicking the ``Android app'' button at the top of the page.
-The application is compiled and built on the server and contains
-all of the information needed for the particular user to
-generate passwords using the Q-A sets entered.
+by clicking the ``Android app'' button at the top.
+The application contains all the information required for generating passwords.
+(The application is compiled and built on the server.)
 
 When the user runs the application and selects the correct answer
-to each question, the password will be generated in the same way as
-on the site, as shown in Figures \ref{android1} and \ref{android2}.
-This can then be copied to the password entry for access
-to a particular service.
+to each question, he can eventually get the password and copy it to the password entry.
+(Figure \ref{android1},\ref{android2})
 
-\begin{figure}
+\begin{figure}[H]
 \centering
-\includegraphics[width=0.4\columnwidth]{figures/429eec261024dc6c85351f51c12f09b4}
+\includegraphics[width=0.7\columnwidth]{figures/429eec261024dc6c85351f51c12f09b4}
 \caption{Running EpisoPass on Android.}
@@
 
-\begin{figure}
+\begin{figure}[H]
 \centering
-\includegraphics[width=0.4\columnwidth]{figures/ba8f5aeaa935ad63437969f4d746746b}
+\includegraphics[width=0.7\columnwidth]{figures/ba8f5aeaa935ad63437969f4d746746b}
 \caption{After finishing selections.}
@@
 
-The calculation is performed on Android without the need for a network connection,
-so the user can safely generate passwords without being concerned about an
-attacker observing any data transfer.
+The calculation is performed on Android without network connection,
+and the user can safely generate passwords 
+without feeling the fear of being observed by attackers.
 
@@
 
-One of the difficulties of the previous two approaches is that the user 
-must re-type or copy the password string into the service's password
-field after it's been generated.
-This isn't ideally convenient, so we have also developed a browser 
-extension that allows EpisoPass to be used directly with the login
-page of services on the Web.
+When a user use the EpisoPass service or the EpisoPass application,
+he has to type or copy the password string after generating the password.
+Since it is not convenient,
+we provide a browser extension for using EpisoPass on the login window of
+various Web services.
 
-\begin{figure}
+A browser extension is a JavaScript add-on program which runs
+on top of existing Web pages.
+%
+Figure \ref{extension} shows the login page of Amazon.com, with which
+EpisoPass questions are automatically displayed by the browser extension.
+%
+Here, when the Amazon login page is accessed from the browser,
+the browser extension program automatically runs on the page,
+acquires questions and answers from the EpisoPass server,
+and shows them to the user just the same way as the Android application.
+%
+After answering all the questions, a password is calculated from the
+selected answers and pasted to the password field of the page.
+Using the extension, users can login to various services just by
+answering questions, without seeing any password string.
+It looks as if these services are offering
+EpisoPass-based authentication.
+
+\begin{figure}[H]
 \centering
-\includegraphics[width=0.8\columnwidth]{figures/aeff16ffcab956e554364e9e5aca8359}
+\includegraphics[width=0.9\columnwidth]{figures/aeff16ffcab956e554364e9e5aca8359}
 \caption{Using EpisoPass on the login window.}
@@
 
-A browser extension is a JavaScript add-on program which runs
-on top of existing Web pages.
-%
-Figure \ref{extension} shows the login page of Amazon.com, with the 
-EpisoPass questions automatically overlaid directly onto the page
-by the browser extension.
-%
-When the user accesses the Amazon login page,
-the browser extension automatically runs on the page,
-acquires the questions and answers from the EpisoPass server,
-and displays them using the same style as for the Android application.
-%
-After answering all of the questions, a password is calculated from the
-selected answers and automatically pasted into the password field of the page
-by the extension. In this way users can log in to various services just by
-answering the questions presented, and without even seeing the password string.
-It appears as if the EpisoPass-based authentication is being provided directly
-by the services themselves.
+\section{Discussions}
 
-\section{Discussion}
-
-In this section, we discuss the advantages and potential disadvantages of using EpisoPass.
+In this section, we discuss the advantages and caveats of using EpisoPass.
 
 \subsection{Recallability of answers}
-
-\marginnote{The fact that an `old' memory is unlikely to be forgotten is perhaps obvious, but this could be a good place
-to cite a paper on memory/psychology about this if you're aware of any?}
 
@@
 %
-The seed string and question-answer data is essentially public,
-and users of EpisoPass can save them wherever is convenient. They can
-then easily generate passwords by running
-EpisoPass and answering the questions.
-If a question is based on old unforgettable episodic memory,
-there is little chance of losing the password for a service
-as long as the seed string and questions are available.
-If the user's memory is related to an episode that took place 20 years ago, say, and the user clearly
-still remembers the episode now, it is unlikely the episode will be forgotten in the future.
+Users of EpisoPass can save the seed string and question-answer data
+at any place, and easily generate passwords by running
+EpisoPass and answering questions.
+If the question is based on old unforgettable episodic memories,
+there is little chance of losing passwords
+as long as the seed string and the questions are available.
+If the user's memory is related to an episode of 20 years ago and the user clearly
+remembers the episode now, it is unlikely that he forgets the episode 10 years later.
 
 \subsection{Selection of seed strings}
-
-\marginnote{In the comments you mention that ``generating service-specific unique seed string is not trivial''. I think this is worth mentioning in the paper.}
 
@@
 ``\textsf{Facebook123456}'' was used for Facebook.
-Such strings were chosen because they are easily memorable.
-In practice any seed string could be used as the seeds for the various services,
-and automatic generation of seed strings is a possibility.
+Such strings are used because they are easily memorable.
+Of course any seed string can be used as seeds for various services,
+and automatic generation of seed strings is possible.
 
@@
 
-The strength of the generated passwords depends on the number and 
-level of secrecy of the questions.
+The strength of the generated password depends on the number of
+questions and the secret level of the questions.
 %
 There have been many studies on the strength of passwords
-\cite{Hayashi:2011:DSP:1978942.1979326,Komanduri:2011:PPM:1978942.1979321}, % What password is strong
-but measuring the strength of secret questions is an area where more study is needed.
+\cite{Hayashi:2011:DSP:1978942.1979326}%
+\cite{Komanduri:2011:PPM:1978942.1979321}, % What password is strong
+but the strength of secret questions has not been studied enough.
 %
-\marginnote{I calculate $20^{10} = 10,240,000,000,000$. This is considerably more than a billion (closer to 10 thousand billion, (US) or 10 million million (UK).}
-%
-Using ten secret questions each with twenty answers, where each answer is considered equally likely,
-an attacker would need to cover a search space of over a billion ($20^{10}$) values to check
-every potential combination of answers,
+When we use 10 secret questions with 20 answers and
+there's no clue for the answer,
+1 billion ($20^{10}$) trials should be performed to check
+all the combinations of the answers,
 and the entropy of the system is 43.2 ($10 \times \log_2 20$) bits.  % 10.0 * (Math.log(20.0)/Math.log(2.0))
 %
-This represents roughly the same entropy as using a random 8-character Latin-alphabet
-password, for which the entropy is 45.6 bits.
+It is almost the same entropy as using random 8-character English alphabets
+as a password, in which case the entropy is 45.6 bits.
 This level is considered to be strong enough for Web services,
-where it's not possible to perform online brute-force attacks \cite{Florencio:2007:SWP:1361419.1361429}.
+where online brute-force attack is impossible\cite{Florencio:2007:SWP:1361419.1361429}.
 
@@
 
-The quality of the questions is key to using EpisoPass effectively.
+The quality of the questions is the key to using EpisoPass.
 If the episode is shared by someone else,
-this other person might easily be able to answer the question and generate the
-user's password.
+that person can easily answer the question and generate the
+password just like the user.
 %
-The episode related to each question should therefore not be known to any other person,
+The episode related to each question should not be known to other people,
 and the episode should be unforgettable.
 %
-Finding such episodes seems difficult at first, but our experience
-has been that we try to remember such experiences from our personal past,
-we can soon recall many trivial episodes which are unforgettable but
-nonetheless not important to other people.
+Finding such episodes seems difficult at first, but
+when we try to remember experiences of old days,
+we can recall many trivial episodes which are unforgettable but
+not important to other people.
 %
-The following list shows some examples of experiences that we believe make good candidates for
-EpisoPass questions.
+Old experiences like the following are candidates for
+good questions used in EpisoPass.
 
 \begin{itemize}
-\item Memories of very minor injuries that nobody would have cared about apart from you.
+\item Memory of small injury. (Nobody cares it but you.)
 
-\item Memories of bad experience such as embarrassing blunders or failures, especially in the case where
-it was never admitted to anyone else.
+\item Memories of bad experience like blunders or defeat.
+(You don't tell it to anybody.)
 
-\item Experiences of finding inconsequential but special items which only you are interested in.
+\item Experience of finding a small special item which only you are interested in.
 \end{itemize}
 
-For example, a question such as
-``who hit you when you were six years old?''
-is about a trivial experience that most people would never have reason to discuss,
-but an experience that may have been unpleasant at the time is hard to forget.
+For example, a question like
+``who hit you when you were 6 years old?''
+is about a trivial experience that people do not mention,
+but a bad experience like this is not forgettable.
 
-Questions such as ``Which food do you like best?'' should be avoided,
-since friends or family might know the user's tastes, thereby allowing 
-others to select the correct answer.
+Questions like ``Which food do you like best?'' should be avoided,
+since some of the friends might know the user's taste.
 Questions related to an episode which the user is proud of should also be
-avoided, since this is a something the user might prefer to discuss with others.
+avoided, since the user might talk about the episode to somebody else.
 
-We don't usually talk about trivial bad experiences with other people,
-but we might boast about good experiences (some might even write blog posts about them).
-Similarly our tastes ({\it e.g.\/} favorite foods) might change in the long run.
-Using such episodes for questions should therefore be avoided.
+We usually don't tell our bad trivial experiences to other people,
+but we might boast of good experiences or even write a blog about it.
+Also, our tastes (e.g. favorite food) might change in the long run.
+Using such episodes for questions should be avoided.
 
@@
 
-It can be difficult to provide a large number of false answers to a question like
-``what is your favorite sport?''
-because the number of possible answers is limited.
+It is difficult to provide enough number of fake answers to a question like
+``what was your favorite sport?''
+because the number of possible answers are limited.
 %
 On the other hand, if the right answer to the question is a name of a place or a person,
-generating similar answers is straightforward.
+generating similar answers is easy.
 For example, if the answer to the question is ``Colorado'',
 we can easily provide fake answers like ``California'', ``Utah'', etc.
-because we can use the list of states in the U.S. as possible answers.
+because we can use the list of states in the U.S.
 
-In this way, false answers can be easily generated
+In this way, fake answers can be easily generated
 if it is possible to collect words which belong to the same
@@
 Various methods have been proposed for collecting words in the
-same category, mainly for information retrieval tasks
-\cite{Huang:2012:LFC:2426725.2426728,BooWa,Wang:2007:LSE:1441428.1442086}. % Boo!Wa!
-We can use such systems to provide a list of potential false answers almost automatically.
+same category, mainly for information retrieval tasks%
+\cite{Huang:2012:LFC:2426725.2426728}% 
+\cite{BooWa}% Boo!Wa!
+\cite{Wang:2007:LSE:1441428.1442086}.
+Using such systems, we can get a list of fake answers almost automatically.
 
@@
 
-Although everyone has to make use of authentication systems, not everyone
-is good at handling passwords.
+Although everyone has to use authentication systems on the Internet these days,
+not all the people are good at handling passwords.
 Even experienced computer users have trouble with passwords,
-since choosing a good password is unintuitive and remembering complex
-passwords is hard.
+since choosing a good password is not intuitive and
+people forget passwords very easily.
 %
-Using EpisoPass, people can use password-based systems without having to invent
-techniques for creating and remembering strong passwords. The Q-A configuration step
-is a one-time process, after which the system becomes straightforward to use.
+Using EpisoPass, people can use password-based systems without knowing
+techniques for creating and remembering strong passwords.
+They only have to provide
+questions and answers based on secret episodic memories.
 %
@@
 Our experience of using browser extensions suggests that
-this approach offers the most seamless experience.
+this approach is worth consideration.
 
-\subsection{Password requiring frequent updates}
+\subsection{Frequent password update}
 
-Many services still require users to change passwords periodically in an attempt
+On many services, users are requested to change passwords periodically
 to strengthen security.
 %
-Although this is no longer considered good-practice, since humans struggle to
-generate a stream of strong passwords \cite{Schneier:change}, the practice is
-still widespread.
+Such a practice is not recommended these days
+because humans cannot create strong passwords frequently\cite{Schneier:change}.
 %
@@
 %
-Using EpisoPass, users can provide a date-related question
-similar to that shown as the final question in Figure \ref{web1}. This allows
-different strong passwords to be generated depending on the answer chosen
-for this question. Using this technique, people can easily manage both old and new 
-passwords efficiently.
+Using EpisoPass, users can just provide a date-related question
+like the last question shown in Figure \ref{web1},
+and generate different strong passwords based on the answer.
+Using this technique, people can easily manage old and new passwords.
 

### 2016-12-11 paper/Password2016/junk.tex
...

--- 2016-12-11 paper/Password2016/dlj.tex
@@
 \usepackage{graphicx}
-\usepackage{marginnote}
 
@@
 \usepackage{url}
-% \urldef{\mailsa}\path|masui@pitecan.com|
-\urldef{\mailsa}\path|***@***.***.***|
+\urldef{\mailsa}\path|masui@pitecan.com|
 \newcommand{\keywords}[1]{\par\addvspace\baselineskip
@@
 % a short form should be given in case it is too long for the running head
-\titlerunning{EpisoPass: Password Management based on Episodic Memories}
+\titlerunning{Lecture Notes in Computer Science: Authors' Instructions}
 
@@
 %
-% \author{Toshiyuki Masui%
-\author{***** ****
-% \thanks{Thanks...}%
+\author{Toshiyuki Masui%
+\thanks{Thanks...}%
 }
@@
 
-Passwords have been used as a means of authenticating to Web services and applications
-for a long time, and remain the most popular authentication method on the Internet.
+Passwords have been used for various Web services and applications
+for a long time, and currently the most popular authentication method on the Internet.
 %
-Since short passwords are easily guessable by attackers and
-using the same password for multiple services is unsafe,
-a different long password should be used for each service a person uses.
-However, remembering numerous long passwords is almost impossible for ordinary humans.
+Since short passwords are easily guessed by attackers and
+using the same password for different services is unsafe,
+different long passwords should be used for different services.
+However,
+remembering many long passwords is almost impossible for ordinary humans.
 %
-According to research conducted by Flor\^{e}ncio {\it et al.\/} in 2007,
-people use on average only 6.5 different passwords to access 25 Web services, and
-4.28\% of users forget their passwords within 3 months \cite{Florencio:2007:LSW:1242572.1242661}.
+According to a research in 2007,
+people use 6.5 passwords on 25 Web services on average, and
+4.28\% of the users forget their passwords in 3 months\cite{Florencio:2007:LSW:1242572.1242661}.
 
-Since passwords are difficult to handle, various other authentication methods have been proposed.
-For example, image-based authentication \cite{Biddle:2012:GPL:2333112.2333114,GraphicalPasswords}, 
-biometrics\footnote{
+Since passwords are difficult to handle,
+various other authentication methods have been proposed.
+For example,
+image-based authentication\cite{Biddle:2012:GPL:2333112.2333114}\cite{GraphicalPasswords}, 
+biometrics authentication\footnote{
   % \textsf{https:{\slash}{\slash}en.wikipedia.org{\slash}wiki{\slash}Biometrics}
-  \url{https://en.wikipedia.org/w/index.php?title=Biometrics&oldid=736189000}
+  \url{https://en.wikipedia.org/wiki/Biometrics}
 },
-behavior-based authentication \cite{Dandapat:2015:AYD:2702123.2702457}, and many others.
+behavior-based authentication\cite{Dandapat:2015:AYD:2702123.2702457}, 
+and many other authentication methods have been proposed.
 
@@
 
-\marginnote{I'd hesitate to call passwords the {\it strongest\/} method. Perhaps {\it most widely deployed\/} would be less contreversial?}
-However, password-based authentication is still the most
-convenient and widely deployed method \cite{Bonneau:ReplacePasswords},
-and is not expected to disappear any time soon \cite{Herley:2009:PSS:1601990.1602010}.
+However,
+password-based authentication is still the most
+convenient and strong method\cite{Bonneau:ReplacePasswords},
+and it is not supposed to become extinct
+in a short period of time\cite{Herley:2009:PSS:1601990.1602010}.
 
-Given we will have to continue to live with password-based authentication systems for the foreseeable future,
-we have to devise practical methods for handling many passwords, and various ``password managers'' have been proposed
-\cite{OnePassword,Dashlane,MilPass,LastPass,KeyPass,NortonIDSafe,IDManager}.
+If we have to live with password-based authentication systems,
+we have to devise some ways to handle many passwords, and
+various ``password managers'' have been proposed
+\cite{OnePassword}%
+\cite{Dashlane}%
+\cite{MilPass}%
+\cite{LastPass}%
+\cite{KeyPass}%
+\cite{NortonIDSafe}%
+\cite{IDManager}.
 %
-Password managers remember users' passwords and aim to directly enter them into the login pages of the various services a user wants to access.
+Password managers remember users' passwords and help them enter
+passwords on various services.
 %
-The burden on the user is reduced by requiring just a single ``master password'' to access the database of stored passwords.
+Most password managers can manage various passwords by
+asking users to remember a single ``master password'' to access the database.
 %
-Although password managers are widely used and a clear step forward from having to remember multiple passwords, uses nonetheless have to remember the master password or use a special hardware device for safely handling the password database, and password managers usually run on only a limited set of devices.
+Although password managers are useful,
+users have to remember the master password
+or use a special hardware device
+for safely handling password managers, and
+password managers usually run on limited devices.
 
@@
 
-If we want to avoid having to carry any special device for authentication,
+If we don't want to carry any special device for authentication,
 all the information required for the authentication should be
-kept in the users' brain.
+kept in the brain.
 %
@@
 We keep various memories in our brain, but different memories have different natures.
-Some memories are very short-lived, and others remain for a long time.
+Some memories are very short-lived, and others are unforgettable.
 When we have a very impressive experience,
@@
 The idea of using episodic memories for authentication has a long history.
-Early papers suggested using episodic memories for creating passwords.
-Authentication by using secret questions,
+Early papers suggested using episodic memories for creating passwords, and
+authentication by using secret questions,
 sometimes called as ``cognitive passwords''\cite{Zviran:1990:UAC:100512.100538},
@@
 %
-% However, conversion from episodic memories to password strings
-% was not studied at all.
+However, conversion from episodic memories to password strings
+was not studied at all.
 
@@
 
-\begin{figure}[H]
-\centering
-% \includegraphics[width=1.0\columnwidth]{figures/c1bd6e7f67698c70978f528ccd2339d9}
-\includegraphics[width=1.0\columnwidth]{figures/4d13e6804ba790624c1f8e2b8255bde5}
-\caption{Generating an Amazon password with EpisoPass.}
-\label{web1}
-\end{figure}
-
 \subsection{Using EpisoPass on a browser}
@@
 candidate password string based on the selections.
-When the user selects the correct answers to all the questions,
+When the user selects the right answers to all the questions,
 the right password is calculated and shown at the top.
@@
 % use the converted string as the password.
+
+\begin{figure}[H]
+\centering
+% \includegraphics[width=1.0\columnwidth]{figures/c1bd6e7f67698c70978f528ccd2339d9}
+\includegraphics[width=1.0\columnwidth]{figures/4d13e6804ba790624c1f8e2b8255bde5}
+\caption{Generating an Amazon password with EpisoPass.}
+\label{web1}
+\end{figure}
 
@@
 The Q-A data in JSON format can be downloaded to the local machine
-by clicking the ``save to file'' button.
+by cliking the ``save to file'' button.
 the data can be uploaded to the server by dragging the JSON file to the EpisoPass page.
@@
 Character substitution is performed based on the hash value
-calculated from concatenating all the questions and selected answers.
+calculated from concatinating all the selected answers.
 %
-For example, if the user selects ``\textbf{\texttt{Ebisawa}}''
-to the question ``\textbf{\texttt{Who's the bully?}}'',
-a string including ``\textbf{\texttt{Who's the bully:Ebisawa}}''
-is used for calculating the hash value.
+For example, if the user selects ``\textbf{\texttt{Ebisawa}}'' to the question ``\textbf{\texttt{Who's the bully?}}'',
+a hash value calculated from  ``\textbf{\texttt{Who's the bully:Ebisawa}}''
+is used for the substitution.
 
@@
 
-If a user doesn't like to use the EpisoPass service on the Net,
+If a user doesn't like to use EpisoPass service on the Net,
 he can use an EpisoPass application on Android
@@
 and the user can safely generate passwords 
-without feeling the fear of being observed by attackers.
+without feeling the fear of being observed by attackers
 
 \subsection{Using the browser extension}
-\label{extensionsection}
 
@@
 A browser extension is a JavaScript add-on program which runs
-on top of existing Web pages.
+on top of existing HTML and JavaScript.
 %
@@
 After answering all the questions, a password is calculated from the
-selected answers and pasted to the password field of the page.
+selected answers and pasted to the password input form of the page.
 Using the extension, users can login to various services just by
@@
 
-In the previous examples showing the author's EpisoPass questions,
+In the previous examples showing the author's real EpisoPass questions,
 a seed string ``\textsf{Amazon123456}'' was used for Amazon.com, and
@@
 Of course any seed string can be used as seeds for various services,
-and automatic generation of seed strings is possible.
-
-% although generating service-specific unique seed string is not trivial.
-% For example, users can use the same username and password both
-% for Amazon.com and Amazon.co.uk, but not for Amazon.co.jp.
+and automatic generation of seed strings is possible,
+although generating service specific unique seed string is not trivial.
+For example, users can use the same username and password both
+for Amazon.com and Amazon.co.uk, but not for Amazon.co.jp.
 
@@
 ``what was your favorite sport?''
-because the number of possible answers are limited.
+because possible answers are limited.
 %
@@
 \cite{BooWa}% Boo!Wa!
-\cite{Wang:2007:LSE:1441428.1442086}.
+\cite{Wang:2007:LSE:1441428.1442086}.% 
 Using such systems, we can get a list of fake answers almost automatically.
@@
 Our experience of using browser extensions suggests that
-this approach is worth consideration.
+that approach is worth consideration.
 
@@
 %
-% A user can generate a new strong password by using a random character generator
+% A user can generate a new strong password by using a randam character generator
 % on a password manager, but he might want to old passwords in case some trouble happens.
@@
 
-% \subsection{Comparison with challenge-response authentication}
+\subsection{Comparison with challenge-response authentication}
+
+% 一方、{\SQ}を利用する認証の脆弱性を利用した攻撃が近年問題になっている。
+% {\PW}を忘れたときのために、
+% あらかじめ設定した{\SQ}に答えることによって{\PW}をリセットできるサービスがあり、
+% 「母親の旧姓は?」や「最初に飼ったペットの名前は?」のような
+% 質問に対してユーザが答を登録するようになっている。
+% このような問題は他人が調べたり推測したりすることが容易であるうえに
+% {\SQ}の数は一般的に少なく、
+% {\PW}よりも脆弱だといえる\cite{Rabkin:2008:PKQ:1408664.1408667}。% 銀行20個調べて{\SQ}の弱さを指摘
+
+In many services, users are adviced to define answers to secret questions like
+``what is your mother's maiden name''
+so that he can log into the service even when he forgets the password.
+This kind of authentication is far less secure than simple password systems,
+since it is fairly easy for attackers to know the right answer.
+The variation of system-provided questions are usually small, and
+such challenge-response systems are considered to be
+insecure\cite{Rabkin:2008:PKQ:1408664.1408667}.
+
+It would be better if the user can register his own secret questions
+based on his episodic memory.
+However, answers to user-generated challenge questions are more easily
+forgotten or cracked,
+and using simple challenge-responce is not considered to be safe enough
+\cite{Just:2009:PCC:1572532.1572543}\cite{Schechter:2009:NSM:1607723.1608145}.
 %
-% % 一方、{\SQ}を利用する認証の脆弱性を利用した攻撃が近年問題になっている。
-% % {\PW}を忘れたときのために、
-% % あらかじめ設定した{\SQ}に答えることによって{\PW}をリセットできるサービスがあり、
-% % 「母親の旧姓は?」や「最初に飼ったペットの名前は?」のような
-% % 質問に対してユーザが答を登録するようになっている。
-% % このような問題は他人が調べたり推測したりすることが容易であるうえに
-% % {\SQ}の数は一般的に少なく、
-% % {\PW}よりも脆弱だといえる\cite{Rabkin:2008:PKQ:1408664.1408667}。% 銀行20個調べて{\SQ}の弱さを指摘
+Also, in this case,
+the user should register the answer to the system in addition to the question.
+Telling secret facts to service providers is like
+registering raw password string on the server,
+and it is not safe unless the strings are properly hashed and salted on the server.
+
 %
-% In many services, users are advised to define answers to secret questions like
-% ``what is your mother's maiden name''
-% so that he can log into the service even when he forgets the password.
-% This kind of authentication is far less secure than simple password systems,
-% since it is fairly easy for attackers to know the right answer.
-% The variation of system-provided questions are usually small, and
-% such challenge-response systems are considered to be
-% insecure\cite{Rabkin:2008:PKQ:1408664.1408667}.
+%ユーザが作成した{\SQ}を使えばこのような問題はなくなるはずであるが、
+%他人に解かれにくい問題をユーザが作成することは難しく、
+%またユーザ自身が答を忘れてしまうことも多いと考えられている\cite{Just:2009:PCC:1572532.1572543}\cite{Schechter:2009:NSM:1607723.1608145}。
 %
-% It would be better if the user can register his own secret questions
-% based on his episodic memory.
-% However, answers to user-generated challenge questions are more easily
-% forgotten or cracked,
-% and using simple challenge-responce is not considered to be safe enough
-% \cite{Just:2009:PCC:1572532.1572543}\cite{Schechter:2009:NSM:1607723.1608145}.
-% %
-% Also, in this case,
-% the user should register the answer to the system in addition to the question.
-% Telling secret facts to service providers is like
-% registering raw password string on the server,
-% and it is not safe unless the strings are properly hashed and salted on the server.
+%また、古い記憶にもとづいて作成した秘密の問題は
+%ユーザが想像するよりも解かれやすいという実験結果にもとづき、
+%忘れない{\SQ}を複数利用する方法、
+%問題と答を連想するために画像を利用する方法、
+%複数の問題を連続的に利用する手法などが提案されている\cite{Renaud:2010:PQE:2146303.2146318}。
+
+% {\EP}では、
+% 他人には解くことが難しく自分では忘れないような{\SQ}を自由にいくつでも利用できるようになっている。
+% 問題作成に慣れていないユーザには有効な{\SQ}を作成することは難しいかもしれないが、
+% 次節で述べるように、適切な質問を選ぶことによりこの問題を解決できるはずである。
 
@@
 
-To prevent such trouble, it is safer to keep all the questions and answers
+To prevent such troble, it is safer to keep all the questions and answers
 in a secret place or
@@
 Old pictures can be used as the questions of EpisoPass,
-just like the question shown at the bottom of Figure \ref{web1}.
+just like the 5th question shown in Figure \ref{web1}.
 Even when people cannot create good secret questions,
@@
 As shown in previous sections,
-there have been many attempts for replacing password-based authentication systems,
+there have been many attemps for replacing password-based authentication systems,
 but none of them are found to be better than
@@
 
-The idea of using episodic memories for authentication is not new.
+The idea of using episodic memories for authtication is not new.
 In fact, using episodic memories for selecting password
@@
 ``who did you call last night?'' correctly, the authentication will succeed.
-Using mobile or wearable devices for authentication will become more usable
-in the future,
+Using mobile or wearable devices for authentication works in many cases,
 but users should have a fairly good long-term memory about their behaviors,
@@
 a pain for the authors, but
-currently all the information for generating passwords is put on the cloud
+currently all the information for generating passswords is put on the cloud
 and no trouble has been found during the period.
@@
 
-EpisoPass service have been on the Web and the source code is
-available on GitHub\footnote{
-  (url removed for double-blind review)
-  % \url{https://EpisoPass.com/},
-  % \url{https://github.com/masui/EpisoPass}
-}, but
-unfortunately EpisoPass is currently not used by many people.
+Unfortunately EpisoPass is currently not used by many people.
 One big reason is that most people cannot fully understand the
 idea of EpisoPass and also cannot fully trust it
-because it is not operated by a big IT company.
-% nor supported by famous computer users.
+because it is not operated by a big IT company nor supported by
+famous computer users.
 Another reason might be that users cannot estimate the strength
@@
 
-\subsection*{Note.}
-
-This paper is largely a translation of a 2013 paper published by the
-author in Japanese\cite{WISS2013}. This is the first time that the
-work is presented to an international audience in English.
-Additionally, in the intervening three years the author has
-developed the browser extension described in section \ref{extensionsection}.
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2016-12-11 Expand/expand_e.js

@@ -1,0 +1,617 @@
+(function e(t,n,r){function s(o,u){if(!n[o]){if(!t[o]){var a=typeof require=="function"&&require;if(!u&&a)return a(o,!0);if(i)return i(o,!0);var f=new Error("Cannot find module '"+o+"'");throw f.code="MODULE_NOT_FOUND",f}var l=n[o]={exports:{}};t[o][0].call(l.exports,function(e){var n=t[o][1][e];return s(n?n:e)},l,l.exports,e,t,n,r)}return n[o].exports}var i=typeof require=="function"&&require;for(var o=0;o<r.length;o++)s(r[o]);return s})({1:[function(require,module,exports){
+// Generated by CoffeeScript 1.9.3
+var Generator, amusement, animals, events, f, freqgo, generator, hasDom, i, j, len, len1, q, questions, recs, schools, search, shops, specialplace, sports, time, ul;
+
+hasDom = require('has-dom');
+
+Generator = require('re_expand');
+
+generator = new Generator();
+
+schools = "(kindergarten|elementary school|middle school|high school)";
+
+time = "(昔|子供のころ|" + schools + "のころ)";
+
+freqgo = "(よく行ってた|行ったことがある|たまに行った)";
+
+shops = "(本屋|床屋|散髪屋|レストラン|食堂|スーパー|市場|八百屋|魚屋|肉屋|店)";
+
+recs = "(旅行|BBQ|バーベキュー)";
+
+sports = "(baseball|football|hiking|climbing|surfing)";
+
+events = "(コンサート|合宿|遠足|花見)";
+
+animals = "(dog|cat|rabbit|rat|hamster)";
+
+amusement = "(the thema park|Disneyland|the zoo)";
+
+specialplace = "(the seashore|the top of the mountain|the shrine|the park|the sandbox)";
+
[…]

### 2016-12-11 Expand/junk.js

@@ -1,0 +1,11 @@
+// Generated by CoffeeScript 1.9.3
+(function() {
+  var a, i, len, ref;
+
+  ref = [10, 20, 30];
+  for (i = 0, len = ref.length; i < len; i++) {
+    a = ref[i];
+    console.log("----" + a + "----");
+  }
+
+}).call(this);

### 2016-12-11 Expand/main.js

@@ -1,0 +1,67 @@
+// Generated by CoffeeScript 1.9.3
+var Generator, amusement, animals, cat, events, f, freqgo, generator, hasDom, i, j, len, len1, q, questions, recs, schools, search, shops, specialplace, sports, time, ul;
+
+hasDom = require('has-dom');
+
+Generator = require('re_expand');
+
+generator = new Generator();
+
+schools = "(幼稚園|小学生|中学生|高校生)";
+
+time = "(昔|子供のころ|" + schools + "のころ)";
+
+freqgo = "(よく行ってた|行ったことがある|たまに行った)";
+
+shops = "(本屋|床屋|散髪屋|レストラン|食堂|スーパー|市場|八百屋|魚屋|肉屋|店)";
+
+recs = "(旅行|BBQ|バーベキュー)";
+
+sports = "(野球|サッカー|ハイキング|サーフィン|散歩)";
+
+events = "(コンサート|合宿|遠足|花見)";
+
+cat = "(ネコ|猫)";
+
+animals = "(犬|" + cat + "|ウサギ|ネズミ|ハムスター)";
+
+amusement = "(遊園地|動物園)";
+
+specialplace = "(海岸|山頂|神社|砂場)";
+
[…]

### 2016-12-11 Expand/main_e.js

@@ -1,0 +1,65 @@
+// Generated by CoffeeScript 1.9.3
+var Generator, amusement, animals, events, f, freqgo, generator, hasDom, i, j, len, len1, q, questions, recs, schools, search, shops, specialplace, sports, time, ul;
+
+hasDom = require('has-dom');
+
+Generator = require('re_expand');
+
+generator = new Generator();
+
+schools = "(kindergarten|elementary school|middle school|high school)";
+
+time = "(昔|子供のころ|" + schools + "のころ)";
+
+freqgo = "(よく行ってた|行ったことがある|たまに行った)";
+
+shops = "(本屋|床屋|散髪屋|レストラン|食堂|スーパー|市場|八百屋|魚屋|肉屋|店)";
+
+recs = "(旅行|BBQ|バーベキュー)";
+
+sports = "(baseball|football|hiking|climbing|surfing)";
+
+events = "(コンサート|合宿|遠足|花見)";
+
+animals = "(dog|cat|rabbit|rat|hamster)";
+
+amusement = "(the thema park|Disneyland|the zoo)";
+
+specialplace = "(the seashore|the top of the mountain|the shrine|the park|the sandbox)";
+
+questions = ["I had an (pain|injury) when I was going to " + schools + ".", "Bicycle collision", "Tallest person in the " + schools, "I wanted to practice (piano|guitar) when I was going to " + schools + ".", "I want to apologize for ...", "The place I used to enjoy " + sports + " at " + schools, "My (best|worst) score at math", "The person I (hated|liked|loved) in my " + schools + " days.", "The person I loved", "The person who (hated|liked|loved) me", "People who loved each other secretly", "Places I visited when I was going to " + schools, "Scared to death at (mountain|river|lake)", "Car engine stop", "Flat tire", "Lost in the city", "Stolen wallet on a trip", "Couldn't change (trains|buses|subways)", "Broken a bed in a hotel", "No paper in a toilet", "Strange thing at " + amusement, "Terrible hotel", "The restaurant we went very often", "Kind of food I always ate at the restaurant", "Missed event because of circles", "Jellyfish lie", "Blunder at job interview", "Flat tire", "What I hided at the back of the TV", "Hidden an app as a filetype", "Secret place for getting insects", "Worst guy ever", "Always complaining something", "The place I saw a snake", "My first (car|motorcycle|bicycle|guiter|CD|phone|toy)", "First experience of (mountain climbing|campin
[…]

### 2016-12-11 Extension/crypt.js

@@ -1,0 +1,81 @@
+// Generated by CoffeeScript 1.9.3
+(function() {
+  var charkind, charset, crypt_char, md5, utf2bytestr;
+
+  md5 = typeof require === 'undefined' ? exports : require('./md5.js');
+
+  charset = ['abcdefghijklmnopqrstuvwxyz', 'ABCDEFGHIJKLMNOPQRSTUVWXYZ', '0123456789', '-', '~!@#$%^&*()_=+[{]}|;:.,#?', ' ', "\"'/<>\\`"];
+
+  charkind = function(c) {
+    var ind, k, ref, results;
+    ind = null;
+    (function() {
+      results = [];
+      for (var k = 0, ref = charset.length; 0 <= ref ? k < ref : k > ref; 0 <= ref ? k++ : k--){ results.push(k); }
+      return results;
+    }).apply(this).forEach(function(i) {
+      if (charset[i].indexOf(c) >= 0) {
+        return ind = i;
+      }
+    });
+    return ind;
+  };
+
+  crypt_char = function(c, n) {
+    var chars, cind, ind, kind, len;
+    kind = charkind(c);
+    chars = charset[kind];
+    cind = chars.indexOf(c);
+    len = chars.length;
+    ind = (n - cind + len) % len;
+    return chars[ind];
+  };
+
+  utf2bytestr = function(text) {
+    var k, ref, result, results;
+    result = "";
+    if (text === null) {
+      return result;
+    }
+    (function() {
+      results = [];
+      for (var k = 0, ref = text.length; 0 <= ref ? k < ref : k > ref; 0 <= ref ? k++ : k--){ results.push(k); }
+      return results;
+    }).apply(this).forEach(function(i) {
+      var c;
+      c = text.charCodeAt(i);
+      if (c <= 0x7f) {
+        return result += String.fromCharCode(c);
+      } else {
+        if (c <= 0x07ff) {
+          result += String.fromCharCode(((c >> 6) & 0x1F) | 0xC0);
+          return result += String.fromCharCode((c & 0x3F) | 0x80);
+        } else {
+          result += String.fromCharCode(((c >> 12) & 0x0F) | 0xE0);
+          result += String.fromCharCode(((c >> 6) & 0x3F) | 0x80);
+          return result += String.fromCharCode((c & 0x3F) | 0x80);
+        }
+      }
+    });
+    return result;
+  };
+
+  exports.crypt = function(str, seeddata) {
[…]

### 2017-03-09 Expand/expand.js
...

@@ -1,0 +1,619 @@
+(function e(t,n,r){function s(o,u){if(!n[o]){if(!t[o]){var a=typeof require=="function"&&require;if(!u&&a)return a(o,!0);if(i)return i(o,!0);var f=new Error("Cannot find module '"+o+"'");throw f.code="MODULE_NOT_FOUND",f}var l=n[o]={exports:{}};t[o][0].call(l.exports,function(e){var n=t[o][1][e];return s(n?n:e)},l,l.exports,e,t,n,r)}return n[o].exports}var i=typeof require=="function"&&require;for(var o=0;o<r.length;o++)s(r[o]);return s})({1:[function(require,module,exports){
+// Generated by CoffeeScript 1.9.3
+var Generator, amusement, animals, cat, events, f, freqgo, generator, hasDom, i, j, len, len1, q, questions, recs, schools, search, shops, specialplace, sports, time, ul;
+
+hasDom = require('has-dom');
+
+Generator = require('re_expand');
+
+generator = new Generator();
+
+schools = "(幼稚園|小学生|中学生|高校生)";
+
+time = "(昔|子供のころ|" + schools + "のころ)";
+
+freqgo = "(よく行ってた|行ったことがある|たまに行った)";
+
+shops = "(本屋|床屋|散髪屋|レストラン|食堂|スーパー|市場|八百屋|魚屋|肉屋|店)";
+
+recs = "(旅行|BBQ|バーベキュー)";
+
+sports = "(野球|サッカー|ハイキング|サーフィン|散歩)";
+
+events = "(コンサート|合宿|遠足|花見)";
+
+cat = "(ネコ|猫)";
+
+animals = "(犬|" + cat + "|ウサギ|ネズミ|ハムスター)";
+
+amusement = "(遊園地|動物園)";
+
+specialplace = "(海岸|山頂|神社|砂場)";
+
[…]

### 2017-03-09 Expand/q.rb

@@ -1,0 +1,12 @@
+# -*- coding: utf-8 -*-
+require 're_expand'
+
+time = "(昔|(子供|小学生|中学生)のころ)"
+freq = "(よく行ってた|行ったことがある|たまに行った)"
+shops = "(本屋|床屋|散髪屋)"
+shopevent = "#{freq}#{shops}"
+
+s = "#{time}#{shopevent}"
+
+puts s.expand
+

### 2017-03-09 Expand/q_english.rb

@@ -1,0 +1,19 @@
+require 're_expand'
+
+questions = [
+  "I injured my (leg|hand|arm|head) at XXXX when I was (a child|very young|at school).",
+  "I had an accident at (Mt. XXX|XXX river) when I was (a child|very young|at school).",
+  "One of my friends, Mr. XXX, always did bad things to me when I was (a child|very young|at school).",
+  "I sent a special letter to Miss XXX, but didn't received any reply from her.",
+  "I personally dislike Mr. XXX.",
+  "XXX was always complainig about his (health|misfortune).",
+  "I found a very special stone at Mt. XXX.",
+  "",
+]
+
+questions.each { |question|
+  question.expand { |s,a|
+    puts s
+  }
+}
+

### 2017-03-09 Extension/app.js

@@ -1,0 +1,68 @@
+// Generated by CoffeeScript 1.9.3
+(function() {
+  var display, secretstr;
+
+  display = function(data, name, seed, passelement, qno, answer) {
+    var answers, center, div, episodiv, i, input, j, qtext, ref, results, seedinput;
+    episodiv = $('#episopass');
+    episodiv.children().remove();
+    qtext = data['qas'][qno]['question'];
+    center = $('<center>');
+    episodiv.append(center);
+    center.css('width', '100%');
+    if (qtext.match(/\/([^\/]+\.(gif|png|jpg|jpeg))$/i)) {
+      div = $('<img>').css('width', 120).attr('src', qtext);
+    } else {
+      div = $('<div>').text(qtext).css('background-color', '#ccc').css('width', '390px').css('border-radius', '5px').css('padding', '4px').css('margin', '2 auto');
+    }
+    center.append(div);
+    center.append($('<p>'));
+    div = $('<div>');
+    center.append(div);
+    if (qno === 0) {
+      seedinput = $('<input>');
+      seedinput.attr('type', 'text');
+      seedinput.val(seed);
+      div.append(seedinput);
+      div.append($('<p>'));
+    }
+    answers = data['qas'][qno]['answers'];
+    results = [];
+    for (i = j = 0, ref = answers.length; 0 <= ref ? j < ref : j > ref; i = 0 <= ref ? ++j : --j) {
+      input = $('<input>');
+      input.attr('type', 'button').attr('value', answers[i]).attr('anumber', i).css('margin', '2pt').css('padding', '1pt').click(function(event) {
+        var newpass;
+        event.preventDefault();
+        if (qno === 0) {
+          seed = seedinput.val();
+        }
+        answer[qno] = Number($(this).attr('anumber'));
+        if (qno < data['qas'].length - 1) {
+          return display(data, name, seed, passelement, qno + 1, answer);
+        } else {
+          newpass = exports.crypt(seed, secretstr(data, answer));
+          passelement.val(newpass);
+          return episodiv.remove();
+        }
+      });
+      results.push(div.append(input));
+    }
+    return results;
+  };
+
+  secretstr = function(data, answer) {
+    var i, j, qas, ref, secret;
+    secret = "";
+    qas = data['qas'];
+    for (i = j = 0, ref = qas.length; 0 <= ref ? j < ref : j > ref; i = 0 <= ref ? ++j : --j) {
+      secret += qas[i]['question'];
[…]

### 2017-03-09 Extension/episopass.js

@@ -1,0 +1,57 @@
+// Generated by CoffeeScript 1.9.3
+(function() {
+  $(function() {
+    var idelement, passelement, seed;
+    passelement = [];
+    idelement = null;
+    seed = '';
+    if (location.href.match(/facebook.com/)) {
+      passelement = $('#pass');
+      idelement = $('#email');
+      seed = 'Facebook123456';
+    }
+    if (location.href.match(/amazon/)) {
+      passelement = $('#ap_password');
+      idelement = $('#ap_email');
+      seed = 'Amazon123456';
+    }
+    if (location.href.match(/twitter.com/)) {
+      idelement = $('.LoginForm-username').children();
+      passelement = $('.LoginForm-password').children();
+      seed = 'Twitter123456';
+    }
+    if (idelement && passelement && passelement[0] !== void 0 && passelement.val() === '') {
+      return passelement.on('click', function() {
+        var browser, div, id, xhr;
+        if (!window.clicked) {
+          id = idelement.val();
+          if (!id || id === '') {
+            id = 'masui';
+          }
+          div = $('<div>').css('position', 'absolute').css('left', '200px').css('top', '250px').css('width', '400px').css('height', '250px').css('background-color', '#ddd').css('border-radius', '5px').css('z-index', '100').attr('id', 'episopass');
+          $('body').append(div);
+          browser = window.navigator.userAgent.toLowerCase();
+          if (browser.indexOf("firefox" > -1)) {
+            $.getJSON("http://episopass.com/" + id + ".json", function(data) {
+              return exports.run(data, id, seed, passelement);
+            });
+          }
+          if (browser.indexOf("chrome" > -1)) {
+            xhr = new XMLHttpRequest();
+            xhr.open("GET", "https://episopass.com/" + id + ".json", true);
+            xhr.onreadystatechange = function() {
+              var data;
+              if (xhr.readyState === 4) {
+                data = JSON.parse(xhr.responseText);
+                return exports.run(data, id, seed, passelement);
+              }
+            };
+            xhr.send();
+          }
+        }
+        return window.clicked = true;
+      });
+    }
+  });
+
+}).call(this);

### 2018-01-17 public/javascripts/easy.js
...

@@ -26,7 +26,7 @@ $(function() {
     });
     $('.button').click(function(){
         var id = $('#id').val();
-        if(id == '' || !id.match(/^[a-zA-Z0-9_@-]+$/)){
+        if(id == '' || !id.match(/^[a-zA-Z0-9_@\-\.]+$/)){
             alert("IDを半角文字列で指定して下さい");
             return;
         }

### 2018-01-19 paper/AVI2018/paper.tex
...

\documentclass[sigconf]{acmart}

\usepackage{booktabs} % For formal tables

\usepackage{graphicx}

% Copyright
%\setcopyright{none}
%\setcopyright{acmcopyright}
%\setcopyright{acmlicensed}
\setcopyright{rightsretained}
%\setcopyright{usgov}
%\setcopyright{usgovmixed}
%\setcopyright{cagov}
%\setcopyright{cagovmixed}

% % DOI
% \acmDOI{10.475/123_4}
% 
% % ISBN
% \acmISBN{123-4567-24-567/08/06}
% 
% %Conference
% \acmConference[AVI2018]{ACM Woodstock conference}{July 2018}
%               {Rome, Italy}
% \acmYear{2018}
% \copyrightyear{2018}
% 
% 
% \acmArticle{4}
% \acmPrice{15.00}

% These commands are optional
%\acmBooktitle{Transactions of the ACM Woodstock conference}
% \editor{Jennifer B. Sartor}
% \editor{Theo D'Hondt}
% \editor{Wolfgang De Meuter}

\begin{document}
\title{EpisoDAS - DAS-based password generation \\
using episodic memories}
% \titlenote{Produces the permission block, and copyright information}

\author{Toshiyuki Masui}
% \authornote{Is this necessary?.}
\orcid{1234-5678-9012}
\affiliation{%
  \institution{Keio University}
  \streetaddress{Endo}
  \city{Fujisawa}
  \state{Kanagawa}
  \postcode{43017-6221}
}
\email{masui@masui.org}

\renewcommand{\shortauthors}{T. Masui}

\begin{abstract}

We introduce a simple and powerful visual interaction technique for
managing strong passwords.  Passwords have been used for
qauthentication for decades, but appropriate handling of passwords is
difficult because people can easily forget passwords and they can be
easily cracked.
%
To make the authentication process easier, various visual interaction
methods have been proposed, including the DAS (draw-a-secret)
method. Using DAS, users can log into various services just by drawing
a secret pattern on the screen.
%
Using a DAS-based authentication method, users can quickly log into a
service without typing a password. However, remembering complex secret
patterns can be as difficult as remembering passwords. We developed
EpisoDAS, with which users can generate strong passwords based on
their secret episodic memories with a simple DAS interface.
%
users can use secret patterns for authentication, based on their
secret episodic memories which they cannot easily forget.

\end{abstract}

%
% The code below should be generated by the tool at
% http://dl.acm.org/ccs.cfm
% Please copy and paste the code instead of the example below.
%
% \begin{CCSXML}
% <ccs2012>
%  <concept>
%   <concept_id>10010520.10010553.10010562</concept_id>
%   <concept_desc>Computer systems organization~Embedded systems</concept_desc>
%   <concept_significance>500</concept_significance>
%  </concept>
%  <concept>
%   <concept_id>10010520.10010575.10010755</concept_id>
%   <concept_desc>Computer systems organization~Redundancy</concept_desc>
%   <concept_significance>300</concept_significance>
%  </concept>
%  <concept>
%   <concept_id>10010520.10010553.10010554</concept_id>
%   <concept_desc>Computer systems organization~Robotics</concept_desc>
%   <concept_significance>100</concept_significance>
%  </concept>
%  <concept>
%   <concept_id>10003033.10003083.10003095</concept_id>
%   <concept_desc>Networks~Network reliability</concept_desc>
%   <concept_significance>100</concept_significance>
%  </concept>
% </ccs2012>
% \end{CCSXML}

% \ccsdesc[500]{Computer systems organization~Embedded systems}
% \ccsdesc[300]{Computer systems organization~Redundancy}
% \ccsdesc{Computer systems organization~Robotics}
% \ccsdesc[100]{Networks~Network reliability}

% \keywords{ACM proceedings, \LaTeX, text tagging}

\maketitle

%\input{samplebody-conf}
\section{Introduction}

Passwords have been used as a means of authenticating to Web services
and applications for a long time, and remain the most popular
authentication method on the Internet.
Since short passwords are easily guessable by attackers and using the
same password for multiple services is unsafe, a different long
password should be used for each service a person uses.  However,
remembering numerous long passwords is almost impossible for ordinary
humans.

However, password-based authentication is still the most convenient
and widely deployed method \cite{Bonneau:ReplacePasswords}, and is not
expected to disappear any time soon \cite{Herley:2009:PSS:1601990.1602010}.

We have been proposing the \textit{EpisoPass} password generator with which 
users can generate strong passwords easily
based only on a user's secret and unforgettable episodic memories.

% For this reason, we believe that it is far better to ``generate''
% something for the authentication, based on a user's episodic
% memories. This has the benefit that unlike a password, a person is
% highly unlikely to forget such episodic memories.

\begin{figure}
  \centerline{\includegraphics[width=9cm,bb=0 0 1522 1114]{figures/episopass.png}}
  \caption{EpisoPass}
  \label{fig:sample}
\end{figure}

On the EpisoPass application,
a user selects the correct answers to all the listed questions.
A md5 ... (説明)

Password generation on EpisoPass is performed through the following steps:

\begin{enumerate}
\item A user registers multiple question texts related to their own personal
secret unforgettable episodic memories. For each question they must provides
a single correct answer and multiple additional incorrect answers.

\item The user provides a long ``seed string'' for each service that requires
a password.

\item EpisoPass shows the questions and answers to the user allowing
them to select the correct answer for each question.
Based on the user's selections,
EpisoPass substitutes characters in the seed string and generates a
strong password candidate string.
After selecting all of the correct answers,
the user copies the calculated string
and registers it as the password for the service.
\end{enumerate}

Other than password handling,
various different authentication
methods have also been proposed.  Especially, visual authentication methods
like graphical passwords\cite{Biddle:2012:GPL:2333112.2333114,GraphicalPasswords}
and Draw-a-Secret (DAS) \cite{DAS} are promising approaches, because
people can remember visual patterns better than password strings.

\begin{figure}
  \includegraphics[width=8cm,bb=0 0 448 351]{figures/Dejavu.png}
  \caption{D\'{e}j\`{a} Vu}
  \label{fig:sample}
\end{figure}

\begin{figure}
  \includegraphics[width=8cm,bb=0 0 840 792]{figures/DAS.png}
  \caption{DAS Android}
  \label{fig:sample}
\end{figure}

We propose a new visual password generation system \textit{EpisoDAS},
with which users can generate strong password based on their
memory of visual patterns and episodic memories.
Users can either select answers based on the user's secret episodic memories or
draw a secret pattern represented by the pattern of selected answers.

Thus, users can recognize EpisoDas as a DAS system or
use it as an implementation of EpisoPass.

If the series of correct answers form a pattern
that is easy for the user to remember,
the user can select correct answers just like
using the DAS system.

\section{EpisoDAS}

% http://episopass.com/Amazon_john@example.com/Amazon123456

Figure \ref{EpisoDAS1} shows how a user can generate a password from
his episodic memories.

\begin{figure}
  \includegraphics[width=9cm,bb=0 0 1130 1236]{figures/EpisoDAS1.png}
  \caption{First question}
  \label{EpisoDAS1}
\end{figure}

If the user remembers a trouble at MacDonald's in Boston,
he clicks ``Boston'', and the next question is displayed.
The same next question appears regardless of the selection
the user has made.

\begin{figure}
  \includegraphics[width=9cm,bb=0 0 1130 1236]{figures/EpisoDAS1.png}
  \caption{Second question}
  \label{EpisoDAS2}
\end{figure}

If he remembers that he had a bad time at Los Angeles,
he clicks ``Los Angeles'', and another question is displayed.

After repeating the operation ten times,
the user can get his password.

\begin{figure}
  \includegraphics[width=9cm,bb=0 0 1160 468]{figures/result.png}
  \caption{Generated password}
  \label{EpisoDAS2}
\end{figure}

If the series of buttons are aligned next to each others,
the user can move the pointing device like below and get the password
without clicking buttons.

\begin{figure}
  \includegraphics[width=9cm,bb=0 0 1130 1236]{figures/draw.png}
  \caption{Drawing a secret pattern}
  \label{EpisoDAS2}
\end{figure}

This operation is close to many conventional DAS systems.
Users can quickly retrieve his password just by
drawing a pattern on the EpisoDAS screen.

Using a conventional DAS system, users should be carefull about
remembering the DAS pattern.
DAS patterns may be more easily remembered than password texts,
but there is always some risks about forgetting them.
Using EpisoDAS, users can easily remember the DAS pattern
just by reading the questions and answers.
Users can be very sure that they will never forget the pattern,
because the pattern can be retrieved by answering the questions.

Figure xxxx shows how a user can use EpisoDAS on a login page,
using a browser extension software.
The extension shows a EpisoDAS window when a user tries to log into
an Web service, and after the user selects the right answers,
a password is generated from the input and pasted in to the
password text box.

\section{Registering a DAS pattern}

EpisoDAS is an extension to the EpisoPass system, and questions and
answers should be registered on the EpisoPass system.
After registering them, a user can register a DAS pattern
based on the question-answer pairs saved a

\section{Discussion}

* Saved as a single HTML file
* マスターパスワードが要らない
* 入力が高速 -
拡張機能を利用すると
記憶しているパスワード入力よりも高速なぐらいで入力できる

\section{Conclusion}

% \begin{acks}
% \end{acks}

% \bibliographystyle{ACM-Reference-Format}
\bibliography{sample-bibliography}

\end{document}

### 2018-01-20 paper/AVI2018/paper.tex
...

@@
 \usepackage{graphicx}
+\usepackage{here} % [H]とするとその場所に配置されるらしい
 
@@
 We introduce a simple and powerful visual interaction technique for
-managing strong passwords.  Passwords have been used for
-qauthentication for decades, but appropriate handling of passwords is
-difficult because people can easily forget passwords and they can be
-easily cracked.
+managing strong passwords.
+%
+Passwords have been used for qauthentication for decades, but
+appropriate handling of passwords is difficult because people can
+easily forget passwords and they can be easily cracked.
 %
@@
 
-%
-% The code below should be generated by the tool at
-% http://dl.acm.org/ccs.cfm
-% Please copy and paste the code instead of the example below.
-%
-% \begin{CCSXML}
-% <ccs2012>
-%  <concept>
-%   <concept_id>10010520.10010553.10010562</concept_id>
-%   <concept_desc>Computer systems organization~Embedded systems</concept_desc>
-%   <concept_significance>500</concept_significance>
-%  </concept>
-%  <concept>
-%   <concept_id>10010520.10010575.10010755</concept_id>
-%   <concept_desc>Computer systems organization~Redundancy</concept_desc>
-%   <concept_significance>300</concept_significance>
-%  </concept>
-%  <concept>
-%   <concept_id>10010520.10010553.10010554</concept_id>
-%   <concept_desc>Computer systems organization~Robotics</concept_desc>
-%   <concept_significance>100</concept_significance>
-%  </concept>
-%  <concept>
-%   <concept_id>10003033.10003083.10003095</concept_id>
-%   <concept_desc>Networks~Network reliability</concept_desc>
-%   <concept_significance>100</concept_significance>
-%  </concept>
-% </ccs2012>
-% \end{CCSXML}
-
-% \ccsdesc[500]{Computer systems organization~Embedded systems}
-% \ccsdesc[300]{Computer systems organization~Redundancy}
-% \ccsdesc{Computer systems organization~Robotics}
-% \ccsdesc[100]{Networks~Network reliability}
-
-% \keywords{ACM proceedings, \LaTeX, text tagging}
-
 \maketitle
 
-%\input{samplebody-conf}
 \section{Introduction}
@@
 same password for multiple services is unsafe, a different long
-password should be used for each service a person uses.  However,
-remembering numerous long passwords is almost impossible for ordinary
-humans.
+password should be used for each service a person uses.
+However, remembering numerous long passwords is almost impossible for
+ordinary humans.
 
@@
 expected to disappear any time soon \cite{Herley:2009:PSS:1601990.1602010}.
-
-We have been proposing the \textit{EpisoPass} password generator with which 
+%
+To tackle this problem,
+we have been proposing the \textit{EpisoPass} password generator with which 
 users can generate strong passwords easily
@@
 
-\begin{figure}
-  \centerline{\includegraphics[width=9cm,bb=0 0 1522 1114]{figures/episopass.png}}
+\begin{figure}[H]
+  \centerline{\includegraphics[width=12cm,bb=-300 -100 1222 1014]{figures/episopass.png}}
   \caption{EpisoPass}
-  \label{fig:sample}
+  \label{EpisoPass}
 \end{figure}
-
-On the EpisoPass application,
-a user selects the correct answers to all the listed questions.
-A md5 ... (説明)
 
@@
 
-Other than password handling,
-various different authentication
-methods have also been proposed.  Especially, visual authentication methods
+The biggest advantage of using EpisoPass is that
+users don't have to remember strong password strings.
+%
+Users of EpisoPass can save the questions and answers
+wherever is convenient. They can
+then easily generate passwords by running
+EpisoPass and answering the questions.
+%
+If a question is based on old unforgettable episodic memory,
+there is little chance of losing the password for a service
+as long as the seed string and questions are available.
+%
+Answering to many questions takes much longer time than typing a
+remembered password, so people may prefer typing password
+rather than using EpisoPass if they have to log in to a service frequently.
+
+For the people who don't like to use passwords for authentication,
+various types of authentication methods have been proposed.
+Especially, visual authentication methods
 like graphical passwords\cite{Biddle:2012:GPL:2333112.2333114,GraphicalPasswords}
 and Draw-a-Secret (DAS) \cite{DAS} are promising approaches, because
-people can remember visual patterns better than password strings.
+people can remember visual patterns easier than passwords.
+
+% \begin{figure}[H]
+%   \includegraphics[width=8cm,bb=0 0 448 351]{figures/Dejavu.png}
+%   \caption{D\'{e}j\`{a} Vu}
+%   \label{fig:sample}
+% \end{figure}
 
 \begin{figure}
-  \includegraphics[width=8cm,bb=0 0 448 351]{figures/Dejavu.png}
-  \caption{D\'{e}j\`{a} Vu}
-  \label{fig:sample}
+  % \includegraphics[width=8cm,bb=0 0 840 792]{figures/DAS.png}
+  % \includegraphics[width=8cm,bb=0 0 320 321]{figures/DASexample.jpg}
+  \includegraphics[width=12cm,bb=0 0 1000 667]{figures/AndroidLock.jpg}
+  \caption{An example DAS pattern for Android.}
+  \label{AndroidLock}
 \end{figure}
 
-\begin{figure}
-  \includegraphics[width=8cm,bb=0 0 840 792]{figures/DAS.png}
-  \caption{DAS Android}
-  \label{fig:sample}
-\end{figure}
+Visual authentication methods have better characteristics than
+password-based authentication, but
+they are either more fragile to attacks
+or remembering is difficult.
 
 We propose a new visual password generation system \textit{EpisoDAS},
-with which users can generate strong password based on their
-memory of visual patterns and episodic memories.
-Users can either select answers based on the user's secret episodic memories or
-draw a secret pattern represented by the pattern of selected answers.
-
-Thus, users can recognize EpisoDas as a DAS system or
-use it as an implementation of EpisoPass.
-
-If the series of correct answers form a pattern
-that is easy for the user to remember,
-the user can select correct answers just like
-using the DAS system.
+which have the advantages of both EpisoPass and DAS-based methods.
 
@@
 
+EpisoDAS is a visual authentication interface
+based on the user's episodic memories.
+Like EpisoPass,
+EpisoDAS displays a list of questions to the user and
+ask the user to choose the most appropriate answers.
+EpisoDAS then generates a password string based on the user's selections.
+%
+% with which users can generate strong password based on their
+% memory of visual patterns and episodic memories.
+% Users can either select answers based on the user's secret episodic memories or
+% draw a secret pattern represented by the pattern of selected answers.
+% 
+% Thus, users can recognize EpisoDas as a DAS system or
+% use it as an implementation of EpisoPass.
+%
+The candidate answers are shown to the user as a grid of buttons,
+and the user can select the most appropriate answer
+by clicking one of the buttons in the grid.
+
+If the series of correct answers form a special pattern
+that the user can remember,
+the user can select the series of correct answers quickly
+just like using other DAS systems.
+
 % http://episopass.com/Amazon_john@example.com/Amazon123456
+% http://episopass.com/Amazon_john@example.com.html
 
-Figure \ref{EpisoDAS1} shows how a user can generate a password from
-his episodic memories.
-
-\begin{figure}
-  \includegraphics[width=9cm,bb=0 0 1130 1236]{figures/EpisoDAS1.png}
+\begin{figure}[H]
+  \includegraphics[width=12cm,bb=0 0 1398 1060]{figures/EpisoDAS1.jpg}
   \caption{First question}
@@
 
-If the user remembers a trouble at MacDonald's in Boston,
-he clicks ``Boston'', and the next question is displayed.
-The same next question appears regardless of the selection
-the user has made.
+Figure \ref{EpisoDAS1} shows
+the initial screen of an EpisoDAS session.
+% how a user can generate a password from his episodic memories.
+%
+If the user remembers that he had trouble at a MacDonald's in Boston in the past,
+he would click ``Boston'', and the next question (Figure \ref{EpisoDAS2}) is displayed.
+The contents and the order of the questions
+do not depend on the user's actions, and
+the user cannot tell whether he has selected a right answer.
 
-\begin{figure}
-  \includegraphics[width=9cm,bb=0 0 1130 1236]{figures/EpisoDAS1.png}
+\begin{figure}[H]
+  \includegraphics[width=12cm,bb=0 0 1396 1062]{figures/EpisoDAS2.jpg}
   \caption{Second question}
@@
 
-If he remembers that he had a bad time at Los Angeles,
-he clicks ``Los Angeles'', and another question is displayed.
+If he remembers that he had a bad time at Los Angeles
+after reading the question in Figure \ref{EpisoDAS2},
+he would click ``Los Angeles'' and proceed to the third question.
+%
+After repeating the slection process ten times,
+the user can get his password
+calculated from his selections. (Figure \ref{Result})
 
-After repeating the operation ten times,
-the user can get his password.
-
-\begin{figure}
-  \includegraphics[width=9cm,bb=0 0 1160 468]{figures/result.png}
+\begin{figure}[H]
+  \includegraphics[width=12cm,bb=0 0 1160 468]{figures/result.png}
   \caption{Generated password}
-  \label{EpisoDAS2}
+  \label{result}
 \end{figure}
 
-If the series of buttons are aligned next to each others,
-the user can move the pointing device like below and get the password
-without clicking buttons.
+If the series of right-answer buttons form a special DAS pattern,
+% If the series of buttons are aligned next to each others,
+the user can drag the pointing device like
+Figure \ref{draw} and quickly get the generated
+password without clicking buttons.
+%
+The candidate answers change according to the drag or click of the
+pointing device, and the user can mix the dragging and clicking actions
+at any point.
 
-\begin{figure}
-  \includegraphics[width=9cm,bb=0 0 1130 1236]{figures/draw.png}
+\begin{figure}[H]
+  \includegraphics[width=12cm,bb=0 0 1130 1236]{figures/draw.png}
   \caption{Drawing a secret pattern}
-  \label{EpisoDAS2}
+  \label{draw}
 \end{figure}
 
-This operation is close to many conventional DAS systems.
-Users can quickly retrieve his password just by
+The drawing action by the user is close to the actions
+used on conventional DAS systems.
+Users can quickly generate his password for authentication
+just by
 drawing a pattern on the EpisoDAS screen.
+
+EpisoDAS can be used for generating passwords for any kind of systems and
+services, but it is most useful when used on a login window.
+Figure \ref{Amazon} shows how a user can use EpisoDAS when
+he wants to log in to Amazon.com.
+If the EpisoDAS extension is installed on the browser,
+an EpisoDAS window appears when the user enters his
+email address and clicks the password field at Amazon.com.
+After selecting answers, a password is generated and pasted
+into the password field, making the user to log in without typing a password.
+
+% Figure \ref{Amazon} shows how a user can use EpisoDAS on a login page,
+% using a browser extension software.
+% The extension shows a EpisoDAS window when a user tries to log into
+% an Web service, and after the user selects the right answers,
+% a password is generated from the input and pasted in to the
+% password text box.
+
+\begin{figure}[H]
+  \includegraphics[width=12cm,bb=0 0 1092 1026]{figures/Amazon.png}
+  \caption{Login to Amazon.com}
+  \label{Amazon}
+\end{figure}
+
+The data used in the above example is retrieved from the EpisoDAS database
+on the Web, using the name of the service (e.g. \texttt{Amazon})
+and the user id (e.g. \texttt{joe@example.com}).
+
+\section{Registration}
+
+\subsection{Registering a DAS pattern}
+
+EpisoDAS is the predecessor of the EpisoPass system,
+and questions and answers should be registered on the EpisoPass system.
+After registering questions and answer candidates,
+a user can register a DAS pattern so that
+answer candidates are easily selected on EpisoDAS.
+
+\begin{figure}[H]
+  \includegraphics[width=12cm,bb=0 0 1832 1180]{figures/JohnEpisodes.png}
+  \caption{EpisoPass window}
+  \label{JohnEpisodes}
+\end{figure}
+
+After selecting the correct answers
+(``Boston'', ``Los Angeles'', etc.) on the EpisoPass page,
+the user can click the ``DAS'' button on the top-right portion of the
+EpisoPass page,
+%
+% After cliking the button,
+% a page for registering the DAS pattern id shown to ther user, and
+and the user can specify his DAS patten on the registration page.
+
+\begin{figure}[H]
+  \includegraphics[width=12cm,bb=0 0 1332 1118]{figures/DASRegister.png}
+  \caption{Registring the DAS pattern}
+  \label{DASRegister}
+\end{figure}
+
+If the user wants to use a U-shape as the secret pattern,
+he can draw the shape shown in Figure \ref{draw}
+on the registration window.
+%
+After finishing the registration drawing, the candidate answers fo the EpisoPass is
+shuffled so that the correct answers represent the specified pattern.
+
+\subsection{Registering questions and answers}
+
+Questions and answer candidates can be edited interactively on the
+EpisoPass page (Figure \ref{EpisoPass}).
+However, creating many questions and answer candidates is hard because
+people usually feel it hard to remember secret episodes.
+%
+To help people easily create EpisoPass problems,
+we have provided a special page for easy problem creation
+(Figure \ref{Easy}).
+
+\begin{figure}[H]
+  \includegraphics[width=12cm,bb=0 0 1332 1118]{figures/Easy.png}
+  \caption{Easily creating problems}
+  \label{Easy}
+\end{figure}
+
+First, users enter the names of their old friends and acquaintances.
+After creating a list of such names,
+the users are asked to enter special episodes of the people.
+For example, if the user remembers that Tom was
+very good at drawing, he can add a question
+``Good painter?'' to the list, assuming Tom is the correct answer.
+
+Remembering a special old episode is fairly hard for most people, but
+remembering an attribute of an old friends seems to be much easier.
+
+\section{Evaluation}
+
+The authors have been using EpisoPass for more than 5 years, and
+using EpisoDAS for about an year.
+No formal evaluation has been performed so far, but
+important impressions have been observed during the period.
+
+速度
+
+\section{Discussion}
+
+速度
+拡張機能を利用すると
+記憶しているパスワード入力よりも高速なぐらいで入力できる
+
+覚えることが要らなくなった
+公開しても大丈夫
+  ググれる
+* マスターパスワードが要らない
+
+問題づくり
+
+使い回しが駄目
+
+サイトごとのカスタマイズが大変
+
+覗き見は危険
+
+ひとつのHTML
+
+強度
 
@@
 
-Figure xxxx shows how a user can use EpisoDAS on a login page,
-using a browser extension software.
-The extension shows a EpisoDAS window when a user tries to log into
-an Web service, and after the user selects the right answers,
-a password is generated from the input and pasted in to the
-password text box.
-
-\section{Registering a DAS pattern}
-
-EpisoDAS is an extension to the EpisoPass system, and questions and
-answers should be registered on the EpisoPass system.
-After registering them, a user can register a DAS pattern
-based on the question-answer pairs saved a
-
-\section{Discussion}
-
-* Saved as a single HTML file
-* マスターパスワードが要らない
-* 入力が高速 -
-拡張機能を利用すると
-記憶しているパスワード入力よりも高速なぐらいで入力できる
+EpisoDAS is the combination of EpisoPass and DAS-based authentication methods.
+A user can generate a password using his episodic memories, or
+he can generate a password using the DAS pattern he remembers.
+%
+EpisoDAS has the advantages of both of the systems: i.e.
+users never forget how to generate the password, and
+users can quickly generate his password.
 

### 2018-01-20 Extension/app.js

@@ -1,4 +1,4 @@
-// Generated by CoffeeScript 1.9.3
+// Generated by CoffeeScript 1.12.4
 (function() {
   var display, secretstr;
 

### 2018-01-20 Extension/crypt.js

@@ -1,4 +1,4 @@
-// Generated by CoffeeScript 1.9.3
+// Generated by CoffeeScript 1.12.4
 (function() {
   var charkind, charset, crypt_char, md5, utf2bytestr;
 

### 2018-01-20 Extension/episopass.js

@@ -1,4 +1,4 @@
-// Generated by CoffeeScript 1.9.3
+// Generated by CoffeeScript 1.12.4
 (function() {
   $(function() {
     var idelement, passelement, seed;

### 2018-01-20 public/javascripts/easy.js

@@ -7,15 +7,15 @@ function shuffle(array, n){
     }
 }
 $(function() {
-    $('#id').val('Masui_Twitter');
-    $('#seed').val('Twitter_12345678');
-    $('#answers').attr('placeholder',
-		       "山田\n鈴木\n田中"
-		      );
-    $('#questions').attr('placeholder',
-			 "絵が上手いのは?\n" +
-			 "足が遅いのは?\n" +
-			 "スケート場は?\n");
+    //$('#id').val('Masui_Twitter');
+    //$('#seed').val('Twitter_12345678');
+    //$('#answers').attr('placeholder',
+    //		       "山田\n鈴木\n田中"
+    //		      );
+    //$('#questions').attr('placeholder',
+    //			 "絵が上手いのは?\n" +
+    //			 "足が遅いのは?\n" +
+    //			 "スケート場は?\n");
     $('#addnames').click(function(){
         shuffle(names,30);
         $('#answers').val(names.slice(0,30).join("\n"));

### 2018-01-20 paper/AVI2018/paper.tex
...

@@
 
-\usepackage{booktabs} % For formal tables
+% \usepackage{booktabs} % For formal tables
 
@@
 % 
-% %Conference
-% \acmConference[AVI2018]{ACM Woodstock conference}{July 2018}
-%               {Rome, Italy}
-% \acmYear{2018}
-% \copyrightyear{2018}
+%Conference
+\acmConference[AVI2018]{International Conference on Advanced Visual Interfaces}{May 2018}
+              {Resort Riva del Sole, Castiglione della Pescaia, Grosseto (Italy)}
+\acmYear{2018}
+\copyrightyear{2018}
 % 
@@
 % \authornote{Is this necessary?.}
-\orcid{1234-5678-9012}
+% \orcid{1234-5678-9012}
 \affiliation{%
   \institution{Keio University}
-  \streetaddress{Endo}
+  \streetaddress{5322 Endo}
   \city{Fujisawa}
   \state{Kanagawa}
-  \postcode{43017-6221}
+  \postcode{252-8520}
 }
@@
 \renewcommand{\shortauthors}{T. Masui}
+
+\begin{CCSXML}
+  <ccs2012>
+  <concept>
+  <concept_id>10002978.10002991.10002992.10011618</concept_id>
+  <concept_desc>Security and privacy~Graphical / visual passwords</concept_desc>
+  <concept_significance>500</concept_significance>
+  </concept>
+  </ccs2012>
+\end{CCSXML}
+\ccsdesc[500]{Security and privacy~Graphical / visual passwords}
+
+\keywords{Passwords, Visual passwords, Authentication}
 
@@
   \includegraphics[width=12cm,bb=0 0 1000 667]{figures/AndroidLock.jpg}
-  \caption{An example DAS pattern for Android.}
+  \caption{Pattern lock for Android.}
   \label{AndroidLock}
@@
 \begin{figure}[H]
-  \includegraphics[width=12cm,bb=0 0 1332 1118]{figures/Easy.png}
+  \includegraphics[width=12cm,bb=0 0 1678 1728]{figures/Easy.png}
   \caption{Easily creating problems}
@@
 
-Remembering a special old episode is fairly hard for most people, but
-remembering an attribute of an old friends seems to be much easier.
+Recalling a special old episode is fairly hard for most people, but
+recalling an attribute of an old friends seems to be much easier.
 
-\section{Evaluation}
+\section{Discussion}
 
@@
 
-速度
+\subsection{Authentication speed}
 
-\section{Discussion}
+Using EpisoDAS, very small amount of time is required for
+the authentication process.
+For a skilled computer user,
+selecting answers based on the secret is a little bit slower than
+typing a password on a computer with a hardware keyboard, but
+EpisoDAS is faster on smartphones and tablet computers.
 
-速度
-拡張機能を利用すると
-記憶しているパスワード入力よりも高速なぐらいで入力できる
+% 拡張機能を利用すると
+% 記憶しているパスワード入力よりも高速なぐらいで入力できる
 
-覚えることが要らなくなった
-公開しても大丈夫
-  ググれる
-* マスターパスワードが要らない
+\subsection{Forgetting passwords}
 
-問題づくり
+The biggest advantage of using EpisoPass is that users don't have to
+remember long password strings.
 
-使い回しが駄目
+After the authors began using EpisoPass,
+we have been having no problem forgetting passwords of any kind.
 
-サイトごとのカスタマイズが大変
+As long as a user have the seed string and question-answer data,
+he can easily generate passwords by running
+EpisoPass and answering the questions.
 
-覗き見は危険
+The seed string and question-answer data can be put on a public place
+if they include enough amount of secrets.
 
-ひとつのHTML
+If a question is based on old unforgettable episodic memory,
+there is little chance of losing the password for a service
+as long as the seed string and questions are available.
 
-強度
+If the user's memory is related to an episode that took place 20 years
+ago, say, and the user clearly still remembers the episode now, it is
+unlikely the episode will be forgotten in the future.
+
+\subsection{Universal}
+
+EpisoDAS is implemented as a single HTML file that includes a JavaScript
+script for password calculation.
+We can put the HTML file on the Web or in a handy USB memory device
+and access it from any Web browser.
+If the questions are properly selected and nobody knows the correct answet to
+the questions,
+the data can be put on a public Web page or save it in a secure
+repository like GitHub.
+The data set of the authors are put on the Web, and it can be easily
+found using Web search engines.
+It means that the passwords used by the authors can be generated
+even when the data is not kept locally.
+
+\subsection{Security strength}
+
+The strength of the generated passwords depends on the number and 
+level of secrecy of the questions.
+%
+There have been many studies on the strength of passwords
+\cite{Hayashi:2011:DSP:1978942.1979326,Komanduri:2011:PPM:1978942.1979321}, % What password is strong
+but measuring the strength of secret questions is an area where more study is needed.
+% \marginnote{I calculate $20^{10} = 10,240,000,000,000$. This is
+% considerably more than a billion (closer to 10 thousand billion,
+% (US) or 10 million million (UK).}
+Using ten secret questions each with twenty answers, where each answer is considered equally likely,
+an attacker would need to cover a search space of over ten trillion ($20^{10}$) values to check
+every potential combination of answers,
+and the entropy of the system is 43.2 ($10 \times \log_2 20$) bits.  % 10.0 * (Math.log(20.0)/Math.log(2.0))
+%
+This represents roughly the same entropy as using a random 8-character Latin-alphabet
+password, for which the entropy is 45.6 bits.
+This level is considered to be strong enough for Web services,
+where it's not possible to perform online brute-force attacks \cite{Florencio:2007:SWP:1361419.1361429}.
+
+\subsection{Creating questions}
+
+The quality of the questions is key to using EpisoDAS effectively.  If
+the episode is shared by someone else, this other person might easily
+be able to answer the question and generate the user's password.
+%
+The episode related to each question should therefore not be known to any other person,
+and the episode should be unforgettable.
+%
+Finding such episodes seems difficult at first,
+but using the method shown in the last section,
+it is not super-difficult to recall
+many trivial episodes which are unforgettable but
+nonetheless not important to other people.
+
+Questions such as ``Who did you like best?'' should be avoided,
+since friends or family might know the user's tastes, thereby allowing 
+others to select the correct answer.
+Also, memories related to taste is more fragile than memories of facts.
+
+% \subsection{Question reuse}
+% 
+% 使い回しが駄目
+% どこかのサイトのパスワードが流出し、
+% そのEpisoPassデータが公開されていたら
+% ブルートフォースで答がわかってしまうから
+% 問題を使い回すことは好ましくない
+
+\subsection{Browser extension}
+
+EpisoDAS browser extension is very useful, but creating the extension
+is cumbersome because there is no standard login form for
+different Web services.
+%
+The browser extension should first realize that the Web page is a login page
+of a Web service (e.g. Amazon),
+and then it should be able to get the ID of the user
+and know where the result of EpisoDAS calculation should be pasted.
+
+\subsection{Sholder surfing}
+
+Simple DAS authentication is known to be fragile for ``shoulder surfing''
+attacks\cite{Aviv:2017:TBS:3134600.3134609}.
+If the secret pattern is simple enough and
+the pattern can be easily observed over the user's shoulder,
+attackers can easily 再現する the login pattern.
+
+This problem is common to all the DAS-based authentication systems,
+and great care should be taken when drawing a secret in the public.
+EpisoDAS users can use complex DAS patterns
+because there is no risk of forgetting the pattern,
+because the user can use EpisoDAS even when he does not remember the
+secret pattern.
+
+\subsection{Forgetting pattern risks}
 
@@
 
-% \begin{acks}
-% \end{acks}
-
-% \bibliographystyle{ACM-Reference-Format}
-\bibliography{sample-bibliography}
+\bibliographystyle{ACM-Reference-Format}
+\bibliography{paper}
 

### 2018-01-20 paper/AVI2018/paper.tex
...

@@
 % \usepackage{booktabs} % For formal tables
+
+% \makeatletter
+% \def\@ACM@printacmref\false
+% \makeatother
+
+\settopmatter{printacmref=false} % アブストラクトの下のRef情報を表示しあい
 
@@
 % 
-%Conference
+% Conference
 \acmConference[AVI2018]{International Conference on Advanced Visual Interfaces}{May 2018}
@@
 \copyrightyear{2018}
+\acmISBN{}
+\acmDOI{}
 % 
@@
 
-\author{Toshiyuki Masui}
+\author{xxxxxx xxxx}
 % \authornote{Is this necessary?.}
@@
 \affiliation{%
-  \institution{Keio University}
-  \streetaddress{5322 Endo}
-  \city{Fujisawa}
-  \state{Kanagawa}
-  \postcode{252-8520}
+  % \institution{Keio University}
+  % \streetaddress{5322 Endo}
+  % \city{Fujisawa}
+  % \state{Kanagawa}
+  % \postcode{252-8520}
+  \institution{xxxxxx xxxxxx}
+  \streetaddress{xxxx xxxx}
+  \city{xxxxxxx}
+  \state{xxxxxxx}
+  \postcode{00000000}
 }
-\email{masui@masui.org}
+% \email{masui@masui.org}
+\email{xxxx@xxxxx.xxxx}
 
-\renewcommand{\shortauthors}{T. Masui}
+% \renewcommand{\shortauthors}{T. Masui}
 
@@
 
-\keywords{Passwords, Visual passwords, Authentication}
+\keywords{Passwords, visual passwords, user authentication, episodic memories, draw-a-secret}
 
@@
 users can generate strong passwords easily
-based only on a user's secret and unforgettable episodic memories.
+based only on a user's secret and unforgettable episodic memories \cite{Masui:EpisoPass}.
 
@@
 \begin{figure}[H]
-  \centerline{\includegraphics[width=12cm,bb=-300 -100 1222 1014]{figures/episopass.png}}
+  \centerline{\includegraphics[width=13cm,bb=-250 -100 1272 1014]{figures/episopass.png}}
   \caption{EpisoPass}
@@
 like graphical passwords\cite{Biddle:2012:GPL:2333112.2333114,GraphicalPasswords}
-and Draw-a-Secret (DAS) \cite{DAS} are promising approaches, because
+and Draw-a-Secret (DAS) \cite{Jermyn:1999:DAG:1251421.1251422} are promising approaches, because
 people can remember visual patterns easier than passwords.
@@
 EpisoDAS displays a list of questions to the user and
-ask the user to choose the most appropriate answers.
+asks the user to choose the most appropriate answers
+from the candidate answers.
 EpisoDAS then generates a password string based on the user's selections.
@@
 The candidate answers are shown to the user as a grid of buttons,
-and the user can select the most appropriate answer
+and the user can select the most appropriate answer to each question
 by clicking one of the buttons in the grid.
 
-If the series of correct answers form a special pattern
-that the user can remember,
-the user can select the series of correct answers quickly
-just like using other DAS systems.
+If the location of the series of correct answers form a special
+pattern that the user can remember, the user can select
+correct answers quickly just like using other DAS systems.
 
@@
   \includegraphics[width=12cm,bb=0 0 1398 1060]{figures/EpisoDAS1.jpg}
-  \caption{First question}
+  \caption{First question and answers shown on EpisoDAS.}
   \label{EpisoDAS1}
@@
 he would click ``Boston'', and the next question (Figure \ref{EpisoDAS2}) is displayed.
-The contents and the order of the questions
-do not depend on the user's actions, and
-the user cannot tell whether he has selected a right answer.
 
@@
   \includegraphics[width=12cm,bb=0 0 1396 1062]{figures/EpisoDAS2.jpg}
-  \caption{Second question}
+  \caption{Second question and answers.}
   \label{EpisoDAS2}
@@
 he would click ``Los Angeles'' and proceed to the third question.
-%
+
+The contents and the order of the questions
+do not depend on the user's actions, and
+the user cannot tell whether he has selected a right answer.
+
 After repeating the slection process ten times,
 the user can get his password
-calculated from his selections. (Figure \ref{Result})
+calculated from his selections (Figure \ref{Result}).
 
 \begin{figure}[H]
-  \includegraphics[width=12cm,bb=0 0 1160 468]{figures/result.png}
+  \includegraphics[width=10cm,bb=0 0 1160 468]{figures/result.png}
   \caption{Generated password}
-  \label{result}
+  \label{Result}
 \end{figure}
 
-If the series of right-answer buttons form a special DAS pattern,
+Users can select correct answers not only by clicking each button,
+but by draggin the pointing device on the buttons.
+%
+If the series of button locations form a special pattern,
 % If the series of buttons are aligned next to each others,
 the user can drag the pointing device like
-Figure \ref{draw} and quickly get the generated
-password without clicking buttons.
+Figure \ref{draw} instead of clicking ten buttons,
+and quickly generate a password.
 %
-The candidate answers change according to the drag or click of the
-pointing device, and the user can mix the dragging and clicking actions
+The order of candidate answers change according to the drag or click action,
+and the user can mix the dragging and clicking actions
 at any point.
+The user can either click ``Boston'' and ``Los Angeles'' one by one or
+click on ``Boston'' and move the pointing device downward to select
+``Los Angeles'' without releasing the mouse button or releasing the
+pen or finger from the surface of the tablet computer.
 
 \begin{figure}[H]
-  \includegraphics[width=12cm,bb=0 0 1130 1236]{figures/draw.png}
-  \caption{Drawing a secret pattern}
+  \includegraphics[width=12cm,bb=0 0 1356 1046]{figures/draw.png}
+  \caption{Drawing a secret pattern on EpisoDAS}
   \label{draw}
@@
 The drawing action by the user is close to the actions
-used on conventional DAS systems.
+used on DAS systems.
 Users can quickly generate his password for authentication
-just by
-drawing a pattern on the EpisoDAS screen.
+just by drawing a pattern on the EpisoDAS screen.
 
 EpisoDAS can be used for generating passwords for any kind of systems and
-services, but it is most useful when used on a login window.
+services, but it is most useful when used to log in to a Web service
+on a Web browser.
 Figure \ref{Amazon} shows how a user can use EpisoDAS when
@@
 email address and clicks the password field at Amazon.com.
-After selecting answers, a password is generated and pasted
-into the password field, making the user to log in without typing a password.
+After selecting answers by drawing a secret pattern on the EpisoDAS window,
+a password for Amazon is generated and pasted
+into the password field, making the user to log in without typing any password.
 
@@
 on the Web, using the name of the service (e.g. \texttt{Amazon})
-and the user id (e.g. \texttt{joe@example.com}).
+and the user id (e.g. \texttt{john@example.com}).
 
@@
 
-EpisoDAS is the predecessor of the EpisoPass system,
-and questions and answers should be registered on the EpisoPass system.
+EpisoDAS is based on the EpisoPass system,
+and questions and answers should be registered on the EpisoPass database.
 After registering questions and answer candidates,
@@
 After selecting the correct answers
-(``Boston'', ``Los Angeles'', etc.) on the EpisoPass page,
+(``Boston'', ``Los Angeles'', etc.) on the EpisoPass editor page,
 the user can click the ``DAS'' button on the top-right portion of the
-EpisoPass page,
-%
-% After cliking the button,
-% a page for registering the DAS pattern id shown to ther user, and
-and the user can specify his DAS patten on the registration page.
+EpisoPass page to specify his DAS patten.
 
@@
 If the user wants to use a U-shape as the secret pattern,
-he can draw the shape shown in Figure \ref{draw}
+he can begin drawing the shape shown in Figure \ref{DASRegister}
 on the registration window.
 %
-After finishing the registration drawing, the candidate answers fo the EpisoPass is
-shuffled so that the correct answers represent the specified pattern.
+After registering the pattern, the candidate answers for the EpisoPass is
+shuffled so that the series of correct answers represent the specified pattern.
 
 \subsection{Registering questions and answers}
+\label{easyregister}
 
 Questions and answer candidates can be edited interactively on the
-EpisoPass page (Figure \ref{EpisoPass}).
-However, creating many questions and answer candidates is hard because
-people usually feel it hard to remember secret episodes.
+EpisoPass editor page (Figure \ref{EpisoPass}) and arbitrary
+strings can be specified as questions and answer candidates.
+However, creating many questions and answer candidates is not a
+trivial task, because
+people usually feel it difficult to recall secret episodes.
 %
-To help people easily create EpisoPass problems,
-we have provided a special page for easy problem creation
+To help people easily create EpisoPass questions and answers,
+we provide a special page for easy problem creation
 (Figure \ref{Easy}).
@@
   \includegraphics[width=12cm,bb=0 0 1678 1728]{figures/Easy.png}
-  \caption{Easily creating problems}
+  \caption{Easily creating questions and answers}
   \label{Easy}
@@
 
-First, users enter the names of their old friends and acquaintances.
-After creating a list of such names,
-the users are asked to enter special episodes of the people.
+First, a user provides a list of names of his old friends and acquaintances.
+After registering a list of such names,
+the user is asked to enter special episodes of the people.
 For example, if the user remembers that Tom was
@@
 
-Recalling a special old episode is fairly hard for most people, but
-recalling an attribute of an old friends seems to be much easier.
+Recalling special old episodes is sounds hard for many people, but
+recalling an attribute of an old friends is much easier.
+The questions and answers shown in Figure \ref{EpisoPass} was
+created by this system,
+using place names instead of people's names.
 
@@
 No formal evaluation has been performed so far, but
+some people around the authors are enthusiastically using
+EpisoDAS for their daily work, and
 important impressions have been observed during the period.
 
-\subsection{Authentication speed}
+\subsection{Authentication time}
 
-Using EpisoDAS, very small amount of time is required for
-the authentication process.
+Unlike EpisoPass,
+very small amount of time is required for
+the authentication process on EpisoDAS.
 For a skilled computer user,
-selecting answers based on the secret is a little bit slower than
+selecting answers based on the secret might be a little bit slower than
 typing a password on a computer with a hardware keyboard, but
-EpisoDAS is faster on smartphones and tablet computers.
+authentication with
+EpisoDAS is apparently faster on smartphones and tablet computers
+than entering passwords on such devices.
 
-% 拡張機能を利用すると
-% 記憶しているパスワード入力よりも高速なぐらいで入力できる
-
-\subsection{Forgetting passwords}
+\subsection{Forgetting factors}
 
@@
 remember long password strings.
-
+%
 After the authors began using EpisoPass,
-we have been having no problem forgetting passwords of any kind.
-
+they have been having no problem forgetting passwords of any kind.
+%
 As long as a user have the seed string and question-answer data,
@@
 EpisoPass and answering the questions.
-
-The seed string and question-answer data can be put on a public place
-if they include enough amount of secrets.
-
-If a question is based on old unforgettable episodic memory,
+%
+If the questions are based on old unforgettable episodic memory,
 there is little chance of losing the password for a service
 as long as the seed string and questions are available.
-
+%
 If the user's memory is related to an episode that took place 20 years
@@
 
-\subsection{Universal}
+% The seed string and question-answer data can be put on a public place
+% if they include enough amount of secret information.
+
+\subsection{Running environment}
 
@@
 script for password calculation.
-We can put the HTML file on the Web or in a handy USB memory device
-and access it from any Web browser.
-If the questions are properly selected and nobody knows the correct answet to
-the questions,
-the data can be put on a public Web page or save it in a secure
+The HTML file can be put on the Web or saved in a handy USB memory device
+so that it can be accessed from a Web browser.
+%
+If the questions are based on the user's secret memories and
+a sufficient number of questions and fake answers are provided,
+the data can be put on a public Web page or saved in a secure
 repository like GitHub.
+%
 The data set of the authors are put on the Web, and it can be easily
-found using Web search engines.
-It means that the passwords used by the authors can be generated
-even when the data is not kept locally.
+found using Web search engines\footnote{
+  The EpisoDAS data of the authors can be found on major Web
+  search enginges using the name of the author and ``password''.
+}.
+It means that the passwords used by the authors can be retrieved
+even when the data is not available locally.
+
+\subsection{Universality}
+
+Using EpisoDAS, people can use password-based systems
+only by selecting answers based on their episodic memories,
+without remembering passwords or using password management systems.
+Using a browser extension,
+people can use services without noticing that passwords are
+required for the service.
+
+Creating a Q-A database is a one-time process,
+after which the system becomes straightforward to use.
+%
+With a proper help, creating a database is not difficult even for
+people who are not good at using computers.
+A helper can ask the client questions like
+``Do you remember an interesting friend in your childfood?''
+to get the list of old friends, and then ask questions like
+``What kind of child was he?'', ``Do you remember his house?''
+to create a question for locating him.
+With such information, the helper can use the technique shwon
+in Section \ref{easyregister} to create the EpisoDAS database
+for the client.
 
@@
 
-\subsection{Creating questions}
+\subsection{Choosing questions}
 
@@
 but using the method shown in the last section,
-it is not super-difficult to recall
+it is not extremely difficult to recall
 many trivial episodes which are unforgettable but
@@
 others to select the correct answer.
-Also, memories related to taste is more fragile than memories of facts.
+Also, memories related to taste is more fragile than fact-based memories like
+``Where did you find a crystal?''.
 
@@
 
-\subsection{Browser extension}
+\subsection{Developmenet of browser extensions}
 
@@
 is cumbersome because there is no standard login form for
-different Web services.
+Web services.
 %
-The browser extension should first realize that the Web page is a login page
+The browser extension should first detect that the Web page is a login page
 of a Web service (e.g. Amazon),
@@
 and know where the result of EpisoDAS calculation should be pasted.
+%
+Commercial password managers\cite{OnePassword,Dashlane,MilPass,LastPass,KeyPass,NortonIDSafe,IDManager}
+are usually well integrated with Web browsers,
+and EpisoDAS should also be evolved so that
+the browser extension works on many Web services.
 
-\subsection{Sholder surfing}
+\subsection{Battles against sholder surfing}
 
-Simple DAS authentication is known to be fragile for ``shoulder surfing''
+Simple DAS authentication is known to be vulnerable to ``shoulder surfing''
 attacks\cite{Aviv:2017:TBS:3134600.3134609}.
-If the secret pattern is simple enough and
+If the secret pattern is simple and
 the pattern can be easily observed over the user's shoulder,
-attackers can easily 再現する the login pattern.
+attackers can easily reproduce the login pattern.
 
@@
 and great care should be taken when drawing a secret in the public.
-EpisoDAS users can use complex DAS patterns
+EpisoDAS users can use more complex DAS patterns than
+conventional DAS systems,
 because there is no risk of forgetting the pattern,
-because the user can use EpisoDAS even when he does not remember the
-secret pattern.
+since the user can read the question at any time and
+remember the secret pattern which corresponds to the
+answers to the questions.
 
-\subsection{Forgetting pattern risks}
+\subsection{Risks of Forgetting DAS pattern}
 
@@
 he can generate a password using the DAS pattern he remembers.
+
+\section{Conclusions}
+
+We introduced a password management system \textit{EpisoDAS}
+that generates a password from a seed string by
+quicly drawingn a secret pattern backed by the user's episodic memories.
+These memories are represented as a set of questions and answers
+which can be solved only by the user in order to generate a site-specific password.
 %
-EpisoDAS has the advantages of both of the systems: i.e.
-users never forget how to generate the password, and
-users can quickly generate his password.
+Using EpisoDAS, a user can log into Web services quickly without
+worrying about
+having to remember any secret information, other than the episodic memories
+that have been chosen specifically to be easy to recall.
+%
+We are hoping to make EpisoDAS available on all the environments
+where strong passwords are required, and
+relieve everyone's pain of password handling.
 
-\section{Conclusion}
-
+\large
 \bibliographystyle{ACM-Reference-Format}

### 2018-01-21 paper/AVI2018/paper.tex
...

@@
 \begin{document}
-\title{EpisoDAS - DAS-based password generation \\
-using episodic memories}
+\title{EpisoDAS - DAS-based Password Generation \\
+using Episodic Memories}
 % \titlenote{Produces the permission block, and copyright information}
@@
 
-\keywords{Passwords, visual passwords, user authentication, episodic memories, draw-a-secret}
+\keywords{Passwords; visual passwords; user authentication;
+  episodic memories; draw-a-secret.}
 
@@
 %
-Passwords have been used for qauthentication for decades, but
+Passwords have been used for authentication for decades, but
 appropriate handling of passwords is difficult because people can
-easily forget passwords and they can be easily cracked.
+easily forget passwords and they can be easily attacked.
 %
@@
 Using a DAS-based authentication method, users can quickly log into a
-service without typing a password. However, remembering complex secret
-patterns can be as difficult as remembering passwords. We developed
-EpisoDAS, with which users can generate strong passwords based on
-their secret episodic memories with a simple DAS interface.
+service without typing a password, but remembering complex secret
+patterns is as difficult as remembering passwords.
+%
+We developed \textit{EpisoDAS}, with which users can generate strong passwords
+based on their secret episodic memories with a simple DAS interface.
 %
 users can use secret patterns for authentication, based on their
-secret episodic memories which they cannot easily forget.
+secret episodic memories that they cannot easily forget.
 
@@
 To tackle this problem,
-we have been proposing the \textit{EpisoPass} password generator with which 
-users can generate strong passwords easily
-based only on a user's secret and unforgettable episodic memories \cite{Masui:EpisoPass}.
+we have been proposing the \textit{EpisoPass} password generator \cite{Masui:EpisoPass}
+with which users can generate strong passwords easily
+based only on a user's secret and unforgettable episodic memories.
 
@@
 
-\begin{figure}[H]
-  \centerline{\includegraphics[width=13cm,bb=-250 -100 1272 1014]{figures/episopass.png}}
-  \caption{EpisoPass}
+\begin{figure}[t]
+  % \centerline{\includegraphics[width=13cm,bb=-250 -100 1272 1014]{figures/EpisoPass0.png}}
+  \centerline{\includegraphics[width=13cm,bb=-250 -100 1524 1286]{figures/EpisoPass1.png}}
+  \caption{An EpisoPass page for \textsf{John@example.com}. John can edit questions and answers, enter a seed string,
+  and a password is generated based on the selections.}
   \label{EpisoPass}
@@
 \item A user registers multiple question texts related to their own personal
-secret unforgettable episodic memories. For each question they must provides
+secret unforgettable episodic memories. For each question they must provide
 a single correct answer and multiple additional incorrect answers.
@@
 the user copies the calculated string
-and registers it as the password for the service.
+and uses it as the password for the service.
 \end{enumerate}
@@
 Especially, visual authentication methods
-like graphical passwords\cite{Biddle:2012:GPL:2333112.2333114,GraphicalPasswords}
+like graphical passwords \cite{Biddle:2012:GPL:2333112.2333114}\cite{GraphicalPasswords}
 and Draw-a-Secret (DAS) \cite{Jermyn:1999:DAG:1251421.1251422} are promising approaches, because
 people can remember visual patterns easier than passwords.
+%
+Visual authentication methods have better characteristics than
+password-based authentication, but
+they are sometimes fragile to attacks or memorization is difficult.
 
-% \begin{figure}[H]
-%   \includegraphics[width=8cm,bb=0 0 448 351]{figures/Dejavu.png}
-%   \caption{D\'{e}j\`{a} Vu}
-%   \label{fig:sample}
-% \end{figure}
+We propose a new visual password generation system \textit{EpisoDAS}
+that posesses the advantages of both EpisoPass and DAS-based methods.
 
-\begin{figure}
+\begin{figure}[t]
   % \includegraphics[width=8cm,bb=0 0 840 792]{figures/DAS.png}
   % \includegraphics[width=8cm,bb=0 0 320 321]{figures/DASexample.jpg}
-  \includegraphics[width=12cm,bb=0 0 1000 667]{figures/AndroidLock.jpg}
-  \caption{Pattern lock for Android.}
+  % \includegraphics[width=10cm,bb=0 0 1000 667]{figures/AndroidLock.jpg}
+  \includegraphics[width=10cm,bb=-60 0 940 667]{figures/AndroidLock.jpg}
+  \caption{An example DAS system. (``Pattern lock'' for Android)}
   \label{AndroidLock}
 \end{figure}
-
-Visual authentication methods have better characteristics than
-password-based authentication, but
-they are either more fragile to attacks
-or remembering is difficult.
-
-We propose a new visual password generation system \textit{EpisoDAS},
-which have the advantages of both EpisoPass and DAS-based methods.
 
@@
 Like EpisoPass,
-EpisoDAS displays a list of questions to the user and
-asks the user to choose the most appropriate answers
-from the candidate answers.
-EpisoDAS then generates a password string based on the user's selections.
+EpisoDAS displays a list of questions to the user,
+asks the user to choose the most appropriate answer from the candidate answers,
+and generates a password string based on the user's selections.
 %
@@
 by clicking one of the buttons in the grid.
-
+%
 If the location of the series of correct answers form a special
@@
 
-\begin{figure}[H]
-  \includegraphics[width=12cm,bb=0 0 1398 1060]{figures/EpisoDAS1.jpg}
-  \caption{First question and answers shown on EpisoDAS.}
+\begin{figure}[t]
+  \includegraphics[width=10cm,bb=-60 0 1338 1060]{figures/EpisoDAS1.jpg}
+  \caption{First question and candidate answers shown on EpisoDAS.}
   \label{EpisoDAS1}
@@
 
-\begin{figure}[H]
-  \includegraphics[width=12cm,bb=0 0 1396 1062]{figures/EpisoDAS2.jpg}
+\begin{figure}[t]
+  \includegraphics[width=10cm,bb=-60 0 1336 1062]{figures/EpisoDAS2.jpg}
   \caption{Second question and answers.}
@@
 
-If he remembers that he had a bad time at Los Angeles
-after reading the question in Figure \ref{EpisoDAS2},
+If he remembers that he had a bad time at Los Angeles,
+% after reading the question in Figure \ref{EpisoDAS2},
 he would click ``Los Angeles'' and proceed to the third question.
@@
 the user cannot tell whether he has selected a right answer.
-
+%
 After repeating the slection process ten times,
@@
 
-\begin{figure}[H]
+\begin{figure}
   \includegraphics[width=10cm,bb=0 0 1160 468]{figures/result.png}
-  \caption{Generated password}
+  \caption{Generated password.}
   \label{Result}
@@
 %
-The order of candidate answers change according to the drag or click action,
-and the user can mix the dragging and clicking actions
-at any point.
+The order of the list of candidate answers change according to the
+drag or click action,
+and the user can mix the dragging and clicking actions at any point.
 The user can either click ``Boston'' and ``Los Angeles'' one by one or
-click on ``Boston'' and move the pointing device downward to select
+click on ``Boston'' and drag the pointing device downward to select
 ``Los Angeles'' without releasing the mouse button or releasing the
@@
   \includegraphics[width=12cm,bb=0 0 1356 1046]{figures/draw.png}
-  \caption{Drawing a secret pattern on EpisoDAS}
+  \caption{Drawing a secret pattern on EpisoDAS.}
   \label{draw}
@@
 The drawing action by the user is close to the actions
-used on DAS systems.
+used on other DAS systems.
 Users can quickly generate his password for authentication
@@
 EpisoDAS can be used for generating passwords for any kind of systems and
-services, but it is most useful when used to log in to a Web service
-on a Web browser.
+services, but it is most useful when it is used to log into a Web service.
 Figure \ref{Amazon} shows how a user can use EpisoDAS when
@@
 If the EpisoDAS extension is installed on the browser,
-an EpisoDAS window appears when the user enters his
-email address and clicks the password field at Amazon.com.
-After selecting answers by drawing a secret pattern on the EpisoDAS window,
+an EpisoDAS window appears when a user enters their
+email address and clicks the password field.
+After selecting answers by drawing a secret pattern on the EpisoDAS area,
 a password for Amazon is generated and pasted
-into the password field, making the user to log in without typing any password.
+into the password field, making the user to log in without typing a password.
 
@@
 
-\begin{figure}[H]
+\begin{figure}[t]
   \includegraphics[width=12cm,bb=0 0 1092 1026]{figures/Amazon.png}
-  \caption{Login to Amazon.com}
+  \caption{Using EpisoDAS on Amazon.com login page.
+    When the user clicks the password field, EpisoDAS window automatically appears
+    and a password is generated and pasted to the field after drawing a
+    secret pattern.}
   \label{Amazon}
@@
 The data used in the above example is retrieved from the EpisoDAS database
-on the Web, using the name of the service (e.g. \texttt{Amazon})
-and the user id (e.g. \texttt{john@example.com}).
+on the Web, using the name of the service (\texttt{Amazon})
+and the user id (\texttt{john@example.com}).
 
-\section{Registration}
+\section{Data Registration}
+
+A user has to register a DAS pattern and
+Q-A database before using EpisoDAS.
 
@@
 
-\begin{figure}[H]
-  \includegraphics[width=12cm,bb=0 0 1832 1180]{figures/JohnEpisodes.png}
-  \caption{EpisoPass window}
-  \label{JohnEpisodes}
-\end{figure}
+% \begin{figure}[H]
+%   \includegraphics[width=12cm,bb=0 0 1832 1180]{figures/JohnEpisodes.png}
+%   \caption{EpisoPass window}
+%   \label{JohnEpisodes}
+% \end{figure}
 
 After selecting the correct answers
-(``Boston'', ``Los Angeles'', etc.) on the EpisoPass editor page,
+(``Boston'', ``Los Angeles'', etc.) on the EpisoPass editor page (Figure \ref{EpisoPass}),
 the user can click the ``DAS'' button on the top-right portion of the
-EpisoPass page to specify his DAS patten.
+page to proceed to specify their DAS patten.
 
@@
 If the user wants to use a U-shape as the secret pattern,
-he can begin drawing the shape shown in Figure \ref{DASRegister}
-on the registration window.
+he can draw the shape shown in Figure \ref{DASRegister}
+on the DAS registration window.
 %
@@
 strings can be specified as questions and answer candidates.
-However, creating many questions and answer candidates is not a
-trivial task, because
-people usually feel it difficult to recall secret episodes.
+However, creating many questions and answer candidates is
+time-consuming and hard task, because
+people usually feel it difficult to recall old secret episodes.
 %
 To help people easily create EpisoPass questions and answers,
-we provide a special page for easy problem creation
+a support page can be used for easy problem creation
 (Figure \ref{Easy}).
@@
 %
-Commercial password managers\cite{OnePassword,Dashlane,MilPass,LastPass,KeyPass,NortonIDSafe,IDManager}
+Commercial password managers\cite{OnePassword,Dashlane,LastPass,KeyPass,NortonIDSafe,IDManager}
 are usually well integrated with Web browsers,

### 2018-01-21 paper/AVI2018/paper.tex
投稿版 (たぶん)

@@
 We propose a new visual password generation system \textit{EpisoDAS}
-that posesses the advantages of both EpisoPass and DAS-based methods.
+that possesses the advantages of both EpisoPass and DAS-based methods.
 
@@
 %
-After repeating the slection process ten times,
+After repeating the selection process ten times,
 the user can get his password
@@
 Users can select correct answers not only by clicking each button,
-but by draggin the pointing device on the buttons.
+but by dragging the pointing device on the buttons.
 %
@@
 %
-The order of the list of candidate answers change according to the
+The order of the list of candidate answers changes according to the
 drag or click action,
@@
 \begin{figure}[H]
-  \includegraphics[width=12cm,bb=0 0 1356 1046]{figures/draw.png}
+  \includegraphics[width=10cm,bb=-60 0 1296 1046]{figures/draw.png}
   \caption{Drawing a secret pattern on EpisoDAS.}
@@
 Figure \ref{Amazon} shows how a user can use EpisoDAS when
-he wants to log in to Amazon.com.
+he wants to log into Amazon.com.
 If the EpisoDAS extension is installed on the browser,
@@
 The data used in the above example is retrieved from the EpisoDAS database
-on the Web, using the name of the service (\texttt{Amazon})
+created and saved on the EpisoPass page (Figure \ref{EpisoPass}),
+with the name of the service (\texttt{Amazon})
 and the user id (\texttt{john@example.com}).
@@
 the user can click the ``DAS'' button on the top-right portion of the
-page to proceed to specify their DAS patten.
+page to proceed to specify their DAS pattern.
 
 \begin{figure}[H]
-  \includegraphics[width=12cm,bb=0 0 1332 1118]{figures/DASRegister.png}
-  \caption{Registring the DAS pattern}
+  \includegraphics[width=10cm,bb=-60 0 1272 1118]{figures/DASRegister.png}
+  \caption{Registering the DAS pattern}
   \label{DASRegister}
@@
 After registering the pattern, the candidate answers for the EpisoPass is
-shuffled so that the series of correct answers represent the specified pattern.
+shuffled so that the series of correct answers represent the
+specified pattern (U-shape in this case).
 
@@
 However, creating many questions and answer candidates is
-time-consuming and hard task, because
+time-consuming and hard, because
 people usually feel it difficult to recall old secret episodes.
@@
 To help people easily create EpisoPass questions and answers,
-a support page can be used for easy problem creation
+a support page can be used for creating problems easily
 (Figure \ref{Easy}).
 
-\begin{figure}[H]
-  \includegraphics[width=12cm,bb=0 0 1678 1728]{figures/Easy.png}
-  \caption{Easily creating questions and answers}
+\begin{figure}[t]
+  \includegraphics[width=12cm,bb=0 0 1522 1632]{figures/Easy.png}
+  \caption{A Q-A creation helper.}
   \label{Easy}
@@
 
-Recalling special old episodes is sounds hard for many people, but
+Recalling special old episodes sounds hard for many people, but
 recalling an attribute of an old friends is much easier.
@@
 some people around the authors are enthusiastically using
-EpisoDAS for their daily work, and
+EpisoDAS for their daily activities, and
 important impressions have been observed during the period.
@@
 
-The biggest advantage of using EpisoPass is that users don't have to
+The biggest advantage of using EpisoPass and EpisoDAS is that users don't have to
 remember long password strings.
@@
 As long as a user have the seed string and question-answer data,
-he can easily generate passwords by running
+they can easily generate passwords by running
 EpisoPass and answering the questions.
 %
-If the questions are based on old unforgettable episodic memory,
+If the questions are based on old unforgettable episodic memories,
 there is little chance of losing the password for a service
@@
 EpisoDAS is implemented as a single HTML file that includes a JavaScript
-script for password calculation.
-The HTML file can be put on the Web or saved in a handy USB memory device
-so that it can be accessed from a Web browser.
+code for password calculation.
+The HTML file can be put on the Web or saved in a handy memory device
+so that it can be accessed from any Web browser easily.
 %
@@
   The EpisoDAS data of the authors can be found on major Web
-  search enginges using the name of the author and ``password''.
+  search engines using the name of the author and
+  the keyword ``\texttt{password}''.
 }.
@@
 Using a browser extension,
-people can use services without noticing that passwords are
+people can use Web services without noticing that passwords are
 required for the service.
@@
 A helper can ask the client questions like
-``Do you remember an interesting friend in your childfood?''
+``Do you remember your friends in your childhood?''
 to get the list of old friends, and then ask questions like
-``What kind of child was he?'', ``Do you remember his house?''
-to create a question for locating him.
-With such information, the helper can use the technique shwon
+``What kind of person was this guy?'', ``Do you remember his house?''
+to create a question for locating a person.
+With such information, the helper can use the support page shown
 in Section \ref{easyregister} to create the EpisoDAS database
@@
 There have been many studies on the strength of passwords
-\cite{Hayashi:2011:DSP:1978942.1979326,Komanduri:2011:PPM:1978942.1979321}, % What password is strong
+\cite{Hayashi:2011:DSP:1978942.1979326}\cite{Komanduri:2011:PPM:1978942.1979321}, % What password is strong
 but measuring the strength of secret questions is an area where more study is needed.
@@
 Finding such episodes seems difficult at first,
-but using the method shown in the last section,
+but using the method shown in Section \ref{easyregister},
 it is not extremely difficult to recall
@@
 
-\subsection{Developmenet of browser extensions}
+\subsection{Development of browser extensions}
 
@@
 %
-Commercial password managers\cite{OnePassword,Dashlane,LastPass,KeyPass,NortonIDSafe,IDManager}
+Commercial password managers\cite{OnePassword}\cite{Dashlane}\cite{LastPass}\cite{KeyPass}\cite{NortonIDSafe}\cite{IDManager}
 are usually well integrated with Web browsers,
@@
 
-\subsection{Battles against sholder surfing}
+\subsection{Caution about shoulder surfing}
 
@@
 This problem is common to all the DAS-based authentication systems,
-and great care should be taken when drawing a secret in the public.
+and great care should be taken when drawing a secret pattern in the public.
 EpisoDAS users can use more complex DAS patterns than
@@
 since the user can read the question at any time and
-remember the secret pattern which corresponds to the
+recall the secret pattern which corresponds to the
 answers to the questions.
 
-\subsection{Risks of Forgetting DAS pattern}
+\subsection{Risks of forgetting DAS patterns}
 
-Using a conventional DAS system, users should be carefull about
+Using a conventional DAS system, users should be careful about
 remembering the DAS pattern.
@@
 but there is always some risks about forgetting them.
-Using EpisoDAS, users can easily remember the DAS pattern
+Using EpisoDAS, users can easily recall the DAS pattern
 just by reading the questions and answers.
 Users can be very sure that they will never forget the pattern,
-because the pattern can be retrieved by answering the questions.
+because the pattern can easily be retrieved by answering the questions.
 
-EpisoDAS is the combination of EpisoPass and DAS-based authentication methods.
-A user can generate a password using his episodic memories, or
-he can generate a password using the DAS pattern he remembers.
+% EpisoDAS is the combination of EpisoPass and DAS-based authentication methods.
+% A user can generate a password using his episodic memories, or
+% he can generate a password using the DAS pattern he remembers.
 
@@
 that generates a password from a seed string by
-quicly drawingn a secret pattern backed by the user's episodic memories.
+quickly drawing a secret pattern backed by the user's episodic memories.
 These memories are represented as a set of questions and answers
-which can be solved only by the user in order to generate a site-specific password.
+that can be solved only by the user in order to generate a site-specific password.
 %
